---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order
### for lineplot as prof as to make####
### need to write all days name manually

   gpt_summary_data$Attribute <- 
   factor(gpt_summary_data$Attribute,levels = c(  "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

### for lineplot
libualt_data$Attribute <- factor(libualt_data$Attribute,levels = c(  "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

# ##for boxplt change last data##
```


```{r}
 ##### Make the line plot of labreads for male and female####
 ##### filter the male and female for individual plot #####
###############################################################################
gpt_summary_data <- libualt_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
    )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)


# Create a vector with the x-axis labels in the desired order

### for lineplot as prof as to make####
### need to write all days name manually

ggplot(gpt_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread),       ##width = 0.2, color = "blue") + 
  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), 
                width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + 
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  # SEM error bars in red
  labs(title = "liver_ibu mean ALT in time course for female with patient count",    ###NEW###
       x = "Day of measurement",                     ###NEW###
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####


```{r}

library(ggplot2)
library(dplyr)

max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libualt_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        ####NEW#####
  labs(title = "liver_ibu boxplot for ALT by day of measurement",      ###NEW###
       x = "day of measurement",                            ###NEW###
       y = "ALT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
   scale_y_continuous(breaks = all_breaks,
                      limits = c(0, max_value))


```
######################################################################
###AST###
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ast_summary_data$Attribute <- factor(ast_summary_data$Attribute,
                                     levels = c("GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))
# 
# ##for boxplt change last data##
 libuast_data$Attribute <- factor(libuast_data$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
ast_summary_data <- libuast_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ast_summary_data$mean_labread + ast_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 600, by = 200)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 500) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ast_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean AST in time course for female with patient count",
       x = "Day of measurement",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 

  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```




##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ast_summary_data$mean_labread + ast_summary_data$sem_labread, na.rm = TRUE)
max_value <- 3000
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##


libuast_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        ####NEW#####
  labs(title = "liver_ibu boxplot for AST by day of measurement",      ###NEW###
       x = "day of measurement",                            ###NEW###
       y = "AST U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                    limits = c(0, max_value))


```

######################################################################
###quick###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
quick_summary_data$attribute <- factor(quick_summary_data$attribute,levels = c("Quick Day1", "Quick Day2", "Quick Day3","Quick Day4","Quick Day5", "Quick Day6","Quick Day7","Quick Day8","Quick Day9","Quick Day10", "Quick Day11","Quick Day12","Quick Day13","Quick Day14","Quick Day15","Quick Day16","Quick Day17","Quick Day18","Quick Day19","Quick Day20","Quick Day21","Quick Day22","Quick Day23","Quick Day24","Quick Day25","Quick Day26","Quick Day27","Quick Day28","Quick Day29","Quick Day30","Quick Day31","Quick Day32","Quick Day33","Quick Day34","Quick Day35","Quick Day36","Quick Day37","Quick Day38","Quick Day39","Quick Day40","Quick Day41","Quick Day42","Quick Day43","Quick Day44","Quick Day45","Quick Day46","Quick Day47","Quick Day48","Quick Day49","Quick Day50","Quick Day51","Quick Day52","Quick Day53","Quick Day54","Quick Day55","Quick Day56","Quick Day57","Quick Day58","Quick Day59","Quick Day60","Quick Day61","Quick Day62","Quick Day63","Quick Day64","Quick Day65","Quick Day66","Quick Day67","Quick Day68","Quick Day69","Quick Day70","Quick Day71","Quick Day72","Quick Day73","Quick Day74","Quick Day75","Quick Day76","Quick Day77","Quick Day78","Quick Day79","Quick Day80","Quick Day81","Quick Day82","Quick Day83","Quick Day84","Quick Day85","Quick Day86","Quick Day87","Quick Day88","Quick Day89","Quick Day90","Quick Day91","Quick Day92","Quick Day93","Quick Day94","Quick Day95","Quick Day96","Quick Day97","Quick Day98","Quick Day99","Quick Day100"))

##for boxplt change last data##
libuquick_data$attribute <- factor(libuquick_data$attribute,levels = c("Quick Day1", "Quick Day2", "Quick Day3","Quick Day4","Quick Day5", "Quick Day6","Quick Day7","Quick Day8","Quick Day9","Quick Day10", "Quick Day11","Quick Day12","Quick Day13","Quick Day14","Quick Day15","Quick Day16","Quick Day17","Quick Day18","Quick Day19","Quick Day20","Quick Day21","Quick Day22","Quick Day23","Quick Day24","Quick Day25","Quick Day26","Quick Day27","Quick Day28","Quick Day29","Quick Day30","Quick Day31","Quick Day32","Quick Day33","Quick Day34","Quick Day35","Quick Day36","Quick Day37","Quick Day38","Quick Day39","Quick Day40","Quick Day41","Quick Day42","Quick Day43","Quick Day44","Quick Day45","Quick Day46","Quick Day47","Quick Day48","Quick Day49","Quick Day50","Quick Day51","Quick Day52","Quick Day53","Quick Day54","Quick Day55","Quick Day56","Quick Day57","Quick Day58","Quick Day59","Quick Day60","Quick Day61","Quick Day62","Quick Day63","Quick Day64","Quick Day65","Quick Day66","Quick Day67","Quick Day68","Quick Day69","Quick Day70","Quick Day71","Quick Day72","Quick Day73","Quick Day74","Quick Day75","Quick Day76","Quick Day77","Quick Day78","Quick Day79","Quick Day80","Quick Day81","Quick Day82","Quick Day83","Quick Day84","Quick Day85","Quick Day86","Quick Day87","Quick Day88","Quick Day89","Quick Day90","Quick Day91","Quick Day92","Quick Day93","Quick Day94","Quick Day95","Quick Day96","Quick Day97","Quick Day98","Quick Day99","Quick Day100"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
quick_summary_data <- libuquick_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(quick_summary_data$mean_labread + quick_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(quick_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels  
  labs(title = "liver_ibu mean quick in time course for male with patient count",
       x = "Day of measurement",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(quick_summary_data$mean_labread + quick_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuquick_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
   geom_jitter()+        				####NEW#####
  labs(title = "Boxplot of quick by day of measurement",
       x = "day of measurement",
       y = "quick %") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###inr###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
inr_summary_data$attribute <- factor(inr_summary_data$attribute,levels = c( "INR Day1", "INR Day2", "INR Day3","INR Day4","INR Day5", "INR Day6","INR Day7","INR Day8","INR Day9","INR Day10", "INR Day11","INR Day12","INR Day13","INR Day14","INR Day15","INR Day16","INR Day17","INR Day18","INR Day19","INR Day20","INR Day21","INR Day22","INR Day23","INR Day24","INR Day25","INR Day26","INR Day27","INR Day28","INR Day29","INR Day30","INR Day31","INR Day32","INR Day33","INR Day34","INR Day35","INR Day36","INR Day37","INR Day38","INR Day39","INR Day40","INR Day41","INR Day42","INR Day43","INR Day44","INR Day45","INR Day46","INR Day47","INR Day48","INR Day49","INR Day50","INR Day51","INR Day52","INR Day53","INR Day54","INR Day55","INR Day56","INR Day57","INR Day58","INR Day59","INR Day60","INR Day61","INR Day62","INR Day63","INR Day64","INR Day65","INR Day66","INR Day67","INR Day68","INR Day69","INR Day70","INR Day71","INR Day72","INR Day73","INR Day74","INR Day75","INR Day76","INR Day77","INR Day78","INR Day79","INR Day80","INR Day81","INR Day82","INR Day83","INR Day84","INR Day85","INR Day86","INR Day87","INR Day88","INR Day89","INR Day90","INR Day91","INR Day92","INR Day93","INR Day94","INR Day95","INR Day96","INR Day97","INR Day98","INR Day99","INR Day100"))

##for boxplt change last data##
libuinr_data$attribute <- factor(libuinr_data$attribute,levels = c( "INR Day1", "INR Day2", "INR Day3","INR Day4","INR Day5", "INR Day6","INR Day7","INR Day8","INR Day9","INR Day10", "INR Day11","INR Day12","INR Day13","INR Day14","INR Day15","INR Day16","INR Day17","INR Day18","INR Day19","INR Day20","INR Day21","INR Day22","INR Day23","INR Day24","INR Day25","INR Day26","INR Day27","INR Day28","INR Day29","INR Day30","INR Day31","INR Day32","INR Day33","INR Day34","INR Day35","INR Day36","INR Day37","INR Day38","INR Day39","INR Day40","INR Day41","INR Day42","INR Day43","INR Day44","INR Day45","INR Day46","INR Day47","INR Day48","INR Day49","INR Day50","INR Day51","INR Day52","INR Day53","INR Day54","INR Day55","INR Day56","INR Day57","INR Day58","INR Day59","INR Day60","INR Day61","INR Day62","INR Day63","INR Day64","INR Day65","INR Day66","INR Day67","INR Day68","INR Day69","INR Day70","INR Day71","INR Day72","INR Day73","INR Day74","INR Day75","INR Day76","INR Day77","INR Day78","INR Day79","INR Day80","INR Day81","INR Day82","INR Day83","INR Day84","INR Day85","INR Day86","INR Day87","INR Day88","INR Day89","INR Day90","INR Day91","INR Day92","INR Day93","INR Day94","INR Day95","INR Day96","INR Day97","INR Day98","INR Day99","INR Day100"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
inr_summary_data <- libuinr_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(inr_summary_data$mean_labread + inr_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(inr_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean INR in time course for male with patient count",
       x = "Day of measurement",
       y = "INR",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- 5#max(inr_summary_data$mean_labread + inr_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1
                        )
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuinr_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for INR by day of measurement",
       x = "day of measurement",
       y = "INR") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Leukozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5","Leukozyten Day6","Leukozyten Day8",
"Leukozyten Day9","Leukozyten Day10", "Leukozyten Day11","Leukozyten Day12","Leukozyten Day13","Leukozyten Day15","Leukozyten Day26"))

##for boxplt change last data##
libuleukozyten_data$attribute <- factor(libuleukozyten_data$attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5","Leukozyten Day6","Leukozyten Day8",
"Leukozyten Day9","Leukozyten Day10", "Leukozyten Day11","Leukozyten Day12","Leukozyten Day13","Leukozyten Day15","Leukozyten Day26"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
leukozyten_summary_data <- libuleukozyten_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(leukozyten_summary_data$mean_labread + leukozyten_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(leukozyten_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean leukocytes in time course for male with patient count",
       x = "Day of measurement",
       y = "Leukocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(leukozyten_summary_data$mean_labread + leukozyten_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 600) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuleukozyten_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for leukocytes by day of measurement",
       x = "day of measurement",
       y = "Leukocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###GGT###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ggt_summary_data$Attribute <- factor(ggt_summary_data$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3", "GGT Day4", "GGT Day5", "GGT Day6", "GGT Day7", "GGT Day8", "GGT Day9", "GGT Day10", "GGT Day11", "GGT Day12", "GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17", "GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day24", "GGT Day26","GGT Day30","GGT Day31"))

##for boxplt change last data##
libuggt_data$attribute <- factor(libuggt_data$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3", "GGT Day4", "GGT Day5", "GGT Day6", "GGT Day7", "GGT Day8", "GGT Day9", "GGT Day10", "GGT Day11", "GGT Day12", "GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17", "GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day24", "GGT Day26","GGT Day30","GGT Day31"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ggt_summary_data <- libuggt_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ggt_summary_data$mean_labread + ggt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 600, by = 100)
#additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500)

ggplot(ggt_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean GGT in time course for male with patient count",
       x = "Day of measurement",
       y = "GGT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ggt_summary_data$mean_labread + ggt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
#additional_breaks <- if (max_value > 500) seq(600, max_value, by = 600) else numeric(0)
all_breaks <- c(breaks_up_to_500)

## use the last joined data gender with labreads##
libuggt_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+    
  labs(title = "liver_ibu boxplot for GGT by day of measurement",
       x = "day of measurement",
       y = "GGT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###LDH###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ldh_summary_data$attribute <- factor(ldh_summary_data$attribute,levels = c( "LDH Day1","LDH Day2","LDH Day4","LDH Day5","LDH Day6","LDH Day8","LDH Day10"))

##for boxplt change last data##
ldldh_data$attribute <- factor(ldldh_data$attribute,levels = c("LDH Day1","LDH Day2","LDH Day4","LDH Day5","LDH Day6","LDH Day8","LDH Day10"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ldh_summary_data <- libuldh_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ldh_summary_data$mean_labread + ldh_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ldh_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean LDH in time course for female with patient count",
       x = "Day of measurement",
       y = "LDH U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ldh_summary_data$mean_labread + ldh_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuldh_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for LDH by day of measurement",
       x = "day of measurement",
       y = "LDH U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###HB###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
hb_summary_data$attribute <- factor(hb_summary_data$attribute,levels = c("Hb Day1", "Hb Day2", "Hb Day3", "Hb Day4", "Hb Day5","Hb Day6", "Hb Day7","Hb Day8","Hb Day9","Hb Day10","Hb Day11", "Hb Day12","Hb Day14","Hb Day15", "Hb Day16"))

##for boxplt change last data##
libuhb_data$attribute <- factor(libuhb_data$attribute,levels = c("Hb Day1", "Hb Day2", "Hb Day3", "Hb Day4", "Hb Day5","Hb Day6", "Hb Day7","Hb Day8","Hb Day9","Hb Day10","Hb Day11", "Hb Day12","Hb Day14","Hb Day15", "Hb Day16"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hb_summary_data <- libuhb_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hb_summary_data$mean_labread + hb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hb_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean HB in time course for female with patient count",
       x = "Day of measurement",
       y = "HB g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hb_summary_data$mean_labread + hb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuhb_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+      
  labs(title = "liver_ibu boxplot for HB by day of measurement",
       x = "day of measurement",
       y = "HB g/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###totales Bilirubin###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
totbili_summary_data$attribute <- factor(totbili_summary_data$attribute,levels = c("TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", "TotalBilirubin Day8", "TotalBilirubin Day9", 
"TotalBilirubin Day10", "TotalBilirubin Day11","TotalBilirubin Day12","TotalBilirubin Day13","TotalBilirubin Day14","TotalBilirubin Day15","TotalBilirubin Day16","TotalBilirubin Day17","TotalBilirubin Day18","TotalBilirubin Day19","TotalBilirubin Day21","TotalBilirubin Day24","TotalBilirubin Day26"))

##for boxplt change last data##
libutotbili_data$attribute <- factor(libutotbili_data$attribute,levels = c("TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", "TotalBilirubin Day8", "TotalBilirubin Day9", 
"TotalBilirubin Day10", "TotalBilirubin Day11","TotalBilirubin Day12","TotalBilirubin Day13","TotalBilirubin Day14","TotalBilirubin Day15","TotalBilirubin Day16","TotalBilirubin Day17","TotalBilirubin Day18","TotalBilirubin Day19","TotalBilirubin Day21","TotalBilirubin Day24","TotalBilirubin Day26"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
totbili_summary_data <- libutotbili_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(totbili_summary_data$mean_labread + totbili_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(totbili_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean total bilirubin in time course for female with patient count",
       x = "Day of measurement",
       y = "total Bilirubin mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(totbili_summary_data$mean_labread + totbili_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libutotbili_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for total bilirubin by day of measurement",
       x = "day of measurement",
       y = "total Bilirubin mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###AP###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ap_summary_data$attribute <- factor(ap_summary_data$attribute,levels = c("AP Day1", "AP Day2","AP Day3","AP Day4","AP Day5","AP Day6","AP Day7","AP Day8","AP Day9","AP Day10","AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day18","AP Day21","AP Day22","AP Day23","AP Day24"))

##for boxplt change last data##
libuap_data$attribute <- factor(libuap_data$attribute,levels = c("AP Day1", "AP Day2","AP Day3","AP Day4","AP Day5","AP Day6","AP Day7","AP Day8","AP Day9","AP Day10","AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day18","AP Day21","AP Day22","AP Day23","AP Day24"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ap_summary_data <- libuap_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ap_summary_data$mean_labread + ap_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ap_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean AP in time course for female with patient count",
       x = "Day of measurement",
       y = "AP U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ap_summary_data$mean_labread + ap_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuap_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for AP by day of measurement",
       x = "day of measurement",
       y = "AP U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Kreatinin###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
krea_summary_data$attribute <- factor(krea_summary_data$attribute,levels = c("Kreatinin Day1","Kreatinin Day2","Kreatinin Day3", "Kreatinin Day4","Kreatinin Day5","Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10","Kreatinin Day13","Kreatinin Day15","Kreatinin Day22"))

##for boxplt change last data##
libukrea_data$attribute <- factor(libukrea_data$attribute,levels = c("Kreatinin Day1","Kreatinin Day2","Kreatinin Day3", "Kreatinin Day4","Kreatinin Day5","Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10","Kreatinin Day13","Kreatinin Day15","Kreatinin Day22"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
krea_summary_data <- libukrea_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(krea_summary_data$mean_labread + krea_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(krea_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean Creatinine in time course for male with patient count",
       x = "Day of measurement",
       y = "Creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(krea_summary_data$mean_labread + krea_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libukrea_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for creatinine by day of measurement",
       x = "day of measurement",
       y = "Creatinine mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###CRP###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
crp_summary_data$attribute <- factor(crp_summary_data$attribute,levels = c("CRP Day1","CRP Day2","CRP Day3","CRP Day4","CRP Day5","CRP Day6","CRP Day7","CRP Day10","CRP Day15"))

##for boxplt change last data##
libucrp_data$attribute <- factor(libucrp_data$attribute,levels = c("CRP Day1","CRP Day2","CRP Day3","CRP Day4","CRP Day5","CRP Day6","CRP Day7","CRP Day10","CRP Day15"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
crp_summary_data <- libucrp_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(crp_summary_data$mean_labread + crp_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(crp_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean CRP in time course for male with patient count",
       x = "Day of measurement",
       y = "CRP mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(crp_summary_data$mean_labread + crp_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libucrp_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for CRP by day of measurement",
       x = "day of measurement",
       y = "CRP mg/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Harnstoff###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
hst_summary_data$attribute <- factor(hst_summary_data$attribute,levels = c( "Harnstoff Day1","Harnstoff Day2","Harnstoff Day3","Harnstoff Day4","Harnstoff Day5","Harnstoff Day6","Harnstoff Day9","Harnstoff Day10","Harnstoff Day13","Harnstoff Day22"))

##for boxplt change last data##
libuhst_data$attribute <- factor(libuhst_data$attribute,levels = c( "Harnstoff Day1","Harnstoff Day2","Harnstoff Day3","Harnstoff Day4","Harnstoff Day5","Harnstoff Day6","Harnstoff Day9","Harnstoff Day10","Harnstoff Day13","Harnstoff Day22"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hst_summary_data <- libuhst_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hst_summary_data$mean_labread + hst_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hst_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean urea in time course for male with patient count",
       x = "Day of measurement",
       y = "Urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hst_summary_data$mean_labread + hst_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuhst_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for urea by day of measurement",
       x = "Day of measurement",
       y = "Urea mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```




######################################################################
###Thrombozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
thromb_summary_data$attribute <- factor(thromb_summary_data$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day6","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day15","Thrombozyten Day26"))

##for boxplt change last data##
libuthromb_data$attribute <- factor(libuthromb_data$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day6","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day15","Thrombozyten Day26"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
thromb_summary_data <- libuthromb_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(thromb_summary_data$mean_labread + thromb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(thromb_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean thrombocytes in time course for male with patient count",
       x = "Day of measurement",
       y = "Thrombocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(thromb_summary_data$mean_labread + thromb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuthromb_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for thrombocytes by day of measurement",
       x = "day of measurement",
       y = "Thrombocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Hämatokrit###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
hkt_summary_data$attribute <- factor(hkt_summary_data$attribute,levels = c( "Hämatokrit Day1","Hämatokrit Day2","Hämatokrit Day3","Hämatokrit Day4","Hämatokrit Day5","Hämatokrit Day6","Hämatokrit Day8","Hämatokrit Day9","Hämatokrit Day10","Hämatokrit Day11","Hämatokrit Day12","Hämatokrit Day13","Hämatokrit Day15","Hämatokrit Day16"))

##for boxplt change last data##
libuhkt_data$attribute <- factor(libuhkt_data$attribute,levels = c("Hämatokrit Day1","Hämatokrit Day2","Hämatokrit Day3","Hämatokrit Day4","Hämatokrit Day5","Hämatokrit Day6","Hämatokrit Day8","Hämatokrit Day9","Hämatokrit Day10","Hämatokrit Day11","Hämatokrit Day12","Hämatokrit Day13","Hämatokrit Day15","Hämatokrit Day16"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hkt_summary_data <- libuhkt_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hkt_summary_data$mean_labread + hkt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hkt_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean hematocrit in time course for female with patient count",
       x = "Day of measurement",
       y = "hematocrit %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hkt_summary_data$mean_labread + hkt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libuhkt_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for hematocrit by day of measurement",
       x = "day of measurement",
       y = "hematocrit %") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


######################################################################
###Kalium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
kal_summary_data$attribute <- factor(kal_summary_data$attribute,levels = c("Kalium Day1","Kalium Day2","Kalium Day3","Kalium Day4","Kalium Day5","Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day15"))

##for boxplt change last data##
ldkal_data$attribute <- factor(ldkal_data$attribute,levels = c("Kalium Day1","Kalium Day2","Kalium Day3","Kalium Day4","Kalium Day5","Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day15"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
kal_summary_data <- libukal_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- 10#max(kal_summary_data$mean_labread + kal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(kal_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean potassium in time course for female with patient count",
       x = "Day of measurement",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(kal_summary_data$mean_labread + kal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libukal_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for potassium by day of measurement",
       x = "day of measurement",
       y = "Potassium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Kalzium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
cal_summary_data$Attribute <- factor(cal_summary_data$attribute,levels = c("Kalzium Day1","Kalzium Day4","Kalzium Day10"))

##for boxplt change last data##
libucal_data$attribute <- factor(libucal_data$attribute,levels = c("Kalzium Day1","Kalzium Day4","Kalzium Day10"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
cal_summary_data <- libucal_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(cal_summary_data$mean_labread + cal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(cal_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_ibu mean calcium in time course for male with patient count",
       x = "Day of measurement",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(cal_summary_data$mean_labread + cal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
libucal_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_ibu boxplot for calcium by day of measurement",
       x = "day of measurement",
       y = "Calcium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Glucose###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
glu_summary_data <- ldglu_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(glu_summary_data$mean_labread + glu_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(glu_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "Mean glucose in time course for Male",
       x = "Day of measurement",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(glu_summary_data$mean_labread + glu_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldglu_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "Boxplot of glucose by day of measurement",
       x = "day of measurement",
       y = "Glucose mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```






























































































































































