---
title: "Untitled"
output: html_document
date: "2025-05-14"
---

```{r}
library(readxl)
library(tidyr)
library(dplyr)
library(ggstatsplot)
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
```


```{r}
gpt_long_cgt_filtered <- gpt_long_cgt%>%
 filter(!grepl("DBS", attribute))
gpt_long_cgt_filtered
```


```{r}
gpt_long_cgnt
```

```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_gpt_combined <- bind_rows(gpt_long_cgt_filtered,gpt_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_gpt_combined
```


```{r}
gpt_long_f <- gpt_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
gpt_long_f
```



```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_gpt_combined_TTOq <- cgt_cgnt_gpt_combined %>%
  mutate(tto_group = "TTOq")

gpt_long_f_TTOd <- gpt_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_gpt <- bind_rows(cgt_cgnt_gpt_combined_TTOq, gpt_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_gpt
```


```{r}
library(dlookr)
combined_table_peak_gpt %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_gpt
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_gpt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # ALT for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ALT u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_gpt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###GPT liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_gpt <- bind_rows(cgt_cgnt_gpt_combined_TTOq, gpt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_gpt
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_gpt
)
```


```{r}
library(ggstatsplot)

ldiclo_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_gpt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # ALT for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ALT u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_gpt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_comparison_of_peak_labvalues)
dev.off()
ldiclo_comparison_of_peak_labvalues
```


###GPT liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_gpt <- bind_rows(cgt_cgnt_gpt_combined_TTOq, gpt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_gpt
)
```


```{r}
library(ggstatsplot)

libu_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_gpt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # ALT for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ALT u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_gpt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_comparison_of_peak_labvalues)
dev.off()
libu_comparison_of_peak_labvalues
```


###GPT liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_gpt <- bind_rows(cgt_cgnt_gpt_combined_TTOq, gpt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_gpt
)
```


```{r}
library(ggstatsplot)

lpara_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_gpt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # ALT for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ALT u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_gpt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_comparison_of_peak_labvalues)
dev.off()
lpara_comparison_of_peak_labvalues
```



###got###########################################################################################

```{r}
got_long_cgt_filtered <- got_long_cgt%>%
 filter(!grepl("DBS", attribute))
got_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_got_combined <- bind_rows(got_long_cgt_filtered,got_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_got_combined
```


```{r}
got_long_f <- got_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
got_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_got_combined_TTOq <- cgt_cgnt_got_combined %>%
  mutate(tto_group = "TTOq")

got_long_f_TTOd <- got_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_got <- bind_rows(cgt_cgnt_got_combined_TTOq, got_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_got
```


```{r}
library(dlookr)
combined_table_peak_got %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_got
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_got,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # ast for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ast u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_ast_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###got liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_got <- bind_rows(cgt_cgnt_got_combined_TTOq, got_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_got
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_got
)
```


```{r}
library(ggstatsplot)

ldiclo_got_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_got,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # ast for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ast u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_got_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_got_comparison_of_peak_labvalues)
dev.off()
ldiclo_got_comparison_of_peak_labvalues
```


###got liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_got <- bind_rows(cgt_cgnt_got_combined_TTOq, got_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_got
)
```


```{r}
library(ggstatsplot)

libu_got_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_got,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # ast for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ast u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_got_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_got_comparison_of_peak_labvalues)
dev.off()
libu_got_comparison_of_peak_labvalues
```


###got liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_got <- bind_rows(cgt_cgnt_got_combined_TTOq, got_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_got
)
```


```{r}
library(ggstatsplot)

lpara_got_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_got,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # ast for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ast u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_got_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_got_comparison_of_peak_labvalues)
dev.off()
lpara_got_comparison_of_peak_labvalues
```


###ggt###########################################################################################

```{r}
ggt_long_cgt_filtered <- ggt_long_cgt%>%
 filter(!grepl("DBS", attribute))
ggt_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_ggt_combined <- bind_rows(ggt_long_cgt_filtered,ggt_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_ggt_combined
```


```{r}
ggt_long_f <- ggt_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
ggt_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_ggt_combined_TTOq <- cgt_cgnt_ggt_combined %>%
  mutate(tto_group = "TTOq")

ggt_long_f_TTOd <- ggt_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_ggt <- bind_rows(cgt_cgnt_ggt_combined_TTOq, ggt_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_ggt
```


```{r}
library(dlookr)
combined_table_peak_ggt %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_ggt
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_ggt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # ggt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ggt u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_ggt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###ggt liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_ggt <- bind_rows(cgt_cgnt_ggt_combined_TTOq, ggt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_ggt
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_ggt
)
```


```{r}
library(ggstatsplot)

ldiclo_ggt_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_ggt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # ggt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ggt u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_ggt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_ggt_comparison_of_peak_labvalues)
dev.off()
ldiclo_ggt_comparison_of_peak_labvalues
```


###ggt liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_ggt <- bind_rows(cgt_cgnt_ggt_combined_TTOq, ggt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_ggt
)
```


```{r}
library(ggstatsplot)

libu_ggt_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_ggt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # ggt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ggt u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_ggt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_ggt_comparison_of_peak_labvalues)
dev.off()
libu_ggt_comparison_of_peak_labvalues
```


###ggt liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_ggt <- bind_rows(cgt_cgnt_ggt_combined_TTOq, ggt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_ggt
)
```


```{r}
library(ggstatsplot)

lpara_ggt_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_ggt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # ggt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ggt u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_ggt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_ggt_comparison_of_peak_labvalues)
dev.off()
lpara_ggt_comparison_of_peak_labvalues
```



###ldh###########################################################################################

```{r}
ldh_long_cgt_filtered <- ldh_long_cgt%>%
 filter(!grepl("DBS", attribute))
ldh_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_ldh_combined <- bind_rows(ldh_long_cgt_filtered,ldh_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_ldh_combined
```


```{r}
ldh_long_f <- ldh_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
ldh_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_ldh_combined_TTOq <- cgt_cgnt_ldh_combined %>%
  mutate(tto_group = "TTOq")

ldh_long_f_TTOd <- ldh_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_ldh <- bind_rows(cgt_cgnt_ldh_combined_TTOq, ldh_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_ldh
```


```{r}
library(dlookr)
combined_table_peak_ldh %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_ldh
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_ldh,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # ldh for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ldh u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_ldh_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###ldh liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_ldh <- bind_rows(cgt_cgnt_ldh_combined_TTOq, ldh_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_ldh
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_ldh
)
```


```{r}
library(ggstatsplot)

ldiclo_ldh_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_ldh,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # ldh for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ldh u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_ldh_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_ldh_comparison_of_peak_labvalues)
dev.off()
ldiclo_ldh_comparison_of_peak_labvalues
```


###ldh liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_ldh <- bind_rows(cgt_cgnt_ldh_combined_TTOq, ldh_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_ldh
)
```


```{r}
library(ggstatsplot)

libu_ldh_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_ldh,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # ldh for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ldh u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_ldh_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_ldh_comparison_of_peak_labvalues)
dev.off()
libu_ldh_comparison_of_peak_labvalues
```


###ldh liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_ldh <- bind_rows(cgt_cgnt_ldh_combined_TTOq, ldh_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_ldh
)
```


```{r}
library(ggstatsplot)

lpara_ldh_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_ldh,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # ldh for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ldh u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_ldh_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_ldh_comparison_of_peak_labvalues)
dev.off()
lpara_ldh_comparison_of_peak_labvalues
```



###alkphos###########################################################################################

```{r}
alkphos_long_cgt_filtered <- ap_long_cgt%>%
 filter(!grepl("DBS", attribute))
alkphos_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_alkphos_combined <- bind_rows(alkphos_long_cgt_filtered,ap_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_alkphos_combined
```


```{r}
alkphos_long_f <- ap_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
alkphos_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_alkphos_combined_TTOq <- cgt_cgnt_alkphos_combined %>%
  mutate(tto_group = "TTOq")

alkphos_long_f_TTOd <- alkphos_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_alkphos <- bind_rows(cgt_cgnt_alkphos_combined_TTOq, alkphos_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_alkphos
```


```{r}
library(dlookr)
combined_table_peak_alkphos %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_alkphos
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_alkphos,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # alkphos for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-alkphos u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_alkphos_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###alkphos liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_alkphos <- bind_rows(cgt_cgnt_alkphos_combined_TTOq, alkphos_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_alkphos
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_alkphos
)
```


```{r}
library(ggstatsplot)

ldiclo_alkphos_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_alkphos,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # alkphos for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-alkphos u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_alkphos_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_alkphos_comparison_of_peak_labvalues)
dev.off()
ldiclo_alkphos_comparison_of_peak_labvalues
```


###alkphos liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_alkphos <- bind_rows(cgt_cgnt_alkphos_combined_TTOq, alkphos_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_alkphos
)
```


```{r}
library(ggstatsplot)

libu_alkphos_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_alkphos,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # alkphos for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-alkphos u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_alkphos_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_alkphos_comparison_of_peak_labvalues)
dev.off()
libu_alkphos_comparison_of_peak_labvalues
```


###alkphos liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_alkphos <- bind_rows(cgt_cgnt_alkphos_combined_TTOq, alkphos_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_alkphos
)
```


```{r}
library(ggstatsplot)

lpara_alkphos_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_alkphos,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # alkphos for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-alkphos u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_alkphos_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_alkphos_comparison_of_peak_labvalues)
dev.off()
lpara_alkphos_comparison_of_peak_labvalues
```


###totbili###########################################################################################

```{r}
totbili_long_cgt_filtered <- total_bilirubin_long_cgt%>%
 filter(!grepl("DBS", attribute))
totbili_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_totbili_combined <- bind_rows(totbili_long_cgt_filtered,total_bilirubin_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_totbili_combined
```


```{r}
totbili_long_f <- total_bilirubin_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
totbili_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_totbili_combined_TTOq <- cgt_cgnt_totbili_combined %>%
  mutate(tto_group = "TTOq")

totbili_long_f_TTOd <- totbili_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_totbili <- bind_rows(cgt_cgnt_totbili_combined_TTOq, totbili_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_totbili
```


```{r}
library(dlookr)
combined_table_peak_totbili %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_totbili
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_totbili,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # totbili for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-totbili mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_totbili_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###totbili liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_totbili <- bind_rows(cgt_cgnt_totbili_combined_TTOq, totbili_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_totbili
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_totbili
)
```


```{r}
library(ggstatsplot)

ldiclo_totbili_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_totbili,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # totbili for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-totbili mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_totbili_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_totbili_comparison_of_peak_labvalues)
dev.off()
ldiclo_totbili_comparison_of_peak_labvalues
```


###totbili liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_totbili <- bind_rows(cgt_cgnt_totbili_combined_TTOq, totbili_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_totbili
)
```


```{r}
library(ggstatsplot)

libu_totbili_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_totbili,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # totbili for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-totbili mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_totbili_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_totbili_comparison_of_peak_labvalues)
dev.off()
libu_totbili_comparison_of_peak_labvalues
```


###totbili liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_totbili <- bind_rows(cgt_cgnt_totbili_combined_TTOq, totbili_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_totbili
)
```


```{r}
library(ggstatsplot)

lpara_totbili_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_totbili,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # totbili for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-totbili mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_totbili_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_totbili_comparison_of_peak_labvalues)
dev.off()
lpara_totbili_comparison_of_peak_labvalues
```

###hb###########################################################################################

```{r}
hb_long_cgt_filtered <- hb_long_cgt%>%
 filter(!grepl("DBS", attribute))
hb_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_hb_combined <- bind_rows(hb_long_cgt_filtered,hb_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_hb_combined
```


```{r}
hb_long_f <- hb_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
hb_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_hb_combined_TTOq <- cgt_cgnt_hb_combined %>%
  mutate(tto_group = "TTOq")

hb_long_f_TTOd <- hb_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_hb <- bind_rows(cgt_cgnt_hb_combined_TTOq, hb_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_hb
```


```{r}
library(dlookr)
combined_table_peak_hb %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_hb
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_hb,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # hb for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hb g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_hb_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###hb liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_hb <- bind_rows(cgt_cgnt_hb_combined_TTOq, hb_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_hb
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_hb
)
```


```{r}
library(ggstatsplot)

ldiclo_hb_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_hb,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # hb for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hb g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_hb_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_hb_comparison_of_peak_labvalues)
dev.off()
ldiclo_hb_comparison_of_peak_labvalues
```


###hb liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_hb <- bind_rows(cgt_cgnt_hb_combined_TTOq, hb_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_hb
)
```


```{r}
library(ggstatsplot)

libu_hb_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_hb,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # hb for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hb g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_hb_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_hb_comparison_of_peak_labvalues)
dev.off()
libu_hb_comparison_of_peak_labvalues
```


###hb liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_hb <- bind_rows(cgt_cgnt_hb_combined_TTOq, hb_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_hb
)
```


```{r}
library(ggstatsplot)

lpara_hb_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_hb,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # hb for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hb g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_hb_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_hb_comparison_of_peak_labvalues)
dev.off()
lpara_hb_comparison_of_peak_labvalues
```


###crp###########################################################################################

```{r}
crp_long_cgt_filtered <- crp_long_cgt%>%
 filter(!grepl("DBS", attribute))
crp_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_crp_combined <- bind_rows(crp_long_cgt_filtered,crp_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_crp_combined
```


```{r}
crp_long_f <- crp_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
crp_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_crp_combined_TTOq <- cgt_cgnt_crp_combined %>%
  mutate(tto_group = "TTOq")

crp_long_f_TTOd <- crp_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_crp <- bind_rows(cgt_cgnt_crp_combined_TTOq, crp_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_crp
```


```{r}
library(dlookr)
combined_table_peak_crp %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_crp
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_crp,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # crp for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-crp mg/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_crp_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###crp liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_crp <- bind_rows(cgt_cgnt_crp_combined_TTOq, crp_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_crp
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_crp
)
```


```{r}
library(ggstatsplot)

ldiclo_crp_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_crp,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # crp for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-crp mg/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_crp_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_crp_comparison_of_peak_labvalues)
dev.off()
ldiclo_crp_comparison_of_peak_labvalues
```


###crp liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_crp <- bind_rows(cgt_cgnt_crp_combined_TTOq, crp_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_crp
)
```


```{r}
library(ggstatsplot)

libu_crp_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_crp,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # crp for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-crp mg/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_crp_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_crp_comparison_of_peak_labvalues)
dev.off()
libu_crp_comparison_of_peak_labvalues
```


###crp liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_crp <- bind_rows(cgt_cgnt_crp_combined_TTOq, crp_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_crp
)
```


```{r}
library(ggstatsplot)

lpara_crp_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_crp,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # crp for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-crp mg/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_crp_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_crp_comparison_of_peak_labvalues)
dev.off()
lpara_crp_comparison_of_peak_labvalues
```



###leucocytes###########################################################################################

```{r}
leucocytes_long_cgt_filtered <- leukozyten_long_cgt%>%
 filter(!grepl("DBS", attribute))
leucocytes_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_leucocytes_combined <- bind_rows(leucocytes_long_cgt_filtered,leukozyten_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_leucocytes_combined
```


```{r}
leucocytes_long_f <- leukozyten_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
leucocytes_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_leucocytes_combined_TTOq <- cgt_cgnt_leucocytes_combined %>%
  mutate(tto_group = "TTOq")

leucocytes_long_f_TTOd <- leucocytes_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_leucocytes <- bind_rows(cgt_cgnt_leucocytes_combined_TTOq, leucocytes_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_leucocytes
```


```{r}
library(dlookr)
combined_table_peak_leucocytes %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_leucocytes
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_leucocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # leucocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-leucocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_leucocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###leucocytes liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_leucocytes <- bind_rows(cgt_cgnt_leucocytes_combined_TTOq, leucocytes_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_leucocytes
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_leucocytes
)
```


```{r}
library(ggstatsplot)

ldiclo_leucocytes_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_leucocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # leucocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-leucocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_leucocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_leucocytes_comparison_of_peak_labvalues)
dev.off()
ldiclo_leucocytes_comparison_of_peak_labvalues
```


###leucocytes liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_leucocytes <- bind_rows(cgt_cgnt_leucocytes_combined_TTOq, leucocytes_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_leucocytes
)
```


```{r}
library(ggstatsplot)

libu_leucocytes_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_leucocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # leucocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-leucocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_leucocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_leucocytes_comparison_of_peak_labvalues)
dev.off()
libu_leucocytes_comparison_of_peak_labvalues
```


###leucocytes liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_leucocytes <- bind_rows(cgt_cgnt_leucocytes_combined_TTOq, leucocytes_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_leucocytes
)
```


```{r}
library(ggstatsplot)

lpara_leucocytes_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_leucocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # leucocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-leucocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_leucocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_leucocytes_comparison_of_peak_labvalues)
dev.off()
lpara_leucocytes_comparison_of_peak_labvalues
```



###thrombocytes###########################################################################################

```{r}
thrombocytes_long_cgt_filtered <- thrombozyten_long_cgt%>%
 filter(!grepl("DBS", attribute))
thrombocytes_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_thrombocytes_combined <- bind_rows(thrombocytes_long_cgt_filtered,thrombozyten_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_thrombocytes_combined
```


```{r}
thrombocytes_long_f <- thrombozyten_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
thrombocytes_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_thrombocytes_combined_TTOq <- cgt_cgnt_thrombocytes_combined %>%
  mutate(tto_group = "TTOq")

thrombocytes_long_f_TTOd <- thrombocytes_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_thrombocytes <- bind_rows(cgt_cgnt_thrombocytes_combined_TTOq, thrombocytes_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_thrombocytes
```


```{r}
library(dlookr)
combined_table_peak_thrombocytes %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_thrombocytes
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_thrombocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # thrombocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-thrombocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_thrombocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###thrombocytes liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_thrombocytes <- bind_rows(cgt_cgnt_thrombocytes_combined_TTOq, thrombocytes_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_thrombocytes
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_thrombocytes
)
```


```{r}
library(ggstatsplot)

ldiclo_thrombocytes_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_thrombocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # thrombocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-thrombocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_thrombocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_thrombocytes_comparison_of_peak_labvalues)
dev.off()
ldiclo_thrombocytes_comparison_of_peak_labvalues
```


###thrombocytes liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_thrombocytes <- bind_rows(cgt_cgnt_thrombocytes_combined_TTOq, thrombocytes_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_thrombocytes
)
```


```{r}
library(ggstatsplot)

libu_thrombocytes_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_thrombocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # thrombocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-thrombocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_thrombocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_thrombocytes_comparison_of_peak_labvalues)
dev.off()
libu_thrombocytes_comparison_of_peak_labvalues
```


###thrombocytes liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_thrombocytes <- bind_rows(cgt_cgnt_thrombocytes_combined_TTOq, thrombocytes_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_thrombocytes
)
```


```{r}
library(ggstatsplot)

lpara_thrombocytes_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_thrombocytes,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # thrombocytes for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-thrombocytes cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_thrombocytes_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_thrombocytes_comparison_of_peak_labvalues)
dev.off()
lpara_thrombocytes_comparison_of_peak_labvalues
```


###erythrozyten###########################################################################################

```{r}
erythrozyten_long_cgt_filtered <- erythrozyten_long_cgt%>%
 filter(!grepl("DBS", attribute))
erythrozyten_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_erythrozyten_combined <- bind_rows(erythrozyten_long_cgt_filtered,erythrozyten_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_erythrozyten_combined
```


```{r}
erythrozyten_long_f <- erythrozyten_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
erythrozyten_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_erythrozyten_combined_TTOq <- cgt_cgnt_erythrozyten_combined %>%
  mutate(tto_group = "TTOq")

erythrozyten_long_f_TTOd <- erythrozyten_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_erythrozyten <- bind_rows(cgt_cgnt_erythrozyten_combined_TTOq, erythrozyten_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_erythrozyten
```


```{r}
library(dlookr)
combined_table_peak_erythrozyten %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_erythrozyten
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_erythrozyten,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # erythrozyten for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-erythrozyten cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_erythrozyten_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###erythrozyten liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_erythrozyten <- bind_rows(cgt_cgnt_erythrozyten_combined_TTOq, erythrozyten_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_erythrozyten
```



```{}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_erythrozyten
)
```


```{r}
library(ggstatsplot)

ldiclo_erythrozyten_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_erythrozyten,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # erythrozyten for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-erythrozyten cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_erythrozyten_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_erythrozyten_comparison_of_peak_labvalues)
dev.off()
ldiclo_erythrozyten_comparison_of_peak_labvalues
```


###erythrozyten liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_erythrozyten <- bind_rows(cgt_cgnt_erythrozyten_combined_TTOq, erythrozyten_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_erythrozyten
)
```


```{r}
library(ggstatsplot)

libu_erythrozyten_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_erythrozyten,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # erythrozyten for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-erythrozyten cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_erythrozyten_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_erythrozyten_comparison_of_peak_labvalues)
dev.off()
libu_erythrozyten_comparison_of_peak_labvalues
```


###erythrozyten liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_erythrozyten <- bind_rows(cgt_cgnt_erythrozyten_combined_TTOq, erythrozyten_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_erythrozyten
)
```


```{r}
library(ggstatsplot)

lpara_erythrozyten_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_erythrozyten,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # erythrozyten for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-erythrozyten cells/ul") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_erythrozyten_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_erythrozyten_comparison_of_peak_labvalues)
dev.off()
lpara_erythrozyten_comparison_of_peak_labvalues
```


###ck###########################################################################################

```{r}
ck_long_cgt_filtered <- ck_long_cgt%>%
 filter(!grepl("DBS", attribute))
ck_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_ck_combined <- bind_rows(ck_long_cgt_filtered,ck_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_ck_combined
```


```{r}
ck_long_f <- ck_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
ck_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_ck_combined_TTOq <- cgt_cgnt_ck_combined %>%
  mutate(tto_group = "TTOq")

ck_long_f_TTOd <- ck_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_ck <- bind_rows(cgt_cgnt_ck_combined_TTOq, ck_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_ck
```


```{r}
library(dlookr)
combined_table_peak_ck %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_ck
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_ck,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # ck for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ck u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_ck_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###ck liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_ck <- bind_rows(cgt_cgnt_ck_combined_TTOq, ck_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_ck
```



```{}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_ck
)
```


```{r}
library(ggstatsplot)

ldiclo_ck_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_ck,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # ck for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ck u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_ck_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_ck_comparison_of_peak_labvalues)
dev.off()
ldiclo_ck_comparison_of_peak_labvalues
```


###ck liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_ck <- bind_rows(cgt_cgnt_ck_combined_TTOq, ck_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_ck
)
```

```{r}
library(ggstatsplot)

libu_ck_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_ck,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # ck for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ck u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_ck_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_ck_comparison_of_peak_labvalues)
dev.off()
libu_ck_comparison_of_peak_labvalues
```


###ck liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_ck <- bind_rows(cgt_cgnt_ck_combined_TTOq, ck_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_ck
)
```


```{r}
library(ggstatsplot)

lpara_ck_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_ck,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # ck for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ck u/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_ck_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_ck_comparison_of_peak_labvalues)
dev.off()
lpara_ck_comparison_of_peak_labvalues
```



###quick###########################################################################################

```{r}
quick_long_cgt_filtered <- quick_long_cgt%>%
 filter(!grepl("DBS", attribute))
quick_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_quick_combined <- bind_rows(quick_long_cgt_filtered,quick_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_quick_combined
```


```{r}
quick_long_f <- quick_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
quick_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_quick_combined_TTOq <- cgt_cgnt_quick_combined %>%
  mutate(tto_group = "TTOq")

quick_long_f_TTOd <- quick_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_quick <- bind_rows(cgt_cgnt_quick_combined_TTOq, quick_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_quick
```


```{r}
library(dlookr)
combined_table_peak_quick %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_quick
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_quick,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # quick for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-quick %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_quick_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###quick liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_quick <- bind_rows(cgt_cgnt_quick_combined_TTOq, quick_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_quick
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_quick
)
```


```{r}
library(ggstatsplot)

ldiclo_quick_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_quick,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # quick for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-quick %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_quick_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_quick_comparison_of_peak_labvalues)
dev.off()
ldiclo_quick_comparison_of_peak_labvalues
```


###quick liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_quick <- bind_rows(cgt_cgnt_quick_combined_TTOq, quick_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_quick
)
```

```{r}
library(ggstatsplot)

libu_quick_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_quick,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # quick for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-quick %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_quick_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_quick_comparison_of_peak_labvalues)
dev.off()
libu_quick_comparison_of_peak_labvalues
```


###quick liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_quick <- bind_rows(cgt_cgnt_quick_combined_TTOq, quick_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_quick
)
```


```{r}
library(ggstatsplot)

lpara_quick_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_quick,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # quick for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-quick %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_quick_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_quick_comparison_of_peak_labvalues)
dev.off()
lpara_quick_comparison_of_peak_labvalues
```



###ptt###########################################################################################

```{r}
ptt_long_cgt_filtered <- ptt_long_cgt%>%
 filter(!grepl("DBS", attribute))
ptt_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_ptt_combined <- bind_rows(ptt_long_cgt_filtered,ptt_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_ptt_combined
```


```{r}
ptt_long_f <- ptt_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
ptt_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_ptt_combined_TTOq <- cgt_cgnt_ptt_combined %>%
  mutate(tto_group = "TTOq")

ptt_long_f_TTOd <- ptt_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_ptt <- bind_rows(cgt_cgnt_ptt_combined_TTOq, ptt_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_ptt
```


```{r}
library(dlookr)
combined_table_peak_ptt %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_ptt
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_ptt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # ptt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ptt sec.") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_ptt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###ptt liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_ptt <- bind_rows(cgt_cgnt_ptt_combined_TTOq, ptt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_ptt
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_ptt
)
```


```{r}
library(ggstatsplot)

ldiclo_ptt_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_ptt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # ptt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ptt sec.") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_ptt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_ptt_comparison_of_peak_labvalues)
dev.off()
ldiclo_ptt_comparison_of_peak_labvalues
```


###ptt liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_ptt <- bind_rows(cgt_cgnt_ptt_combined_TTOq, ptt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_ptt
)
```

```{r}
library(ggstatsplot)

libu_ptt_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_ptt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # ptt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ptt sec.") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_ptt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_ptt_comparison_of_peak_labvalues)
dev.off()
libu_ptt_comparison_of_peak_labvalues
```


###ptt liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_ptt <- bind_rows(cgt_cgnt_ptt_combined_TTOq, ptt_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_ptt
)
```


```{r}
library(ggstatsplot)

lpara_ptt_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_ptt,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # ptt for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-ptt sec.") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_ptt_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_ptt_comparison_of_peak_labvalues)
dev.off()
lpara_ptt_comparison_of_peak_labvalues
```


###direct_bilirubin###########################################################################################

```{r}
direct_bilirubin_long_cgt_filtered <- direct_bilirubin_long_cgt%>%
 filter(!grepl("DBS", attribute))
direct_bilirubin_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_direct_bilirubin_combined <- bind_rows(direct_bilirubin_long_cgt_filtered,direct_bilirubin_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_direct_bilirubin_combined
```


```{r}
direct_bilirubin_long_f <- direct_bilirubin_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
direct_bilirubin_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_direct_bilirubin_combined_TTOq <- cgt_cgnt_direct_bilirubin_combined %>%
  mutate(tto_group = "TTOq")

direct_bilirubin_long_f_TTOd <- direct_bilirubin_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_direct_bilirubin <- bind_rows(cgt_cgnt_direct_bilirubin_combined_TTOq, direct_bilirubin_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_direct_bilirubin
```


```{r}
library(dlookr)
combined_table_peak_direct_bilirubin %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_direct_bilirubin
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_direct_bilirubin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # direct_bilirubin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-direct_bilirubin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_direct_bilirubin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###direct_bilirubin liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_direct_bilirubin <- bind_rows(cgt_cgnt_direct_bilirubin_combined_TTOq, direct_bilirubin_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_direct_bilirubin
```



```{}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_direct_bilirubin
)
```


```{r}
library(ggstatsplot)

ldiclo_direct_bilirubin_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_direct_bilirubin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # direct_bilirubin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-direct_bilirubin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_direct_bilirubin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_direct_bilirubin_comparison_of_peak_labvalues)
dev.off()
ldiclo_direct_bilirubin_comparison_of_peak_labvalues
```


###direct_bilirubin liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_direct_bilirubin <- bind_rows(cgt_cgnt_direct_bilirubin_combined_TTOq, direct_bilirubin_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_direct_bilirubin
)
```

```{r}
library(ggstatsplot)

libu_direct_bilirubin_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_direct_bilirubin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # direct_bilirubin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-direct_bilirubin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_direct_bilirubin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_direct_bilirubin_comparison_of_peak_labvalues)
dev.off()
libu_direct_bilirubin_comparison_of_peak_labvalues
```


###direct_bilirubin liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_direct_bilirubin <- bind_rows(cgt_cgnt_direct_bilirubin_combined_TTOq, direct_bilirubin_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_direct_bilirubin
)
```


```{r}
library(ggstatsplot)

lpara_direct_bilirubin_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_direct_bilirubin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # direct_bilirubin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-direct_bilirubin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_direct_bilirubin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_direct_bilirubin_comparison_of_peak_labvalues)
dev.off()
lpara_direct_bilirubin_comparison_of_peak_labvalues
```



###kreatinin###########################################################################################

```{r}
kreatinin_long_cgt_filtered <- kreatinin_long_cgt%>%
 filter(!grepl("DBS", attribute))
kreatinin_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_kreatinin_combined <- bind_rows(kreatinin_long_cgt_filtered,kreatinin_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_kreatinin_combined
```


```{r}
kreatinin_long_f <- kreatinin_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
kreatinin_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_kreatinin_combined_TTOq <- cgt_cgnt_kreatinin_combined %>%
  mutate(tto_group = "TTOq")

kreatinin_long_f_TTOd <- kreatinin_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_kreatinin <- bind_rows(cgt_cgnt_kreatinin_combined_TTOq, kreatinin_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_kreatinin
```


```{r}
library(dlookr)
combined_table_peak_kreatinin %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_kreatinin
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_kreatinin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # kreatinin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kreatinin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_kreatinin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###kreatinin liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_kreatinin <- bind_rows(cgt_cgnt_kreatinin_combined_TTOq, kreatinin_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_kreatinin
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_kreatinin
)
```


```{r}
library(ggstatsplot)

ldiclo_kreatinin_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_kreatinin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # kreatinin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kreatinin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_kreatinin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_kreatinin_comparison_of_peak_labvalues)
dev.off()
ldiclo_kreatinin_comparison_of_peak_labvalues
```


###kreatinin liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_kreatinin <- bind_rows(cgt_cgnt_kreatinin_combined_TTOq, kreatinin_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_kreatinin
)
```

```{r}
library(ggstatsplot)

libu_kreatinin_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_kreatinin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # kreatinin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kreatinin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_kreatinin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_kreatinin_comparison_of_peak_labvalues)
dev.off()
libu_kreatinin_comparison_of_peak_labvalues
```


###kreatinin liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_kreatinin <- bind_rows(cgt_cgnt_kreatinin_combined_TTOq, kreatinin_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_kreatinin
)
```


```{r}
library(ggstatsplot)

lpara_kreatinin_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_kreatinin,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # kreatinin for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kreatinin mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_kreatinin_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_kreatinin_comparison_of_peak_labvalues)
dev.off()
lpara_kreatinin_comparison_of_peak_labvalues
```


###harnstoff###########################################################################################

```{r}
harnstoff_long_cgt_filtered <- harnstoff_long_cgt%>%
 filter(!grepl("DBS", attribute))
harnstoff_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_harnstoff_combined <- bind_rows(harnstoff_long_cgt_filtered,harnstoff_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_harnstoff_combined
```


```{r}
harnstoff_long_f <- harnstoff_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
harnstoff_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_harnstoff_combined_TTOq <- cgt_cgnt_harnstoff_combined %>%
  mutate(tto_group = "TTOq")

harnstoff_long_f_TTOd <- harnstoff_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_harnstoff <- bind_rows(cgt_cgnt_harnstoff_combined_TTOq, harnstoff_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_harnstoff
```


```{r}
library(dlookr)
combined_table_peak_harnstoff %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_harnstoff
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_harnstoff,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # harnstoff for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-harnstoff mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_harnstoff_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###harnstoff liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_harnstoff <- bind_rows(cgt_cgnt_harnstoff_combined_TTOq, harnstoff_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_harnstoff
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_harnstoff
)
```


```{r}
library(ggstatsplot)

ldiclo_harnstoff_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_harnstoff,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # harnstoff for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-harnstoff mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_harnstoff_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_harnstoff_comparison_of_peak_labvalues)
dev.off()
ldiclo_harnstoff_comparison_of_peak_labvalues
```


###harnstoff liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_harnstoff <- bind_rows(cgt_cgnt_harnstoff_combined_TTOq, harnstoff_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_harnstoff
)
```

```{r}
library(ggstatsplot)

libu_harnstoff_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_harnstoff,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # harnstoff for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-harnstoff mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_harnstoff_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_harnstoff_comparison_of_peak_labvalues)
dev.off()
libu_harnstoff_comparison_of_peak_labvalues
```


###harnstoff liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_harnstoff <- bind_rows(cgt_cgnt_harnstoff_combined_TTOq, harnstoff_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_harnstoff
)
```


```{r}
library(ggstatsplot)

lpara_harnstoff_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_harnstoff,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # harnstoff for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-harnstoff mg/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_harnstoff_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_harnstoff_comparison_of_peak_labvalues)
dev.off()
lpara_harnstoff_comparison_of_peak_labvalues
```



###gesamteiweiß###########################################################################################

```{r}
gesamteiweiß_long_cgt_filtered <- gesamteiweiß_long_cgt%>%
 filter(!grepl("DBS", attribute))
gesamteiweiß_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_gesamteiweiß_combined <- bind_rows(gesamteiweiß_long_cgt_filtered,gesamteiweiß_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_gesamteiweiß_combined
```


```{r}
gesamteiweiß_long_f <- gesamteiweiß_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
gesamteiweiß_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_gesamteiweiß_combined_TTOq <- cgt_cgnt_gesamteiweiß_combined %>%
  mutate(tto_group = "TTOq")

gesamteiweiß_long_f_TTOd <- gesamteiweiß_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_gesamteiweiß <- bind_rows(cgt_cgnt_gesamteiweiß_combined_TTOq, gesamteiweiß_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_gesamteiweiß
```


```{r}
library(dlookr)
combined_table_peak_gesamteiweiß %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_gesamteiweiß
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_gesamteiweiß,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # gesamteiweiß for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-gesamteiweiß g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_gesamteiweiß_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###gesamteiweiß liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_gesamteiweiß <- bind_rows(cgt_cgnt_gesamteiweiß_combined_TTOq, gesamteiweiß_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_gesamteiweiß
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_gesamteiweiß
)
```


```{r}
library(ggstatsplot)

ldiclo_gesamteiweiß_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_gesamteiweiß,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # gesamteiweiß for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-gesamteiweiß g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_gesamteiweiß_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_gesamteiweiß_comparison_of_peak_labvalues)
dev.off()
ldiclo_gesamteiweiß_comparison_of_peak_labvalues
```


###gesamteiweiß liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_gesamteiweiß <- bind_rows(cgt_cgnt_gesamteiweiß_combined_TTOq, gesamteiweiß_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_gesamteiweiß
)
```

```{r}
library(ggstatsplot)

libu_gesamteiweiß_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_gesamteiweiß,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # gesamteiweiß for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-gesamteiweiß g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_gesamteiweiß_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_gesamteiweiß_comparison_of_peak_labvalues)
dev.off()
libu_gesamteiweiß_comparison_of_peak_labvalues
```


###gesamteiweiß liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_gesamteiweiß <- bind_rows(cgt_cgnt_gesamteiweiß_combined_TTOq, gesamteiweiß_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_gesamteiweiß
)
```


```{r}
library(ggstatsplot)

lpara_gesamteiweiß_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_gesamteiweiß,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # gesamteiweiß for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-gesamteiweiß g/dl") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_gesamteiweiß_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_gesamteiweiß_comparison_of_peak_labvalues)
dev.off()
lpara_gesamteiweiß_comparison_of_peak_labvalues
```


###natrium###########################################################################################

```{r}
natrium_long_cgt_filtered <- natrium_long_cgt%>%
 filter(!grepl("DBS", attribute))
natrium_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_natrium_combined <- bind_rows(natrium_long_cgt_filtered,natrium_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_natrium_combined
```


```{r}
natrium_long_f <- natrium_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
natrium_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_natrium_combined_TTOq <- cgt_cgnt_natrium_combined %>%
  mutate(tto_group = "TTOq")

natrium_long_f_TTOd <- natrium_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_natrium <- bind_rows(cgt_cgnt_natrium_combined_TTOq, natrium_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_natrium
```


```{r}
library(dlookr)
combined_table_peak_natrium %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_natrium
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_natrium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # natrium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-natrium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_natrium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###natrium liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_natrium <- bind_rows(cgt_cgnt_natrium_combined_TTOq, natrium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_natrium
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_natrium
)
```


```{r}
library(ggstatsplot)

ldiclo_natrium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_natrium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # natrium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-natrium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_natrium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_natrium_comparison_of_peak_labvalues)
dev.off()
ldiclo_natrium_comparison_of_peak_labvalues
```


###natrium liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_natrium <- bind_rows(cgt_cgnt_natrium_combined_TTOq, natrium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_natrium
)
```

```{r}
library(ggstatsplot)

libu_natrium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_natrium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # natrium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-natrium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_natrium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_natrium_comparison_of_peak_labvalues)
dev.off()
libu_natrium_comparison_of_peak_labvalues
```


###natrium liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_natrium <- bind_rows(cgt_cgnt_natrium_combined_TTOq, natrium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_natrium
)
```


```{r}
library(ggstatsplot)

lpara_natrium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_natrium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # natrium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-natrium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_natrium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_natrium_comparison_of_peak_labvalues)
dev.off()
lpara_natrium_comparison_of_peak_labvalues
```



###kalium###########################################################################################

```{r}
kalium_long_cgt_filtered <- kalium_long_cgt%>%
 filter(!grepl("DBS", attribute))
kalium_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_kalium_combined <- bind_rows(kalium_long_cgt_filtered,kalium_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_kalium_combined
```


```{r}
kalium_long_f <- kalium_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
kalium_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_kalium_combined_TTOq <- cgt_cgnt_kalium_combined %>%
  mutate(tto_group = "TTOq")

kalium_long_f_TTOd <- kalium_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_kalium <- bind_rows(cgt_cgnt_kalium_combined_TTOq, kalium_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_kalium
```


```{r}
library(dlookr)
combined_table_peak_kalium %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_kalium
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_kalium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # kalium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_kalium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###kalium liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_kalium <- bind_rows(cgt_cgnt_kalium_combined_TTOq, kalium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_kalium
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_kalium
)
```


```{r}
library(ggstatsplot)

ldiclo_kalium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_kalium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # kalium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_kalium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_kalium_comparison_of_peak_labvalues)
dev.off()
ldiclo_kalium_comparison_of_peak_labvalues
```


###kalium liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_kalium <- bind_rows(cgt_cgnt_kalium_combined_TTOq, kalium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_kalium
)
```

```{r}
library(ggstatsplot)

libu_kalium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_kalium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # kalium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_kalium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_kalium_comparison_of_peak_labvalues)
dev.off()
libu_kalium_comparison_of_peak_labvalues
```


###kalium liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_kalium <- bind_rows(cgt_cgnt_kalium_combined_TTOq, kalium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_kalium
)
```


```{r}
library(ggstatsplot)

lpara_kalium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_kalium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # kalium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_kalium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_kalium_comparison_of_peak_labvalues)
dev.off()
lpara_kalium_comparison_of_peak_labvalues
```


###kalzium###########################################################################################

```{r}
kalzium_long_cgt_filtered <- kalzium_long_cgt%>%
 filter(!grepl("DBS", attribute))
kalzium_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_kalzium_combined <- bind_rows(kalzium_long_cgt_filtered,kalzium_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_kalzium_combined
```


```{r}
kalzium_long_f <- kalzium_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
kalzium_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_kalzium_combined_TTOq <- cgt_cgnt_kalzium_combined %>%
  mutate(tto_group = "TTOq")

kalzium_long_f_TTOd <- kalzium_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_kalzium <- bind_rows(cgt_cgnt_kalzium_combined_TTOq, kalzium_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_kalzium
```


```{r}
library(dlookr)
combined_table_peak_kalzium %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_kalzium
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_kalzium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # kalzium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalzium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_kalzium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###kalzium liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_kalzium <- bind_rows(cgt_cgnt_kalzium_combined_TTOq, kalzium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_kalzium
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_kalzium
)
```


```{r}
library(ggstatsplot)

ldiclo_kalzium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_kalzium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # kalzium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalzium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_kalzium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_kalzium_comparison_of_peak_labvalues)
dev.off()
ldiclo_kalzium_comparison_of_peak_labvalues
```


###kalzium liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_kalzium <- bind_rows(cgt_cgnt_kalzium_combined_TTOq, kalzium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_kalzium
)
```

```{r}
library(ggstatsplot)

libu_kalzium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_kalzium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # kalzium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalzium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_kalzium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_kalzium_comparison_of_peak_labvalues)
dev.off()
libu_kalzium_comparison_of_peak_labvalues
```


###kalzium liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_kalzium <- bind_rows(cgt_cgnt_kalzium_combined_TTOq, kalzium_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_kalzium
)
```


```{r}
library(ggstatsplot)

lpara_kalzium_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_kalzium,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # kalzium for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-kalzium mmol/l") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_kalzium_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_kalzium_comparison_of_peak_labvalues)
dev.off()
lpara_kalzium_comparison_of_peak_labvalues
```


###hämatokrit###########################################################################################

```{r}
hämatokrit_long_cgt_filtered <- hämatokrit_long_cgt%>%
 filter(!grepl("DBS", attribute))
hämatokrit_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_hämatokrit_combined <- bind_rows(hämatokrit_long_cgt_filtered,hämatokrit_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_hämatokrit_combined
```


```{r}
hämatokrit_long_f <- hämatokrit_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
hämatokrit_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_hämatokrit_combined_TTOq <- cgt_cgnt_hämatokrit_combined %>%
  mutate(tto_group = "TTOq")

hämatokrit_long_f_TTOd <- hämatokrit_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_hämatokrit <- bind_rows(cgt_cgnt_hämatokrit_combined_TTOq, hämatokrit_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_hämatokrit
```


```{r}
library(dlookr)
combined_table_peak_hämatokrit %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_hämatokrit
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_hämatokrit,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # hämatokrit for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hämatokrit %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_hämatokrit_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###hämatokrit liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_hämatokrit <- bind_rows(cgt_cgnt_hämatokrit_combined_TTOq, hämatokrit_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_hämatokrit
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_hämatokrit
)
```


```{r}
library(ggstatsplot)

ldiclo_hämatokrit_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_hämatokrit,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # hämatokrit for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hämatokrit %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_hämatokrit_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_hämatokrit_comparison_of_peak_labvalues)
dev.off()
ldiclo_hämatokrit_comparison_of_peak_labvalues
```


###hämatokrit liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_hämatokrit <- bind_rows(cgt_cgnt_hämatokrit_combined_TTOq, hämatokrit_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_hämatokrit
)
```

```{r}
library(ggstatsplot)

libu_hämatokrit_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_hämatokrit,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # hämatokrit for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hämatokrit %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_hämatokrit_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_hämatokrit_comparison_of_peak_labvalues)
dev.off()
libu_hämatokrit_comparison_of_peak_labvalues
```


###hämatokrit liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_hämatokrit <- bind_rows(cgt_cgnt_hämatokrit_combined_TTOq, hämatokrit_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_hämatokrit
)
```


```{r}
library(ggstatsplot)

lpara_hämatokrit_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_hämatokrit,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # hämatokrit for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-hämatokrit %") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_hämatokrit_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_hämatokrit_comparison_of_peak_labvalues)
dev.off()
lpara_hämatokrit_comparison_of_peak_labvalues
```




###inr###########################################################################################

```{r}
inr_long_cgt_filtered <- inr_long_cgt%>%
 filter(!grepl("DBS", attribute))
inr_long_cgt_filtered
```


```{r}
# Angenommen, deine Tabellen heißen tabelle1 und tabelle2
cgt_cgnt_inr_combined <- bind_rows(inr_long_cgt_filtered,inr_long_cgnt)

# Ergebnis anzeigen
cgt_cgnt_inr_combined
```


```{r}
inr_long_f <- inr_long %>% 
#  group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") %>%
  filter(!str_detect(attribute, "_From Start|_From start|DBS"))
inr_long_f
```


```{r}
# Beispiel: tabelle1 = Gruppe A, tabelle2 = Gruppe B
cgt_cgnt_inr_combined_TTOq <- cgt_cgnt_inr_combined %>%
  mutate(tto_group = "TTOq")

inr_long_f_TTOd <- inr_long_f %>%
  mutate(tto_group = "TTOd")

# Jetzt zusammenfügen
combined_table_peak_inr <- bind_rows(cgt_cgnt_inr_combined_TTOq, inr_long_f_TTOd) %>%   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   ungroup()

combined_table_peak_inr
```


```{r}
library(dlookr)
combined_table_peak_inr %>% 
  group_by(tto_group) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ tto_group,
  data = combined_table_peak_inr
)
```


```{r}
library(ggstatsplot)

all_patients_comparison_of_peak_labvalues <- ggbetweenstats(
  data = combined_table_peak_inr,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "all patients_comparison of peak labvalues", # inr for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-inr") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/all_patients_inr_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(all_patients_comparison_of_peak_labvalues)
dev.off()
all_patients_comparison_of_peak_labvalues
```


###inr liver_diclo######################


```{r}
# Jetzt zusammenfügen
ldiclo_combined_table_peak_inr <- bind_rows(cgt_cgnt_inr_combined_TTOq, inr_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Diclo") 
ldiclo_combined_table_peak_inr
```



```{r}
t.test(
   labreads ~ tto_group,
  data = ldiclo_combined_table_peak_inr
)
```


```{r}
library(ggstatsplot)

ldiclo_inr_comparison_of_peak_labvalues <- ggbetweenstats(
  data = ldiclo_combined_table_peak_inr,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver diclo_comparison of peak labvalues", # inr for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-inr") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/ldiclo_inr_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(ldiclo_inr_comparison_of_peak_labvalues)
dev.off()
ldiclo_inr_comparison_of_peak_labvalues
```


###inr liver_ibu######################


```{r}
# Jetzt zusammenfügen
libu_combined_table_peak_inr <- bind_rows(cgt_cgnt_inr_combined_TTOq, inr_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Ibu") 
```



```{}
t.test(
   labreads ~ tto_group,
  data = libu_combined_table_peak_inr
)
```

```{r}
library(ggstatsplot)

libu_inr_comparison_of_peak_labvalues <- ggbetweenstats(
  data = libu_combined_table_peak_inr,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver ibu_comparison of peak labvalues", # inr for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-inr") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/libu_inr_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(libu_inr_comparison_of_peak_labvalues)
dev.off()
libu_inr_comparison_of_peak_labvalues
```


###inr liver para######################


```{r}
# Jetzt zusammenfügen
lpara_combined_table_peak_inr <- bind_rows(cgt_cgnt_inr_combined_TTOq, inr_long_f_TTOd )%>%
   group_by(`Edited_BfArM Nummer2`) %>%   filter(labreads == max(labreads, na.rm = TRUE)) %>%   slice(1) %>% ungroup() %>% filter(Treatment == "Leber_Para") 
```



```{r}
t.test(
   labreads ~ tto_group,
  data = lpara_combined_table_peak_inr
)
```


```{r}
library(ggstatsplot)

lpara_inr_comparison_of_peak_labvalues <- ggbetweenstats(
  data = lpara_combined_table_peak_inr,
  x = "tto_group",
  y = "labreads",
  type = "np",
  title = "liver para_comparison of peak labvalues", # inr for labvalue and daily dose",
       xlab = "TTO group",
       ylab = "Peak-inr") 
dir.create("plots_peak", showWarnings = FALSE)
svg("plots_peak/lpara_inr_comparison_of_peak_labvalues.svg", height = 8, width = 6.5)
print(lpara_inr_comparison_of_peak_labvalues)
dev.off()
lpara_inr_comparison_of_peak_labvalues
```








