---
title: "Untitled"
output: html_document
date: "2025-06-01"
---


```{r}
library(readxl)
library(tidyr)
library(dplyr)
library(ggstatsplot)
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(rstantools)
library(ggpubr)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


############################################################################
### got ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_gpt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_gpt_both_groups[ldiclo_gpt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_gpt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ALT U/l",
    title = "liver diclo_gpt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/gpt_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_gpt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_gpt_both_groups[libu_gpt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_gpt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ALT U/l",
    title = "liver ibu_gpt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/gpt_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_gpt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_gpt_both_groups[lpara_gpt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_gpt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ALT U/l",
    title = "liver para_gpt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/gpt_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### got ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_got_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_got_both_groups[ldiclo_got_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_got_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "AST U/l",
    title = "liver diclo_got_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/got_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_got_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_got_both_groups[libu_got_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_got_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "AST U/l",
    title = "liver ibu_got_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/got_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_got_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_got_both_groups[lpara_got_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_got_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "AST U/L",
    title = "liver para_got_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/got_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### ggt ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_ggt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_ggt_both_groups[ldiclo_ggt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_ggt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "GGT U/l",
    title = "liver diclo_ggt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ggt_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_ggt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_ggt_both_groups[libu_ggt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_ggt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "GGT U/l",
    title = "liver ibu_ggt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ggt_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_ggt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_ggt_both_groups[lpara_ggt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_ggt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "GGT U/L",
    title = "liver para_ggt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ggt_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### ap ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_ap_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_ap_both_groups[ldiclo_ap_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_ap_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ap U/l",
    title = "liver diclo_ap_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ap_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_ap_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_ap_both_groups[libu_ap_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_ap_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ap U/l",
    title = "liver ibu_ap_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ap_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_ap_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_ap_both_groups[lpara_ap_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_ap_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ap U/L",
    title = "liver para_ap_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ap_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### ck ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_ck_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_ck_both_groups[ldiclo_ck_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_ck_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ck U/l",
    title = "liver diclo_ck_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ck_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_ck_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_ck_both_groups[libu_ck_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_ck_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ck U/l",
    title = "liver ibu_ck_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ck_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_ck_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_ck_both_groups[lpara_ck_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_ck_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ck U/L",
    title = "liver para_ck_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ck_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### ldh ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_ldh_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_ldh_both_groups[ldiclo_ldh_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_ldh_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ldh U/l",
    title = "liver diclo_ldh_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ldh_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_ldh_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_ldh_both_groups[libu_ldh_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_ldh_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ldh U/l",
    title = "liver ibu_ldh_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ldh_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_ldh_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_ldh_both_groups[lpara_ldh_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_ldh_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ldh U/L",
    title = "liver para_ldh_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ldh_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### ck ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_ck_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_ck_both_groups[ldiclo_ck_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_ck_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ck U/l",
    title = "liver diclo_ck_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ck_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_ck_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_ck_both_groups[libu_ck_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_ck_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ck U/l",
    title = "liver ibu_ck_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ck_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_ck_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_ck_both_groups[lpara_ck_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_ck_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ck U/L",
    title = "liver para_ck_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ck_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### ap ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_ap_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_ap_both_groups[ldiclo_ap_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_ap_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ap U/l",
    title = "liver diclo_ap_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ap_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_ap_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_ap_both_groups[libu_ap_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_ap_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ap U/l",
    title = "liver ibu_ap_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ap_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_ap_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_ap_both_groups[lpara_ap_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_ap_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ap U/L",
    title = "liver para_ap_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ap_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### ptt ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_ptt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_ptt_both_groups[ldiclo_ptt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_ptt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ptt sec.",
    title = "liver diclo_ptt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ptt_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_ptt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_ptt_both_groups[libu_ptt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_ptt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ptt sec.",
    title = "liver ibu_ptt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ptt_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_ptt_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_ptt_both_groups[lpara_ptt_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_ptt_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "ptt sec.",
    title = "liver para_ptt_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/ptt_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### leukozyten ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_leukozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_leukozyten_both_groups[ldiclo_leukozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_leukozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "leukozyten cells/ul",
    title = "liver diclo_leukozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/leukozyten_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_leukozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_leukozyten_both_groups[libu_leukozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_leukozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "leukozyten cells/ul",
    title = "liver ibu_leukozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/leukozyten_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_leukozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_leukozyten_both_groups[lpara_leukozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_leukozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "leukozyten cells/ul",
    title = "liver para_leukozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/leukozyten_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### thrombozyten ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_thrombozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_thrombozyten_both_groups[ldiclo_thrombozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_thrombozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "thrombozyten cells/ul",
    title = "liver diclo_thrombozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/thrombozyten_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_thrombozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_thrombozyten_both_groups[libu_thrombozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_thrombozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "thrombozyten cells/ul",
    title = "liver ibu_thrombozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/thrombozyten_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_thrombozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_thrombozyten_both_groups[lpara_thrombozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_thrombozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "thrombozyten cells/ul",
    title = "liver para_thrombozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/thrombozyten_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### erythrozyten ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_erythrozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_erythrozyten_both_groups[ldiclo_erythrozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_erythrozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "erythrozyten cells/ul",
    title = "liver diclo_erythrozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/erythrozyten_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_erythrozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_erythrozyten_both_groups[libu_erythrozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_erythrozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "erythrozyten cells/ul",
    title = "liver ibu_erythrozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/erythrozyten_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_erythrozyten_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_erythrozyten_both_groups[lpara_erythrozyten_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_erythrozyten_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "erythrozyten cells/ul",
    title = "liver para_erythrozyten_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/erythrozyten_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### hb ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_hb_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_hb_both_groups[ldiclo_hb_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_hb_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "hb g/dl",
    title = "liver diclo_hb_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/hb_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_hb_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_hb_both_groups[libu_hb_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_hb_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "hb g/dl",
    title = "liver ibu_hb_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/hb_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_hb_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_hb_both_groups[lpara_hb_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_hb_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "hb g/dl",
    title = "liver para_hb_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/hb_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### gesamteiweiß ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_gesamteiweiß_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_gesamteiweiß_both_groups[ldiclo_gesamteiweiß_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_gesamteiweiß_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "gesamteiweiß g/dl",
    title = "liver diclo_gesamteiweiß_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/gesamteiweiß_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_gesamteiweiß_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_gesamteiweiß_both_groups[libu_gesamteiweiß_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_gesamteiweiß_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "gesamteiweiß g/dl",
    title = "liver ibu_gesamteiweiß_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/gesamteiweiß_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_gesamteiweiß_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_gesamteiweiß_both_groups[lpara_gesamteiweiß_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_gesamteiweiß_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "gesamteiweiß g/dl",
    title = "liver para_gesamteiweiß_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/gesamteiweiß_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### total_bilirubin ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_total_bilirubin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_total_bilirubin_both_groups[ldiclo_total_bilirubin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_total_bilirubin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "total_bilirubin mg/dl",
    title = "liver diclo_total_bilirubin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/total_bilirubin_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_total_bilirubin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_total_bilirubin_both_groups[libu_total_bilirubin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_total_bilirubin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "total_bilirubin mg/dl",
    title = "liver ibu_total_bilirubin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/total_bilirubin_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_total_bilirubin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_total_bilirubin_both_groups[lpara_total_bilirubin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_total_bilirubin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "total_bilirubin mg/dl",
    title = "liver para_total_bilirubin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/total_bilirubin_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### direct_bilirubin ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_direct_bilirubin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_direct_bilirubin_both_groups[ldiclo_direct_bilirubin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_direct_bilirubin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "direct_bilirubin mg/dl",
    title = "liver diclo_direct_bilirubin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/direct_bilirubin_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_direct_bilirubin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_direct_bilirubin_both_groups[libu_direct_bilirubin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_direct_bilirubin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "direct_bilirubin mg/dl",
    title = "liver ibu_direct_bilirubin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/direct_bilirubin_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_direct_bilirubin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_direct_bilirubin_both_groups[lpara_direct_bilirubin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_direct_bilirubin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "direct_bilirubin mg/dl",
    title = "liver para_direct_bilirubin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/direct_bilirubin_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### kreatinin ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_kreatinin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_kreatinin_both_groups[ldiclo_kreatinin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_kreatinin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kreatinin mg/dl",
    title = "liver diclo_kreatinin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kreatinin_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_kreatinin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_kreatinin_both_groups[libu_kreatinin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_kreatinin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kreatinin mg/dl",
    title = "liver ibu_kreatinin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kreatinin_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_kreatinin_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_kreatinin_both_groups[lpara_kreatinin_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_kreatinin_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kreatinin mg/dl",
    title = "liver para_kreatinin_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kreatinin_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### harnstoff ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_harnstoff_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_harnstoff_both_groups[ldiclo_harnstoff_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_harnstoff_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "harnstoff mg/dl",
    title = "liver diclo_harnstoff_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/harnstoff_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_harnstoff_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_harnstoff_both_groups[libu_harnstoff_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_harnstoff_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "harnstoff mg/dl",
    title = "liver ibu_harnstoff_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/harnstoff_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_harnstoff_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_harnstoff_both_groups[lpara_harnstoff_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_harnstoff_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "harnstoff mg/dl",
    title = "liver para_harnstoff_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/harnstoff_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### crp ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_crp_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_crp_both_groups[ldiclo_crp_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_crp_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "crp mg/l",
    title = "liver diclo_crp_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/crp_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_crp_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_crp_both_groups[libu_crp_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_crp_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "crp mg/l",
    title = "liver ibu_crp_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/crp_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_crp_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_crp_both_groups[lpara_crp_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_crp_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "crp mg/l",
    title = "liver para_crp_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/crp_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### natrium ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_natrium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_natrium_both_groups[ldiclo_natrium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_natrium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "natrium mmol/l",
    title = "liver diclo_natrium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/natrium_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_natrium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_natrium_both_groups[libu_natrium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_natrium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "natrium mmol/l",
    title = "liver ibu_natrium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/natrium_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_natrium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_natrium_both_groups[lpara_natrium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_natrium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "natrium mmol/l",
    title = "liver para_natrium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/natrium_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


############################################################################
### kalium ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_kalium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_kalium_both_groups[ldiclo_kalium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_kalium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kalium mmol/l",
    title = "liver diclo_kalium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kalium_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_kalium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_kalium_both_groups[libu_kalium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_kalium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kalium mmol/l",
    title = "liver ibu_kalium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kalium_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_kalium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_kalium_both_groups[lpara_kalium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_kalium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kalium mmol/l",
    title = "liver para_kalium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kalium_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### kalzium ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_kalzium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_kalzium_both_groups[ldiclo_kalzium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_kalzium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kalzium mmol/l",
    title = "liver diclo_kalzium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kalzium_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_kalzium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_kalzium_both_groups[libu_kalzium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_kalzium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kalzium mmol/l",
    title = "liver ibu_kalzium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kalzium_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_kalzium_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_kalzium_both_groups[lpara_kalzium_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_kalzium_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "kalzium mmol/l",
    title = "liver para_kalzium_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/kalzium_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```




############################################################################
### quick ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_quick_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_quick_both_groups[ldiclo_quick_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_quick_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "quick %",
    title = "liver diclo_quick_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/quick_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_quick_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_quick_both_groups[libu_quick_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_quick_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "quick %",
    title = "liver ibu_quick_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/quick_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_quick_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_quick_both_groups[lpara_quick_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_quick_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "quick %",
    title = "liver para_quick_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/quick_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```



############################################################################
### hämatokrit ####################################################################
############################################################################

#####liver_diclo#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(ldiclo_hämatokrit_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- ldiclo_hämatokrit_both_groups[ldiclo_hämatokrit_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(ldiclo_hämatokrit_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "hämatokrit %",
    title = "liver diclo_hämatokrit_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/hämatokrit_full_ldiclo_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```

#####liver_ibu#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(libu_hämatokrit_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- libu_hämatokrit_both_groups[libu_hämatokrit_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(libu_hämatokrit_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "hämatokrit %",
    title = "liver ibu_hämatokrit_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/hämatokrit_full_libu_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```


#####liver_para#############################

```{r}
#quantile(df$labreads, 0.25)
# Calculate Q1
Q1 <- quantile(lpara_hämatokrit_both_groups$labreads, 0.25)

# Subset rows where labreads <= Q1
q1_subset <- lpara_hämatokrit_both_groups[lpara_hämatokrit_both_groups
                                          $labreads <= Q1, ]
print(q1_subset)

# Number of unique patients in Q1 group
num_patients_q1 <- length(unique(q1_subset$`Edited_BfArM Nummer2`))

# Total number of reads in Q1 group
total_reads_q1 <- nrow(q1_subset)

# Output
cat("Q1 value of labreads:", Q1, "\n")
cat("Number of Unique Patients with labreads <= Q1:", num_patients_q1, "\n")
cat("Number of Reads with labreads <= Q1:", total_reads_q1, "\n")

```


```{r}
#q1data_dili <- bind_rows(lpara_hämatokrit_full_after_start,q1_subset)
q1data_dili <- q1_subset %>% 
  mutate(Treatment = as.factor(Treatment))



group_counts <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(total_unique = n_distinct(`Edited_BfArM Nummer2`), .groups = "drop")
group_counts


y_pos <- q1data_dili %>%
  group_by(Treatment) %>%
  summarise(y = max(labreads, na.rm = TRUE) * 1.09, .groups = "drop")

y_pos


group_counts <- left_join(group_counts, y_pos, by = "Treatment")
group_counts

```

```{r}
q1plot_dili <- ggbetweenstats(
  data = q1data_dili,
  x = Treatment,
  y = labreads,
  type = "parametric"
)+
  theme_classic()+
  labs(
    x = "Patient group",
    y = "hämatokrit %",
    title = "liver para_hämatokrit_full_comparison labreads after reactionstart for patients with and without controlvisit in Q1")+
  
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 12, hjust =0.5))+
  geom_text(
    data = group_counts,
    aes(
      x = Treatment,
      y = y,
      label = paste0("N = ", total_unique)
    ),
    inherit.aes = FALSE,
    size = 4,
    vjust = -0.5
  )

q1plot_dili

dir.create("plots_comparison_control_visit_group_Q1", showWarnings = FALSE)
svg("plots_comparison_control_visit_group_Q1/hämatokrit_full_lpara_comparison_control_visit_group_Q1.svg", height = 8, width = 10)
print(q1plot_dili)
dev.off()
```







