---
title: "Untitled"
output: html_document
date: "2025-05-15"
---

```{r}
library(readxl)
library(tidyr)
library(dplyr)
library(ggstatsplot)
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
```

```{r}
fs_gpt_full <- gpt_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_gpt_full$attribute))
fs_gpt_full
```

```{r}

fs_gpt_full_filtered <- gpt_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_gpt_full_filtered
```

```{r}
fs_gpt_full_filtered_grouped <- fs_gpt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_gpt_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_gpt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_ALT <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-ALT", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_ALT.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_ALT)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_gpt_full_filtered <- fs_gpt_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_gpt_full_filtered
```


```{r}
ldiclo_fs_gpt_full_filtered_grouped <- ldiclo_fs_gpt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_gpt_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_gpt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_ALT <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-ALT", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_ALT.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_ALT)
dev.off()
```



####liver ibu############

```{r}

libu_fs_gpt_full_filtered <- fs_gpt_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_gpt_full_filtered_grouped <- libu_fs_gpt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_gpt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_ALT <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-ALT", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_ALT.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_ALT)
dev.off()
```



####liver_para############

```{r}

lpara_fs_gpt_full_filtered <- fs_gpt_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_gpt_full_filtered_grouped <- lpara_fs_gpt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_gpt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_AST <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-AST", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_ALT


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_AST.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_AST)
dev.off()


```


### got #######################################################################

```{r}
fs_got_full <- got_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_got_full$attribute))
fs_got_full
```

```{r}

fs_got_full_filtered <- got_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_got_full_filtered
```

```{r}
fs_got_full_filtered_grouped <- fs_got_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_got_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_got_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_got <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-got", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_got.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_got)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_got_full_filtered <- fs_got_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_got_full_filtered
```


```{r}
ldiclo_fs_got_full_filtered_grouped <- ldiclo_fs_got_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_got_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_got_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_got <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-got", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_got.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_got)
dev.off()
```



####liver ibu############

```{r}

libu_fs_got_full_filtered <- fs_got_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_got_full_filtered_grouped <- libu_fs_got_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_got_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_got <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-got", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_got.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_got)
dev.off()
```



####liver_para############

```{r}

lpara_fs_got_full_filtered <- fs_got_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_got_full_filtered_grouped <- lpara_fs_got_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 21 & peak_labread <= 62.9 ~ "1-2 times ULN",
      peak_labread >= 63 & peak_labread <= 127.9 ~ "3-5 times ULN",
      peak_labread >= 128 & peak_labread <= 212.9 ~ "6-9 times ULN",
      peak_labread >= 213 & peak_labread <= 1062.9 ~ "10-49 times ULN",
      peak_labread >= 1063 & peak_labread <= 2124.9 ~ "50-99 times ULN",
      peak_labread >= 2125 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 10625 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_got_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_got <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-got", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_got


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_got.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_got)
dev.off()


```








### ggt #######################################################################

```{r}
fs_ggt_full <- ggt_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_ggt_full$attribute))
fs_ggt_full
```

```{r}

fs_ggt_full_filtered <- ggt_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_ggt_full_filtered
```

```{r}
fs_ggt_full_filtered_grouped <- fs_ggt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
     peak_labread <= 25.9 ~ "within normal reference",
      peak_labread >= 26 & peak_labread <= 77.9 ~ "1-2 times ULN",
      peak_labread >= 78 & peak_labread <= 155.9 ~ "3-5 times ULN",
      peak_labread >= 156 & peak_labread <= 259.9 ~ "6-9 times ULN",
      peak_labread >= 260 & peak_labread <= 1299.9 ~ "10-49 times ULN",
      peak_labread >= 1300 & peak_labread <= 2599.9 ~ "50-99 times ULN",
      peak_labread >= 2600 & peak_labread <= 12999.9 ~ "100-499 times ULN",
      peak_labread >= 13000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_ggt_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_ggt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_ggt <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-ggt", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_ggt.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_ggt)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_ggt_full_filtered <- fs_ggt_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_ggt_full_filtered
```


```{r}
ldiclo_fs_ggt_full_filtered_grouped <- ldiclo_fs_ggt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 25.9 ~ "within normal reference",
      peak_labread >= 26 & peak_labread <= 77.9 ~ "1-2 times ULN",
      peak_labread >= 78 & peak_labread <= 155.9 ~ "3-5 times ULN",
      peak_labread >= 156 & peak_labread <= 259.9 ~ "6-9 times ULN",
      peak_labread >= 260 & peak_labread <= 1299.9 ~ "10-49 times ULN",
      peak_labread >= 1300 & peak_labread <= 2599.9 ~ "50-99 times ULN",
      peak_labread >= 2600 & peak_labread <= 12999.9 ~ "100-499 times ULN",
      peak_labread >= 13000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_ggt_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_ggt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_ggt <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-ggt", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_ggt.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_ggt)
dev.off()
```



####liver ibu############

```{r}

libu_fs_ggt_full_filtered <- fs_ggt_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_ggt_full_filtered_grouped <- libu_fs_ggt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 25.9 ~ "within normal reference",
      peak_labread >= 26 & peak_labread <= 77.9 ~ "1-2 times ULN",
      peak_labread >= 78 & peak_labread <= 155.9 ~ "3-5 times ULN",
      peak_labread >= 156 & peak_labread <= 259.9 ~ "6-9 times ULN",
      peak_labread >= 260 & peak_labread <= 1299.9 ~ "10-49 times ULN",
      peak_labread >= 1300 & peak_labread <= 2599.9 ~ "50-99 times ULN",
      peak_labread >= 2600 & peak_labread <= 12999.9 ~ "100-499 times ULN",
      peak_labread >= 13000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_ggt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_ggt <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-ggt", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_ggt.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_ggt)
dev.off()
```



####liver_para############

```{r}

lpara_fs_ggt_full_filtered <- fs_ggt_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_ggt_full_filtered_grouped <- lpara_fs_ggt_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 25.9 ~ "within normal reference",
      peak_labread >= 26 & peak_labread <= 77.9 ~ "1-2 times ULN",
      peak_labread >= 78 & peak_labread <= 155.9 ~ "3-5 times ULN",
      peak_labread >= 156 & peak_labread <= 259.9 ~ "6-9 times ULN",
      peak_labread >= 260 & peak_labread <= 1299.9 ~ "10-49 times ULN",
      peak_labread >= 1300 & peak_labread <= 2599.9 ~ "50-99 times ULN",
      peak_labread >= 2600 & peak_labread <= 12999.9 ~ "100-499 times ULN",
      peak_labread >= 13000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_ggt_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_ggt <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-ggt", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_ALT


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_ggt.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_ggt)
dev.off()


```



### ldh #######################################################################

```{r}
fs_ldh_full <- ldh_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_ldh_full$attribute))
fs_ldh_full
```

```{r}

fs_ldh_full_filtered <- ldh_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_ldh_full_filtered
```

```{r}
fs_ldh_full_filtered_grouped <- fs_ldh_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 382.9 ~ "within normal reference",
      peak_labread >= 383 & peak_labread <= 1148.9 ~ "1-2 times ULN",
      peak_labread >= 1149 & peak_labread <= 2297.9 ~ "3-5 times ULN",
      peak_labread >= 2298 & peak_labread <= 3829.9 ~ "6-9 times ULN",
      peak_labread >= 3830 & peak_labread <= 19149.9 ~ "10-49 times ULN",
      peak_labread >= 19150 & peak_labread <= 38299.9 ~ "50-99 times ULN",
      peak_labread >= 38300 & peak_labread <= 191499.9 ~ "100-499 times ULN",
      peak_labread >= 191500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_ldh_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_ldh_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_ldh <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-ldh", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_ldh.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_ldh)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_ldh_full_filtered <- fs_ldh_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_ldh_full_filtered
```


```{r}
ldiclo_fs_ldh_full_filtered_grouped <- ldiclo_fs_ldh_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 382.9 ~ "within normal reference",
      peak_labread >= 383 & peak_labread <= 1148.9 ~ "1-2 times ULN",
      peak_labread >= 1149 & peak_labread <= 2297.9 ~ "3-5 times ULN",
      peak_labread >= 2298 & peak_labread <= 3829.9 ~ "6-9 times ULN",
      peak_labread >= 3830 & peak_labread <= 19149.9 ~ "10-49 times ULN",
      peak_labread >= 19150 & peak_labread <= 38299.9 ~ "50-99 times ULN",
      peak_labread >= 38300 & peak_labread <= 191499.9 ~ "100-499 times ULN",
      peak_labread >= 191500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_ldh_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_ldh_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_ldh <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-ldh", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_ldh.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_ldh)
dev.off()
```



####liver ibu############

```{r}

libu_fs_ldh_full_filtered <- fs_ldh_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_ldh_full_filtered_grouped <- libu_fs_ldh_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 382.9 ~ "within normal reference",
      peak_labread >= 383 & peak_labread <= 1148.9 ~ "1-2 times ULN",
      peak_labread >= 1149 & peak_labread <= 2297.9 ~ "3-5 times ULN",
      peak_labread >= 2298 & peak_labread <= 3829.9 ~ "6-9 times ULN",
      peak_labread >= 3830 & peak_labread <= 19149.9 ~ "10-49 times ULN",
      peak_labread >= 19150 & peak_labread <= 38299.9 ~ "50-99 times ULN",
      peak_labread >= 38300 & peak_labread <= 191499.9 ~ "100-499 times ULN",
      peak_labread >= 191500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_ldh_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_ldh <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-ldh", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_ldh.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_ldh)
dev.off()
```



####liver_para############

```{r}

lpara_fs_ldh_full_filtered <- fs_ldh_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_ldh_full_filtered_grouped <- lpara_fs_ldh_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 382.9 ~ "within normal reference",
      peak_labread >= 383 & peak_labread <= 1148.9 ~ "1-2 times ULN",
      peak_labread >= 1149 & peak_labread <= 2297.9 ~ "3-5 times ULN",
      peak_labread >= 2298 & peak_labread <= 3829.9 ~ "6-9 times ULN",
      peak_labread >= 3830 & peak_labread <= 19149.9 ~ "10-49 times ULN",
      peak_labread >= 19150 & peak_labread <= 38299.9 ~ "50-99 times ULN",
      peak_labread >= 38300 & peak_labread <= 191499.9 ~ "100-499 times ULN",
      peak_labread >= 191500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_ldh_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_ldh <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-ldh", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_ldh


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_ldh.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_ldh)
dev.off()


```



### ap #######################################################################

```{r}
fs_ap_full <- ap_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_ap_full$attribute))
fs_ap_full
```

```{r}

fs_ap_full_filtered <- ap_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_ap_full_filtered
```

```{r}
fs_ap_full_filtered_grouped <- fs_ap_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 119 & peak_labread <= 356.9 ~ "1-2 times ULN",
      peak_labread >= 357 & peak_labread <= 713.9 ~ "3-5 times ULN",
      peak_labread >= 714 & peak_labread <= 1189.9 ~ "6-9 times ULN",
      peak_labread >= 1190 & peak_labread <= 5949.9 ~ "10-49 times ULN",
      peak_labread >= 5950 & peak_labread <= 11899.9 ~ "50-99 times ULN",
      peak_labread >= 11900 & peak_labread <= 59499.9 ~ "100-499 times ULN",
      peak_labread >= 59500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_ap_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_ap_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_ap <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-ap", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_ap.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_ap)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_ap_full_filtered <- fs_ap_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_ap_full_filtered
```


```{r}
ldiclo_fs_ap_full_filtered_grouped <- ldiclo_fs_ap_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 119 & peak_labread <= 356.9 ~ "1-2 times ULN",
      peak_labread >= 357 & peak_labread <= 713.9 ~ "3-5 times ULN",
      peak_labread >= 714 & peak_labread <= 1189.9 ~ "6-9 times ULN",
      peak_labread >= 1190 & peak_labread <= 5949.9 ~ "10-49 times ULN",
      peak_labread >= 5950 & peak_labread <= 11899.9 ~ "50-99 times ULN",
      peak_labread >= 11900 & peak_labread <= 59499.9 ~ "100-499 times ULN",
      peak_labread >= 59500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_ap_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_ap_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_ap <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-ap", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_ap.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_ap)
dev.off()
```



####liver ibu############

```{r}

libu_fs_ap_full_filtered <- fs_ap_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_ap_full_filtered_grouped <- libu_fs_ap_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 119 & peak_labread <= 356.9 ~ "1-2 times ULN",
      peak_labread >= 357 & peak_labread <= 713.9 ~ "3-5 times ULN",
      peak_labread >= 714 & peak_labread <= 1189.9 ~ "6-9 times ULN",
      peak_labread >= 1190 & peak_labread <= 5949.9 ~ "10-49 times ULN",
      peak_labread >= 5950 & peak_labread <= 11899.9 ~ "50-99 times ULN",
      peak_labread >= 11900 & peak_labread <= 59499.9 ~ "100-499 times ULN",
      peak_labread >= 59500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_ap_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_ap <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-ap", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_ap.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_ap)
dev.off()
```



####liver_para############

```{r}

lpara_fs_ap_full_filtered <- fs_ap_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_ap_full_filtered_grouped <- lpara_fs_ap_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 20.9 ~ "within normal reference",
      peak_labread >= 119 & peak_labread <= 356.9 ~ "1-2 times ULN",
      peak_labread >= 357 & peak_labread <= 713.9 ~ "3-5 times ULN",
      peak_labread >= 714 & peak_labread <= 1189.9 ~ "6-9 times ULN",
      peak_labread >= 1190 & peak_labread <= 5949.9 ~ "10-49 times ULN",
      peak_labread >= 5950 & peak_labread <= 11899.9 ~ "50-99 times ULN",
      peak_labread >= 11900 & peak_labread <= 59499.9 ~ "100-499 times ULN",
      peak_labread >= 59500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_ap_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_ap <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-ap", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_ap


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_ap.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_ap)
dev.off()


```



### ck #######################################################################

```{r}
fs_ck_full <- ck_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_ck_full$attribute))
fs_ck_full
```

```{r}

fs_ck_full_filtered <- ck_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_ck_full_filtered
```

```{r}
fs_ck_full_filtered_grouped <- fs_ck_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 77.9 ~ "within normal reference",
      peak_labread >= 78 & peak_labread <= 233.9 ~ "1-2 times ULN",
      peak_labread >= 234 & peak_labread <= 467.9 ~ "3-5 times ULN",
      peak_labread >= 468 & peak_labread <= 770.9 ~ "6-9 times ULN",
      peak_labread >= 780 & peak_labread <= 3899.9 ~ "10-49 times ULN",
      peak_labread >= 3900 & peak_labread <= 7799.9 ~ "50-99 times ULN",
      peak_labread >= 7800 & peak_labread <= 38999.9 ~ "100-499 times ULN",
      peak_labread >= 39000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_ck_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_ck_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_ck <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-ck", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_ck.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_ck)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_ck_full_filtered <- fs_ck_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_ck_full_filtered
```


```{r}
ldiclo_fs_ck_full_filtered_grouped <- ldiclo_fs_ck_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 77.9 ~ "within normal reference",
      peak_labread >= 78 & peak_labread <= 233.9 ~ "1-2 times ULN",
      peak_labread >= 234 & peak_labread <= 467.9 ~ "3-5 times ULN",
      peak_labread >= 468 & peak_labread <= 770.9 ~ "6-9 times ULN",
      peak_labread >= 780 & peak_labread <= 3899.9 ~ "10-49 times ULN",
      peak_labread >= 3900 & peak_labread <= 7799.9 ~ "50-99 times ULN",
      peak_labread >= 7800 & peak_labread <= 38999.9 ~ "100-499 times ULN",
      peak_labread >= 39000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_ck_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_ck_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_ck <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-ck", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_ck.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_ck)
dev.off()
```



####liver ibu############

```{r}

libu_fs_ck_full_filtered <- fs_ck_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_ck_full_filtered_grouped <- libu_fs_ck_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 77.9 ~ "within normal reference",
      peak_labread >= 78 & peak_labread <= 233.9 ~ "1-2 times ULN",
      peak_labread >= 234 & peak_labread <= 467.9 ~ "3-5 times ULN",
      peak_labread >= 468 & peak_labread <= 770.9 ~ "6-9 times ULN",
      peak_labread >= 780 & peak_labread <= 3899.9 ~ "10-49 times ULN",
      peak_labread >= 3900 & peak_labread <= 7799.9 ~ "50-99 times ULN",
      peak_labread >= 7800 & peak_labread <= 38999.9 ~ "100-499 times ULN",
      peak_labread >= 39000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_ck_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_ck <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-ck", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_ck.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_ck)
dev.off()
```



####liver_para############

```{r}

lpara_fs_ck_full_filtered <- fs_ck_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_ck_full_filtered_grouped <- lpara_fs_ck_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 77.9 ~ "within normal reference",
      peak_labread >= 78 & peak_labread <= 233.9 ~ "1-2 times ULN",
      peak_labread >= 234 & peak_labread <= 467.9 ~ "3-5 times ULN",
      peak_labread >= 468 & peak_labread <= 770.9 ~ "6-9 times ULN",
      peak_labread >= 780 & peak_labread <= 3899.9 ~ "10-49 times ULN",
      peak_labread >= 3900 & peak_labread <= 7799.9 ~ "50-99 times ULN",
      peak_labread >= 7800 & peak_labread <= 38999.9 ~ "100-499 times ULN",
      peak_labread >= 39000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_ck_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_ck <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-ck", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_ck


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_ck.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_ck)
dev.off()


```


### leukozyten #######################################################################

```{r}
fs_leukozyten_full <- leukozyten_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_leukozyten_full$attribute))
fs_leukozyten_full
```

```{r}

fs_leukozyten_full_filtered <- leukozyten_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_leukozyten_full_filtered
```

```{r}
fs_leukozyten_full_filtered_grouped <- fs_leukozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7999.9 ~ "within normal reference",
      peak_labread >= 8000 & peak_labread <= 23999.9 ~ "1-2 times ULN",
      peak_labread >= 24000 & peak_labread <= 47999.9 ~ "3-5 times ULN",
      peak_labread >= 48000 & peak_labread <= 79999.9 ~ "6-9 times ULN",
      peak_labread >= 80000 & peak_labread <= 399999.9 ~ "10-49 times ULN",
      peak_labread >= 400000 & peak_labread <= 799999.9 ~ "50-99 times ULN",
      peak_labread >= 800000 & peak_labread <= 3999999.9 ~ "100-499 times ULN",
      peak_labread >= 4000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_leukozyten_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_leukozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_leukozyten <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-leukozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_leukozyten.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_leukozyten)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_leukozyten_full_filtered <- fs_leukozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_leukozyten_full_filtered
```


```{r}
ldiclo_fs_leukozyten_full_filtered_grouped <- ldiclo_fs_leukozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7999.9 ~ "within normal reference",
      peak_labread >= 8000 & peak_labread <= 23999.9 ~ "1-2 times ULN",
      peak_labread >= 24000 & peak_labread <= 47999.9 ~ "3-5 times ULN",
      peak_labread >= 48000 & peak_labread <= 79999.9 ~ "6-9 times ULN",
      peak_labread >= 80000 & peak_labread <= 399999.9 ~ "10-49 times ULN",
      peak_labread >= 400000 & peak_labread <= 799999.9 ~ "50-99 times ULN",
      peak_labread >= 800000 & peak_labread <= 3999999.9 ~ "100-499 times ULN",
      peak_labread >= 4000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_leukozyten_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_leukozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_leukozyten <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-leukozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_leukozyten.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_leukozyten)
dev.off()
```



####liver ibu############

```{r}

libu_fs_leukozyten_full_filtered <- fs_leukozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_leukozyten_full_filtered_grouped <- libu_fs_leukozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7999.9 ~ "within normal reference",
      peak_labread >= 8000 & peak_labread <= 23999.9 ~ "1-2 times ULN",
      peak_labread >= 24000 & peak_labread <= 47999.9 ~ "3-5 times ULN",
      peak_labread >= 48000 & peak_labread <= 79999.9 ~ "6-9 times ULN",
      peak_labread >= 80000 & peak_labread <= 399999.9 ~ "10-49 times ULN",
      peak_labread >= 400000 & peak_labread <= 799999.9 ~ "50-99 times ULN",
      peak_labread >= 800000 & peak_labread <= 3999999.9 ~ "100-499 times ULN",
      peak_labread >= 4000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_leukozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_leukozyten <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-leukozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_leukozyten.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_leukozyten)
dev.off()
```



####liver_para############

```{r}

lpara_fs_leukozyten_full_filtered <- fs_leukozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_leukozyten_full_filtered_grouped <- lpara_fs_leukozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7999.9 ~ "within normal reference",
      peak_labread >= 8000 & peak_labread <= 23999.9 ~ "1-2 times ULN",
      peak_labread >= 24000 & peak_labread <= 47999.9 ~ "3-5 times ULN",
      peak_labread >= 48000 & peak_labread <= 79999.9 ~ "6-9 times ULN",
      peak_labread >= 80000 & peak_labread <= 399999.9 ~ "10-49 times ULN",
      peak_labread >= 400000 & peak_labread <= 799999.9 ~ "50-99 times ULN",
      peak_labread >= 800000 & peak_labread <= 3999999.9 ~ "100-499 times ULN",
      peak_labread >= 4000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_leukozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_leukozyten <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-leukozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_leukozyten


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_leukozyten.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_leukozyten)
dev.off()


```



### thrombozyten #######################################################################

```{r}
fs_thrombozyten_full <- thrombozyten_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_thrombozyten_full$attribute))
fs_thrombozyten_full
```

```{r}

fs_thrombozyten_full_filtered <- thrombozyten_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_thrombozyten_full_filtered
```

```{r}
fs_thrombozyten_full_filtered_grouped <- fs_thrombozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 224999 ~ "within normal reference",
      peak_labread >= 225000 & peak_labread <= 674999 ~ "1-2 times ULN",
      peak_labread >= 675000 & peak_labread <= 1349999 ~ "3-5 times ULN",
      peak_labread >= 1350000 & peak_labread < 2249999 ~ "6-9 times ULN",
      peak_labread >= 2250000 & peak_labread <= 11249999 ~ "10-49 times ULN",
      peak_labread >= 11250000 & peak_labread <= 22499999 ~ "50-99 times ULN",
      peak_labread >= 22500000 & peak_labread <= 112499999 ~ "100-499 times ULN",
      peak_labread >= 112500000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_thrombozyten_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_thrombozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_thrombozyten <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-thrombozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_thrombozyten.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_thrombozyten)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_thrombozyten_full_filtered <- fs_thrombozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_thrombozyten_full_filtered
```


```{r}
ldiclo_fs_thrombozyten_full_filtered_grouped <- ldiclo_fs_thrombozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 224999 ~ "within normal reference",
      peak_labread >= 225000 & peak_labread <= 674999 ~ "1-2 times ULN",
      peak_labread >= 675000 & peak_labread <= 1349999 ~ "3-5 times ULN",
      peak_labread >= 1350000 & peak_labread < 2249999 ~ "6-9 times ULN",
      peak_labread >= 2250000 & peak_labread <= 11249999 ~ "10-49 times ULN",
      peak_labread >= 11250000 & peak_labread <= 22499999 ~ "50-99 times ULN",
      peak_labread >= 22500000 & peak_labread <= 112499999 ~ "100-499 times ULN",
      peak_labread >= 112500000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_thrombozyten_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_thrombozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_thrombozyten <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-thrombozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_thrombozyten.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_thrombozyten)
dev.off()
```



####liver ibu############

```{r}

libu_fs_thrombozyten_full_filtered <- fs_thrombozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_thrombozyten_full_filtered_grouped <- libu_fs_thrombozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 224999 ~ "within normal reference",
      peak_labread >= 225000 & peak_labread <= 674999 ~ "1-2 times ULN",
      peak_labread >= 675000 & peak_labread <= 1349999 ~ "3-5 times ULN",
      peak_labread >= 1350000 & peak_labread < 2249999 ~ "6-9 times ULN",
      peak_labread >= 2250000 & peak_labread <= 11249999 ~ "10-49 times ULN",
      peak_labread >= 11250000 & peak_labread <= 22499999 ~ "50-99 times ULN",
      peak_labread >= 22500000 & peak_labread <= 112499999 ~ "100-499 times ULN",
      peak_labread >= 112500000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_thrombozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_thrombozyten <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-thrombozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_thrombozyten.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_thrombozyten)
dev.off()
```



####liver_para############

```{r}

lpara_fs_thrombozyten_full_filtered <- fs_thrombozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_thrombozyten_full_filtered_grouped <- lpara_fs_thrombozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 224999 ~ "within normal reference",
      peak_labread >= 225000 & peak_labread <= 674999 ~ "1-2 times ULN",
      peak_labread >= 675000 & peak_labread <= 1349999 ~ "3-5 times ULN",
      peak_labread >= 1350000 & peak_labread < 2249999 ~ "6-9 times ULN",
      peak_labread >= 2250000 & peak_labread <= 11249999 ~ "10-49 times ULN",
      peak_labread >= 11250000 & peak_labread <= 22499999 ~ "50-99 times ULN",
      peak_labread >= 22500000 & peak_labread <= 112499999 ~ "100-499 times ULN",
      peak_labread >= 112500000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_thrombozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_thrombozyten <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-thrombozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_thrombozyten


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_thrombozyten.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_thrombozyten)
dev.off()


```


### erythrozyten #######################################################################

```{r}
fs_erythrozyten_full <- erythrozyten_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_erythrozyten_full$attribute))
fs_erythrozyten_full
```

```{r}

fs_erythrozyten_full_filtered <- erythrozyten_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_erythrozyten_full_filtered
```

```{r}
fs_erythrozyten_full_filtered_grouped <- fs_erythrozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4749999 ~ "within normal reference",
      peak_labread >= 4750000 & peak_labread <= 14249999 ~ "1-2 times ULN",
      peak_labread >= 14250000 & peak_labread <= 28499999 ~ "3-5 times ULN",
      peak_labread >= 28500000 & peak_labread <= 47499999 ~ "6-9 times ULN",
      peak_labread >= 47500000 & peak_labread <= 237499999 ~ "10-49 times ULN",
      peak_labread >= 237500000 & peak_labread <= 474999999 ~ "50-99 times ULN",
      peak_labread >= 475000000 & peak_labread <= 2374999999 ~ "100-499 times ULN",
      peak_labread >= 2375000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_erythrozyten_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_erythrozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_erythrozyten <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-erythrozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_erythrozyten.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_erythrozyten)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_erythrozyten_full_filtered <- fs_erythrozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_erythrozyten_full_filtered
```


```{r}
ldiclo_fs_erythrozyten_full_filtered_grouped <- ldiclo_fs_erythrozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4749999 ~ "within normal reference",
      peak_labread >= 4750000 & peak_labread <= 14249999 ~ "1-2 times ULN",
      peak_labread >= 14250000 & peak_labread <= 28499999 ~ "3-5 times ULN",
      peak_labread >= 28500000 & peak_labread <= 47499999 ~ "6-9 times ULN",
      peak_labread >= 47500000 & peak_labread <= 237499999 ~ "10-49 times ULN",
      peak_labread >= 237500000 & peak_labread <= 474999999 ~ "50-99 times ULN",
      peak_labread >= 475000000 & peak_labread <= 2374999999 ~ "100-499 times ULN",
      peak_labread >= 2375000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_erythrozyten_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_erythrozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_erythrozyten <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-erythrozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_erythrozyten.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_erythrozyten)
dev.off()
```



####liver ibu############

```{r}

libu_fs_erythrozyten_full_filtered <- fs_erythrozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_erythrozyten_full_filtered_grouped <- libu_fs_erythrozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4749999 ~ "within normal reference",
      peak_labread >= 4750000 & peak_labread <= 14249999 ~ "1-2 times ULN",
      peak_labread >= 14250000 & peak_labread <= 28499999 ~ "3-5 times ULN",
      peak_labread >= 28500000 & peak_labread <= 47499999 ~ "6-9 times ULN",
      peak_labread >= 47500000 & peak_labread <= 237499999 ~ "10-49 times ULN",
      peak_labread >= 237500000 & peak_labread <= 474999999 ~ "50-99 times ULN",
      peak_labread >= 475000000 & peak_labread <= 2374999999 ~ "100-499 times ULN",
      peak_labread >= 2375000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_erythrozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_erythrozyten <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-erythrozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_erythrozyten.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_erythrozyten)
dev.off()
```



####liver_para############

```{r}

lpara_fs_erythrozyten_full_filtered <- fs_erythrozyten_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_erythrozyten_full_filtered_grouped <- lpara_fs_erythrozyten_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4749999 ~ "within normal reference",
      peak_labread >= 4750000 & peak_labread <= 14249999 ~ "1-2 times ULN",
      peak_labread >= 14250000 & peak_labread <= 28499999 ~ "3-5 times ULN",
      peak_labread >= 28500000 & peak_labread <= 47499999 ~ "6-9 times ULN",
      peak_labread >= 47500000 & peak_labread <= 237499999 ~ "10-49 times ULN",
      peak_labread >= 237500000 & peak_labread <= 474999999 ~ "50-99 times ULN",
      peak_labread >= 475000000 & peak_labread <= 2374999999 ~ "100-499 times ULN",
      peak_labread >= 2375000000 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_erythrozyten_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_erythrozyten <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-erythrozyten", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_erythrozyten


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_erythrozyten.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_erythrozyten)
dev.off()


```


### total_bilirubin #######################################################################

```{r}
fs_total_bilirubin_full <- total_bilirubin_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_total_bilirubin_full$attribute))
fs_total_bilirubin_full
```

```{r}

fs_total_bilirubin_full_filtered <- total_bilirubin_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_total_bilirubin_full_filtered
```

```{r}
fs_total_bilirubin_full_filtered_grouped <- fs_total_bilirubin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.499 ~ "within normal reference",
      peak_labread >= 0.5 & peak_labread <= 1.499 ~ "1-2 times ULN",
      peak_labread >= 1.5 & peak_labread <= 2.99 ~ "3-5 times ULN",
      peak_labread >= 3 & peak_labread <= 4.99 ~ "6-9 times ULN",
      peak_labread >= 5 & peak_labread <= 24.99 ~ "10-49 times ULN",
      peak_labread >= 25 & peak_labread <= 49.99 ~ "50-99 times ULN",
      peak_labread >= 50 & peak_labread <= 249.99 ~ "100-499 times ULN",
      peak_labread >= 250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_total_bilirubin_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_total_bilirubin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_total_bilirubin <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-total_bilirubin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_total_bilirubin.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_total_bilirubin)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_total_bilirubin_full_filtered <- fs_total_bilirubin_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_total_bilirubin_full_filtered
```


```{r}
ldiclo_fs_total_bilirubin_full_filtered_grouped <- ldiclo_fs_total_bilirubin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.499 ~ "within normal reference",
      peak_labread >= 0.5 & peak_labread <= 1.499 ~ "1-2 times ULN",
      peak_labread >= 1.5 & peak_labread <= 2.99 ~ "3-5 times ULN",
      peak_labread >= 3 & peak_labread <= 4.99 ~ "6-9 times ULN",
      peak_labread >= 5 & peak_labread <= 24.99 ~ "10-49 times ULN",
      peak_labread >= 25 & peak_labread <= 49.99 ~ "50-99 times ULN",
      peak_labread >= 50 & peak_labread <= 249.99 ~ "100-499 times ULN",
      peak_labread >= 250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_total_bilirubin_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_total_bilirubin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_total_bilirubin <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-total_bilirubin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_total_bilirubin.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_total_bilirubin)
dev.off()
```



####liver ibu############

```{r}

libu_fs_total_bilirubin_full_filtered <- fs_total_bilirubin_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_total_bilirubin_full_filtered_grouped <- libu_fs_total_bilirubin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.499 ~ "within normal reference",
      peak_labread >= 0.5 & peak_labread <= 1.499 ~ "1-2 times ULN",
      peak_labread >= 1.5 & peak_labread <= 2.99 ~ "3-5 times ULN",
      peak_labread >= 3 & peak_labread <= 4.99 ~ "6-9 times ULN",
      peak_labread >= 5 & peak_labread <= 24.99 ~ "10-49 times ULN",
      peak_labread >= 25 & peak_labread <= 49.99 ~ "50-99 times ULN",
      peak_labread >= 50 & peak_labread <= 249.99 ~ "100-499 times ULN",
      peak_labread >= 250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_total_bilirubin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_total_bilirubin <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-total_bilirubin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_total_bilirubin.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_total_bilirubin)
dev.off()
```



####liver_para############

```{r}

lpara_fs_total_bilirubin_full_filtered <- fs_total_bilirubin_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_total_bilirubin_full_filtered_grouped <- lpara_fs_total_bilirubin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.499 ~ "within normal reference",
      peak_labread >= 0.5 & peak_labread <= 1.499 ~ "1-2 times ULN",
      peak_labread >= 1.5 & peak_labread <= 2.99 ~ "3-5 times ULN",
      peak_labread >= 3 & peak_labread <= 4.99 ~ "6-9 times ULN",
      peak_labread >= 5 & peak_labread <= 24.99 ~ "10-49 times ULN",
      peak_labread >= 25 & peak_labread <= 49.99 ~ "50-99 times ULN",
      peak_labread >= 50 & peak_labread <= 249.99 ~ "100-499 times ULN",
      peak_labread >= 250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_total_bilirubin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_total_bilirubin <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-total_bilirubin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_total_bilirubin


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_total_bilirubin.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_total_bilirubin)
dev.off()


```



### hb #######################################################################

```{r}
fs_hb_full <- hb_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_hb_full$attribute))
fs_hb_full
```

```{r}

fs_hb_full_filtered <- hb_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_hb_full_filtered
```

```{r}
fs_hb_full_filtered_grouped <- fs_hb_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 14.9 ~ "within normal reference",
      peak_labread >= 15 & peak_labread <= 44.9 ~ "1-2 times ULN",
      peak_labread >= 45 & peak_labread <= 89.9 ~ "3-5 times ULN",
      peak_labread >= 90 & peak_labread <= 149.9 ~ "6-9 times ULN",
      peak_labread >= 150 & peak_labread <= 749.9 ~ "10-49 times ULN",
      peak_labread >= 750 & peak_labread <= 1499.9 ~ "50-99 times ULN",
      peak_labread >= 1500 & peak_labread <= 7499.9 ~ "100-499 times ULN",
      peak_labread >= 7500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_hb_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_hb_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_hb <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-hb", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_hb.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_hb)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_hb_full_filtered <- fs_hb_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_hb_full_filtered
```


```{r}
ldiclo_fs_hb_full_filtered_grouped <- ldiclo_fs_hb_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 14.9 ~ "within normal reference",
      peak_labread >= 15 & peak_labread <= 44.9 ~ "1-2 times ULN",
      peak_labread >= 45 & peak_labread <= 89.9 ~ "3-5 times ULN",
      peak_labread >= 90 & peak_labread <= 149.9 ~ "6-9 times ULN",
      peak_labread >= 150 & peak_labread <= 749.9 ~ "10-49 times ULN",
      peak_labread >= 750 & peak_labread <= 1499.9 ~ "50-99 times ULN",
      peak_labread >= 1500 & peak_labread <= 7499.9 ~ "100-499 times ULN",
      peak_labread >= 7500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_hb_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_hb_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_hb <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-hb", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_hb.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_hb)
dev.off()
```



####liver ibu############

```{r}

libu_fs_hb_full_filtered <- fs_hb_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_hb_full_filtered_grouped <- libu_fs_hb_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 14.9 ~ "within normal reference",
      peak_labread >= 15 & peak_labread <= 44.9 ~ "1-2 times ULN",
      peak_labread >= 45 & peak_labread <= 89.9 ~ "3-5 times ULN",
      peak_labread >= 90 & peak_labread <= 149.9 ~ "6-9 times ULN",
      peak_labread >= 150 & peak_labread <= 749.9 ~ "10-49 times ULN",
      peak_labread >= 750 & peak_labread <= 1499.9 ~ "50-99 times ULN",
      peak_labread >= 1500 & peak_labread <= 7499.9 ~ "100-499 times ULN",
      peak_labread >= 7500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_hb_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_hb <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-hb", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_hb.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_hb)
dev.off()
```



####liver_para############

```{r}

lpara_fs_hb_full_filtered <- fs_hb_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_hb_full_filtered_grouped <- lpara_fs_hb_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 14.9 ~ "within normal reference",
      peak_labread >= 15 & peak_labread <= 44.9 ~ "1-2 times ULN",
      peak_labread >= 45 & peak_labread <= 89.9 ~ "3-5 times ULN",
      peak_labread >= 90 & peak_labread <= 149.9 ~ "6-9 times ULN",
      peak_labread >= 150 & peak_labread <= 749.9 ~ "10-49 times ULN",
      peak_labread >= 750 & peak_labread <= 1499.9 ~ "50-99 times ULN",
      peak_labread >= 1500 & peak_labread <= 7499.9 ~ "100-499 times ULN",
      peak_labread >= 7500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_hb_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_hb <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-hb", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_hb


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_hb.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_hb)
dev.off()


```



### kreatinin #######################################################################

```{r}
fs_kreatinin_full <- kreatinin_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_kreatinin_full$attribute))
fs_kreatinin_full
```

```{r}

fs_kreatinin_full_filtered <- kreatinin_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_kreatinin_full_filtered
```

```{r}
fs_kreatinin_full_filtered_grouped <- fs_kreatinin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.99 ~ "within normal reference",
      peak_labread >= 1 & peak_labread <= 2.99 ~ "1-2 times ULN",
      peak_labread >= 3 & peak_labread <= 5.99 ~ "3-5 times ULN",
      peak_labread >= 6 & peak_labread <= 9.99 ~ "6-9 times ULN",
      peak_labread >= 10 & peak_labread <= 49.99 ~ "10-49 times ULN",
      peak_labread >= 50 & peak_labread <= 99.99 ~ "50-99 times ULN",
      peak_labread >= 100 & peak_labread <= 499.99 ~ "100-499 times ULN",
      peak_labread >= 500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_kreatinin_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_kreatinin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_kreatinin <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-kreatinin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_kreatinin.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_kreatinin)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_kreatinin_full_filtered <- fs_kreatinin_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_kreatinin_full_filtered
```


```{r}
ldiclo_fs_kreatinin_full_filtered_grouped <- ldiclo_fs_kreatinin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.99 ~ "within normal reference",
      peak_labread >= 1 & peak_labread <= 2.99 ~ "1-2 times ULN",
      peak_labread >= 3 & peak_labread <= 5.99 ~ "3-5 times ULN",
      peak_labread >= 6 & peak_labread <= 9.99 ~ "6-9 times ULN",
      peak_labread >= 10 & peak_labread <= 49.99 ~ "10-49 times ULN",
      peak_labread >= 50 & peak_labread <= 99.99 ~ "50-99 times ULN",
      peak_labread >= 100 & peak_labread <= 499.99 ~ "100-499 times ULN",
      peak_labread >= 500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_kreatinin_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_kreatinin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_kreatinin <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-kreatinin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_kreatinin.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_kreatinin)
dev.off()
```



####liver ibu############

```{r}

libu_fs_kreatinin_full_filtered <- fs_kreatinin_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_kreatinin_full_filtered_grouped <- libu_fs_kreatinin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.99 ~ "within normal reference",
      peak_labread >= 1 & peak_labread <= 2.99 ~ "1-2 times ULN",
      peak_labread >= 3 & peak_labread <= 5.99 ~ "3-5 times ULN",
      peak_labread >= 6 & peak_labread <= 9.99 ~ "6-9 times ULN",
      peak_labread >= 10 & peak_labread <= 49.99 ~ "10-49 times ULN",
      peak_labread >= 50 & peak_labread <= 99.99 ~ "50-99 times ULN",
      peak_labread >= 100 & peak_labread <= 499.99 ~ "100-499 times ULN",
      peak_labread >= 500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_kreatinin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_kreatinin <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-kreatinin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_kreatinin.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_kreatinin)
dev.off()
```



####liver_para############

```{r}

lpara_fs_kreatinin_full_filtered <- fs_kreatinin_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_kreatinin_full_filtered_grouped <- lpara_fs_kreatinin_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 0.99 ~ "within normal reference",
      peak_labread >= 1 & peak_labread <= 2.99 ~ "1-2 times ULN",
      peak_labread >= 3 & peak_labread <= 5.99 ~ "3-5 times ULN",
      peak_labread >= 6 & peak_labread <= 9.99 ~ "6-9 times ULN",
      peak_labread >= 10 & peak_labread <= 49.99 ~ "10-49 times ULN",
      peak_labread >= 50 & peak_labread <= 99.99 ~ "50-99 times ULN",
      peak_labread >= 100 & peak_labread <= 499.99 ~ "100-499 times ULN",
      peak_labread >= 500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_kreatinin_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_kreatinin <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-kreatinin", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_kreatinin


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_kreatinin.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_kreatinin)
dev.off()


```


### crp #######################################################################

```{r}
fs_crp_full <- crp_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_crp_full$attribute))
fs_crp_full
```

```{r}

fs_crp_full_filtered <- crp_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_crp_full_filtered
```

```{r}
fs_crp_full_filtered_grouped <- fs_crp_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7.49 ~ "within normal reference",
      peak_labread >= 7.5 & peak_labread <= 22.49 ~ "1-2 times ULN",
      peak_labread >= 22.5 & peak_labread <= 44.9 ~ "3-5 times ULN",
      peak_labread >= 45 & peak_labread <= 74.9 ~ "6-9 times ULN",
      peak_labread >= 75 & peak_labread <= 374.9 ~ "10-49 times ULN",
      peak_labread >= 375 & peak_labread <= 749.9 ~ "50-99 times ULN",
      peak_labread >= 750 & peak_labread <= 3749.9 ~ "100-499 times ULN",
      peak_labread >= 3750 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_crp_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_crp_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_crp <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-crp", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_crp.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_crp)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_crp_full_filtered <- fs_crp_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_crp_full_filtered
```


```{r}
ldiclo_fs_crp_full_filtered_grouped <- ldiclo_fs_crp_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7.49 ~ "within normal reference",
      peak_labread >= 7.5 & peak_labread <= 22.49 ~ "1-2 times ULN",
      peak_labread >= 22.5 & peak_labread <= 44.9 ~ "3-5 times ULN",
      peak_labread >= 45 & peak_labread <= 74.9 ~ "6-9 times ULN",
      peak_labread >= 75 & peak_labread <= 374.9 ~ "10-49 times ULN",
      peak_labread >= 375 & peak_labread <= 749.9 ~ "50-99 times ULN",
      peak_labread >= 750 & peak_labread <= 3749.9 ~ "100-499 times ULN",
      peak_labread >= 3750 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_crp_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_crp_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_crp <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-crp", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_crp.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_crp)
dev.off()
```



####liver ibu############

```{r}

libu_fs_crp_full_filtered <- fs_crp_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_crp_full_filtered_grouped <- libu_fs_crp_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7.49 ~ "within normal reference",
      peak_labread >= 7.5 & peak_labread <= 22.49 ~ "1-2 times ULN",
      peak_labread >= 22.5 & peak_labread <= 44.9 ~ "3-5 times ULN",
      peak_labread >= 45 & peak_labread <= 74.9 ~ "6-9 times ULN",
      peak_labread >= 75 & peak_labread <= 374.9 ~ "10-49 times ULN",
      peak_labread >= 375 & peak_labread <= 749.9 ~ "50-99 times ULN",
      peak_labread >= 750 & peak_labread <= 3749.9 ~ "100-499 times ULN",
      peak_labread >= 3750 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_crp_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_crp <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-crp", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_crp.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_crp)
dev.off()
```



####liver_para############

```{r}

lpara_fs_crp_full_filtered <- fs_crp_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_crp_full_filtered_grouped <- lpara_fs_crp_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 7.49 ~ "within normal reference",
      peak_labread >= 7.5 & peak_labread <= 22.49 ~ "1-2 times ULN",
      peak_labread >= 22.5 & peak_labread <= 44.9 ~ "3-5 times ULN",
      peak_labread >= 45 & peak_labread <= 74.9 ~ "6-9 times ULN",
      peak_labread >= 75 & peak_labread <= 374.9 ~ "10-49 times ULN",
      peak_labread >= 375 & peak_labread <= 749.9 ~ "50-99 times ULN",
      peak_labread >= 750 & peak_labread <= 3749.9 ~ "100-499 times ULN",
      peak_labread >= 3750 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_crp_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_crp <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-crp", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_crp


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_crp.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_crp)
dev.off()


```



### natrium #######################################################################

```{r}
fs_natrium_full <- natrium_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_natrium_full$attribute))
fs_natrium_full
```

```{r}

fs_natrium_full_filtered <- natrium_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_natrium_full_filtered
```

```{r}
fs_natrium_full_filtered_grouped <- fs_natrium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 282.9 ~ "within normal reference",
      peak_labread >= 283 & peak_labread <= 848.9 ~ "1-2 times ULN",
      peak_labread >= 849 & peak_labread <= 1697.9 ~ "3-5 times ULN",
      peak_labread >= 1698 & peak_labread <= 2829.9 ~ "6-9 times ULN",
      peak_labread >= 2830 & peak_labread <= 14149.9 ~ "10-49 times ULN",
      peak_labread >= 14150 & peak_labread <= 28299.9 ~ "50-99 times ULN",
      peak_labread >= 28300 & peak_labread <= 141499.9 ~ "100-499 times ULN",
      peak_labread >= 141500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_natrium_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_natrium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_natrium <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-natrium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_natrium.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_natrium)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_natrium_full_filtered <- fs_natrium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_natrium_full_filtered
```


```{r}
ldiclo_fs_natrium_full_filtered_grouped <- ldiclo_fs_natrium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 282.9 ~ "within normal reference",
      peak_labread >= 283 & peak_labread <= 848.9 ~ "1-2 times ULN",
      peak_labread >= 849 & peak_labread <= 1697.9 ~ "3-5 times ULN",
      peak_labread >= 1698 & peak_labread <= 2829.9 ~ "6-9 times ULN",
      peak_labread >= 2830 & peak_labread <= 14149.9 ~ "10-49 times ULN",
      peak_labread >= 14150 & peak_labread <= 28299.9 ~ "50-99 times ULN",
      peak_labread >= 28300 & peak_labread <= 141499.9 ~ "100-499 times ULN",
      peak_labread >= 141500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_natrium_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_natrium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_natrium <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-natrium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_natrium.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_natrium)
dev.off()
```



####liver ibu############

```{r}

libu_fs_natrium_full_filtered <- fs_natrium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_natrium_full_filtered_grouped <- libu_fs_natrium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 282.9 ~ "within normal reference",
      peak_labread >= 283 & peak_labread <= 848.9 ~ "1-2 times ULN",
      peak_labread >= 849 & peak_labread <= 1697.9 ~ "3-5 times ULN",
      peak_labread >= 1698 & peak_labread <= 2829.9 ~ "6-9 times ULN",
      peak_labread >= 2830 & peak_labread <= 14149.9 ~ "10-49 times ULN",
      peak_labread >= 14150 & peak_labread <= 28299.9 ~ "50-99 times ULN",
      peak_labread >= 28300 & peak_labread <= 141499.9 ~ "100-499 times ULN",
      peak_labread >= 141500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_natrium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_natrium <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-natrium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_natrium.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_natrium)
dev.off()
```



####liver_para############

```{r}

lpara_fs_natrium_full_filtered <- fs_natrium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_natrium_full_filtered_grouped <- lpara_fs_natrium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 282.9 ~ "within normal reference",
      peak_labread >= 283 & peak_labread <= 848.9 ~ "1-2 times ULN",
      peak_labread >= 849 & peak_labread <= 1697.9 ~ "3-5 times ULN",
      peak_labread >= 1698 & peak_labread <= 2829.9 ~ "6-9 times ULN",
      peak_labread >= 2830 & peak_labread <= 14149.9 ~ "10-49 times ULN",
      peak_labread >= 14150 & peak_labread <= 28299.9 ~ "50-99 times ULN",
      peak_labread >= 28300 & peak_labread <= 141499.9 ~ "100-499 times ULN",
      peak_labread >= 141500 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_natrium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_natrium <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-natrium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_natrium


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_natrium.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_natrium)
dev.off()


```


### kalium #######################################################################

```{r}
fs_kalium_full <- kalium_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_kalium_full$attribute))
fs_kalium_full
```

```{r}

fs_kalium_full_filtered <- kalium_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_kalium_full_filtered
```

```{r}
fs_kalium_full_filtered_grouped <- fs_kalium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4.39 ~ "within normal reference",
      peak_labread >= 4.4 & peak_labread <= 13.19 ~ "1-2 times ULN",
      peak_labread >= 13.2 & peak_labread <= 25.39 ~ "3-5 times ULN",
      peak_labread >= 26.4 & peak_labread <= 43.99 ~ "6-9 times ULN",
      peak_labread >= 44 & peak_labread <= 219.9 ~ "10-49 times ULN",
      peak_labread >= 220 & peak_labread <= 439.9 ~ "50-99 times ULN",
      peak_labread >= 440 & peak_labread <= 2221.9 ~ "100-499 times ULN",
      peak_labread >= 2222 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_kalium_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_kalium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_kalium <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-kalium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_kalium.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_kalium)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_kalium_full_filtered <- fs_kalium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_kalium_full_filtered
```


```{r}
ldiclo_fs_kalium_full_filtered_grouped <- ldiclo_fs_kalium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4.39 ~ "within normal reference",
      peak_labread >= 4.4 & peak_labread <= 13.19 ~ "1-2 times ULN",
      peak_labread >= 13.2 & peak_labread <= 25.39 ~ "3-5 times ULN",
      peak_labread >= 26.4 & peak_labread <= 43.99 ~ "6-9 times ULN",
      peak_labread >= 44 & peak_labread <= 219.9 ~ "10-49 times ULN",
      peak_labread >= 220 & peak_labread <= 439.9 ~ "50-99 times ULN",
      peak_labread >= 440 & peak_labread <= 2221.9 ~ "100-499 times ULN",
      peak_labread >= 2222 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_kalium_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_kalium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_kalium <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-kalium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_kalium.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_kalium)
dev.off()
```



####liver ibu############

```{r}

libu_fs_kalium_full_filtered <- fs_kalium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_kalium_full_filtered_grouped <- libu_fs_kalium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4.39 ~ "within normal reference",
      peak_labread >= 4.4 & peak_labread <= 13.19 ~ "1-2 times ULN",
      peak_labread >= 13.2 & peak_labread <= 25.39 ~ "3-5 times ULN",
      peak_labread >= 26.4 & peak_labread <= 43.99 ~ "6-9 times ULN",
      peak_labread >= 44 & peak_labread <= 219.9 ~ "10-49 times ULN",
      peak_labread >= 220 & peak_labread <= 439.9 ~ "50-99 times ULN",
      peak_labread >= 440 & peak_labread <= 2221.9 ~ "100-499 times ULN",
      peak_labread >= 2222 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_kalium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_kalium <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-kalium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_kalium.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_kalium)
dev.off()
```



####liver_para############

```{r}

lpara_fs_kalium_full_filtered <- fs_kalium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_kalium_full_filtered_grouped <- lpara_fs_kalium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 4.39 ~ "within normal reference",
      peak_labread >= 4.4 & peak_labread <= 13.19 ~ "1-2 times ULN",
      peak_labread >= 13.2 & peak_labread <= 25.39 ~ "3-5 times ULN",
      peak_labread >= 26.4 & peak_labread <= 43.99 ~ "6-9 times ULN",
      peak_labread >= 44 & peak_labread <= 219.9 ~ "10-49 times ULN",
      peak_labread >= 220 & peak_labread <= 439.9 ~ "50-99 times ULN",
      peak_labread >= 440 & peak_labread <= 2221.9 ~ "100-499 times ULN",
      peak_labread >= 2222 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_kalium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_kalium <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-kalium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_kalium


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_kalium.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_kalium)
dev.off()


```


### kalzium #######################################################################

```{r}
fs_kalzium_full <- kalzium_full %>% 
#  filter(attribute == "_From Start") %>%
  filter(str_detect(attribute, "_From start|_From Start|DBS"))
#  filter(grepl("_From Start", fs_kalzium_full$attribute))
fs_kalzium_full
```

```{r}

fs_kalzium_full_filtered <- kalzium_full %>% 
  filter(str_detect(attribute, "_From start|_From Start|DBS"))%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
fs_kalzium_full_filtered
```

```{r}
fs_kalzium_full_filtered_grouped <- fs_kalzium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 2.49 ~ "within normal reference",
      peak_labread >= 2.5 & peak_labread <= 7.49 ~ "1-2 times ULN",
      peak_labread >= 7.5 & peak_labread <= 14.9 ~ "3-5 times ULN",
      peak_labread >= 15 & peak_labread <= 24.9 ~ "6-9 times ULN",
      peak_labread >= 25 & peak_labread <= 124.9 ~ "10-49 times ULN",
      peak_labread >= 125 & peak_labread <= 249.9 ~ "50-99 times ULN",
      peak_labread >= 250 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 1250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
fs_kalzium_full_filtered_grouped
```




####labreads per Group count###
```{r}
labvalue_group_count <- fs_kalzium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
labvalue_group_count
```



```{r}
labvalue_group_count$Labvalue_Group <-  factor(labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
all_patients_control_visit_labvalue_dimension_of_peak_kalzium <- labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "all patients_control visit_labvalue dimension of peak-kalzium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/all_patients_control_visit_labvalue_dimension_of_peak_kalzium.svg", height = 8, width = 6.5)
print(all_patients_control_visit_labvalue_dimension_of_peak_kalzium)
dev.off()
```

####liver diclo############

```{r}

ldiclo_fs_kalzium_full_filtered <- fs_kalzium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
ldiclo_fs_kalzium_full_filtered
```


```{r}
ldiclo_fs_kalzium_full_filtered_grouped <- ldiclo_fs_kalzium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 2.49 ~ "within normal reference",
      peak_labread >= 2.5 & peak_labread <= 7.49 ~ "1-2 times ULN",
      peak_labread >= 7.5 & peak_labread <= 14.9 ~ "3-5 times ULN",
      peak_labread >= 15 & peak_labread <= 24.9 ~ "6-9 times ULN",
      peak_labread >= 25 & peak_labread <= 124.9 ~ "10-49 times ULN",
      peak_labread >= 125 & peak_labread <= 249.9 ~ "50-99 times ULN",
      peak_labread >= 250 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 1250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
ldiclo_fs_kalzium_full_filtered_grouped
```


```{r}
ldiclo_labvalue_group_count <- ldiclo_fs_kalzium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
ldiclo_labvalue_group_count
```


```{r}
ldiclo_labvalue_group_count$Labvalue_Group <-  factor(ldiclo_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
ldiclo_control_visit_labvalue_dimension_of_peak_kalzium <- ldiclo_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = ldiclo_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver diclo_control visit_labvalue dimension of peak-kalzium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/ldiclo_control_visit_labvalue_dimension_of_peak_kalzium.svg", height = 8, width = 6.5)
print(ldiclo_control_visit_labvalue_dimension_of_peak_kalzium)
dev.off()
```



####liver ibu############

```{r}

libu_fs_kalzium_full_filtered <- fs_kalzium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Ibu")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
libu_fs_kalzium_full_filtered_grouped <- libu_fs_kalzium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 2.49 ~ "within normal reference",
      peak_labread >= 2.5 & peak_labread <= 7.49 ~ "1-2 times ULN",
      peak_labread >= 7.5 & peak_labread <= 14.9 ~ "3-5 times ULN",
      peak_labread >= 15 & peak_labread <= 24.9 ~ "6-9 times ULN",
      peak_labread >= 25 & peak_labread <= 124.9 ~ "10-49 times ULN",
      peak_labread >= 125 & peak_labread <= 249.9 ~ "50-99 times ULN",
      peak_labread >= 250 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 1250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
libu_labvalue_group_count <- libu_fs_kalzium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
libu_labvalue_group_count$Labvalue_Group <-  factor(libu_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
libu_control_visit_labvalue_dimension_of_peak_kalzium <-libu_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = libu_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver ibu_control visit_labvalue dimension of peak-kalzium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
#dir.create("plots_labvalue dimension of rise_from start", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/libu_control_visit_labvalue_dimension_of_peak_kalzium.svg", height = 8, width = 6.5)
print(libu_control_visit_labvalue_dimension_of_peak_kalzium)
dev.off()
```



####liver_para############

```{r}

lpara_fs_kalzium_full_filtered <- fs_kalzium_full %>% 
#  filter(Treatment == "Leber_Diclo") %>%
#  filter(!grepl("_From Start", attribute))%>%
  filter(Treatment == "Leber_Diclo")%>%
  mutate(`Edited_BfArM Nummer2` = as.factor(`Edited_BfArM Nummer2`)) %>% 
  group_by(`Edited_BfArM Nummer2`) %>%
  summarise(peak_labread = max(labreads, na.rm = TRUE)) %>%
  arrange(desc(peak_labread))  # optional: sortieren
```


```{r}
lpara_fs_kalzium_full_filtered_grouped <- lpara_fs_kalzium_full_filtered %>%
  mutate(
    Labvalue_Group = case_when(
      peak_labread <= 2.49 ~ "within normal reference",
      peak_labread >= 2.5 & peak_labread <= 7.49 ~ "1-2 times ULN",
      peak_labread >= 7.5 & peak_labread <= 14.9 ~ "3-5 times ULN",
      peak_labread >= 15 & peak_labread <= 24.9 ~ "6-9 times ULN",
      peak_labread >= 25 & peak_labread <= 124.9 ~ "10-49 times ULN",
      peak_labread >= 125 & peak_labread <= 249.9 ~ "50-99 times ULN",
      peak_labread >= 250 & peak_labread <= 10624.9 ~ "100-499 times ULN",
      peak_labread >= 1250 ~ ">500 times ULN",
      TRUE ~ NA_character_
    )
  )
```


```{r}
lpara_labvalue_group_count <- lpara_fs_kalzium_full_filtered_grouped %>%
  count(Labvalue_Group, sort = TRUE)
```


```{r}
lpara_labvalue_group_count$Labvalue_Group <-  factor(lpara_labvalue_group_count$Labvalue_Group, 
                                   levels = c( "within normal reference","1-2 times ULN", "3-5 times ULN", 
"6-9 times ULN", "10-49 times ULN", "50-99 times ULN","100-499 times ULN",  ">500 times ULN"))

 
lpara_control_visit_labvalue_dimension_of_peak_kalzium <- lpara_labvalue_group_count %>%
  mutate(n = as.numeric(n)) %>% 
  ggplot(aes(x = Labvalue_Group, y =n)) +
  geom_col() +
  theme_classic() +
  geom_text(data = lpara_labvalue_group_count, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 5)+       # Optional: kleinere Schriftgröße
  labs(title = "liver para_control visit_labvalue dimension of peak-kalzium", 
       x = "Factor of reference value", 
       y = "number of patients") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) #-> liver_para_control_visit_labvalue_dimension_of_peak_kalzium


dir.create("plots_labvalue dimension of rise_control visit", showWarnings = FALSE)
svg("plots_labvalue dimension of rise_control visit/lpara_control_visit_labvalue_dimension_of_peak_kalzium.svg", height = 8, width = 6.5)
print(lpara_control_visit_labvalue_dimension_of_peak_kalzium)
dev.off()


```

