---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
gpt_summary_data$Attribute <- factor(gpt_summary_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))

##for boxplt change last data##
ldalt_data$Attribute <- factor(ldalt_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
gpt_summary_data <- ldalt_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(gpt_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in red
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean ALT for Male",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####


```{r}

library(ggplot2)
library(dplyr)

max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldalt_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of ALT for both gender",
       x = "Attribute",
       y = "ALT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```
###################################################################
###AST mit veränderten Skalen und automatischer Speicherung in ###

### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
gpt_summary_data$Attribute <- factor(gpt_summary_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))

##for boxplt change last data##
ldalt_data$Attribute <- factor(ldalt_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
ast_summary_data <- ldast_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ast_summary_data$mean_labread + ast_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

p1 = ggplot(ast_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean ALT for Female",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size =20),
        axis.text.y = element_text(size =20),
        axis.title = element_text(size =24),
        plot.title = element_text(size =24)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
p1
ggsave(p1,file="output Grafiken von R/ALT.png",height = 5,width = 8)

```

```{r}

library(ggplot2)
library(dplyr)

max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldalt_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of ALT for both gender",
       x = "Attribute",
       y = "ALT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###AST###
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ast_summary_data$Attribute <- factor(ast_summary_data$Attribute,
                                     levels = c( "GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10","GOT Day11","GOT Day12","GOT Day16","GOT Day17","GOT Day20","GOT Day_Unknown"))
# 
# ##for boxplt change last data##
 ldast_data$Attribute <- factor(ldast_data$Attribute,levels = c( "GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10","GOT Day11","GOT Day12","GOT Day16","GOT Day17","GOT Day20","GOT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
ast_summary_data <- ldast_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ast_summary_data$mean_labread + ast_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 600, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 500) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ast_summary_data$Attribute <- factor(ast_summary_data$Attribute,
                                     levels = c( "GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10","GOT Day11","GOT Day12","GOT Day16","GOT Day17","GOT Day20","GOT Day_Unknown"))

ggplot(ast_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean AST for Female",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```




##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ast_summary_data$mean_labread + ast_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldast_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of AST for both gender",
       x = "Attribute",
       y = "AST U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###CK###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
got_summary_data$Attribute <- factor(got_summary_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))

##for boxplt change last data##
ldast_data$Attribute <- factor(ldgot_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ck_summary_data <- ldck_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ck_summary_data$mean_labread + ck_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ck_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean CK for Male",
       x = "Attribute",
       y = "CK U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ck_summary_data$mean_labread + ck_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldck_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of CK for both gender",
       x = "Attribute",
       y = "CK U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###quick###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
quick_summary_data$Attribute <- factor(quick_summary_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))

##for boxplt change last data##
ldast_data$Attribute <- factor(ldast_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
quick_summary_data <- ldquick_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(quick_summary_data$mean_labread + quick_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(quick_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean quick for Female",
       x = "Attribute",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(quick_summary_data$mean_labread + quick_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldquick_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of quick for both gender",
       x = "Attribute",
       y = "quick %") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###inr###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
quick_summary_data$Attribute <- factor(quick_summary_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))

##for boxplt change last data##
ldast_data$Attribute <- factor(ldast_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
inr_summary_data <- ldinr_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(inr_summary_data$mean_labread + inr_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(inr_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean INR for Male",
       x = "Attribute",
       y = "INR",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(inr_summary_data$mean_labread + inr_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldinr_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of INR for both gender",
       x = "Attribute",
       y = "INR") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###ptt###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
quick_summary_data$Attribute <- factor(quick_summary_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))

##for boxplt change last data##
ldast_data$Attribute <- factor(ldast_data$Attribute,levels = c( "GOT Day2_From Start","GOT Day1_From Start","GOT Day1","GOT Day2","GOT Day3","GOT Day4","GOT Day5","GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day11","GOT Day12","GOT Day14","GOT Day15","GOT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ptt_summary_data <- ldptt_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ptt_summary_data$mean_labread + ptt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ptt_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean PTT for Female",
       x = "Attribute",
       y = "PTT Sec.",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ptt_summary_data$mean_labread + ptt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldptt_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of PTT for both gender",
       x = "Attribute",
       y = "PTT Sec.") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Leukozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5",
"Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$attribute <- factor(ldleukozyten_data$attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
leukozyten_summary_data <- ldleukozyten_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(leukozyten_summary_data$mean_labread + leukozyten_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(leukozyten_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Leukocytes for Male",
       x = "Attribute",
       y = "Leukocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(leukozyten_summary_data$mean_labread + leukozyten_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 600) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldleukozyten_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Leukocytes for both gender",
       x = "Attribute",
       y = "Leukocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###GGT###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ggt_summary_data$Attribute <- factor(ggt_summary_data$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3", "GGT Day4", "GGT Day5", "GGT Day6", "GGT Day7", "GGT Day8", "GGT Day9", "GGT Day10", "GGT Day11", "GGT Day16", "GGT Day17", "GGT Day20", "GGT Day_Unknown"))

##for boxplt change last data##
ldggt_data$attribute <- factor(ldggt_data$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3", "GGT Day4", "GGT Day5", "GGT Day6", "GGT Day7", "GGT Day8", "GGT Day9", "GGT Day10", "GGT Day11", "GGT Day16", "GGT Day17", "GGT Day20", "GGT Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ggt_summary_data <- ldggt_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ggt_summary_data$mean_labread + ggt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 600, by = 100)
#additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500)

ggplot(ggt_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean GGT for Male",
       x = "Attribute",
       y = "GGT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ggt_summary_data$mean_labread + ggt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
#additional_breaks <- if (max_value > 500) seq(600, max_value, by = 600) else numeric(0)
all_breaks <- c(breaks_up_to_500)

## use the last joined data gender with labreads##
ldggt_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of GGT for both gender",
       x = "Attribute",
       y = "GGT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###LDH###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ldh_summary_data <- ldldh_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ldh_summary_data$mean_labread + ldh_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ldh_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean LDH for Male",
       x = "Attribute",
       y = "LDH U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ldh_summary_data$mean_labread + ldh_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldldh_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of LDH for both gender",
       x = "Attribute",
       y = "LDH U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###HB###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
hb_summary_data$attribute <- factor(hb_summary_data$attribute,levels = c("Hb Day1", "Hb Day2", "Hb Day3", "Hb Day4", "Hb Day5", "Hb Day9", "Hb Day15", "Hb Day_Unknown"))

##for boxplt change last data##
ldhb_data$attribute <- factor(ldhb_data$attribute,levels = c("Hb Day1", "Hb Day2", "Hb Day3", "Hb Day4", "Hb Day5", "Hb Day9", "Hb Day15", "Hb Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hb_summary_data <- ldhb_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hb_summary_data$mean_labread + hb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hb_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean HB for Female",
       x = "Attribute",
       y = "HB g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hb_summary_data$mean_labread + hb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldhb_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of HB for both gender",
       x = "Attribute",
       y = "HB g/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###totales Bilirubin###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
totbili_summary_data$attribute <- factor(totbili_summary_data$attribute,levels = c("TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", 
"TotalBilirubin Day10", "TotalBilirubin Day11", "TotalBilirubin Day_Unknown"))

##for boxplt change last data##
ldtotbili_data$attribute <- factor(ldtotbili_data$attribute,levels = c("TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", 
"TotalBilirubin Day10", "TotalBilirubin Day11", "TotalBilirubin Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
totbili_summary_data <- ldtotbili_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(totbili_summary_data$mean_labread + totbili_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(totbili_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean total Bilirubin for Female",
       x = "Attribute",
       y = "total Bilirubin mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(totbili_summary_data$mean_labread + totbili_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldtotbili_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of total Bilirubin for both gender",
       x = "Attribute",
       y = "total Bilirubin mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###AP###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ap_summary_data$attribute <- factor(ap_summary_data$attribute,levels = c("AP Day1", "AP Day2","AP Day3","AP Day4","AP Day5","AP Day6","AP Day7","AP Day9","AP Day10","AP Day11","AP Day_Unknown"))

##for boxplt change last data##
ldap_data$attribute <- factor(ldap_data$attribute,levels = c("AP Day1", "AP Day2","AP Day3","AP Day4","AP Day5","AP Day6","AP Day7","AP Day9","AP Day10","AP Day11","AP Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ap_summary_data <- ldap_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ap_summary_data$mean_labread + ap_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ap_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean AP for Female",
       x = "Attribute",
       y = "AP U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ap_summary_data$mean_labread + ap_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldap_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of AP for both gender",
       x = "Attribute",
       y = "AP U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Kreatinin###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
krea_summary_data <- ldkrea_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(krea_summary_data$mean_labread + krea_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(krea_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Creatinine for Male",
       x = "Attribute",
       y = "Creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(krea_summary_data$mean_labread + krea_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldkrea_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Creatinine for both gender",
       x = "Attribute",
       y = "Creatinine mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###CRP###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
crp_summary_data <- ldcrp_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(crp_summary_data$mean_labread + crp_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(crp_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean CRP for Female",
       x = "Attribute",
       y = "CRP mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(crp_summary_data$mean_labread + crp_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldcrp_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of CRP for both gender",
       x = "Attribute",
       y = "CRP mg/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Harnstoff###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hst_summary_data <- ldhst_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hst_summary_data$mean_labread + hst_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hst_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Urea for Male",
       x = "Attribute",
       y = "Urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hst_summary_data$mean_labread + hst_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldhst_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Urea for both gender",
       x = "Attribute",
       y = "Urea mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Erythrozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ery_summary_data <- ldery_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ery_summary_data$mean_labread + ery_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ery_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Erythrocytes for Male",
       x = "Attribute",
       y = "Erythrocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ery_summary_data$mean_labread + ery_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldery_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Erythrocytes for both gender",
       x = "Attribute",
       y = "Erythrocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Thrombozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
thromb_summary_data$attribute <- factor(thromb_summary_data$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day_Unknown"))

##for boxplt change last data##
ldthromb_data$attribute <- factor(ldthromb_data$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
thromb_summary_data <- ldthromb_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(thromb_summary_data$mean_labread + thromb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(thromb_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Thrombocytes for Female",
       x = "Attribute",
       y = "Thrombocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(thromb_summary_data$mean_labread + thromb_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldthromb_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Thrombocytes for both gender",
       x = "Attribute",
       y = "Thrombocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Hämatokrit###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hkt_summary_data <- ldhkt_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hkt_summary_data$mean_labread + hkt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hkt_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean hematocrit for Female",
       x = "Attribute",
       y = "hematocrit %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hkt_summary_data$mean_labread + hkt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldhkt_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of hematocrit for both gender",
       x = "Attribute",
       y = "hematocrit %") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Natrium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
nat_summary_data <- ldnat_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(nat_summary_data$mean_labread + nat_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(nat_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Sodium for Male",
       x = "Attribute",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(nat_summary_data$mean_labread + nat_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldnat_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Sodium for both gender",
       x = "Attribute",
       y = "Sodium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Kalium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
kal_summary_data <- ldkal_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(kal_summary_data$mean_labread + kal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(kal_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Potassium for Female",
       x = "Attribute",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(kal_summary_data$mean_labread + kal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldkal_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Potassium for both gender",
       x = "Attribute",
       y = "Potassium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Kalzium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
cal_summary_data <- ldcal_data  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(cal_summary_data$mean_labread + cal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(cal_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Calcium for Male",
       x = "Attribute",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(cal_summary_data$mean_labread + cal_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldcal_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Calcium for both gender",
       x = "Attribute",
       y = "Calcium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Glucose###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data$Attribute <- factor(leukozyten_summary_data$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data$Attribute <- factor(ldleukozyten_data$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
glu_summary_data <- ldglu_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(glu_summary_data$mean_labread + glu_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(glu_summary_data, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean Glucose for Female",
       x = "Attribute",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(glu_summary_data$mean_labread + glu_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldglu_data %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of Glucose for both gender",
       x = "Attribute",
       y = "Glucose mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```






























































































































































