---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```



##### 
#####
#####
#####
#####
# all graphs new for Erythrocytes #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_thromb <- left_join(ldthromb_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_thromb %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_thromb,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "Thrombocytes cells/ul") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "Thrombocytes cells/ul",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "Thrombocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "Thrombocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "Thrombocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "Thrombocytes cells/ul") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldthromb_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "Thrombocytes cells/ul") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Natrium/Sodium #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_nat <- left_join(ldnat_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_nat %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_nat,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "Sodium mmol/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(100, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "Sodium mmol/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "Sodium mmol/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldnat_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "Sodium mmol/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Kalium/Potassium #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_kal <- left_join(ldkal_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_kal %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_kal,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "Potassium mmol/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "Potassium mmol/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "Potassium mmol/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldkal_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "Potassium mmol/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Kalzium/Calcium #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_cal <- left_join(ldcal_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_cal %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_cal,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "Calcium mmol/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "Calcium mmol/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "Calcium mmol/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldcal_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "Calcium mmol/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Glucose #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_glu <- left_join(ldglu_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_glu %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_glu,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "Glucose mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "Glucose mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "Glucose mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldglu_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "Glucose mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```
