---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
gpt_summary_data$Attribute <- factor(gpt_summary_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))

##for boxplt
gptalst_data$Attribute <- factor(gptalst_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
gpt_summary_data <- libualt_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(gpt_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 0.5, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean ALT for Female",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####


```{r}

library(ggplot2)
library(dplyr)

max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldalt_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of ALT for both gender",
       x = "Attribute",
       y = "ALT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###dose data##
```{r}

setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")

dose_data <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 3)  
  
lvibu_dosedata <- dose_data %>% 
  filter(Attribut == "Leber_Ibu") %>% 
  rename( "Edited_BfArM Nummer2" ="BfArM Nummer_2" )

lvibu_dosedata
```


```{r}
lvibu_dosedata_gptalst <- left_join(libualt_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptalst %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptalst,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ALT for both gender",
       x = "dailydose in mg",
       y = "ALT U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```


### plot##
```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ALT U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$Attribute <- 
  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_100mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$Attribute <- 
 factor(dd_150mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- 
   factor(dd_150mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```



##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " ALT in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```


###################cumulative dose = CD #######

```{r}
CD_dose <- lvibu_dosedata_gptalst %>% 
  filter(Kathegorie == "Kumulative Dosis" & Treatment == "Ibuprofen")

num_dosetaken <- lvibu_dosedata_gptalst %>% 
  filter(Kathegorie == "Dauer der Einnahme (Tage)" & Treatment == "Ibuprofen") %>% 
  rename("daysofintake" = "Dose_mg") %>% dplyr::select(1,10)

CD_dose_weekdata <- left_join(CD_dose, num_dosetaken, by = ("Edited_BfArM Nummer2")) %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  drop_na(daysofintake)


```


```{r}
cumulativ_4week <- CD_dose_weekdata %>% 
  filter(daysofintake <= 28) %>% 
  mutate(daysofintake = as.factor(daysofintake)) %>% 
  drop_na(Dose_mg)  
  
  
  cumulativ_4week <- cumulativ_4week[cumulativ_4week$`Edited_BfArM Nummer2` != "93008468", ]
  
 cumulativ_4week %>% 
   ggplot( aes(x = daysofintake, y = Dose_mg)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(se = TRUE, color = "red", linetype = "dashed")+
     labs(title = "Ibuprofen cummulative dose",
       x = "Number of day",
       y = "Cummulative dose (mg)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
   
```

### Cumulative Dose lower than 10000(mg)########
```{r}

library(dplyr)
library(readxl)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liveribu <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 5, skip = 1) %>%
  filter(Cumulative_Dose > 0.0 & Cumulative_Dose <= 10000 & Treatment == "Leber_Ibu")

# Summarize the counts of each Cumulative_Dose
dose_counts <- CD_liveribu %>%
  group_by(Cumulative_Dose) %>%
  summarise(count = n())

# Add the count column back into the original data frame
CD_liveribu <- CD_liveribu %>%
  left_join(dose_counts, by = "Cumulative_Dose")

# View the result
print(CD_liveribu)

  
```

```{r}
CD_liveribu %>% 
  mutate(Cumulative_Dose = as.factor(Cumulative_Dose)) %>% 
  ggplot(aes(x = Cumulative_Dose, y = count))+
  geom_point()+
  labs(title = "Cumultive Dose Ibuprofen",
       x = "cumulative Dose(mg)",
       y = "Number of Patient") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Cumulative Dose higer than 10000(mg)########
```{r}

library(dplyr)
library(readxl)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liveribu10k <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 5, skip = 1) %>%
  filter(Cumulative_Dose >= 10000 & Treatment == "Leber_Ibu")

dose_counts10K <-CD_liveribu10k %>%
  group_by(Cumulative_Dose) %>%
  summarise(count = n())

# View the result
#print(CD_liverdiclo1k)

  
```

```{r}
 dose_counts10K %>% 
  mutate(Cumulative_Dose = Cumulative_Dose/10000) %>% 
   mutate(Cumulative_Dose = as.factor(Cumulative_Dose)) %>% 
  ggplot(aes(x = Cumulative_Dose, y = count))+
  geom_point()+
  labs(title = "Cumultive Dose Diclofenac",
       x = "cumulative Dose(g)",
       y = "Number of Patient") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  

```




```{r}
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
read_excel("Medikamente Arun Testversion.xlsx", sheet = 5, skip = 1) %>% 
  filter(Cumulative_Dose > 0.0 & Treatment == "Leber_Ibu")



 

```



```{r}
library(dplyr)
library(readxl)
library(ggplot2)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liverIbu <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 5, skip = 1) %>%
  filter(Cumulative_Dose > 0.0 & Treatment == "Leber_Ibu")

# Create dose groups
CD_liveribu <- CD_liveribu %>%
  mutate(Dose_Group = cut(Cumulative_Dose,
                          breaks = c(0, 1000, 5000,20000, Inf),
                          labels = c("50mg to 1g", "1g to 5g", "5g to 20g", "20g < Higher"),
                          right = FALSE)) # right = FALSE to make intervals inclusive of lower bound and exclusive of upper bound

# View the result with dose groups
print(CD_liveribu)

# Plot frequency of each dose group
ggplot(CD_liveribu, aes(x = Dose_Group)) +
  geom_bar() +
  labs(title = "Frequency of Cumulative Dose Groups",
       x = "Dose Group",
       y = "Frequency") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  )

```


```{r}
library(dplyr)
library(readxl)
library(ggplot2)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liveribu <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 5, skip = 1) %>%
  filter(Cumulative_Dose > 0.0  & Treatment == "Leber_Ibu")

# Create dose groups
CD_liveribu <- CD_liveribu %>%
  mutate(Dose_Group = cut(Cumulative_Dose,
                          breaks = c(0, 1000, 5000, 20000, Inf),
                          labels = c("50mg to 1g", "1g to 5g", "5g to 20g", " Higher to 20"),
                          right = FALSE)) # right = FALSE to make intervals inclusive of lower bound and exclusive of upper bound

# View the result with dose groups
print(CD_liveribu)

# Plot frequency of each dose group
ggplot(CD_liveribu, aes(x = Dose_Group)) +
  geom_bar() +
  labs(title = "Frequency of Cumulative Dose Groups",
       x = "Dose Group",
       y = "Frequency") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(table(CD_liverdiclo$Dose_Group))))

```


```{r}
CD_liveribu_labreads <- left_join(CD_liveribu,libualt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  filter(Attribute == "GPT Day1") %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreads
```

```{r}
 
 
ggplot(CD_liveribu_labreads, aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen ALT",
       x = "Dose Group",
       y = "ALT U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liveribu_labreads$labreads)))
```



```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libualt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```


```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen ALT",
       x = "Dose Group",
       y = "ALT U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```


##### 
#####
#####
#####
#####
# all graphs new for AST #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptast <- left_join(libuast_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptast %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptast,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of AST for both gender",
       x = "dailydose in mg",
       y = "AST U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "AST U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- factor(dd_100mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_100mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " AST in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuast_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen ALT",
       x = "Dose Group",
       y = "AST U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for quick #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptquick <- left_join(libuquick_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptquick %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptquick,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of AST for both gender",
       x = "dailydose in mg",
       y = "quick %") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "quick %",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- factor(dd_100mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " quick %") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuquick_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen quick",
       x = "Dose Group",
       y = "quick %") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for inr #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptinr <- left_join(libuinr_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptinr %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptinr,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of AST for both gender",
       x = "dailydose in mg",
       y = "inr") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "inr",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- factor(dd_100mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " inr") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuinr_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen quick",
       x = "Dose Group",
       y = "inr") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for ggt #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptggt <- left_join(libuggt_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptggt %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptggt,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of AST for both gender",
       x = "dailydose in mg",
       y = "ggt u/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ggt u/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "ggt u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "GGT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "GGT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ggt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " ggt u/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuggt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen quick",
       x = "Dose Group",
       y = "ggt u/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for ldh #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptldh <- left_join(libuldh_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptldh %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptldh,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of AST for both gender",
       x = "dailydose in mg",
       y = "ldh u/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ldh u/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "ldh u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " ldh u/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuldh_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen quick",
       x = "Dose Group",
       y = "ldh u/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for total bilirubin #
#####
#####
#####
#####
```{r}
lvibu_dosedata_totbili <- left_join(libutotbili_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_totbili %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_totbili,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of AST for both gender",
       x = "dailydose in mg",
       y = "totbili mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "totbili mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day4","TotalBilirubin Day8","TotalBilirubin Day10","TotalBilirubin_day unknown" ))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day4","TotalBilirubin Day7","TotalBilirubin Day8","TotalBilirubin Day10","TotalBilirubin_day unknown"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day4","TotalBilirubin Day7","TotalBilirubin Day8","TotalBilirubin Day10","TotalBilirubin_day unknown"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " totbili mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 50, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 50, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libutotbili_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen quick",
       x = "Dose Group",
       y = "totbili mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for ap #
#####
#####
#####
#####
```{r}
lvibu_dosedata_ap <- left_join(libuap_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_ap %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_ap,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "ap u/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ap u/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "ap u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " ap u/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuap_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen quick",
       x = "Dose Group",
       y = "ap u/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```


##### 
#####
#####
#####
#####
# all graphs new for Creatinine #
#####
#####
#####
#####
```{r}
lvibu_dosedata_krea <- left_join(libukrea_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_krea %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_krea,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "creatinine mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "creatinine mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "ap u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " creatinine mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 5, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 5, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libukrea_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen quick",
       x = "Dose Group",
       y = "creatinine mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, 3))
```

##### 
#####
#####
#####
#####
# all graphs new for crp #
#####
#####
#####
#####
```{r}
lvibu_dosedata_crp <- left_join(libucrp_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_crp %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_crp,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of crp for both gender",
       x = "dailydose in mg",
       y = "crp mg/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(200,390,400,600,800,8000,1200,1600,1800,2400,3000,3200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "crp mg/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 500mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,300,390,400,500)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for <500mg drug",
       x = "Attribute",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 1000mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(500,600,700,800,900,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- factor(dd_100mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 501-1000mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 1001-2000mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1100,1200,1300,1400,1500,1600,1700,1800,1900,2000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 1001-2000mg drug",
       x = "Attribute",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for >2000mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2100,2200,2300,2400,2500,2600,2700,2800,2900,3000,3100,3200,3300,3400,3500,3600,3700,3800,3900,4000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for >2000mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Ibuprofen",
       x = "daily dose in mg",
       y = " crp mg/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 50, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 50, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libucrp_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Ibuprofen crp",
       x = "Dose Group",
       y = "crp") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```