---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
gpt_summary_data$Attribute <- factor(gpt_summary_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))

##for boxplt
gptalst_data$Attribute <- factor(gptalst_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
gpt_summary_data <- ldalt_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(gpt_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 0.5, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean ALT for Female",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####


```{r}

library(ggplot2)
library(dplyr)

max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldalt_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "Boxplot of ALT for both gender",
       x = "Attribute",
       y = "ALT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###dose data##
```{r}

setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")

dose_data <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 3)  
  
lvdiclo_dosedata <- dose_data %>% 
  filter(Attribut == "Leber_Diclo") %>% 
  rename( "Edited_BfArM Nummer2" ="BfArM Nummer_2" )

lvdiclo_dosedata
```


```{r}
lvdiclo_dosedata_gptalst <- left_join(ldalt_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_gptalst %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_gptalst,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ALT for both gender",
       x = "dailydose in mg",
       y = "ALT U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```


### plot##
```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ALT U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$Attribute <- 
  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
                                          "GPT Day4","GPT Day5", "GPT Day6",
                                          "GPT Day7","GPT Day8", "GPT Day9", 
                                          "GPT Day10","GPT Day11","GPT Day12",
                                          "GPT Day17","GPT Day20","GPT Day26",
"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 150mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- 
   factor(dd_150mg$Attribute,levels = c( "GPT Day1","GPT Day3", 
                                           "GPT Day4","GPT Day5", "GPT Day6",
                                           "GPT Day8", "GPT Day9", 
                                           "GPT Day10","GPT Day12",
                                           "GPT Day16","GPT Day26","GPT Day_Unknown"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(187.5,200,900)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
#  filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
  dd_200mg$Attribute <- 
    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "Attribute",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = " ALT in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```


###################cumulative dose = CD #######

```{r}
CD_dose <- lvdiclo_dosedata_gptalst %>% 
  filter(Kathegorie == "Kumulative Dosis" & Treatment == "Diclofenac")

num_dosetaken <- lvdiclo_dosedata_gptalst %>% 
  filter(Kathegorie == "Dauer der Einnahme (Tage)" & Treatment == "Diclofenac") %>% 
  rename("daysofintake" = "Dose_mg") %>% dplyr::select(1,10)

CD_dose_weekdata <- left_join(CD_dose, num_dosetaken, by = ("Edited_BfArM Nummer2")) %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  drop_na(daysofintake)


```


```{r}
cumulativ_4week <- CD_dose_weekdata %>% 
  filter(daysofintake <= 28) %>% 
  mutate(daysofintake = as.factor(daysofintake)) %>% 
  drop_na(Dose_mg)  
  
  
  cumulativ_4week <- cumulativ_4week[cumulativ_4week$`Edited_BfArM Nummer2` != "93008468", ]
  
 cumulativ_4week %>% 
   ggplot( aes(x = daysofintake, y = Dose_mg)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(se = TRUE, color = "red", linetype = "dashed")+
     labs(title = "Diclofene cummulative dose",
       x = "Number of day",
       y = "Cummulative dose (mg)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
   
```

### Cumulative Dose for 50-1000(mg)########
```{r}

library(dplyr)
library(readxl)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liverdiclo <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 4, skip = 1) %>%
  filter(Cumulative_Dose > 0.0 & Cumulative_Dose <= 1000 & Treatment == "Leber_Diclo")

# Summarize the counts of each Cumulative_Dose
dose_counts <- CD_liverdiclo %>%
  group_by(Cumulative_Dose) %>%
  summarise(count = n())

# Add the count column back into the original data frame
CD_liverdiclo <- CD_liverdiclo %>%
  left_join(dose_counts, by = "Cumulative_Dose")

# View the result
print(CD_liverdiclo)

  
```

```{r}
CD_liverdiclo %>% 
  mutate(Cumulative_Dose = as.factor(Cumulative_Dose)) %>% 
  ggplot(aes(x = Cumulative_Dose, y = count))+
  geom_point()+
  labs(title = "Cumultive Dose Diclofenac",
       x = "cumulative Dose(mg)",
       y = "Number of Patient") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Cumulative Dose higer than 1000(mg)########
```{r}

library(dplyr)
library(readxl)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liverdiclo1k <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 4, skip = 1) %>%
  filter(Cumulative_Dose >= 1000 & Treatment == "Leber_Diclo")

dose_counts1K <-CD_liverdiclo1k %>%
  group_by(Cumulative_Dose) %>%
  summarise(count = n())

# View the result
#print(CD_liverdiclo1k)

  
```

```{r}
 dose_counts1K %>% 
  mutate(Cumulative_Dose = Cumulative_Dose/1000) %>% 
   mutate(Cumulative_Dose = as.factor(Cumulative_Dose)) %>% 
  ggplot(aes(x = Cumulative_Dose, y = count))+
  geom_point()+
  labs(title = "Cumultive Dose Diclofenac",
       x = "cumulative Dose(g)",
       y = "Number of Patient") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  

```




```{r}
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
read_excel("Medikamente Arun Testversion.xlsx", sheet = 4, skip = 1) %>% 
  filter(Cumulative_Dose > 0.0 & Treatment == "Leber_Diclo")



 

```



```{r}
library(dplyr)
library(readxl)
library(ggplot2)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liverdiclo <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 4, skip = 1) %>%
  filter(Cumulative_Dose > 0.0 & Treatment == "Leber_Diclo")

# Create dose groups
CD_liverdiclo <- CD_liverdiclo %>%
  mutate(Dose_Group = cut(Cumulative_Dose,
                          breaks = c(0, 1000, 5000,20000, Inf),
                          labels = c("50mg to 1g", "1g to 5g", "5g to 20g", "20g < Higher"),
                          right = FALSE)) # right = FALSE to make intervals inclusive of lower bound and exclusive of upper bound

# View the result with dose groups
print(CD_liverdiclo)

# Plot frequency of each dose group
ggplot(CD_liverdiclo, aes(x = Dose_Group)) +
  geom_bar() +
  labs(title = "Frequency of Cumulative Dose Groups",
       x = "Dose Group",
       y = "Frequency") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  )

```


```{r}
library(dplyr)
library(readxl)
library(ggplot2)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
CD_liverdiclo <- read_excel("Medikamente Arun Testversion.xlsx", sheet = 4, skip = 1) %>%
  filter(Cumulative_Dose > 0.0  & Treatment == "Leber_Diclo")

# Create dose groups
CD_liverdiclo <- CD_liverdiclo %>%
  mutate(Dose_Group = cut(Cumulative_Dose,
                          breaks = c(0, 1000, 5000, 20000, Inf),
                          labels = c("50mg to 1g", "1g to 5g", "5g to 20g", " Higher to 20"),
                          right = FALSE)) # right = FALSE to make intervals inclusive of lower bound and exclusive of upper bound

# View the result with dose groups
print(CD_liverdiclo)

# Plot frequency of each dose group
ggplot(CD_liverdiclo, aes(x = Dose_Group)) +
  geom_bar() +
  labs(title = "Frequency of Cumulative Dose Groups",
       x = "Dose Group",
       y = "Frequency") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(table(CD_liverdiclo$Dose_Group))))

```


```{r}
CD_liverdiclo_labreads <- left_join(CD_liverdiclo,gptalst_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  filter(Attribute == "GPT Day1") %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreads
```

```{r}
 
 
ggplot(CD_liverdiclo_labreads, aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac ALT",
       x = "Dose Group",
       y = "ALT U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreads$labreads)))
```



```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldalt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac ALT",
       x = "Dose Group",
       y = "ALT U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```


##### 
#####
#####
#####
#####
# all graphs new for AST #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_ast <- left_join(ldast_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_ast %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_ast,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

# dose_result %>% 
#   filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
#   mutate(totaldose_mg = as.factor(totaldose_mg)) %>%
#   ggplot(aes(x = totaldose_mg, y = labreads))+
#   geom_boxplot()+
#   labs(title = "Boxplot of ALT for both gender",
#        x = "dailydose in mg",
#        y = "AST U/L") +
#   theme_classic() +
#     theme(
#      plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
#      axis.text.x = element_text(face="bold", angle = 45)
#   )+
#   scale_y_continuous(breaks = all_breaks,
#                      limits = c(0, max_value))
#   
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "AST U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(100)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 150mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
#  filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
# dd_150mg$Attribute <- 
#   factor(dd_150mg$Attribute,levels = c( "GPT Day1","GPT Day3", 
#                                           "GPT Day4","GPT Day5", "GPT Day6",
#                                           "GPT Day8", "GPT Day9", 
#                                           "GPT Day10","GPT Day12",
#                                           "GPT Day16","GPT Day26","GPT Day_Unknown"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
#  filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "Attribute",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = " AST in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

###################cumulative dose = CD #######

```{r}
CD_dose <- lvdiclo_dosedata_ast %>% 
  filter(Kathegorie == "Kumulative Dosis" & Treatment == "Diclofenac")

num_dosetaken <- lvdiclo_dosedata_ast %>% 
  filter(Kathegorie == "Dauer der Einnahme (Tage)" & Treatment == "Diclofenac") %>% 
  rename("daysofintake" = "Dose_mg") %>% dplyr::select(1,10)

CD_dose_weekdata <- left_join(CD_dose, num_dosetaken, by = ("Edited_BfArM Nummer2")) %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  drop_na(daysofintake)


```


```{r}
cumulativ_4week <- CD_dose_weekdata %>% 
  filter(daysofintake <= 28) %>% 
  mutate(daysofintake = as.factor(daysofintake)) %>% 
  drop_na(Dose_mg)  
  
  
  cumulativ_4week <- cumulativ_4week[cumulativ_4week$`Edited_BfArM Nummer2` != "93008468", ]
  
 cumulativ_4week %>% 
   ggplot( aes(x = daysofintake, y = Dose_mg)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(se = TRUE, color = "red", linetype = "dashed")+
     labs(title = "Diclofene cummulative dose",
       x = "Number of day",
       y = "Cummulative dose (mg)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
   
```
```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldast_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac ALT",
       x = "Dose Group",
       y = "ALT U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for CK #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_ck <- left_join(ldck_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_ck %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_ck,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>%
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of AST for both gender",
       x = "dailydose in mg",
       y = "AST U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "CK U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "CK U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "CK U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "CK U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "CK U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = " AST in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```
```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldck_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac ALT",
       x = "Dose Group",
       y = "AST U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```
##### 
#####
#####
#####
#####
# all graphs new for quick #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_quick <- left_join(ldquick_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_quick %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_quick,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of quick for both gender",
       x = "dailydose in mg",
       y = "quick U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "quick U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "quick U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "quick U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "quick U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "quick U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = " quick in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldquick_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac quick",
       x = "Dose Group",
       y = "quick U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for inr #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_inr <- left_join(ldinr_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_inr %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_inr,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of inr for both gender",
       x = "dailydose in mg",
       y = "inr U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "inr U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "inr U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "inr U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "inr U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "inr U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = " inr in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 1, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 1, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldinr_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac inr",
       x = "Dose Group",
       y = "inr U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```
##### 
#####
#####
#####
#####
# all graphs new for ptt #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_ptt <- left_join(ldptt_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_ptt %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_ptt,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of quick for both gender",
       x = "dailydose in mg",
       y = "ptt U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ptt U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "ptt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "ptt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "ptt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "quick U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "pttuick in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldptt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac ptt",
       x = "Dose Group",
       y = "ptt U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for leucocytes #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_leukozyten <- left_join(ldleukozyten_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_leukozyten %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_leukozyten,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of quick for both gender",
       x = "dailydose in mg",
       y = "leucocytes U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "leucocytes cells/ul",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "leucocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "leucocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "leucocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,187.5)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "leucocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "leucocytes cells/ul") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldleukozyten_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac leucocytes",
       x = "Dose Group",
       y = "leucocytes cells/ul") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for ggt #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_ggt <- left_join(ldggt_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_ggt %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_ggt,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of quick for both gender",
       x = "dailydose in mg",
       y = "ptt U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ptt U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "ptt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "ptt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "ptt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "quick U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "pttuick in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldptt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac ptt",
       x = "Dose Group",
       y = "ptt U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for ldh #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_ldh <- left_join(ldldh_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_ldh %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_ldh,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ldh for both gender",
       x = "dailydose in mg",
       y = "ldh U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ldh U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,187.5)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "quick U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "ldh in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldldh_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac ldh",
       x = "Dose Group",
       y = "ldh U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```
##### 
#####
#####
#####
#####
# all graphs new for hb #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_hb <- left_join(ldhb_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_hb %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_hb,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of hb for both gender",
       x = "dailydose in mg",
       y = "hb g/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "hb g/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "hb g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "hb g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "hb g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "hb g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "hb g/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldhb_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac hb",
       x = "Dose Group",
       y = "hb g/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```
##### 
#####
#####
#####
#####
# all graphs new for total bilirubin #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_totbili <- left_join(ldtotbili_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_totbili %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_totbili,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of totbili for both gender",
       x = "dailydose in mg",
       y = "totbili mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "totbili mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "hb g/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldtotbili_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "totbili mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```


##### 
#####
#####
#####
#####
# all graphs new for ap #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_ap <- left_join(ldap_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_ap %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_ap,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "ap u/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "ap u/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "ap u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "ap u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "ap u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "ap u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "ap u/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldap_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "ap u/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for creatinine #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_krea <- left_join(ldkrea_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_krea %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_krea,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "creatinine mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "creatinine mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "creatinine mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldkrea_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "creatinine mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for crp #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_crp <- left_join(ldcrp_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_crp %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_crp,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "crp mg/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "crp mg/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "crp mg/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldcrp_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "crp mg/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for urea #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_hst <- left_join(ldhst_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_hst %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_hst,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "urea mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "urea mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "urea mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldhst_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "urea mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Erythrocytes #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_ery <- left_join(ldery_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_ery %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_ery,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "Boxplot of ap for both gender",
       x = "dailydose in mg",
       y = "Erythrocytes cells/ul") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  type = "np",
  ylab = "Erythrocytes cells/ul",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(25,50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 50mg drug",
       x = "attribute",
       y = "urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75,100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 100mg drug",
       x = "attribute",
       y = "urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 150mg drug",
       x = "attribute",
       y = "urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200,1000)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "Line Plot for 200mg drug",
       x = "attribute",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth()

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "linerar regression for Diclofenac",
       x = "daily dose in mg",
       y = "urea mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldhst_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "Diclofenac totbili",
       x = "Dose Group",
       y = "urea mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```
