---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order
### for lineplot as prof as to make####
### need to write all days name manually

   gpt_summary_data_cgt$Attribute <- 
   factor(gpt_summary_data_cgt$Attribute,levels = c(  "GPT_d1", "GPT_d2", "GPT_d3","GPT_d4","GPT_d5", "GPT_d6","GPT_d7","GPT_d8","GPT_d9","GPT_d10", "GPT_d11","GPT_d12","GPT_d13","GPT_d14","GPT_d14 (guess)","GPT_d15","GPT_d16","GPT_d17","GPT_d18","GPT_d19","GPT_d20","GPT_d21","GPT_d21 (guess)","GPT_d22","GPT_d23","GPT_d24","GPT_d25","GPT_d26","GPT_d27","GPT_d28","GPT_d29","GPT_d30","GPT_d31","GPT_d32","GPT_d33","GPT_d34","GPT_d35","GPT_d36","GPT_d37","GPT_d38","GPT_d39","GPT_d40","GPT_d41","GPT_d42","GPT_d43","GPT_d44","GPT_d45","GPT_d46","GPT_d47","GPT_d48","GPT_d49","GPT_d50","GPT_d51","GPT_d52","GPT_d53","GPT_d54","GPT_d55","GPT_d56","GPT_d57","GPT_d58","GPT_d59","GPT_d60","GPT_d61","GPT_d62","GPT_d63","GPT_d64","GPT_d65","GPT_d66","GPT_d67","GPT_d68","GPT_d69","GPT_d70","GPT_d71","GPT_d72","GPT_d73","GPT_d74","GPT_d75","GPT_d76","GPT_d77","GPT_d78","GPT_d79","GPT_d80","GPT_d81","GPT_d82","GPT_d83","GPT_d84","GPT_d85","GPT_d86","GPT_d87","GPT_d88","GPT_d89","GPT_d90","GPT_d91","GPT_d92","GPT_d93","GPT_d94","GPT_d95","GPT_d96","GPT_d97","GPT_d98","GPT_d99","GPT_d100","GPT_d105","GPT_d131","GPT_d360","GPT_d580 (guess)"))

### for lineplot
lparaalt_data_cgt$Attribute <- factor(lparaalt_data_cgt$Attribute,levels = c(  "GPT_d1", "GPT_d2", "GPT_d3","GPT_d4","GPT_d5", "GPT_d6","GPT_d7","GPT_d8","GPT_d9","GPT_d10", "GPT_d11","GPT_d12","GPT_d13","GPT_d14","GPT_d14 (guess)","GPT_d15","GPT_d16","GPT_d17","GPT_d18","GPT_d19","GPT_d20","GPT_d21","GPT_d21 (guess)","GPT_d22","GPT_d23","GPT_d24","GPT_d25","GPT_d26","GPT_d27","GPT_d28","GPT_d29","GPT_d30","GPT_d31","GPT_d32","GPT_d33","GPT_d34","GPT_d35","GPT_d36","GPT_d37","GPT_d38","GPT_d39","GPT_d40","GPT_d41","GPT_d42","GPT_d43","GPT_d44","GPT_d45","GPT_d46","GPT_d47","GPT_d48","GPT_d49","GPT_d50","GPT_d51","GPT_d52","GPT_d53","GPT_d54","GPT_d55","GPT_d56","GPT_d57","GPT_d58","GPT_d59","GPT_d60","GPT_d61","GPT_d62","GPT_d63","GPT_d64","GPT_d65","GPT_d66","GPT_d67","GPT_d68","GPT_d69","GPT_d70","GPT_d71","GPT_d72","GPT_d73","GPT_d74","GPT_d75","GPT_d76","GPT_d77","GPT_d78","GPT_d79","GPT_d80","GPT_d81","GPT_d82","GPT_d83","GPT_d84","GPT_d85","GPT_d86","GPT_d87","GPT_d88","GPT_d89","GPT_d90","GPT_d91","GPT_d92","GPT_d93","GPT_d94","GPT_d95","GPT_d96","GPT_d97","GPT_d98","GPT_d99","GPT_d100","GPT_d105","GPT_d131","GPT_d360","GPT_d580 (guess)"))

# ##for boxplt change last data##
```


```{r}
 ##### Make the line plot of labreads for male and female####
 ##### filter the male and female for individual plot #####
###############################################################################
gpt_summary_data_cgt <- lparaalt_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
    )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(gpt_summary_data_cgt$mean_labread + gpt_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 200)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)


# Create a vector with the x-axis labels in the desired order

### for lineplot as prof as to make####
### need to write all days name manually

ggplot(gpt_summary_data_cgt, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread),       ##width = 0.2, color = "blue") + 
  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), 
                width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + 
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  # SEM error bars in red
  labs(title = "liver_para_cgt mean ALT in time course for female with patient count",    ###NEW###
       x = "Day of measurement",                     ###NEW###
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 1500))

```

##### code for boxplot ####


```{r}

library(ggplot2)
library(dplyr)

max_value <- max(gpt_summary_data_cgt$mean_labread + gpt_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 200)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaalt_data_cgt %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        ####NEW#####
  labs(title = "liver_para_cgt boxplot for ALT by day of measurement",      ###NEW###
       x = "day of measurement",                            ###NEW###
       y = "ALT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
   scale_y_continuous(breaks = all_breaks,
                      limits = c(0, max_value))


```
######################################################################
###AST###
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ast_summary_data_cgt$Attribute <- factor(ast_summary_data_cgt$Attribute,
                                     levels = c("GOT_d1", "GOT_d2", "GOT_d3","GOT_d4","GOT_d5", "GOT_d6","GOT_d7","GOT_d8","GOT_d9","GOT_d10", "GOT_d11","GOT_d12","GOT_d13","GOT_d14","GOT_d14 (guess)","GOT_d15","GOT_d16","GOT_d17","GOT_d18","GOT_d19","GOT_d20","GOT_d21","GOT_d21 (guess)","GOT_d22","GOT_d23","GOT_d24","GOT_d25","GOT_d26","GOT_d27","GOT_d28","GOT_d29","GOT_d30","GOT_d31","GOT_d32","GOT_d33","GOT_d34","GOT_d35","GOT_d36","GOT_d37","GOT_d38","GOT_d39","GOT_d40","GOT_d41","GOT_d42","GOT_d43","GOT_d44","GOT_d45","GOT_d46","GOT_d47","GOT_d48","GOT_d49","GOT_d50","GOT_d51","GOT_d52","GOT_d53","GOT_d54","GOT_d55","GOT_d56","GOT_d57","GOT_d58","GOT_d59","GOT_d60","GOT_d61","GOT_d62","GOT_d63","GOT_d64","GOT_d65","GOT_d66","GOT_d67","GOT_d68","GOT_d69","GOT_d70","GOT_d71","GOT_d72","GOT_d73","GOT_d74","GOT_d75","GOT_d76","GOT_d77","GOT_d78","GOT_d79","GOT_d80","GOT_d81","GOT_d82","GOT_d83","GOT_d84","GOT_d85","GOT_d86","GOT_d87","GOT_d88","GOT_d89","GOT_d90","GOT_d91","GOT_d92","GOT_d93","GOT_d94","GOT_d95","GOT_d96","GOT_d97","GOT_d98","GOT_d99","GOT_d100","GOT_d105","GOT_d131","GOT_d360","GOT_d580 (guess)"))
# 
# ##for boxplt change last data##
 lparaast_data_cgt$Attribute <- factor(lparaast_data_cgt$Attribute,levels = c( "GOT_d1", "GOT_d2", "GOT_d3","GOT_d4","GOT_d5", "GOT_d6","GOT_d7","GOT_d8","GOT_d9","GOT_d10", "GOT_d11","GOT_d12","GOT_d13","GOT_d14","GOT_d14 (guess)","GOT_d15","GOT_d16","GOT_d17","GOT_d18","GOT_d19","GOT_d20","GOT_d21","GOT_d21 (guess)","GOT_d22","GOT_d23","GOT_d24","GOT_d25","GOT_d26","GOT_d27","GOT_d28","GOT_d29","GOT_d30","GOT_d31","GOT_d32","GOT_d33","GOT_d34","GOT_d35","GOT_d36","GOT_d37","GOT_d38","GOT_d39","GOT_d40","GOT_d41","GOT_d42","GOT_d43","GOT_d44","GOT_d45","GOT_d46","GOT_d47","GOT_d48","GOT_d49","GOT_d50","GOT_d51","GOT_d52","GOT_d53","GOT_d54","GOT_d55","GOT_d56","GOT_d57","GOT_d58","GOT_d59","GOT_d60","GOT_d61","GOT_d62","GOT_d63","GOT_d64","GOT_d65","GOT_d66","GOT_d67","GOT_d68","GOT_d69","GOT_d70","GOT_d71","GOT_d72","GOT_d73","GOT_d74","GOT_d75","GOT_d76","GOT_d77","GOT_d78","GOT_d79","GOT_d80","GOT_d81","GOT_d82","GOT_d83","GOT_d84","GOT_d85","GOT_d86","GOT_d87","GOT_d88","GOT_d89","GOT_d90","GOT_d91","GOT_d92","GOT_d93","GOT_d94","GOT_d95","GOT_d96","GOT_d97","GOT_d98","GOT_d99","GOT_d100","GOT_d105","GOT_d131","GOT_d360","GOT_d580 (guess)"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
ast_summary_data_cgt <- lparaast_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ast_summary_data_cgt$mean_labread + ast_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 600, by = 200)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 500) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ast_summary_data_cgt, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean AST in time course for female with patient count",
       x = "Day of measurement",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 

  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 1500))

```




##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ast_summary_data_cgt$mean_labread + ast_summary_data_cgt$sem_labread, na.rm = TRUE)
max_value <- 3000
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##


lparaast_data_cgt %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        ####NEW#####
  labs(title = "liver_para_cgt boxplot for AST by day of measurement",      ###NEW###
       x = "day of measurement",                            ###NEW###
       y = "AST U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                    limits = c(0, max_value))


```

######################################################################
###ck###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
quick_summary_data_cgt$attribute <- factor(quick_summary_data_cgt$attribute,levels = c("Quick Day1", "Quick Day2", "Quick Day3","Quick Day4","Quick Day5", "Quick Day6","Quick Day7","Quick Day8","Quick Day9","Quick Day10", "Quick Day11","Quick Day12","Quick Day13","Quick Day14","Quick Day15","Quick Day16","Quick Day17","Quick Day18","Quick Day19","Quick Day20","Quick Day21","Quick Day22","Quick Day23","Quick Day24","Quick Day25","Quick Day26","Quick Day27","Quick Day28","Quick Day29","Quick Day30","Quick Day31","Quick Day32","Quick Day33","Quick Day34","Quick Day35","Quick Day36","Quick Day37","Quick Day38","Quick Day39","Quick Day40","Quick Day41","Quick Day42","Quick Day43","Quick Day44","Quick Day45","Quick Day46","Quick Day47","Quick Day48","Quick Day49","Quick Day50","Quick Day51","Quick Day52","Quick Day53","Quick Day54","Quick Day55","Quick Day56","Quick Day57","Quick Day58","Quick Day59","Quick Day60","Quick Day61","Quick Day62","Quick Day63","Quick Day64","Quick Day65","Quick Day66","Quick Day67","Quick Day68","Quick Day69","Quick Day70","Quick Day71","Quick Day72","Quick Day73","Quick Day74","Quick Day75","Quick Day76","Quick Day77","Quick Day78","Quick Day79","Quick Day80","Quick Day81","Quick Day82","Quick Day83","Quick Day84","Quick Day85","Quick Day86","Quick Day87","Quick Day88","Quick Day89","Quick Day90","Quick Day91","Quick Day92","Quick Day93","Quick Day94","Quick Day95","Quick Day96","Quick Day97","Quick Day98","Quick Day99","Quick Day100"))

##for boxplt change last data##
libuquick_data_cgt$attribute <- factor(libuquick_data_cgt$attribute,levels = c("Quick Day1", "Quick Day2", "Quick Day3","Quick Day4","Quick Day5", "Quick Day6","Quick Day7","Quick Day8","Quick Day9","Quick Day10", "Quick Day11","Quick Day12","Quick Day13","Quick Day14","Quick Day15","Quick Day16","Quick Day17","Quick Day18","Quick Day19","Quick Day20","Quick Day21","Quick Day22","Quick Day23","Quick Day24","Quick Day25","Quick Day26","Quick Day27","Quick Day28","Quick Day29","Quick Day30","Quick Day31","Quick Day32","Quick Day33","Quick Day34","Quick Day35","Quick Day36","Quick Day37","Quick Day38","Quick Day39","Quick Day40","Quick Day41","Quick Day42","Quick Day43","Quick Day44","Quick Day45","Quick Day46","Quick Day47","Quick Day48","Quick Day49","Quick Day50","Quick Day51","Quick Day52","Quick Day53","Quick Day54","Quick Day55","Quick Day56","Quick Day57","Quick Day58","Quick Day59","Quick Day60","Quick Day61","Quick Day62","Quick Day63","Quick Day64","Quick Day65","Quick Day66","Quick Day67","Quick Day68","Quick Day69","Quick Day70","Quick Day71","Quick Day72","Quick Day73","Quick Day74","Quick Day75","Quick Day76","Quick Day77","Quick Day78","Quick Day79","Quick Day80","Quick Day81","Quick Day82","Quick Day83","Quick Day84","Quick Day85","Quick Day86","Quick Day87","Quick Day88","Quick Day89","Quick Day90","Quick Day91","Quick Day92","Quick Day93","Quick Day94","Quick Day95","Quick Day96","Quick Day97","Quick Day98","Quick Day99","Quick Day100"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ck_summary_data_cgt <- lparack_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ck_summary_data_cgt$mean_labread + ck_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ck_summary_data_cgt, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels  
  labs(title = "liver_para_cgt mean CK in time course for female with patient count",
       x = "Day of measurement",
       y = "CK U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ck_summary_data_cgt$mean_labread + ck_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparack_data_cgt %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
   geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for CK by day of measurement",
       x = "day of measurement",
       y = "CK U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```




######################################################################
###quick###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
quick_summary_data_cgt$attribute <- factor(quick_summary_data_cgt$attribute,levels = c("Quick_d1", "Quick_d2", "Quick_d3","Quick_d4","Quick_d5", "Quick_d6","Quick_d7","Quick_d8","Quick_d9","Quick_d10", "Quick_d11","Quick_d12","Quick_d13","Quick_d14","Quick_d15","Quick_d16","Quick_d17","Quick_d18","Quick_d19","Quick_d20","Quick_d21","Quick_d22","Quick_d23","Quick_d24","Quick_d25","Quick_d26","Quick_d27","Quick_d28","Quick_d29","Quick_d30","Quick_d31","Quick_d32","Quick_d33","Quick_d34","Quick_d35","Quick_d36","Quick_d37","Quick_d38","Quick_d39","Quick_d40","Quick_d41","Quick_d42","Quick_d43","Quick_d44","Quick_d45","Quick_d46","Quick_d47","Quick_d48","Quick_d49","Quick_d50","Quick_d51","Quick_d52","Quick_d53","Quick_d54","Quick_d55","Quick_d56","Quick_d57","Quick_d58","Quick_d59","Quick_d60","Quick_d61","Quick_d62","Quick_d63","Quick_d64","Quick_d65","Quick_d66","Quick_d67","Quick_d68","Quick_d69","Quick_d70","Quick_d71","Quick_d72","Quick_d73","Quick_d74","Quick_d75","Quick_d76","Quick_d77","Quick_d78","Quick_d79","Quick_d80","Quick_d81","Quick_d82","Quick_d83","Quick_d84","Quick_d85","Quick_d86","Quick_d87","Quick_d88","Quick_d89","Quick_d90","Quick_d91","Quick_d92","Quick_d93","Quick_d94","Quick_d95","Quick_d96","Quick_d97","Quick_d98","Quick_d99","Quick_d100"))

##for boxplt change last data##
lparaquick_data_cgt$attribute <- factor(lparaquick_data_cgt$attribute,levels = c("Quick_d1", "Quick_d2", "Quick_d3","Quick_d4","Quick_d5", "Quick_d6","Quick_d7","Quick_d8","Quick_d9","Quick_d10", "Quick_d11","Quick_d12","Quick_d13","Quick_d14","Quick_d15","Quick_d16","Quick_d17","Quick_d18","Quick_d19","Quick_d20","Quick_d21","Quick_d22","Quick_d23","Quick_d24","Quick_d25","Quick_d26","Quick_d27","Quick_d28","Quick_d29","Quick_d30","Quick_d31","Quick_d32","Quick_d33","Quick_d34","Quick_d35","Quick_d36","Quick_d37","Quick_d38","Quick_d39","Quick_d40","Quick_d41","Quick_d42","Quick_d43","Quick_d44","Quick_d45","Quick_d46","Quick_d47","Quick_d48","Quick_d49","Quick_d50","Quick_d51","Quick_d52","Quick_d53","Quick_d54","Quick_d55","Quick_d56","Quick_d57","Quick_d58","Quick_d59","Quick_d60","Quick_d61","Quick_d62","Quick_d63","Quick_d64","Quick_d65","Quick_d66","Quick_d67","Quick_d68","Quick_d69","Quick_d70","Quick_d71","Quick_d72","Quick_d73","Quick_d74","Quick_d75","Quick_d76","Quick_d77","Quick_d78","Quick_d79","Quick_d80","Quick_d81","Quick_d82","Quick_d83","Quick_d84","Quick_d85","Quick_d86","Quick_d87","Quick_d88","Quick_d89","Quick_d90","Quick_d91","Quick_d92","Quick_d93","Quick_d94","Quick_d95","Quick_d96","Quick_d97","Quick_d98","Quick_d99","Quick_d100"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
quick_summary_data_cgt <- lparaquick_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(quick_summary_data_cgt$mean_labread + quick_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(quick_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels  
  labs(title = "liver_para_cgt mean quick in time course for female with patient count",
       x = "Day of measurement",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0,140))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(quick_summary_data_cgt$mean_labread + quick_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaquick_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
   geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for quick by day of measurement",
       x = "day of measurement",
       y = "quick %") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 140))


```

######################################################################
###inr###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
inr_summary_data_cgt$attribute <- factor(inr_summary_data_cgt$attribute,levels = c( "INR Day1", "INR Day2", "INR Day3","INR Day4","INR Day5", "INR Day6","INR Day7","INR Day8","INR Day9","INR Day10", "INR Day11","INR Day12","INR Day13","INR Day14","INR Day15","INR Day16","INR Day17","INR Day18","INR Day19","INR Day20","INR Day21","INR Day22","INR Day23","INR Day24","INR Day25","INR Day26","INR Day27","INR Day28","INR Day29","INR Day30","INR Day31","INR Day32","INR Day33","INR Day34","INR Day35","INR Day36","INR Day37","INR Day38","INR Day39","INR Day40","INR Day41","INR Day42","INR Day43","INR Day44","INR Day45","INR Day46","INR Day47","INR Day48","INR Day49","INR Day50","INR Day51","INR Day52","INR Day53","INR Day54","INR Day55","INR Day56","INR Day57","INR Day58","INR Day59","INR Day60","INR Day61","INR Day62","INR Day63","INR Day64","INR Day65","INR Day66","INR Day67","INR Day68","INR Day69","INR Day70","INR Day71","INR Day72","INR Day73","INR Day74","INR Day75","INR Day76","INR Day77","INR Day78","INR Day79","INR Day80","INR Day81","INR Day82","INR Day83","INR Day84","INR Day85","INR Day86","INR Day87","INR Day88","INR Day89","INR Day90","INR Day91","INR Day92","INR Day93","INR Day94","INR Day95","INR Day96","INR Day97","INR Day98","INR Day99","INR Day100"))

##for boxplt change last data##
libuinr_data_cgt$attribute <- factor(libuinr_data_cgt$attribute,levels = c( "INR Day1", "INR Day2", "INR Day3","INR Day4","INR Day5", "INR Day6","INR Day7","INR Day8","INR Day9","INR Day10", "INR Day11","INR Day12","INR Day13","INR Day14","INR Day15","INR Day16","INR Day17","INR Day18","INR Day19","INR Day20","INR Day21","INR Day22","INR Day23","INR Day24","INR Day25","INR Day26","INR Day27","INR Day28","INR Day29","INR Day30","INR Day31","INR Day32","INR Day33","INR Day34","INR Day35","INR Day36","INR Day37","INR Day38","INR Day39","INR Day40","INR Day41","INR Day42","INR Day43","INR Day44","INR Day45","INR Day46","INR Day47","INR Day48","INR Day49","INR Day50","INR Day51","INR Day52","INR Day53","INR Day54","INR Day55","INR Day56","INR Day57","INR Day58","INR Day59","INR Day60","INR Day61","INR Day62","INR Day63","INR Day64","INR Day65","INR Day66","INR Day67","INR Day68","INR Day69","INR Day70","INR Day71","INR Day72","INR Day73","INR Day74","INR Day75","INR Day76","INR Day77","INR Day78","INR Day79","INR Day80","INR Day81","INR Day82","INR Day83","INR Day84","INR Day85","INR Day86","INR Day87","INR Day88","INR Day89","INR Day90","INR Day91","INR Day92","INR Day93","INR Day94","INR Day95","INR Day96","INR Day97","INR Day98","INR Day99","INR Day100"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
inr_summary_data_cgt <- lparainr_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(inr_summary_data_cgt$mean_labread + inr_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 5)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(inr_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean INR in time course for female with patient count",
       x = "Day of measurement",
       y = "INR",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- 10#max(inr_summary_data_cgt$mean_labread + inr_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1
                        )
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparainr_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for INR by day of measurement",
       x = "day of measurement",
       y = "INR") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###ptt###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
inr_summary_data_cgt$attribute <- factor(inr_summary_data_cgt$attribute,levels = c( "INR Day1", "INR Day2", "INR Day3","INR Day4","INR Day5", "INR Day6","INR Day7","INR Day8","INR Day9","INR Day10", "INR Day11","INR Day12","INR Day13","INR Day14","INR Day15","INR Day16","INR Day17","INR Day18","INR Day19","INR Day20","INR Day21","INR Day22","INR Day23","INR Day24","INR Day25","INR Day26","INR Day27","INR Day28","INR Day29","INR Day30","INR Day31","INR Day32","INR Day33","INR Day34","INR Day35","INR Day36","INR Day37","INR Day38","INR Day39","INR Day40","INR Day41","INR Day42","INR Day43","INR Day44","INR Day45","INR Day46","INR Day47","INR Day48","INR Day49","INR Day50","INR Day51","INR Day52","INR Day53","INR Day54","INR Day55","INR Day56","INR Day57","INR Day58","INR Day59","INR Day60","INR Day61","INR Day62","INR Day63","INR Day64","INR Day65","INR Day66","INR Day67","INR Day68","INR Day69","INR Day70","INR Day71","INR Day72","INR Day73","INR Day74","INR Day75","INR Day76","INR Day77","INR Day78","INR Day79","INR Day80","INR Day81","INR Day82","INR Day83","INR Day84","INR Day85","INR Day86","INR Day87","INR Day88","INR Day89","INR Day90","INR Day91","INR Day92","INR Day93","INR Day94","INR Day95","INR Day96","INR Day97","INR Day98","INR Day99","INR Day100"))

##for boxplt change last data##
libuinr_data_cgt$attribute <- factor(libuinr_data_cgt$attribute,levels = c( "INR Day1", "INR Day2", "INR Day3","INR Day4","INR Day5", "INR Day6","INR Day7","INR Day8","INR Day9","INR Day10", "INR Day11","INR Day12","INR Day13","INR Day14","INR Day15","INR Day16","INR Day17","INR Day18","INR Day19","INR Day20","INR Day21","INR Day22","INR Day23","INR Day24","INR Day25","INR Day26","INR Day27","INR Day28","INR Day29","INR Day30","INR Day31","INR Day32","INR Day33","INR Day34","INR Day35","INR Day36","INR Day37","INR Day38","INR Day39","INR Day40","INR Day41","INR Day42","INR Day43","INR Day44","INR Day45","INR Day46","INR Day47","INR Day48","INR Day49","INR Day50","INR Day51","INR Day52","INR Day53","INR Day54","INR Day55","INR Day56","INR Day57","INR Day58","INR Day59","INR Day60","INR Day61","INR Day62","INR Day63","INR Day64","INR Day65","INR Day66","INR Day67","INR Day68","INR Day69","INR Day70","INR Day71","INR Day72","INR Day73","INR Day74","INR Day75","INR Day76","INR Day77","INR Day78","INR Day79","INR Day80","INR Day81","INR Day82","INR Day83","INR Day84","INR Day85","INR Day86","INR Day87","INR Day88","INR Day89","INR Day90","INR Day91","INR Day92","INR Day93","INR Day94","INR Day95","INR Day96","INR Day97","INR Day98","INR Day99","INR Day100"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ptt_summary_data_cgt <- lparaptt_data_cgt  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ptt_summary_data_cgt$mean_labread + ptt_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 5)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ptt_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean PTT in time course for male with patient count",
       x = "Day of measurement",
       y = "PTT sec.",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- 80#max(inr_summary_data_cgt$mean_labread + inr_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10
                        )
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaptt_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for PTT by day of measurement",
       x = "day of measurement",
       y = "PTT") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```




######################################################################
###Leukozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data_cgt$Attribute <- factor(leukozyten_summary_data_cgt$attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5","Leukozyten Day6","Leukozyten Day7","Leukozyten Day8",
"Leukozyten Day9","Leukozyten Day10", "Leukozyten Day11","Leukozyten Day12","Leukozyten Day13","Leukozyten Day15","Leukozyten Day26"))

##for boxplt change last data##
lparaleukozyten_data_cgt$attribute <- factor(lparaleukozyten_data_cgt$attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5","Leukozyten Day6","Leukozyten Day7","Leukozyten Day8",
"Leukozyten Day9","Leukozyten Day10", "Leukozyten Day11","Leukozyten Day12","Leukozyten Day13","Leukozyten Day15","Leukozyten Day26"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
leukozyten_summary_data_cgt <- lparaleukozyten_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(leukozyten_summary_data_cgt$mean_labread + leukozyten_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(leukozyten_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean leukocytes in time course for female with patient count",
       x = "Day of measurement",
       y = "Leukocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(leukozyten_summary_data_cgt$mean_labread + leukozyten_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 6000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaleukozyten_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for leukocytes by day of measurement",
       x = "day of measurement",
       y = "Leukocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###GGT###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ggt_summary_data_cgt$Attribute <- factor(ggt_summary_data_cgt$attribute,levels = c("GGT_d1", "GGT_d2", "GGT_d3","GGT_d4","GGT_d5", "GGT_d6","GGT_d7","GGT_d8","GGT_d9","GGT_d10", "GGT_d11","GGT_d12","GGT_d13","GGT_d14","GGT_d14 (guess)","GGT_d15","GGT_d16","GGT_d17","GGT_d18","GGT_d19","GGT_d20","GGT_d21","GGT_d21 (guess)","GGT_d22","GGT_d23","GGT_d24","GGT_d25","GGT_d26","GGT_d27","GGT_d28","GGT_d29","GGT_d30","GGT_d31","GGT_d32","GGT_d33","GGT_d34","GGT_d35","GGT_d36","GGT_d37","GGT_d38","GGT_d39","GGT_d40","GGT_d41","GGT_d42","GGT_d43","GGT_d44","GGT_d45","GGT_d46","GGT_d47","GGT_d48","GGT_d49","GGT_d50","GGT_d51","GGT_d52","GGT_d53","GGT_d54","GGT_d55","GGT_d56","GGT_d57","GGT_d58","GGT_d59","GGT_d60","GGT_d61","GGT_d62","GGT_d63","GGT_d64","GGT_d65","GGT_d66","GGT_d67","GGT_d68","GGT_d69","GGT_d70","GGT_d71","GGT_d72","GGT_d73","GGT_d74","GGT_d75","GGT_d76","GGT_d77","GGT_d78","GGT_d79","GGT_d80","GGT_d81","GGT_d82","GGT_d83","GGT_d84","GGT_d85","GGT_d86","GGT_d87","GGT_d88","GGT_d89","GGT_d90","GGT_d91","GGT_d92","GGT_d93","GGT_d94","GGT_d95","GGT_d96","GGT_d97","GGT_d98","GGT_d99","GGT_d100","GGT_d105","GGT_d131","GGT_d244 (guess)","GGT_d360","GGT_d488 (guess)","GGT_d549 (guess)","GGT_d580 (guess)"))

##for boxplt change last data##
lparaggt_data_cgt$attribute <- factor(lparaggt_data_cgt$attribute,levels = c("GGT_d1", "GGT_d2", "GGT_d3","GGT_d4","GGT_d5", "GGT_d6","GGT_d7","GGT_d8","GGT_d9","GGT_d10", "GGT_d11","GGT_d12","GGT_d13","GGT_d14","GGT_d14 (guess)","GGT_d15","GGT_d16","GGT_d17","GGT_d18","GGT_d19","GGT_d20","GGT_d21","GGT_d21 (guess)","GGT_d22","GGT_d23","GGT_d24","GGT_d25","GGT_d26","GGT_d27","GGT_d28","GGT_d29","GGT_d30","GGT_d31","GGT_d32","GGT_d33","GGT_d34","GGT_d35","GGT_d36","GGT_d37","GGT_d38","GGT_d39","GGT_d40","GGT_d41","GGT_d42","GGT_d43","GGT_d44","GGT_d45","GGT_d46","GGT_d47","GGT_d48","GGT_d49","GGT_d50","GGT_d51","GGT_d52","GGT_d53","GGT_d54","GGT_d55","GGT_d56","GGT_d57","GGT_d58","GGT_d59","GGT_d60","GGT_d61","GGT_d62","GGT_d63","GGT_d64","GGT_d65","GGT_d66","GGT_d67","GGT_d68","GGT_d69","GGT_d70","GGT_d71","GGT_d72","GGT_d73","GGT_d74","GGT_d75","GGT_d76","GGT_d77","GGT_d78","GGT_d79","GGT_d80","GGT_d81","GGT_d82","GGT_d83","GGT_d84","GGT_d85","GGT_d86","GGT_d87","GGT_d88","GGT_d89","GGT_d90","GGT_d91","GGT_d92","GGT_d93","GGT_d94","GGT_d95","GGT_d96","GGT_d97","GGT_d98","GGT_d99","GGT_d100","GGT_d105","GGT_d131","GGT_d244 (guess)","GGT_d360","GGT_d488 (guess)","GGT_d549 (guess)","GGT_d580 (guess)"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ggt_summary_data_cgt <- lparaggt_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ggt_summary_data_cgt$mean_labread + ggt_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 600, by = 100)
#additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000) else numeric(0)
all_breaks <- c(breaks_up_to_500)

ggplot(ggt_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean GGT in time course for female with patient count",
       x = "Day of measurement",
       y = "GGT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 1600))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ggt_summary_data_cgt$mean_labread + ggt_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 1000, by = 100)
#additional_breaks <- if (max_value > 500) seq(600, max_value, by = 600) else numeric(0)
all_breaks <- c(breaks_up_to_500)

## use the last joined data gender with labreads##
lparaggt_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+    
  labs(title = "liver_para_cgt boxplot for GGT by day of measurement",
       x = "day of measurement",
       y = "GGT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 1600))


```

######################################################################
###LDH###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ldh_summary_data_cgt$attribute <- factor(ldh_summary_data_cgt$attribute,levels = c( "LDH Day1","LDH Day2","LDH Day3","LDH Day4","LDH Day5","LDH Day6","LDH Day7","LDH Day8","LDH Day10","LDH Day12"))

##for boxplt change last data##
lparaldh_data_cgt$attribute <- factor(lparaldh_data_cgt$attribute,levels = c("LDH Day1","LDH Day2","LDH Day3","LDH Day4","LDH Day5","LDH Day6","LDH Day7","LDH Day8","LDH Day10","LDH Day12"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ldh_summary_data_cgt <- lparaldh_data_cgt  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ldh_summary_data_cgt$mean_labread + ldh_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 150)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 500) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ldh_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean LDH in time course for male with patient count",
       x = "Day of measurement",
       y = "LDH U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ldh_summary_data_cgt$mean_labread + ldh_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaldh_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for LDH by day of measurement",
       x = "day of measurement",
       y = "LDH U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###HB###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
hb_summary_data_cgt$attribute <- factor(hb_summary_data_cgt$attribute,levels = c("Hb Day1", "Hb Day2", "Hb Day3", "Hb Day4", "Hb Day5","Hb Day6", "Hb Day7","Hb Day8","Hb Day9","Hb Day10","Hb Day11", "Hb Day12","Hb Day14","Hb Day15", "Hb Day16"))

##for boxplt change last data##
lparahb_data_cgt$attribute <- factor(lparahb_data_cgt$attribute,levels = c("Hb Day1", "Hb Day2", "Hb Day3", "Hb Day4", "Hb Day5","Hb Day6", "Hb Day7","Hb Day8","Hb Day9","Hb Day10","Hb Day11", "Hb Day12","Hb Day14","Hb Day15", "Hb Day16"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hb_summary_data_cgt <- lparahb_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hb_summary_data_cgt$mean_labread + hb_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 5)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hb_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean HB in time course for female with patient count",
       x = "Day of measurement",
       y = "HB g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hb_summary_data_cgt$mean_labread + hb_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 5)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparahb_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+      
  labs(title = "liver_para_cgt boxplot for HB by day of measurement",
       x = "day of measurement",
       y = "HB g/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###totales Bilirubin###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
totbili_summary_data_cgt$attribute <- factor(totbili_summary_data_cgt$attribute,levels = c("TotalBilirubin_d1", "TotalBilirubin_d2", "TotalBilirubin_d3","TotalBilirubin_d4","TotalBilirubin_d5", "TotalBilirubin_d6","TotalBilirubin_d7","TotalBilirubin_d7 (guess)","TotalBilirubin_d8","TotalBilirubin_d9","TotalBilirubin_d10", "TotalBilirubin_d11","TotalBilirubin_d12","TotalBilirubin_d13","TotalBilirubin_d14","TotalBilirubin_d14 (guess)","TotalBilirubin_d15","TotalBilirubin_d16","TotalBilirubin_d17","TotalBilirubin_d18","TotalBilirubin_d19","TotalBilirubin_d20","TotalBilirubin_d21","TotalBilirubin_d21 (guess)","TotalBilirubin_d22","TotalBilirubin_d23","TotalBilirubin_d24","TotalBilirubin_d25","TotalBilirubin_d26","TotalBilirubin_d27","TotalBilirubin_d28","TotalBilirubin_d29","TotalBilirubin_d30","TotalBilirubin_d31","TotalBilirubin_d32","TotalBilirubin_d33","TotalBilirubin_d34","TotalBilirubin_d35","TotalBilirubin_d36","TotalBilirubin_d37","TotalBilirubin_d38","TotalBilirubin_d39","TotalBilirubin_d40","TotalBilirubin_d41","TotalBilirubin_d42","TotalBilirubin_d43","TotalBilirubin_d44","TotalBilirubin_d45","TotalBilirubin_d46","TotalBilirubin_d47","TotalBilirubin_d48","TotalBilirubin_d49","TotalBilirubin_d50","TotalBilirubin_d51","TotalBilirubin_d52","TotalBilirubin_d53","TotalBilirubin_d54","TotalBilirubin_d55","TotalBilirubin_d56","TotalBilirubin_d57","TotalBilirubin_d58","TotalBilirubin_d59","TotalBilirubin_d60","TotalBilirubin_d61","TotalBilirubin_d62","TotalBilirubin_d63","TotalBilirubin_d64","TotalBilirubin_d65","TotalBilirubin_d66","TotalBilirubin_d67","TotalBilirubin_d68","TotalBilirubin_d69","TotalBilirubin_d70","TotalBilirubin_d71","TotalBilirubin_d72","TotalBilirubin_d73","TotalBilirubin_d74","TotalBilirubin_d75","TotalBilirubin_d76","TotalBilirubin_d77","TotalBilirubin_d78","TotalBilirubin_d79","TotalBilirubin_d80","TotalBilirubin_d81","TotalBilirubin_d82","TotalBilirubin_d83","TotalBilirubin_d84","TotalBilirubin_d85","TotalBilirubin_d86","TotalBilirubin_d87","TotalBilirubin_d88","TotalBilirubin_d89","TotalBilirubin_d90","TotalBilirubin_d91","TotalBilirubin_d92","TotalBilirubin_d93","TotalBilirubin_d94","TotalBilirubin_d95","TotalBilirubin_d96","TotalBilirubin_d97","TotalBilirubin_d98","TotalBilirubin_d99","TotalBilirubin_d100","TotalBilirubin_d105"))

##for boxplt change last data##
lparatotbili_data_cgt$attribute <- factor(lparatotbili_data_cgt$attribute,levels = c("TotalBilirubin_d1", "TotalBilirubin_d2", "TotalBilirubin_d3","TotalBilirubin_d4","TotalBilirubin_d5", "TotalBilirubin_d6","TotalBilirubin_d7","TotalBilirubin_d7 (guess)","TotalBilirubin_d8","TotalBilirubin_d9","TotalBilirubin_d10", "TotalBilirubin_d11","TotalBilirubin_d12","TotalBilirubin_d13","TotalBilirubin_d14","TotalBilirubin_d14 (guess)","TotalBilirubin_d15","TotalBilirubin_d16","TotalBilirubin_d17","TotalBilirubin_d18","TotalBilirubin_d19","TotalBilirubin_d20","TotalBilirubin_d21","TotalBilirubin_d21 (guess)","TotalBilirubin_d22","TotalBilirubin_d23","TotalBilirubin_d24","TotalBilirubin_d25","TotalBilirubin_d26","TotalBilirubin_d27","TotalBilirubin_d28","TotalBilirubin_d29","TotalBilirubin_d30","TotalBilirubin_d31","TotalBilirubin_d32","TotalBilirubin_d33","TotalBilirubin_d34","TotalBilirubin_d35","TotalBilirubin_d36","TotalBilirubin_d37","TotalBilirubin_d38","TotalBilirubin_d39","TotalBilirubin_d40","TotalBilirubin_d41","TotalBilirubin_d42","TotalBilirubin_d43","TotalBilirubin_d44","TotalBilirubin_d45","TotalBilirubin_d46","TotalBilirubin_d47","TotalBilirubin_d48","TotalBilirubin_d49","TotalBilirubin_d50","TotalBilirubin_d51","TotalBilirubin_d52","TotalBilirubin_d53","TotalBilirubin_d54","TotalBilirubin_d55","TotalBilirubin_d56","TotalBilirubin_d57","TotalBilirubin_d58","TotalBilirubin_d59","TotalBilirubin_d60","TotalBilirubin_d61","TotalBilirubin_d62","TotalBilirubin_d63","TotalBilirubin_d64","TotalBilirubin_d65","TotalBilirubin_d66","TotalBilirubin_d67","TotalBilirubin_d68","TotalBilirubin_d69","TotalBilirubin_d70","TotalBilirubin_d71","TotalBilirubin_d72","TotalBilirubin_d73","TotalBilirubin_d74","TotalBilirubin_d75","TotalBilirubin_d76","TotalBilirubin_d77","TotalBilirubin_d78","TotalBilirubin_d79","TotalBilirubin_d80","TotalBilirubin_d81","TotalBilirubin_d82","TotalBilirubin_d83","TotalBilirubin_d84","TotalBilirubin_d85","TotalBilirubin_d86","TotalBilirubin_d87","TotalBilirubin_d88","TotalBilirubin_d89","TotalBilirubin_d90","TotalBilirubin_d91","TotalBilirubin_d92","TotalBilirubin_d93","TotalBilirubin_d94","TotalBilirubin_d95","TotalBilirubin_d96","TotalBilirubin_d97","TotalBilirubin_d98","TotalBilirubin_d99","TotalBilirubin_d100","TotalBilirubin_d105"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
totbili_summary_data_cgt <- lparatotbili_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(totbili_summary_data_cgt$mean_labread + totbili_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(totbili_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean total bilirubin in time course for female with patient count",
       x = "Day of measurement",
       y = "total Bilirubin mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 25))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(totbili_summary_data_cgt$mean_labread + totbili_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparatotbili_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for total bilirubin by day of measurement",
       x = "day of measurement",
       y = "total Bilirubin mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 25))


```

######################################################################
###direktes Bilirubin###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
totbili_summary_data_cgt$attribute <- factor(totbili_summary_data_cgt$attribute,levels = c("DirectBilirubin Day1","DirectBilirubin Day2","DirectBilirubin Day3","DirectBilirubin Day4","DirectBilirubin Day11"))

##for boxplt change last data##
lparadirbili_data_cgt$attribute <- factor(lparadirbili_data_cgt$attribute,levels = c("DirectBilirubin Day1","DirectBilirubin Day2","DirectBilirubin Day3","DirectBilirubin Day4","DirectBilirubin Day11"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
dirbili_summary_data_cgt <- lparadirbili_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(dirbili_summary_data_cgt$mean_labread + dirbili_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(dirbili_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean direct bilirubin in time course for female with patient count",
       x = "Day of measurement",
       y = "direct Bilirubin mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(dirbili_summary_data_cgt$mean_labread + dirbili_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparadirbili_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for direct bilirubin by day of measurement",
       x = "day of measurement",
       y = "direct Bilirubin mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Gesamteiweiß###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
totbili_summary_data_cgt$attribute <- factor(totbili_summary_data_cgt$attribute,levels = c("DirectBilirubin Day1","DirectBilirubin Day2","DirectBilirubin Day3","DirectBilirubin Day4","DirectBilirubin Day11"))

##for boxplt change last data##
lparadirbili_data_cgt$attribute <- factor(lparadirbili_data_cgt$attribute,levels = c("DirectBilirubin Day1","DirectBilirubin Day2","DirectBilirubin Day3","DirectBilirubin Day4","DirectBilirubin Day11"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ges_summary_data_cgt <- lparages_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- 10#max(ges_summary_data_cgt$mean_labread + ges_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ges_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean total protein in time course for female with patient count",
       x = "Day of measurement",
       y = "total protein g/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- 10#max(ges_summary_data_cgt$mean_labread + ges_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparages_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for total protein by day of measurement",
       x = "day of measurement",
       y = "total protein g/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```






######################################################################
###AP###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
ap_summary_data_cgt$attribute <- factor(ap_summary_data_cgt$attribute,levels = c("AP_d1", "AP_d2", "AP_d3","AP_d4","AP_d5", "AP_d6","AP_d7","AP_d8","AP_d9","AP_d10", "AP_d11","AP_d12","AP_d13","AP_d14","AP_d15","AP_d16","AP_d17","AP_d18","AP_d19","AP_d20","AP_d21","AP_d22","AP_d23","AP_d24","AP_d25","AP_d26","AP_d27","AP_d28","AP_d29","AP_d30","AP_d31","AP_d32","AP_d33","AP_d34","AP_d35","AP_d36","AP_d37","AP_d38","AP_d39","AP_d40","AP_d41","AP_d42","AP_d43","AP_d44","AP_d45","AP_d46","AP_d47","AP_d48","AP_d49","AP_d50","AP_d51","AP_d52","AP_d53","AP_d54","AP_d55","AP_d56","AP_d57","AP_d58","AP_d59","AP_d60","AP_d61","AP_d62","AP_d63","AP_d64","AP_d65","AP_d66","AP_d67","AP_d68","AP_d69","AP_d70","AP_d71","AP_d72","AP_d73","AP_d74","AP_d75","AP_d76","AP_d77","AP_d78","AP_d79","AP_d80","AP_d81","AP_d82","AP_d83","AP_d84","AP_d85","AP_d86","AP_d87","AP_d88","AP_d89","AP_d90","AP_d91","AP_d92","AP_d93","AP_d94","AP_d95","AP_d96","AP_d97","AP_d98","AP_d99","AP_d100","AP_d105"))

##for boxplt change last data##
lparaap_data_cgt$attribute <- factor(lparaap_data_cgt$attribute,levels = c("AP_d1", "AP_d2", "AP_d3","AP_d4","AP_d5", "AP_d6","AP_d7","AP_d8","AP_d9","AP_d10", "AP_d11","AP_d12","AP_d13","AP_d14","AP_d15","AP_d16","AP_d17","AP_d18","AP_d19","AP_d20","AP_d21","AP_d22","AP_d23","AP_d24","AP_d25","AP_d26","AP_d27","AP_d28","AP_d29","AP_d30","AP_d31","AP_d32","AP_d33","AP_d34","AP_d35","AP_d36","AP_d37","AP_d38","AP_d39","AP_d40","AP_d41","AP_d42","AP_d43","AP_d44","AP_d45","AP_d46","AP_d47","AP_d48","AP_d49","AP_d50","AP_d51","AP_d52","AP_d53","AP_d54","AP_d55","AP_d56","AP_d57","AP_d58","AP_d59","AP_d60","AP_d61","AP_d62","AP_d63","AP_d64","AP_d65","AP_d66","AP_d67","AP_d68","AP_d69","AP_d70","AP_d71","AP_d72","AP_d73","AP_d74","AP_d75","AP_d76","AP_d77","AP_d78","AP_d79","AP_d80","AP_d81","AP_d82","AP_d83","AP_d84","AP_d85","AP_d86","AP_d87","AP_d88","AP_d89","AP_d90","AP_d91","AP_d92","AP_d93","AP_d94","AP_d95","AP_d96","AP_d97","AP_d98","AP_d99","AP_d100","AP_d105"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ap_summary_data_cgt <- lparaap_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ap_summary_data_cgt$mean_labread + ap_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ap_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean AP in time course for female with patient count",
       x = "Day of measurement",
       y = "AP U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 1000))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ap_summary_data_cgt$mean_labread + ap_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaap_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for AP by day of measurement",
       x = "day of measurement",
       y = "AP U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 1000))


```

######################################################################
###Kreatinin###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
krea_summary_data_cgt$attribute <- factor(krea_summary_data_cgt$attribute,levels = c("Kreatinin Day1","Kreatinin Day2","Kreatinin Day3", "Kreatinin Day4","Kreatinin Day5","Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10","Kreatinin Day11","Kreatinin Day12","Kreatinin Day13","Kreatinin Day15","Kreatinin Day22"))

##for boxplt change last data##
lparakrea_data_cgt$attribute <- factor(lparakrea_data_cgt$attribute,levels = c("Kreatinin Day1","Kreatinin Day2","Kreatinin Day3", "Kreatinin Day4","Kreatinin Day5","Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10","Kreatinin Day11","Kreatinin Day12","Kreatinin Day13","Kreatinin Day15","Kreatinin Day22"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
krea_summary_data_cgt <- lparakrea_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(krea_summary_data_cgt$mean_labread + krea_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(krea_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean Creatinine in time course for female with patient count",
       x = "Day of measurement",
       y = "Creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(krea_summary_data_cgt$mean_labread + krea_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparakrea_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for creatinine by day of measurement",
       x = "day of measurement",
       y = "Creatinine mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Lipase###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
krea_summary_data_cgt$attribute <- factor(krea_summary_data_cgt$attribute,levels = c("Kreatinin Day1","Kreatinin Day2","Kreatinin Day3", "Kreatinin Day4","Kreatinin Day5","Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10","Kreatinin Day11","Kreatinin Day12","Kreatinin Day13","Kreatinin Day15","Kreatinin Day22"))

##for boxplt change last data##
lparakrea_data_cgt$attribute <- factor(lparakrea_data_cgt$attribute,levels = c("Kreatinin Day1","Kreatinin Day2","Kreatinin Day3", "Kreatinin Day4","Kreatinin Day5","Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10","Kreatinin Day11","Kreatinin Day12","Kreatinin Day13","Kreatinin Day15","Kreatinin Day22"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
lipa_summary_data_cgt <- lparalipa_data_cgt  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(lipa_summary_data_cgt$mean_labread + lipa_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(lipa_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean lipase in time course for male with patient count",
       x = "Day of measurement",
       y = "Lipase mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(lipa_summary_data_cgt$mean_labread + lipa_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparalipa_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for lipase by day of measurement",
       x = "day of measurement",
       y = "Lipase mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```







######################################################################
###CRP###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
crp_summary_data_cgt$attribute <- factor(crp_summary_data_cgt$attribute,levels = c("CRP Day1","CRP Day2","CRP Day3","CRP Day4","CRP Day5","CRP Day6","CRP Day7","CRP Day9","CRP Day10","CRP Day11","CRP Day15"))

##for boxplt change last data##
lparacrp_data_cgt$attribute <- factor(lparacrp_data_cgt$attribute,levels = c("CRP Day1","CRP Day2","CRP Day3","CRP Day4","CRP Day5","CRP Day6","CRP Day7","CRP Day9","CRP Day10","CRP Day11","CRP Day15"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
crp_summary_data_cgt <- lparacrp_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(crp_summary_data_cgt$mean_labread + crp_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(crp_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean CRP in time course for female with patient count",
       x = "Day of measurement",
       y = "CRP mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(crp_summary_data_cgt$mean_labread + crp_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparacrp_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for CRP by day of measurement",
       x = "day of measurement",
       y = "CRP mg/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Harnstoff###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
hst_summary_data_cgt$attribute <- factor(hst_summary_data_cgt$attribute,levels = c( "Harnstoff Day1","Harnstoff Day2","Harnstoff Day3","Harnstoff Day4","Harnstoff Day5","Harnstoff Day6","Harnstoff Day9","Harnstoff Day10","Harnstoff Day13","Harnstoff Day22"))

##for boxplt change last data##
libuhst_data_cgt$attribute <- factor(libuhst_data_cgt$attribute,levels = c( "Harnstoff Day1","Harnstoff Day2","Harnstoff Day3","Harnstoff Day4","Harnstoff Day5","Harnstoff Day6","Harnstoff Day9","Harnstoff Day10","Harnstoff Day13","Harnstoff Day22"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hst_summary_data_cgt <- lparahst_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hst_summary_data_cgt$mean_labread + hst_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 5)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hst_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean urea in time course for female with patient count",
       x = "Day of measurement",
       y = "Urea mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hst_summary_data_cgt$mean_labread + hst_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparahst_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for urea by day of measurement",
       x = "Day of measurement",
       y = "Urea mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Erythrozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
thromb_summary_data_cgt$attribute <- factor(thromb_summary_data_cgt$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day15","Thrombozyten Day26"))

##for boxplt change last data##
lparathromb_data_cgt$attribute <- factor(lparathromb_data_cgt$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day15","Thrombozyten Day26"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
ery_summary_data_cgt <- lparaery_data_cgt  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(ery_summary_data_cgt$mean_labread + ery_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1000000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(ery_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean erythrocytes in time course for male with patient count",
       x = "Day of measurement",
       y = "Erythrocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(ery_summary_data_cgt$mean_labread + ery_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1000000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1000000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaery_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for erythrocytes by day of measurement",
       x = "day of measurement",
       y = "Erythrocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


######################################################################
###Thrombozyten###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
thromb_summary_data_cgt$attribute <- factor(thromb_summary_data_cgt$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day15","Thrombozyten Day26"))

##for boxplt change last data##
lparathromb_data_cgt$attribute <- factor(lparathromb_data_cgt$attribute,levels = c("Thrombozyten Day1","Thrombozyten Day2","Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5","Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10","Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day15","Thrombozyten Day26"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
thromb_summary_data_cgt <- lparathromb_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(thromb_summary_data_cgt$mean_labread + thromb_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(thromb_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
   geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean thrombocytes in time course for female with patient count",
       x = "Day of measurement",
       y = "Thrombocytes Cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(thromb_summary_data_cgt$mean_labread + thromb_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100000)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparathromb_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for thrombocytes by day of measurement",
       x = "day of measurement",
       y = "Thrombocytes Cells/ul") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Hämatokrit###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
hkt_summary_data_cgt$attribute <- factor(hkt_summary_data_cgt$attribute,levels = c( "Hämatokrit Day1","Hämatokrit Day2","Hämatokrit Day3","Hämatokrit Day4","Hämatokrit Day5","Hämatokrit Day6","Hämatokrit Day8","Hämatokrit Day9","Hämatokrit Day10","Hämatokrit Day11","Hämatokrit Day12","Hämatokrit Day13","Hämatokrit Day15","Hämatokrit Day16"))

##for boxplt change last data##
libuhkt_data_cgt$attribute <- factor(libuhkt_data_cgt$attribute,levels = c("Hämatokrit Day1","Hämatokrit Day2","Hämatokrit Day3","Hämatokrit Day4","Hämatokrit Day5","Hämatokrit Day6","Hämatokrit Day8","Hämatokrit Day9","Hämatokrit Day10","Hämatokrit Day11","Hämatokrit Day12","Hämatokrit Day13","Hämatokrit Day15","Hämatokrit Day16"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
hkt_summary_data_cgt <- lparahkt_data_cgt  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(hkt_summary_data_cgt$mean_labread + hkt_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(hkt_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean hematocrit in time course for male with patient count",
       x = "Day of measurement",
       y = "hematocrit %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(hkt_summary_data_cgt$mean_labread + hkt_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparahkt_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for hematocrit by day of measurement",
       x = "day of measurement",
       y = "hematocrit %") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Natrium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
kal_summary_data_cgt$attribute <- factor(kal_summary_data_cgt$attribute,levels = c("Kalium Day1","Kalium Day2","Kalium Day3","Kalium Day4","Kalium Day5","Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day12","Kalium Day15"))

##for boxplt change last data##
lparakal_data_cgt$attribute <- factor(lparakal_data_cgt$attribute,levels = c("Kalium Day1","Kalium Day2","Kalium Day3","Kalium Day4","Kalium Day5","Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day12","Kalium Day15"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
nat_summary_data_cgt <- lparanat_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- 160#max(nat_summary_data_cgt$mean_labread + nat_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(nat_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean sodium in time course for female with patient count",
       x = "Day of measurement",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(nat_summary_data_cgt$mean_labread + nat_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparanat_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for sodium by day of measurement",
       x = "day of measurement",
       y = "Sodium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```




######################################################################
###Kalium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
kal_summary_data_cgt$attribute <- factor(kal_summary_data_cgt$attribute,levels = c("Kalium Day1","Kalium Day2","Kalium Day3","Kalium Day4","Kalium Day5","Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day12","Kalium Day15"))

##for boxplt change last data##
lparakal_data_cgt$attribute <- factor(lparakal_data_cgt$attribute,levels = c("Kalium Day1","Kalium Day2","Kalium Day3","Kalium Day4","Kalium Day5","Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day12","Kalium Day15"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
kal_summary_data_cgt <- lparakal_data_cgt  %>% filter(gender == "Male") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(kal_summary_data_cgt$mean_labread + kal_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(kal_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean potassium in time course for male with patient count",
       x = "Day of measurement",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(kal_summary_data_cgt$mean_labread + kal_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparakal_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for potassium by day of measurement",
       x = "day of measurement",
       y = "Potassium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Kalzium###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
cal_summary_data_cgt$Attribute <- factor(cal_summary_data_cgt$attribute,levels = c("Kalzium Day1","Kalzium Day4","Kalzium Day10"))

##for boxplt change last data##
libucal_data_cgt$attribute <- factor(libucal_data_cgt$attribute,levels = c("Kalzium Day1","Kalzium Day4","Kalzium Day10"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
cal_summary_data_cgt <- lparacal_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- 10#max(cal_summary_data_cgt$mean_labread + cal_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(cal_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean calcium in time course for female with patient count",
       x = "Day of measurement",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(cal_summary_data_cgt$mean_labread + cal_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparacal_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for calcium by day of measurement",
       x = "day of measurement",
       y = "Calcium mmol/l") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

######################################################################
###Glucose###
### labels##
## run the second code before the firste one, change the names an run the first, then run the second again an the x-axis will be in the correct order###
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
leukozyten_summary_data_cgt$Attribute <- factor(leukozyten_summary_data_cgt$Attribute,levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))

##for boxplt change last data##
ldleukozyten_data_cgt$Attribute <- factor(ldleukozyten_data_cgt$Attribute,levels = c("Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3", "Leukozyten Day4", "Leukozyten Day5", "Leukozyten Day9", "Leukozyten Day12", "Leukozyten Day_Unknown"))
```

## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
## when the description of the x-axis ist not readable, adjust the scale by changing the "by=100" to a higher number in the "breaks_up_to_500" line##
```{r}
glu_summary_data_cgt <- lparaglu_data_cgt  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n()),
    count = n()  # Add counts           ####NEW#####
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(glu_summary_data_cgt$mean_labread + glu_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 100) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(glu_summary_data_cgt, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  geom_text(aes(label = count), vjust = -1.5, size = 5) +  # Add counts as text labels    ####NEW####
  labs(title = "liver_para_cgt mean glucose in time course for female with patient count",
       x = "Day of measurement",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####
```{r}

library(ggplot2)
library(dplyr)

max_value <- max(glu_summary_data_cgt$mean_labread + glu_summary_data_cgt$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
lparaglu_data_cgt %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  ggplot(aes(x = attribute, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+        				####NEW#####
  labs(title = "liver_para_cgt boxplot for glucose by day of measurement",
       x = "day of measurement",
       y = "Glucose mg/dl") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```






























































































































































