---
title: "Untitled"
output: html_document
date: "2026-05-24"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(ggprism)
```

```{r}


# ══════════════════════════════════════════════════════════════════════════════
# 1. Data Preparation — CK panel
#    Adjust column names to match your actual data
# ══════════════════════════════════════════════════════════════════════════════

# ck_data <- all_data %>%
#   left_join(
#     diabetic_data,
#     by           = "bf_ar_m_nummer",
#     relationship = "many-to-many"
#   ) %>%
#   left_join(
#     gender_data1,
#     by           = "bf_ar_m_nummer",
#     relationship = "many-to-many"
#   ) %>%
#   filter(panel_id == "ck") %>%
#   filter(grepl("Leber_", treatment.x)) %>%
#   filter(!is.na(diabetes), !is.na(treatment.x)) %>% 
#   mutate(treatment.x = recode(treatment.x,
#     "Leber_Diclo" = "Liver_Diclo", # Note: Check capitalization of your raw data here!
#     "Leber_Ibu"   = "Liver_Ibu",
#     "Leber_Para"  = "Liver_Para"
#   )) %>% 
#   mutate(treatment.x = factor(treatment.x,
#     # Use the NEW recoded names for your factor levels
#     levels = c("Liver_Diclo", "Liver_Ibu", "Liver_Para") 
#   ),
#   diabetes = factor(diabetes),
#   gender = factor(gender)) %>%
#   filter(labreads < 15000) %>%
#   drop_na(labreads, treatment.x, diabetes)


# ══════════════════════════════════════════════════════════════════════════════
# 2. Helper: label data frames  (unchanged from yours)
# ══════════════════════════════════════════════════════════════════════════════

# make_label_dfs <- function(data, group_var, patient_id_var) {
#   label_df <- data %>%
#     group_by({{ group_var }}) %>%
#     summarise(
#       n_patients = n_distinct({{ patient_id_var }}),
#       n_labreads = n(),
#       .groups    = "drop"
#     )
#   
#   list(
#     bottom  = mutate(label_df, label = paste0("N = ", n_patients)),
#     top = mutate(label_df, label = paste0("n = ", n_labreads))
#   )
# }
# 
# 
# # ══════════════════════════════════════════════════════════════════════════════
# # 3. Main plot function  (your original, lightly hardened)
# # ══════════════════════════════════════════════════════════════════════════════
# 
# plot_lab_comparison <- function(
#     data,
#     group_var,
#     y_var,
#     patient_id_var,
#     comparisons,
#     plot_title   = "Comparison of Lab Values",
#     x_label      = NULL,
#     y_label      = "Lab Value",
#     jitter_width = 0.20,
#     jitter_alpha = 0.5,
#     jitter_size  = 5,
#     text_size    = 8,
#     n_breaks     = 7
# ) {
#   group_col <- deparse(substitute(group_var))
#   y_col     <- deparse(substitute(y_var))
#   id_col    <- deparse(substitute(patient_id_var))
#   
#   missing_cols <- setdiff(c(group_col, y_col, id_col), names(data))
#   if (length(missing_cols) > 0)
#     stop("Column(s) not found: ", paste(missing_cols, collapse = ", "))
#   
#   if (!is.numeric(data[[y_col]])) {
#     message("Converting '", y_col, "' to numeric.")
#     data[[y_col]] <- as.numeric(data[[y_col]])
#   }
#   if (all(is.na(data[[y_col]])))
#     stop("'", y_col, "' is all NA after conversion.")
#   
#   labels          <- make_label_dfs(data, {{ group_var }}, {{ patient_id_var }})
#   label_df_top    <- labels$top
#   label_df_bottom <- labels$bottom
#   
#   # ---------------------------------------------------------
#   # 👇 NEW: Create a named vector to replace X-axis labels
#   # Example: "Liver_Diclo" becomes "Liver_Diclo\nN = 13"
#   # ---------------------------------------------------------
#   custom_x_labels <- setNames(
#     paste0(label_df_bottom[[group_col]], "\n", label_df_bottom$label),
#     label_df_bottom[[group_col]]
#   )
#   
#   y_max    <- max(data[[y_col]], na.rm = TRUE)
#   
#   # Note: I reduced these multipliers slightly so your data doesn't 
#   # look as squished at the bottom!
#   y_top    <- y_max * 1.50  
#   
#   ggplot(data,
#          aes(x    = .data[[group_col]],
#              y    = .data[[y_col]],
#              fill = .data[[group_col]])) +
#     
#     geom_boxplot(width = 0.20, outlier.shape = NA, alpha = 0.5, color = "black") +
#     
#     geom_jitter(width = jitter_width, alpha = jitter_alpha,
#                 size  = jitter_size,  color = "#CC79A7") +
#     
#     stat_summary(fun = median, geom = "point",
#                  shape = 23, size = 4, fill = "brown") +
#     
#     geom_text(data = label_df_top,
#               aes(x = .data[[group_col]], y = y_top, label = label),
#               inherit.aes = FALSE, fontface = "bold", size = text_size) +
#     
#     # ---------------------------------------------------------
#     # 👇 REMOVED: geom_text for label_df_bottom
#     # (We no longer need it because of the scale_x_discrete fix below)
#     # ---------------------------------------------------------
#     
#     stat_compare_means(
#       comparisons  = comparisons,
#       method       = "wilcox.test",
#       label        = "p.format",
#       # 👇 Note: I lowered these slightly so the brackets are closer to the data
#       label.y      = c(y_max * 1.05, y_max * 1.20, y_max * 1.35),
#       bracket.size = 1,
#       tip.length   = 0.02,
#       size         = text_size
#     ) +
#     
#     labs(title = plot_title, x = NULL, y = y_label) +
#     
#     # 👇 Lowered the top limit to match the new bracket heights
#     coord_cartesian(ylim = c(0, y_max * 1.60), clip = "off") + 
#     scale_y_continuous(breaks = scales::breaks_pretty(n = n_breaks)) +
#     
#     # ---------------------------------------------------------
#     # 👇 NEW: Apply the custom labels to the X-axis
#     # ---------------------------------------------------------
#     scale_x_discrete(labels = custom_x_labels) +
#     
#     theme_prism() +
#       theme(
#         axis.text.x  = element_text(
#           size = 24, family = "sans", face = "bold",  angle = 0, 
#           hjust = 0.5, vjust = 1,
#           margin = margin(t = 4)  
#         ),
#         axis.text.y = element_text(size = 24, family = "sans", face = "bold"),
#         plot.title.position = "plot",
#         plot.title = element_text(size = 30, hjust = 0.5),
#         axis.title.y = element_text(size = 24, family = "sans", face = "bold"),
#         axis.title.x = element_text(size = 24, family = "sans", face = "bold", 
#                                     margin = margin(t = 12)),
#         legend.position = "none",
#         plot.margin = margin(t = 30, r = 10, b = 30, l = 10)  
#       )
# }
    
    # theme_classic() +
    # theme(
    #   legend.position = "none",
    #   plot.title      = element_text(hjust = 0.5, size = 28, face = "bold",
    #                                  margin = margin(b = 10), lineheight = 1.2),
    #   axis.text.x     = element_text(size = 24, face = "bold"),
    #   axis.text.y     = element_text(size = 24, face = "bold"),
    #   axis.title      = element_text(size = 20, face = "bold"),
    #   axis.line       = element_line(linewidth = 0.5),
    #   plot.margin     = margin(t = 30, r = 30, b = 40, l = 20)
    # )
    


# ══════════════════════════════════════════════════════════════════════════════
# 4. Build comparisons dynamically from factor levels
#    — avoids hardcoding group pairs
# ══════════════════════════════════════════════════════════════════════════════

# make_comparisons <- function(data, group_col) {
#   lvls <- levels(factor(data[[group_col]]))
#   utils::combn(lvls, 2, simplify = FALSE)
# }


```

```{r}
# # ══════════════════════════════════════════════════════════════════════════════
# # Function to Loop, Plot, and Save Multiple Panels
# # ══════════════════════════════════════════════════════════════════════════════
# 
# generate_and_save_panel_plots <- function(
#     panel_ids,
#     all_data,
#     diabetic_data,
#     gender_data,
# 
#     # Export options
#     save_plots_flag     = TRUE,
#     export_dataset_name = "lab_plots",
#     export_base_dir     = "output",
#     export_subfolder    = "panel_comparisons",
#     export_width        = 12,
#     export_height       = 10,
#     export_dpi          = 600,
#     export_formats      = c("svg", "png")
# ) {
# 
#   # Initialize lists to hold the generated plots and their filenames
#   plots_list <- list()
#   plot_names <- c()
# 
#   for (pid in panel_ids) {
# 
#     # 1. Data Preparation (Dynamic filtering based on 'pid')
#     panel_data <-
```

```{r}
# all_data %>%
#       left_join(
#         diabetic_data,
#         by           = "bf_ar_m_nummer",
#         relationship = "many-to-many"
#       ) %>%
#       left_join(
#         gender_data,
#         by           = "bf_ar_m_nummer",
#         relationship = "many-to-many"
#       )
```

```{r}
# ══════════════════════════════════════════════════════════════════════════════
# Function to Loop, Plot, and Save Multiple Panels 
# ══════════════════════════════════════════════════════════════════════════════

# generate_and_save_panel_plots_liver <- function(
#     panel_ids,
#     all_data,
#     diabetic_data,
#     gender_data,
#     
#     # Export options
#     save_plots_flag     = TRUE,
#     export_dataset_name = "lab_plots",
#     export_base_dir     = "output",
#     export_subfolder    = "panel_comparisons",
#     export_width        = 12,
#     export_height       = 10,
#     export_dpi          = 600,
#     export_formats      = c("svg", "png")
# ) {
#   
#   # Dictionary mapping raw panel IDs to their display units
#   unit_map <- c(
#     # (Keep your existing unit_map here - shortened for readability)
#     "ck" = "CK (U/L)", "got" = "AST/GOT (U/L)", "gpt" = "ALT/GPT (U/L)", 
#     "ggt" = "GGT (U/L)", "ldh" = "LDH (U/L)", "crp" = "CRP (mg/L)" # ... add the rest back in
#   )
#   
#   plots_list <- list()
#   plot_names <- c()
#   
#   for (pid in panel_ids) {
#     
#     # 1. Data Preparation
#     panel_data <- all_data %>%
#       left_join(
#         diabetic_data,
#         by           = "bf_ar_m_nummer",
#         relationship = "many-to-many"
#       ) %>%
#       left_join(
#         gender_data,
#         by           = c("bf_ar_m_nummer", "treatment"),
#         relationship = "many-to-many"
#       ) %>%
#       filter(panel_id == pid) %>%
#       filter(grepl("Leber_", treatment)) %>%
#       filter(!is.na(diabetes), !is.na(treatment)) %>% 
#       mutate(treatment = recode(treatment,
#                                 "Leber_Diclo" = "Liver_Diclo", 
#                                 "Leber_Ibu"   = "Liver_Ibu",
#                                 "Leber_Para"  = "Liver_Para"
#       )) %>% 
#       mutate(
#         treatment = factor(treatment, levels = c("Liver_Diclo", "Liver_Ibu", "Liver_Para")),
#         diabetes  = factor(diabetes),
#         gender    = factor(gender)
#       ) %>%
#       filter(labreads < 15000) %>%
#       drop_na(labreads, diabetes)
#     
#     # ---------------------------------------------------------
#     # 👇 NEW SAFETY CHECKS
#     # ---------------------------------------------------------
#     
#     # Check 1: Did the filtering remove ALL rows?
#     if (nrow(panel_data) == 0) {
#       message(paste("Skipping", toupper(pid), "- No data available after filtering."))
#       next
#     }
#     
#     # Check 2: Do we have at least 2 distinct diabetes groups to compare?
#     num_groups <- length(unique(panel_data$diabetes))
#     if (num_groups < 2) {
#       message(paste("Skipping", toupper(pid), "- Only 1 diabetes group present (cannot run Wilcoxon test)."))
#       next
#     }
#     
#     # ---------------------------------------------------------
#     
#     # 2. Dynamic Plot Titles and Labels
#     plot_title <- paste(toupper(pid), "Levels by Diabetes Status")
#     y_label    <- if (pid %in% names(unit_map)) unit_map[[pid]] else toupper(pid)
#     
#     # 3. Generate the Plot 
#     p <- plot_lab_comparison(
#       data           = panel_data,
#       group_var      = diabetes,                       
#       y_var          = labreads,
#       patient_id_var = bf_ar_m_nummer,
#       comparisons    = make_comparisons(panel_data, "diabetes"), 
#       plot_title     = plot_title,
#       x_label        = "Diabetes Status",              
#       y_label        = y_label
#     )
#     
#     # 4. Store the plot
#     plots_list[[length(plots_list) + 1]] <- p
#     plot_names <- c(plot_names, paste0("Plot_", toupper(pid), "_Diabetes"))
#     
#     message(paste("Successfully generated plot for:", toupper(pid)))
#   }
#   
#   # 5. Save the plots
#   if (save_plots_flag && length(plots_list) > 0) {
#     message("\nSaving generated plots...")
#     save_plots( # Assuming you have a custom save_plots function defined
#       plots        = plots_list,
#       names        = plot_names,
#       dataset_name = export_dataset_name,
#       base_dir     = export_base_dir,
#       subfolder    = export_subfolder,
#       width        = export_width,
#       height       = export_height,
#       dpi          = export_dpi,
#       formats      = export_formats
#     )
#   }
#   
#   names(plots_list) <- plot_names
#   return(plots_list)
# }
# 
# # ══════════════════════════════════════════════════════════════════════════════
# # Helper: Build comparisons dynamically from factor levels
# # ══════════════════════════════════════════════════════════════════════════════
# 
# make_comparisons <- function(data, group_col) {
#   lvls <- levels(factor(data[[group_col]]))
#   utils::combn(lvls, 2, simplify = FALSE)
# }


```

```{r}
# Define the panels you want to loop through
# my_panels <- c("got")
# 
# # Run the loop, store the results, and save them automatically
# all_liver_plots <- generate_and_save_panel_plots(
#   panel_ids     = my_panels,
#   all_data      = all_data,          # Your raw long-format data
#   diabetic_data = diabetic_data,     # Your diabetes meta-data
#   gender_data   = gender_data1,      # Your gender meta-data
#   
#   save_plots_flag  = TRUE,
#   export_subfolder = "figure/diabetes/plots_all_labvalues/liver_treatments"
# )
# 
# # You can still view a specific plot in RStudio after the loop finishes:
#  all_liver_plots$Plot_GOT
```

```{r}
# # 1. Define your list of panels (using a few from your large list as an example)
# my_panels <- c("got", "gpt", "ggt", "bilirubin", "crp", "leukozyten", "glucose")
# 
# # 2. Call the function and store the resulting plots in a list
# diabetes_liver_plots <- generate_diabetes_plots_for_liver(
#   panel_ids     = my_panels,
#   all_data      = all_data,       # Your main dataset with 'bf_ar_m_nummer', 'panel_id', 'labreads', 'treatment.x'
#   diabetic_data = diabetic_data,  # Your dataset with 'bf_ar_m_nummer' and 'diabetes' (0/1 or similar)
#   gender_data1   = gender_data1,    # Your dataset with 'bf_ar_m_nummer' and 'gender'
#   
#   # Optional: Customize your export settings here
#   save_plots_flag     = TRUE,
#   export_dataset_name = "liver_cohort",
#   export_subfolder    = "diabetes_comparisons"
# )
# 
# # 3. View a specific plot right in your RStudio viewer!
# # (Replace "Plot_Diabetes_GOT" with whichever panel you want to see)
# print(diabetes_liver_plots[["Plot_Diabetes_GOT"]])
```

```{r}
# 1. Define the lab panels you want to plot 
# (You can pass your full list of 79 panels here, or just a few to test)
# target_panels <- c("ck", "got", "gpt", "crp", "leukozyten", "kreatinin") 
# 
# # 2. Call the master function
# liver_diabetes_plots <- generate_and_save_panel_plots_diabetes_liver(
#   panel_ids        = target_panels,
#   all_data         = all_data,         # Your main lab reads dataframe
#   diabetic_data    = diabetic_data,    # Dataframe with bf_ar_m_nummer & diabetes status
#   gender_data1      = gender_data1,      # Dataframe with bf_ar_m_nummer & treatment
#   
#   # Optional: Adjust your export settings
#   save_plots_flag  = TRUE,
#   export_subfolder = "figure/liver_cohort/diabetes_comparisons" 
# )

# 3. (Optional) If you want to view a specific plot immediately in RStudio:
# print(liver_diabetes_plots[["Plot_CK_Diabetes_LiverCohort"]])
```

##==============================
## diabetes_nondiabets(gender)
##==============================

```{r}
# ══════════════════════════════════════════════════════════════════════════════
# Helper Function: Generate N and n labels for 3-way faceted plots
# ══════════════════════════════════════════════════════════════════════════════

# make_label_dfs_3way <- function(data, group_col, fill_col, facet_col, id_col) {
#   
#   library(dplyr)
#   
#   # Convert string column names to symbols for dplyr evaluation
#   group_sym <- sym(group_col)
#   fill_sym  <- sym(fill_col)
#   facet_sym <- sym(facet_col)
#   id_sym    <- sym(id_col)
#   
#   # 1. Top Label: Count UNIQUE patients (N=)
#   df_top <- data %>%
#     group_by(!!facet_sym, !!group_sym, !!fill_sym) %>%
#     summarise(
#       unique_patients = n_distinct(!!id_sym),
#       .groups = "drop"
#     ) %>%
#     mutate(label = paste0("N = ", unique_patients)) %>%
#     select(-unique_patients)
#   
#   # 2. Bottom Label: Count TOTAL lab readings (n=)
#   df_bottom <- data %>%
#     group_by(!!facet_sym, !!group_sym, !!fill_sym) %>%
#     summarise(
#       total_reads = n(),
#       .groups = "drop"
#     ) %>%
#     mutate(label = paste0("n = ", total_reads)) %>%
#     select(-total_reads)
#   
#   # Return as a list containing both dataframes
#   return(list(top = df_top, bottom = df_bottom))
# }
# ```
# 
# 
# ```{r}
# # ══════════════════════════════════════════════════════════════════════════════
# # Master Loop Function: (Powered by User's Validated Join Logic)
# # ══════════════════════════════════════════════════════════════════════════════
# 
# generate_6boxplot_panel_runs <- function(
#     panel_ids, all_data, diabetic_data, gender_data,
#     save_plots_flag = TRUE, export_dataset_name = "six_boxplot_profiles",
#     export_base_dir = "output", export_subfolder = "treatment_gender_by_diabetes",
#     export_width = 12, export_height = 10, export_dpi = 600, export_formats = c("svg", "png")
# ) {
#   
#   unit_map <- c("ck" = "CK (U/L)", "gpt" = "ALT/GPT (U/L)", "ggt" = "GGT (U/L)") # Add full map here
#   
#   plots_list <- list()
#   plot_names <- c()
#   
#   for (pid in panel_ids) {
#     
#     # ── YOUR EXACT DATA PREP LOGIC ──
#     panel_data <- all_data %>%
#       left_join(diabetic_data, by = "bf_ar_m_nummer", relationship = "many-to-many") %>%
#       left_join(gender_data, by = "bf_ar_m_nummer", relationship = "many-to-many") %>%
#       dplyr::filter(panel_id == pid) %>%
#       dplyr::filter(grepl("Leber_", treatment.x)) %>%
#       # Added bf_ar_m_nummer here so the plotting function can count unique patients (N=)
#       dplyr::select(bf_ar_m_nummer, panel_id, labreads, diabetes, treatment.x, gender) %>%
#       dplyr::rename("treatment" = "treatment.x") %>%
#       drop_na() %>%
#       mutate(
#         # Matched the exact case-sensitive spelling from your test plot
#         treatment = factor(treatment, levels = c("Leber_Diclo", "Leber_Ibu", "Leber_Para")),
#         gender    = factor(gender, levels = c("Male", "Female")),
#         diabetes_status = factor(
#           ifelse(diabetes %in% c(1, "1", "Diabetic", "Yes"), "Diabetic", "Non_Diabetic"), 
#           levels = c("Non_Diabetic", "Diabetic")
#         )
#       ) %>%
#       filter(labreads < 15000)
#     
#     if (nrow(panel_data) == 0) {
#       message(paste("Skipping", toupper(pid), "- No data available."))
#       next
#     }
#     
#     plot_title <- paste(toupper(pid), "Levels across Treatments & Gender\n(Faceted by Diabetes Status)")
#     y_label    <- if (pid %in% names(unit_map)) unit_map[[pid]] else toupper(pid)
#     
#     p <- plot_lab_6box_layout(
#       data           = panel_data,
#       group_var      = treatment,       
#       fill_var       = gender,          
#       facet_var      = diabetes_status, 
#       y_var          = labreads,        
#       patient_id_var = bf_ar_m_nummer,
#       plot_title     = plot_title,
#       y_label        = y_label
#     )
#     
#     plots_list[[length(plots_list) + 1]] <- p
#     plot_names <- c(plot_names, paste0("Plot_", toupper(pid), "_Treatment_Gender_6Box"))
#   }
#   
#   if (save_plots_flag && length(plots_list) > 0) {
#     save_plots(plots = plots_list, names = plot_names, dataset_name = export_dataset_name, base_dir = export_base_dir, subfolder = export_subfolder, width = export_width, height = export_height, dpi = export_dpi, formats = export_formats)
#   }
#   
#   names(plots_list) <- plot_names
#   return(plots_list)
# }
```

```{r}
# ══════════════════════════════════════════════════════════════════════════════
# Main: Plot 6 Boxplots (Uncrowded Labels - N at Bottom)
# ══════════════════════════════════════════════════════════════════════════════

# plot_lab_6box_layout <- function(
#     data, group_var, fill_var, facet_var, y_var, patient_id_var,  
#     plot_title = "Comparison of Lab Values", y_label = "Lab Value",
#     text_size = 5, n_breaks = 10
# ) {
#   
#   library(ggplot2)
#   library(dplyr)
#   library(ggpubr)
#   library(scales)
#   
#   group_col <- as.character(substitute(group_var))
#   fill_col  <- as.character(substitute(fill_var))
#   facet_col <- as.character(substitute(facet_var))
#   y_col     <- as.character(substitute(y_var))
#   id_col    <- as.character(substitute(patient_id_var))
#   
#   if (!is.numeric(data[[y_col]])) data[[y_col]] <- as.numeric(data[[y_col]])
#   
#   # Clean up "Leber_" prefix and map exact spelling
#   data[[group_col]] <- factor(gsub("Leber_", "", as.character(data[[group_col]])),
#                               levels = c("Diclo", "Ibu", "Para"))
#   
#   # Generate labels
#   labels          <- make_label_dfs_3way(data, group_col, fill_col, facet_col, id_col)
#   label_df_top    <- labels$top      # Contains N = (Unique Patients)
#   label_df_bottom <- labels$bottom   # Contains n = (Total Reads)
#   
#   y_max <- max(data[[y_col]], na.rm = TRUE)
# 
#   p <- ggplot(data, aes(x = .data[[group_col]], y = .data[[y_col]], fill = .data[[fill_col]])) +
#     geom_boxplot(width = 0.6, outlier.shape = NA, alpha = 0.6, color = "black", position = position_dodge(0.75)) +
#     geom_jitter(aes(color = .data[[fill_col]]), alpha = 0.35, size = 1.2, position = position_jitterdodge(jitter.width = 0.15, dodge.width = 0.75)) +
#     stat_summary(fun = median, geom = "point", shape = 23, size = 2, fill = "brown", position = position_dodge(0.75)) +
#     
#     # ── FIX 1: Plot 'n' (Total Reads) just above the boxes ──
#     geom_text(data = label_df_bottom, aes(x = .data[[group_col]], y = y_max * 1.05, label = paste0("(", label, ")"), group = .data[[fill_col]]), 
#               inherit.aes = FALSE, fontface = "bold", size = text_size * 0.85, position = position_dodge(0.75), vjust = 0) +
#     
#     # ── FIX 2: Plot P-Values higher up so they don't crash into 'n' ──
#     stat_compare_means(aes(group = .data[[fill_col]]), method = "wilcox.test", label = "p.format", 
#                        label.y = y_max * 1.22, bracket.size = 0.6, tip.length = 0.01, size = text_size * 0.9) +
#                        
#     # ── FIX 3: Plot 'N' (Unique Patients) DOWN below the x-axis line ──
#     geom_text(data = label_df_top, aes(x = .data[[group_col]], y = -(y_max * 0.08), label = label, group = .data[[fill_col]]), 
#               inherit.aes = FALSE, fontface = "bold", size = text_size * 0.85, position = position_dodge(0.75), vjust = 1, color = "grey30") +
#     
#     facet_wrap(vars(!!sym(facet_col)), scales = "fixed", drop = FALSE) + 
#     labs(title = plot_title, x = "Liver Treatment", y = y_label, fill = "Gender", color = "Gender") +
#     
#     # ── FIX 4: Expand coordinates to allow drawing below 0 ──
#     coord_cartesian(ylim = c(0, y_max * 1.35), clip = "off") +
#     scale_y_continuous(breaks = scales::breaks_pretty(n = n_breaks)) +
#     scale_x_discrete(drop = FALSE) + 
#     scale_fill_manual(values = c("Male" = "#56B4E9", "Female" = "#CC79A7"), drop = FALSE) +
#     scale_color_manual(values = c("Male" = "#56B4E9", "Female" = "#CC79A7"), drop = FALSE) +
#     theme_prism() +
#     theme(
#       legend.position = "bottom", 
#       legend.text = element_text(size = 16, face = "bold"), 
#       legend.title = element_text(size = 16, face = "bold"),
#       plot.title = element_text(hjust = 0.5, size = 24, face = "bold", margin = margin(b = 15)),
#       strip.text = element_text(size = 22, face = "bold"), 
#       strip.background = element_rect(fill = "gray95", color = "black", linewidth = 0.5),
#       # Pushed the main X-axis labels down slightly to clear the N labels
#       axis.text.x = element_text(size = 18, face = "bold", margin = margin(t = 20)), 
#       axis.text.y = element_text(size = 20, face = "bold"),
#       axis.title = element_text(size = 18, face = "bold"), 
#       axis.line = element_line(linewidth = 0.5),
#       panel.spacing = unit(3, "lines"), 
#       # ── FIX 5: Increased bottom margin (b=65) so N doesn't get cut off ──
#       plot.margin = margin(t = 15, r = 30, b = 65, l = 20) 
#     )
#   
#   return(p)
# }
```

```{r}
# ══════════════════════════════════════════════════════════════════════════════
# RUN SCRIPT: Execute the Plotting Pipeline
# ══════════════════════════════════════════════════════════════════════════════

# 1. Define the specific labs you want to plot 
# (Make sure these match the panel_id strings in your all_data dataframe)
# target_labs <- c("gpt", "ggt", "ck") 
# 
# # 2. Call the master function
# # Note: I am passing 'gender_data1' here since that is what you used in your test!
# final_plots <- generate_6boxplot_panel_runs(
#   panel_ids           = target_labs,
#   all_data            = all_data,
#   diabetic_data       = diabetic_data,
#   gender_data         = gender_data1,       
#   
#   # Export Settings
#   save_plots_flag     = TRUE,
#   export_dataset_name = "Liver_Cohort_Analysis",
#   #export_base_dir     = "output",
#   #export_subfolder    = "treatment_comparisons/6Box_Layouts",
#   export_width        = 16, 
#   export_height       = 11,
#   export_dpi          = 600,
#   export_formats      = c("svg", "png") # Exporting as JPG/PNG based on your uploads
# )
# 
# # ══════════════════════════════════════════════════════════════════════════════
# # VIEW RESULTS IN RSTUDIO
# # ══════════════════════════════════════════════════════════════════════════════
# 
# # The function returns a list of the generated plots. 
# # You can view them directly in your RStudio viewer by calling them by name:
# 
# if ("Plot_GPT_Treatment_Gender_6Box" %in% names(final_plots)) {
#   print(final_plots[["Plot_GPT_Treatment_Gender_6Box"]])
# }
# 
# if ("Plot_GGT_Treatment_Gender_6Box" %in% names(final_plots)) {
#   print(final_plots[["Plot_GGT_Treatment_Gender_6Box"]])
# }
```

```{r}
# library(ggplot2)
# library(dplyr)
# library(tidyr)
# 
# # Run your quick PNG test with fixed aesthetics, legend, and aligned jitter
# all_data %>%
#   left_join(
#     diabetic_data,
#     by           = "bf_ar_m_nummer",
#     relationship = "many-to-many"
#   ) %>%
#   left_join(
#     gender_data1,
#     by           = "bf_ar_m_nummer",
#     relationship = "many-to-many"
#   ) %>% 
#   dplyr::filter(panel_id == "gpt") %>% 
#   dplyr::filter(grepl("Leber_", treatment.x)) %>% 
#   dplyr::select(panel_id, labreads, diabetes, treatment.x, gender) %>% 
#   dplyr::rename("treatment" = "treatment.x") %>% 
#   drop_na() %>% 
#   mutate(
#     diabetes  = factor(ifelse(diabetes %in% c(1, "1", "Diabetic", "Yes"), "Diabetic", "Non_Diabetic")),
#     treatment = factor(gsub("Leber_", "", as.character(treatment)), levels = c("Diclo", "Ibu", "Para")), 
#     gender    = factor(gender)
#   ) %>% 
#   
#   ggplot(aes(x = treatment, y = labreads, fill = gender)) + 
#   
#   # 1. Main Boxplot Layer (Matches width and dodging metrics)
#   geom_boxplot(width = 0.50, color = "black", linewidth = 0.35, 
#                outlier.shape = NA, alpha = 0.6,
#                position = position_dodge(0.60)) +
#   
#   # 2. Correct Jitter Layer: Uses position_jitterdodge to align dots inside their boxes
#   geom_jitter(aes(color = gender), alpha = 0.35, size = 1.2, 
#               position = position_jitterdodge(jitter.width = 0.12, 
#                                               dodge.width = 0.80)) +
#   
#   facet_wrap(~diabetes) +
#   
#   # 3. Explicit Color Palettes (Ensures matching tones across bars & dots)
#   scale_fill_manual(values = c("Male" = "#56B4E9", "Female" = "#CC79A7")) +
#   scale_color_manual(values = c("Male" = "#56B4E9", "Female" = "#CC79A7")) +
#   
#   theme_classic() +
#   theme(
#     # Lowered font sizes so they match a 10x6 inch canvas
#     text = element_text(family = "sans"),
#     axis.text = element_text(size = 15,face = "bold"),
#     axis.title = element_text(size = 18,face = "bold"),
#     axis.line = element_line(linewidth = 0.9),
#     axis.ticks = element_line(linewidth = 0.8),
#     strip.text = element_text(size = 16, face = "bold"), # Controls facet header size
#     legend.text = element_text(size = 18, margin = margin(l = 3)),
#     legend.key.height = unit(20, "pt"),
#     legend.key.width = unit(25, "pt"),
#     legend.position = "inside",
#     legend.position.inside = c(0.17, 0.85), # Slightly adjusted to clear text
#     legend.background = element_blank(),
#     legend.key.justification = "top",
#     legend.title = element_text(size = 18, face = "bold")
#   )
# 
# # SAVE IN INCHES: This expands the canvas size so the text doesn't overlap
# ggsave("fig_diabetic_comparison6.png", width = 5, height = 4, units = "in", dpi = 600)


```

##=============================================
## Flupritin data Read
##============================================

```{r}
flupirtin_data <- read_excel(here::here("Rawdata/flupirtin dosedata.xlsx"), sheet = 3) %>% 
  janitor::clean_names() %>% 
  dplyr::rename(bf_ar_m_nummer = edited_bf_ar_m_nummer2) %>% 
  drop_na()
flupirtin_data
```

```{r}
all_data %>%
      left_join(flupirtin_data,
                by = join_by("bf_ar_m_nummer","treatment"),
                relationship = "many-to-many") %>%
      filter(
        panel_id == "gpt",
        treatment == "Leber_Diclo"
      ) %>%
      filter(
        !str_detect(attribute, "_from_start|dbs")
      ) %>%
      drop_na(labreads, flupirtin, bf_ar_m_nummer) %>%
      mutate(
        flupirtin = case_when(
          flupirtin %in% c("Yes", "Flupirtin", "flupirtin", 1) ~ "Flupirtin",
          TRUE ~ "No_Flupirtin"
        ),
        flupirtin = factor(
          flupirtin,
          levels = c("No_Flupirtin", "Flupirtin")
        )
      )
```

```{r}
library(dplyr)
library(tidyr)

cleaned_dataset <- 
all_data %>%
  # 1. Initial Cohort Merges
  left_join(
    diabetic_data,
    by           = "bf_ar_m_nummer",
    relationship = "many-to-many"
  ) %>%
  left_join(
    gender_data1,
    by           = c("bf_ar_m_nummer", "treatment"),
    relationship = "many-to-many"
  ) %>%
  left_join(
    flupirtin_data,
    by           = c("bf_ar_m_nummer", "treatment"),
    relationship = "many-to-many"
  ) %>% 
  dplyr::select(-any_of(c("value", "day_raw"))) %>% 
  dplyr::filter(panel_id == "gpt") %>% 
  dplyr::filter(grepl("Leber_", treatment)) %>% 
  drop_na(treatment, diabetes, gender, flupirtin, days, labreads) %>%
  mutate(
      treatment = factor(gsub("Leber_", "", as.character(treatment)), 
                         levels = c("Diclo", "Ibu", "Para")),
      diabetes  = factor(ifelse(diabetes %in% c( "Diabetic", "Yes"), "Diabetic", "Non_Diabetic"),
                       levels = c("Non_Diabetic", "Diabetic")),
      gender    = factor(gender, levels = c("Male", "Female")),
      flupirtin = factor(ifelse(flupirtin %in% c("flupirtin", "Yes"), "Flupirtin", "No_Flupirtin"),
                       levels = c("No_Flupirtin", "Flupirtin")),
      days      = factor(days, levels = sort(unique(as.numeric(as.character(days)))))
  )
cleaned_dataset
```


```{r}
cleaned_dataset %>% 
  dplyr::filter(kathegorie == "Leber_Diclo")
```



##================================================================
##  liver cases with flupirtin in unique patients.
##================================================================


```{r}
all_data %>%
  left_join(diabetic_data, 
            by = join_by("bf_ar_m_nummer","treatment"), 
            relationship = "many-to-many") %>%
  left_join(flupirtin_data, 
           by = join_by("bf_ar_m_nummer","treatment"), 
           relationship = "many-to-many") %>%
  #dplyr::filter(panel_id == "gpt") %>%
  dplyr::filter(grepl("Leber_", treatment)) %>%
  #dplyr::filter(diabetes %in% c("Diabetic", "Yes", 1, "1")) %>%
  group_by(treatment, flupirtin) %>%
  summarise(total_rows = n(), unique_patients = n_distinct(bf_ar_m_nummer), .groups = "drop")
```


################################ Univeral flupritin peak ##################

```{r}
# library(ggplot2)
# library(dplyr)
# library(ggpubr)
# library(stringr)
# 
# # ==========================================
# # 1. PLOT FUNCTION (WITH UNIT MAPPING)
# # ==========================================
# plot_flupirtin_comparison <- function(
#     data,
#     group_var,
#     y_var,
#     patient_id_var,
#     panel_id,
#     unit_map,
#     plot_title = "",
#     text_size = 4
# ) {
# 
#   group_col <- deparse(substitute(group_var))
#   y_col     <- deparse(substitute(y_var))
#   id_col    <- deparse(substitute(patient_id_var))
# 
#   # ------------------------------
#   # y-axis label from unit_map
#   # ------------------------------
#   y_label <- if (panel_id %in% names(unit_map)) {
#     unit_map[[panel_id]]
#   } else {
#     toupper(panel_id)
#   }
# 
#   # ------------------------------
#   # Unique patients (N)
#   # ------------------------------
#   df_top <- data %>%
#     group_by(.data[[group_col]]) %>%
#     summarise(
#       unique_patients = n_distinct(.data[[id_col]]),
#       .groups = "drop"
#     ) %>%
#     mutate(label = paste0("N=", unique_patients))
# 
#   # ------------------------------
#   # Total observations (n)
#   # ------------------------------
#   df_bottom <- data %>%
#     group_by(.data[[group_col]]) %>%
#     summarise(
#       total_reads = n(),
#       .groups = "drop"
#     ) %>%
#     mutate(label = paste0("n=", total_reads))
# 
#   y_max <- max(data[[y_col]], na.rm = TRUE)
# 
#   p <- ggplot(
#     data,
#     aes(
#       x = .data[[group_col]],
#       y = .data[[y_col]],
#       fill = .data[[group_col]]
#     )
#   ) +
# 
#     geom_violin(
#       trim = TRUE,
#       alpha = 0.35,
#       colour = "black",
#       linewidth = 0.3
#     ) +
# 
#     geom_boxplot(
#       width = 0.15,
#       alpha = 0.7,
#       outlier.shape = NA,
#       linewidth = 0.3
#     ) +
# 
#     geom_jitter(
#       width = 0.08,
#       alpha = 0.4,
#       size = 1.5
#     ) +
# 
#     stat_summary(
#       fun = median,
#       geom = "point",
#       shape = 23,
#       size = 2.5,
#       fill = "brown"
#     ) +
# 
#     geom_text(
#       data = df_bottom,
#       aes(
#         x = .data[[group_col]],
#         y = y_max * 1.10,
#         label = label
#       ),
#       inherit.aes = FALSE,
#       fontface = "bold",
#       size = text_size
#     ) +
# 
#     geom_text(
#   data = df_top,
#   aes(
#     x = .data[[group_col]],
#     y = -(y_max * 0.20),
#     label = paste0("(", label, ")")
#   ),
#   inherit.aes = FALSE,
#   fontface = "bold",
#   size = text_size
# ) +
# 
#     stat_compare_means(
#   method = "wilcox.test",
#   comparisons = list(c("No_Flupirtin", "Flupirtin")),
#   label = "p.format",
#   label.y = y_max * 1.12,
#   bracket.size = 0.4,
#   tip.length = 0.01,
#   size = text_size
# ) +
# 
#     labs(
#       title = plot_title,
#       x = NULL,
#       y = y_label
#     ) +
# 
#     coord_cartesian(
#       ylim = c(0, y_max * 1.25),
#       clip = "off"
#     ) +
#     scale_fill_manual(
#   values = c(
#     "No_Flupirtin" = "#E69F00",
#     "Flupirtin"    = "#009E73"
#   )
# )+
# 
#     theme_classic() +
# 
#     theme(
#       legend.position = "none",
#       plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
#       axis.text = element_text(face = "bold", size = 11),
#       axis.title = element_text(face = "bold", size = 12),
#       plot.margin = margin(t = 15, r = 15, b = 30, l = 15)
#     )
# 
#   return(p)
# }
# 
# # ==========================================
# # 2. LOOP FUNCTION (ALL PANELS)
# # ==========================================
# generate_flupirtin_plots <- function(
#     panel_ids,
#     all_data,
#     flupirtin_data,
#     unit_map
# ) {
# 
#   plots <- list()
# 
#   for (pid in panel_ids) {
# 
#     message("Processing: ", pid)
# 
#     panel_data <- all_data %>%
#       left_join(flupirtin_data,
#                 by = "bf_ar_m_nummer",
#                 relationship = "many-to-many") %>%
#       filter(
#         panel_id == pid,
#         treatment == "Leber_Diclo"
#       ) %>%
#       filter(
#         !str_detect(attribute, "_krankheitsbeginn|DBS")
#       ) %>%
#       drop_na(labreads, flupirtin, bf_ar_m_nummer) %>%
#       mutate(
#         flupirtin = case_when(
#           flupirtin %in% c("Yes", "Flupirtin", "flupirtin", 1) ~ "Flupirtin",
#           TRUE ~ "No_Flupirtin"
#         ),
#         flupirtin = factor(
#           flupirtin,
#           levels = c("No_Flupirtin", "Flupirtin")
#         )
#       )
# 
#     if (nrow(panel_data) == 0) next
#     if (length(unique(panel_data$flupirtin)) < 2) next
# 
#     p <- plot_flupirtin_comparison(
#       data = panel_data,
#       group_var = flupirtin,
#       y_var = labreads,
#       patient_id_var = bf_ar_m_nummer,
#       panel_id = pid,
#       unit_map = unit_map,
#       plot_title <- paste("Liver_Diclo:", toupper(pid), "\n(Flupirtin vs Non Flupirtin peak values)")
#     )
# 
#     plots[[pid]] <- p
#   }
# 
#   return(plots)
# }
```


##===================
## gpt_full
##===================

```{r}
gpt_full <- all_data %>% 
  filter(panel_id == "gpt") %>% 
  filter(treatment == "Leber_Diclo") %>% 
  drop_na()

gpt_full
```


```{r}
flupirtin_data %>% 
  filter(treatment == "Leber_Diclo") %>% 
  left_join(.,gpt_full, by = join_by(bf_ar_m_nummer)) %>% 
  drop_na(labreads,days) %>% 
  mutate(flupirtin = factor(flupirtin)) %>% 
  group_by(flupirtin) %>% 
  summarise(
    n_rows = n(),
    n_patients = n_distinct(bf_ar_m_nummer),
    patient_ids = paste(unique(bf_ar_m_nummer), collapse = ", "),
    .groups = "drop"
  )
```

##=============================
## Unit_map
##=============================

```{r}
unit_map <- c(
    "got" = "AST/GOT (U/L)", "gpt" = "ALT/GPT (U/L)", "ggt" = "GGT (U/L)",
    "ap" = "Alkaline Phosphatase (U/L)", "gldh" = "GLDH (U/L)", "ldh" = "LDH (U/L)",
    "cholinesterase" = "Cholinesterase (U/L)", "bilirubin" = "Total Bilirubin (mg/dL)",
    "total_bilirubin" = "Total Bilirubin (mg/dL)", "direktes" = "Direct Bilirubin (mg/dL)",
    "direct_bilirubin" = "Direct Bilirubin (mg/dL)", "indirektes" = "Indirect Bilirubin (mg/dL)",
    "indirect_bilirubin" = "Indirect Bilirubin (mg/dL)", "ammoniak" = "Ammonia (µg/dL)",
    "ck" = "CK (U/L)", "keratinkinase" = "Creatine Kinase (U/L)", "ck_mb" = "CK-MB (U/L)", 
    "troponin" = "Troponin (ng/L)", "serummyoglobin" = "Myoglobin (µg/L)",
    "kreatinin" = "Creatinine (mg/dL)", "harnstoff" = "Urea (mg/dL)",
    "harnsaure" = "Uric Acid (mg/dL)", "gfr" = "eGFR (mL/min/1.73m²)",
    "grf" = "eGFR (mL/min/1.73m²)", "glomarulare" = "eGFR (mL/min/1.73m²)",
    "glucose" = "Glucose (mg/dL)", "lactat" = "Lactate (mmol/L)",
    "cholesterin" = "Cholesterol (mg/dL)", "triglyceride" = "Triglycerides (mg/dL)",
    "hdl" = "HDL Cholesterol (mg/dL)", "ldl" = "LDL Cholesterol (mg/dL)",
    "gesamteiweiss" = "Total Protein (g/dL)", "albumin" = "Albumin (g/dL)",
    "alpha" = "Alpha-Globulin (%)", "beta" = "Beta-Globulin (%)", "gamma" = "Gamma-Globulin (%)",
    "amylase" = "Amylase (U/L)", "lipase" = "Lipase (U/L)",
    "crp" = "CRP (mg/L)", "bsg" = "ESR (mm/h)", "leukozyten" = "Leukocytes (G/L)", "fieber" = "Temperature (°C)",
    "quick" = "Quick (%)", "inr" = "INR", "ptt" = "PTT (s)", "prothrombin" = "Prothrombin Time (s)", 
    "tz" = "Thrombin Time (s)", "antithrombin" = "Antithrombin III (%)", "antithrombin_3" = "Antithrombin III (%)",
    "fibrinogen" = "Fibrinogen (mg/dL)", "d" = "D-Dimer (mg/L)",
    "erythrozyten" = "Erythrocytes (T/L)", "hb" = "Hemoglobin (g/dL)", "hamatokrit" = "Hematocrit (%)", 
    "mcv" = "MCV (fL)", "mch" = "MCH (pg)", "mchc" = "MCHC (g/dL)", 
    "thrombozyten" = "Thrombocytes (G/L)", "trhombozyten" = "Thrombocytes (G/L)",
    "lymphozyten" = "Lymphocytes (%)", "monozyten" = "Monocytes (%)", "eosinophile" = "Eosinophils (%)", 
    "basophile" = "Basophils (%)", "neutrophile" = "Neutrophils (%)", 
    "stabkernige" = "Band Neutrophils (%)", "segmentkernige" = "Segmented Neutrophils (%)",
    "natrium" = "Sodium (mmol/L)", "kalium" = "Potassium (mmol/L)", "kalzium" = "Calcium (mmol/L)", 
    "magnesium" = "Magnesium (mmol/L)", "chlorid" = "Chloride (mmol/L)", "phosphat" = "Phosphate (mg/dL)",
    "serum_eisen" = "Serum Iron (µg/dL)", "transferrin" = "Transferrin (mg/dL)",
    "ferritin" = "Ferritin (µg/L)", "haptoglobin" = "Haptoglobin (mg/dL)",
    "total" = "Total Value", "totales" = "Total Value", "blut" = "Blood Value", "serum" = "Serum Value"
  )
```


##===============================================================
##  format code for y axis break when outlier exist.(diabetes)
##===============================================================

```{r}

# ── Libraries ──────────────────────────────────────────────────────────────
library(ggbreak)
library(ggpubr)
library(dplyr)
library(stringr)
library(ggprism)

# ── Function ───────────────────────────────────────────────────────────────
plot_liver_boxplot_break <- function(
    all_data,
    diabetic_data,
    gender_data1,
    panel = "gpt",
    unit_map = NULL,
    comparisons = list(
      c("Liver_Diclo", "Liver_Ibu"),
      c("Liver_Diclo", "Liver_Para"),
      c("Liver_Ibu",   "Liver_Para")
    ),
    stat_method   = "wilcox.test",
    stat_label    = "p.format",
    tip_length    = 0.01,
    bracket_size  = 0.5,
    y_break       = c(3000, 4500),
    y_break_scale = 0.3,
    top_margin    = 80,
    colors        = c(
      "Liver_Diclo" = "#4E79A7",
      "Liver_Ibu"   = "#F28E2B",
      "Liver_Para"  = "#59A14F"
    )
) {

  # ── Title & label ────────────────────────────────────────────────────────
  plot_title <- paste(toupper(panel), "Levels by treatment (Liver Cohort)")

  y_label <- if (!is.null(unit_map) && panel %in% names(unit_map)) {
    unit_map[[panel]]
  } else {
    toupper(panel)
  }

  # ── Data ─────────────────────────────────────────────────────────────────
  plot_data <- all_data %>%
    left_join(diabetic_data,
              by = join_by("bf_ar_m_nummer", "treatment"),
              relationship = "many-to-many") %>%
    left_join(gender_data1,
              by = join_by("bf_ar_m_nummer", "treatment"),
              relationship = "many-to-many") %>%
    mutate(
      treatment = recode(
        treatment,
        "Leber_Diclo" = "Liver_Diclo",
        "Leber_Ibu"   = "Liver_Ibu",
        "Leber_Para"  = "Liver_Para"
      )
    ) %>%
    filter(
      panel_id == .env$panel,
      grepl("Liver_", treatment),
      !str_detect(attribute, "_krankheitsbeginn|dbs"),
      !is.na(diabetes),
      !is.na(treatment),
      !is.na(labreads)
    )

  if (nrow(plot_data) == 0) {
    stop("No data remaining after filtering.")
  }

  # ── Stats ───────────────────────────────────────────────────────────────
  group_stats <- plot_data %>%
    group_by(treatment) %>%
    summarise(
      N = n_distinct(bf_ar_m_nummer),
      n = n(),
      y_top = max(labreads, na.rm = TRUE),
      .groups = "drop"
    )

  x_labels <- setNames(
    paste0(group_stats$treatment, "\nN = ", group_stats$N),
    group_stats$treatment
  )

  # ── y scaling ───────────────────────────────────────────────────────────
  y_max <- max(plot_data$labreads, na.rm = TRUE)

  n_comp <- length(comparisons)

  label_y_pos <- y_max * (1.28 + seq(0, by = 0.10, length.out = n_comp))

  plot_top <- max(label_y_pos) * 1.10

  n_label_y <- y_max * 1.05

  # ── Plot ────────────────────────────────────────────────────────────────
  p <- ggplot(
    plot_data,
    aes(
      x = treatment,
      y = labreads,
      fill = treatment,
      colour = treatment
    )
  ) +

    geom_boxplot(
      width = 0.6,
      alpha = 0.35,
      linewidth = 0.8,
      outlier.shape = NA
    ) +

    geom_jitter(
      aes(shape = treatment),
      width = 0.2,
      size = 2,
      alpha = 0.8
    ) +

    geom_text(
      data = group_stats,
      aes(x = treatment,
          y = n_label_y,
          label = paste0("n = ", n)),
      inherit.aes = FALSE,
      fontface = "bold",
      size = 5
    ) +

    stat_compare_means(
      comparisons  = comparisons,
      method       = stat_method,
      label        = stat_label,
      label.y      = label_y_pos,
      tip.length   = tip_length,
      bracket.size = bracket_size,
      step.increase = 0.11,
      size = 5
    ) +

    scale_x_discrete(labels = x_labels) +
    scale_fill_manual(values = colors) +
    scale_colour_manual(values = colors) +
    scale_shape_prism() +

    scale_y_break(y_break, scales = y_break_scale) +
    expand_limits(y = max(label_y_pos) * 1.55) +
    guides(y = "prism_offset_minor") +

    labs(
      title = plot_title,
      x = NULL,
      y = y_label
    ) +

    theme_prism() +

    theme(
      text = element_text(family = "sans"),
      legend.position = "none",

      plot.title = element_text(
        hjust = 0.5,
        size = 26,
        face = "bold",
        margin = margin(b = 6)
      ),

      axis.text.x = element_text(
        size = 22,
        face = "bold",
        margin = margin(t = 6)
      ),

      axis.text.y = element_text(
        size = 22,
        face = "bold"
      ),

      axis.title = element_text(
        size = 24,
        face = "bold"
      ),

      axis.title.y = element_text(
        margin = margin(r = -10, unit = "pt")
      ),

      axis.text.x.top = element_blank(),
      axis.ticks.x.top = element_blank(),
      axis.line.x.top = element_blank(),

      plot.margin = margin(
        t = top_margin,
        r = 10,
        b = 10,
        l = 10,
        unit = "pt"
      )
    )

  return(p)
}
```

```{r}
base_dir <- here::here("output/figure/diabetes/plots_all_labvalues/liver")

svg_dir <- file.path(base_dir, "svg")
png_dir <- file.path(base_dir, "png")

dir.create(svg_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(png_dir, recursive = TRUE, showWarnings = FALSE)
```

```{r}
panel <- "gpt"
p <- plot_liver_boxplot_break(
  all_data,
  diabetic_data,
  gender_data1,
  unit_map = unit_map,
  panel = panel,
  top_margin = 10,
  y_break = c(4000, 10000)
)
p 
```


```{r}
panel <- "ferritin"
print(p)

ggsave(
  filename = file.path(svg_dir, paste0(panel, "_plot.svg")),
  plot     = p,
  width    = 8,
  height   = 6,
  device   = svglite::svglite
)

ggsave(
  filename = file.path(png_dir, paste0(panel, "_plot.png")),
  plot     = p,
  width    = 8,
  height   = 6,
  dpi      = 600,
  bg       = "white"
)
```

##=============================
##
##==============================


```{r}
panel <- "gpt"

p <- plot_diabetes_boxplot_break(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel = panel,
  y_break = c(3000, 4500),
  y_break_scale = 0.3
)

p
```


```{r}
# all_data %>%
#     left_join(diabetic_data,
#               by = "bf_ar_m_nummer",
#               relationship = "many-to-many") %>%
#     left_join(gender_data1,
#               by = join_by("bf_ar_m_nummer", "treatment"),
#               relationship = "many-to-many") %>%
#     filter(
#       panel_id == "gpt",
#       grepl("Leber_", kathegorie),
#       !str_detect(attribute, "_krankheitsbeginn|dbs"),
#       !is.na(diabetes),
#       !is.na(kathegorie),
#       !is.na(gender),
#       !is.na(labreads)
#     ) %>%
#     mutate(
#       kathegorie = recode(
#         kathegorie,
#         "Leber_Diclo" = "Liver_Diclo",
#         "Leber_Ibu"   = "Liver_Ibu",
#         "Leber_Para"  = "Liver_Para"),
#       diabetes = factor(diabetes),
#       gender = factor(gender)
#     ) %>% 
#   ggplot(aes(x = diabetes, y = labreads))+
#   geom_boxplot()+
#   geom_jitter()+
#   facet_wrap(~ gender)
```

```{r}
# all_data %>%
#   filter(
#       panel_id == "got",
#       grepl("Leber_", treatment),
#       !str_detect(attribute, "_from_start|dbs|_dbs"),
#       !is.na(treatment),
#       !is.na(labreads)
#     ) %>% 
#     left_join(
#       diabetic_data,
#       by = join_by("bf_ar_m_nummer", "treatment")
#     ) %>%
#     # left_join(
#     #   gender_data1,
#     #   by = join_by("bf_ar_m_nummer", "treatment")
#     # ) %>%
#     
#     mutate(
#       treatment = recode(
#         treatment,
#         "Leber_Diclo" = "Liver_Diclo",
#         "Leber_Ibu"   = "Liver_Ibu",
#         "Leber_Para"  = "Liver_Para"
#       ),
#       diabetes = factor(
#         diabetes,
#         levels = c("Diabetic", "Non_Diabetic")
#       )#,
#       #gender = factor(
#       #  gender,
#       #  levels = c("Female", "Male")
#       #)
#     ) %>% 
#   group_by(diabetes,treatment) %>%
#   summarise(
#     N = n_distinct(bf_ar_m_nummer),
#     n = n_distinct(labreads),
#     .groups = "drop"
#   ) %>%
#   filter(!is.na(diabetes))
```



```{r}
# all_data %>%
#   filter(
#       panel_id == "got",
#       grepl("Leber_", treatment),
#       !str_detect(attribute, "_from_start|dbs|_dbs"),
#       !is.na(treatment),
#       !is.na(labreads)
#     ) %>% 
#     left_join(
#       diabetic_data,
#       by = join_by("bf_ar_m_nummer", "treatment")
#     ) %>%
#       mutate(
#       treatment = recode(
#         treatment,
#         "Leber_Diclo" = "Liver_Diclo",
#         "Leber_Ibu"   = "Liver_Ibu",
#         "Leber_Para"  = "Liver_Para"
#       ),
#       diabetes = factor(
#         diabetes,
#         levels = c("Diabetic", "Non_Diabetic")
#       )) %>% 
#   ggplot(aes(x = diabetes , y = labreads))+
#   geom_boxplot()+
#   geom_jitter()
```


```{r}
 # all_data %>%
 #    left_join(
 #      diabetic_data,
 #      by = join_by("bf_ar_m_nummer","treatment"),
 #      relationship = "many-to-many"
 #    ) %>%
 #    filter(
 #      panel_id == "gpt",
 #      grepl("Leber_", treatment),
 #      !str_detect(attribute, "_from_start|dbs|_dbs"),
 #      !is.na(diabetes),
 #      !is.na(treatment),
 #      !is.na(labreads)
 #    ) %>%
 #    mutate(
 #      treatment = recode(
 #       treatment,
 #        "Leber_Diclo" = "Liver_Diclo",
 #        "Leber_Ibu"   = "Liver_Ibu",
 #        "Leber_Para"  = "Liver_Para"
 #      ),
 #      diabetes = factor(
 #        diabetes,
 #        levels = c("Diabetic", "Non_Diabetic")
 #      )
 #    ) %>%
 #    distinct(bf_ar_m_nummer, labreads, .keep_all = TRUE)
```

##======================================
## gpt table summary (gtsummary package)
##======================================


```{r}
gptliver <- all_data %>%
    left_join(
      diabetic_data,
      by = join_by("bf_ar_m_nummer", "treatment"),
      relationship = "many-to-many"
    ) %>%
    left_join(
      gender_data1,
      by = join_by("bf_ar_m_nummer", "treatment"),
      relationship = "many-to-many"
    ) %>%
    filter(
      panel_id == "gpt", #.env$panel,
      grepl("Leber_", treatment),
      !str_detect(attribute, "_from_start|dbs"),
      !is.na(diabetes),
      !is.na(gender),
      !is.na(treatment),
      !is.na(labreads)
    ) %>%
    mutate(
      treatment = recode(
        treatment,
        "Leber_Diclo" = "Liver_Diclo",
        "Leber_Ibu"   = "Liver_Ibu",
        "Leber_Para"  = "Liver_Para"
      ),
      diabetes = factor(diabetes, levels = c("Diabetic", "Non_Diabetic")),
      gender   = factor(gender,   levels = c("Female", "Male"))
    ) %>%
    distinct(bf_ar_m_nummer, labreads, .keep_all = TRUE)
gptliver
```

```{r}
gptliver %>%
  group_by(diabetes) %>%
  summarise(
    N = n_distinct(bf_ar_m_nummer),
    n = n(),
    .groups = "drop"
  )
```




```{r}
subject_data <- gptliver %>%
  distinct(bf_ar_m_nummer, diabetes, gender, treatment)
subject_data

table1 <- subject_data %>%
  tbl_summary(
    by = diabetes,
    include = c(gender, treatment),
    missing = "no"
  ) %>%
  add_n() %>%
  add_p() %>%
  add_difference()

table1_flex <- as_flex_table(table1)



doc <- read_docx() %>%
  body_add_par("Table 1: GPT_T2D_NT2D", 
               style = "heading 1") %>%
               body_add_flextable(table1_flex)

print(doc, target = "gpt_T2D_Table.docx")

```

##==============================================
## summary table for diabetes, gender, treatment
##==============================================
## in this case tbl_stack is working 
##==============================================

```{r}
tbl_diabetes <- subject_data %>%
  tbl_summary(by = diabetes, include = c(gender, treatment)) %>%
  add_n() %>%
  add_p()

tbl_gender <- subject_data %>%
  tbl_summary(by = gender, include = c(diabetes, treatment)) %>%
  add_n() %>%
  add_p()

tbl_treatment <- subject_data %>%
  tbl_summary(by = treatment, include = c(diabetes, gender)) %>%
  add_n() %>%
  add_p()
```


```{r}
table1_final <- tbl_stack(
  tbls = list(tbl_diabetes, tbl_gender, tbl_treatment),
  group_header = c("Diabetes", "Gender", "Treatment")
)
table1_final
```



```{r}
gender_bmi_data %>%
  filter(
    #treatment == "Leber_Diclo",
    !is.na(gender),
    !is.na(bmi)) %>% 
  group_by(gender) %>%
  summarise(
    N = n_distinct(bf_ar_m_nummer),  # subjects
    n = n(),                         # BMI measurements
    ymax = max(bmi, na.rm = TRUE),
    .groups = "drop"
  )
```



```{r}
all_data %>%
   left_join(
     gender_bmi_data,
     by = join_by("bf_ar_m_nummer","treatment"),
     relationship = "many-to-many"
   ) %>%
   filter(
     panel_id == "gpt",
     grepl("Leber_", treatment),
     !str_detect(attribute, "_from_start|dbs|_dbs"),
     !is.na(bmi),
     !is.na(treatment),
     !is.na(labreads),
     !is.na(days)
   ) %>%
   mutate(
     treatment = recode(
      treatment,
       "Leber_Diclo" = "Liver_Diclo",
       "Leber_Ibu"   = "Liver_Ibu",
       "Leber_Para"  = "Liver_Para"
     ),
     gender = factor(
       gender,
       levels = c("Female", "Male")
     ),
     obese = factor(
     recode(
     obese,
     "yes" = "obese",
     "no"  = "no_obese"),
     levels = c("obese", "no_obese")),
     facet_group = paste(gender, obese, sep = " ")) %>% 
     distinct(bf_ar_m_nummer, labreads, .keep_all = TRUE) %>% 
     filter(labreads <= 4000) %>% 
     ggplot(aes(x = treatment, y = labreads))+
     geom_boxplot()+
     geom_jitter()+
     facet_wrap(~ facet_group )+
     theme_classic()+
      theme(
        strip.text = element_text(size = 16, face = "bold")
      )
```


```{r}
gender_bmi_data %>% 
   mutate(
    obese = case_when(
      obese == "no"  ~ "no_obese",
      obese == "yes" ~ "obese",
      TRUE ~ NA_character_
    )
  )
```


##=============================
## BMI_treatment_gender_obesity
##=============================

```{r}
plot_data <- all_data %>%
  left_join(
    gender_bmi_data,
    by = join_by("bf_ar_m_nummer", "treatment"),
    relationship = "many-to-many"
  ) %>%
  filter(
    panel_id == "gpt",
    grepl("Leber_", treatment),
    !str_detect(attribute, "_from_start|dbs|_dbs"),
    !is.na(bmi),
    !is.na(treatment),
    !is.na(labreads),
    !is.na(days)
  ) %>%
  mutate(
    treatment = recode(
      treatment,
      "Leber_Diclo" = "Liver_Diclo",
      "Leber_Ibu"   = "Liver_Ibu",
      "Leber_Para"  = "Liver_Para"
    ),
    gender = factor(gender, levels = c("Female", "Male")),
    obese = factor(
      recode(obese,
             "yes" = "obese",
             "no"  = "no_obese"),
      levels = c("obese", "no_obese")
    ),
    facet_group = paste(gender, obese, sep = " "),
    facet_group = recode(facet_group,
  "Female no_obese" = "Female / Non-obese",
  "Female obese"    = "Female / Obese",
  "Male no_obese"   = "Male / Non-obese",
  "Male obese"      = "Male / Obese"
)) %>%
  distinct(bf_ar_m_nummer, labreads, .keep_all = TRUE) #%>%
  #filter(labreads <= 4000)
plot_data
```

```{r}
comparisons <- list(
  c("Liver_Diclo", "Liver_Ibu"),
  c("Liver_Diclo", "Liver_Para"),
  c("Liver_Ibu", "Liver_Para")
)

library(purrr)

stat_test <- plot_data %>%
  group_by(facet_group) %>%
  group_split() %>%
  map(\(df) {
    fg <- unique(df$facet_group)
    max_y <- max(df$labreads, na.rm = TRUE)
    
    df %>%
      wilcox_test(labreads ~ treatment, comparisons = comparisons) %>%
      adjust_pvalue(method = "BH") %>%
      add_significance("p.adj") %>%
      add_xy_position(x = "treatment") %>%   # now sees only 3 rows
      mutate(
        facet_group = fg,
        y.position  = max_y + c(600, 1300, 2000)
      )
  }) %>%
  bind_rows()

ggplot(plot_data, aes(x = treatment, y = labreads, color= treatment )) +
  geom_boxplot() +
  geom_jitter(width = 0.15, alpha = 0.6) +
  facet_wrap(~facet_group) +
  stat_pvalue_manual(
    stat_test,
    label    = " p {p.adj}",
    hide.ns  = FALSE,
    facet.by = "facet_group"
  ) +
  scale_x_discrete(labels = c(
  "Liver_Diclo" = "Diclofenac",
  "Liver_Ibu"   = "Ibuprofen",
  "Liver_Para"  = "Paracetamol"
))+
   scale_y_continuous(
   limits = c(0, 6000),
   breaks = seq(0, 6000, by = 1000))+
  scale_color_manual(values = c("#0072B2", "#E69F00", "#009E73"))+
  labs(
    y = ("GPT Activity (U/L)"),
    title = "GPT Activity by Treatment, Sex, and Obesity Status")+
  theme_classic() +
  theme(strip.text = element_text(size = 16, face = "bold",
                                  margin = margin(b = 5)),
        strip.background = element_blank(),
        text = element_text(family = "sans"),
      legend.position = "none",

      plot.title = element_text(
        hjust = 0.5,
        size = 25,
        face = "bold",
        margin = margin(b = 10)
      ),

      axis.text.x = element_text(
        size = 18,
        face = "bold",
        margin = margin(t = 1)
      ),

      axis.text.y = element_text(
        size = 18,
        face = "bold"
      ),

      axis.title = element_text(
        size = 24,
        face = "bold"
      ),
      plot.margin = margin(
        t = 10,
        r = 10,
        b = 10,
        l = 10,
        unit = "pt"
      ))
```

##========================================
## function (BMI_treatment_gender_obesity)
##========================================

```{r}
plot_liver_treatment_sex_obesity <- function(
    all_data,
    gender_bmi_data,
    panel,
    y_var       = "labreads",
    y_label     = "GPT Activity (U/L)",
    title       = "GPT Activity by Treatment, Sex, and Obesity Status",
    max_filter  = 4000,
    y_limits    = c(0, 6000),
    y_breaks    = seq(0, 6000, by = 1000),
    pval_steps  = c(600, 1300, 2000),
    colors      = c("#0072B2", "#E69F00", "#009E73"),
    comparisons = list(
      c("Liver_Diclo", "Liver_Ibu"),
      c("Liver_Diclo", "Liver_Para"),
      c("Liver_Ibu",   "Liver_Para")
    )
) {
  
  # ── 1. Prepare data ──────────────────────────────────────────────────────────
  plot_data <- all_data %>%
    left_join(
      gender_bmi_data,
      by           = join_by("bf_ar_m_nummer", "treatment"),
      relationship = "many-to-many"
    ) %>%
    filter(
      panel_id == .env$panel,
      grepl("Leber_", treatment),
      !str_detect(attribute, "_from_start|dbs|_dbs"),
      !is.na(bmi),
      !is.na(treatment),
      !is.na(.data[[y_var]]),
      !is.na(days)
    ) %>%
    mutate(
      treatment = recode(treatment,
        "Leber_Diclo" = "Liver_Diclo",
        "Leber_Ibu"   = "Liver_Ibu",
        "Leber_Para"  = "Liver_Para"
      ),
      gender = factor(gender, levels = c("Female", "Male")),
      obese  = factor(
        recode(obese, "yes" = "obese", "no" = "no_obese"),
        levels = c("obese", "no_obese")
      ),
      facet_group = paste(gender, obese, sep = " "),
      facet_group = recode(facet_group,
        "Female no_obese" = "Female / Non-obese",
        "Female obese"    = "Female / Obese",
        "Male no_obese"   = "Male / Non-obese",
        "Male obese"      = "Male / Obese"
      )
    ) %>%
    distinct(bf_ar_m_nummer, .data[[y_var]], .keep_all = TRUE) %>%
    filter(.data[[y_var]] <= max_filter)
  
  # ── Guard: stop early if no data ─────────────────────────────────────────────
  if (nrow(plot_data) == 0) {
    stop("No data after filtering for panel '", panel, "'. Check panel_id and treatment names.")
  }
  
  # ── Guard: report which facet groups have all 3 treatments ───────────────────
  valid_groups <- plot_data %>%
    group_by(facet_group) %>%
    summarise(n_treatments = n_distinct(treatment), .groups = "drop") %>%
    filter(n_treatments == 3) %>%
    pull(facet_group)
  
  skipped <- setdiff(unique(plot_data$facet_group), valid_groups)
  if (length(skipped) > 0) {
    warning("Skipping facet group(s) with fewer than 3 treatments: ",
            paste(skipped, collapse = ", "))
  }
  
  plot_data <- filter(plot_data, facet_group %in% valid_groups)
  
  # ── 2. Statistical tests ─────────────────────────────────────────────────────
  test_formula <- as.formula(paste(y_var, "~ treatment"))
  
  stat_test <- plot_data %>%
    group_by(facet_group) %>%
    group_split() %>%
    map(\(df) {
      fg    <- unique(df$facet_group)
      max_y <- max(df[[y_var]], na.rm = TRUE)
      
      tryCatch({
        df %>%
          wilcox_test(test_formula, comparisons = comparisons) %>%
          adjust_pvalue(method = "BH") %>%
          add_significance("p.adj") %>%
          add_xy_position(x = "treatment") %>%
          mutate(
            facet_group = fg,
            y.position  = max_y + pval_steps
          )
      }, error = function(e) {
        warning("Statistical test failed for '", fg, "': ", e$message)
        NULL   # dropped by compact() below
      })
    }) %>%
    compact() %>%   # removes NULL entries from failed groups
    bind_rows()
  
  # ── Guard: stop if no tests succeeded ────────────────────────────────────────
  if (nrow(stat_test) == 0) {
    stop("All statistical tests failed. Check that each facet group has ",
         "sufficient observations per treatment.")
  }
  
  # ── 3. Plot ──────────────────────────────────────────────────────────────────
  ggplot(plot_data, aes(x = treatment, y = .data[[y_var]], color = treatment)) +
    geom_boxplot() +
    geom_jitter(width = 0.15, alpha = 0.6) +
    facet_wrap(~facet_group) +
    stat_pvalue_manual(
      stat_test,
      label    = "p {p.adj}",
      hide.ns  = FALSE,
      facet.by = "facet_group"
    ) +
    scale_x_discrete(labels = c(
      "Liver_Diclo" = "Diclofenac",
      "Liver_Ibu"   = "Ibuprofen",
      "Liver_Para"  = "Paracetamol"
    )) +
    scale_y_continuous(limits = y_limits, breaks = y_breaks) +
    scale_color_manual(values = colors) +
    labs(y = y_label, title = title) +
    theme_classic() +
    theme(
      strip.text       = element_text(size = 16, face = "bold", margin = margin(b = 5)),
      strip.background = element_blank(),
      text             = element_text(family = "sans"),
      legend.position  = "none",
      plot.title       = element_text(hjust = 0.5, size = 25, face = "bold", margin = margin(b = 10)),
      axis.text.x      = element_text(size = 18, face = "bold", margin = margin(t = 1)),
      axis.text.y      = element_text(size = 18, face = "bold"),
      axis.title       = element_text(size = 24, face = "bold"),
      plot.margin      = margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")
    )
}
```






====================================================================
====================================================================


```{r}
library(tidyverse)
library(rstatix)
library(ggpubr)
library(purrr)
library(glue)

# ════════════════════════════════════════════════════════════════════════════
# FUNCTION
# ════════════════════════════════════════════════════════════════════════════

plot_liver_treatment_sex_obesity <- function(
    all_data,
    gender_bmi_data,
    panel,
    y_var            = "labreads",
    y_label          = "GPT Activity (U/L)",
    title            = "GPT Activity by Treatment, Sex, and Obesity Status",
    max_filter       = 4000,
    y_limits         = c(0, 6000),
    y_breaks         = NULL,
    pval_multipliers = c(0.16, 0.24, 0.32),
    colors           = c("#0072B2", "#E69F00", "#009E73"),
    comparisons      = list(
      c("Liver_Diclo", "Liver_Ibu"),
      c("Liver_Diclo", "Liver_Para"),
      c("Liver_Ibu",   "Liver_Para")
    )
) {

  # ── auto y_breaks ─────────────────────────────────────────────────────────
  if (is.null(y_breaks)) {
    y_breaks <- pretty(c(0, max_filter), n = 6)
  }

  # ── p-value offset steps (as fractions of y_limits max) ───────────────────
  # pval_steps[k] = offset ABOVE max_y for the k-th bracket
  pval_steps <- max(y_limits) * pval_multipliers          # e.g. c(1400, 2100, 2800)
  step_size  <- pval_steps[2] - pval_steps[1]             # spacing between brackets

  # FIX 1 ── hard-code integer x positions; never use add_xy_position()
  # step.increase in add_xy_position() nudges xmin/xmax by a fraction,
  # producing non-integers that cause seq_len() to crash inside stat_pvalue_manual.
  x_levels <- c("Liver_Diclo" = 1L, "Liver_Ibu" = 2L, "Liver_Para" = 3L)

  # ── 1. Prepare data ───────────────────────────────────────────────────────
  plot_data <- all_data %>%
    left_join(
      gender_bmi_data,
      by           = join_by("bf_ar_m_nummer", "treatment"),
      relationship = "many-to-many"
    ) %>%
    filter(
      panel_id == .env$panel,
      grepl("Leber_", treatment),
      !str_detect(attribute, "_from_start|dbs|_dbs"),
      !is.na(bmi),
      !is.na(treatment),
      !is.na(.data[[y_var]]),
      !is.na(days)
    ) %>%
    mutate(
      treatment = recode(treatment,
        "Leber_Diclo" = "Liver_Diclo",
        "Leber_Ibu"   = "Liver_Ibu",
        "Leber_Para"  = "Liver_Para"
      ),
      gender = factor(gender, levels = c("Female", "Male")),
      obese  = factor(
        recode(obese, "yes" = "obese", "no" = "no_obese"),
        levels = c("obese", "no_obese")
      ),
      facet_group = paste(gender, obese, sep = " "),
      facet_group = recode(facet_group,
        "Female no_obese" = "Female / Non-obese",
        "Female obese"    = "Female / Obese",
        "Male no_obese"   = "Male / Non-obese",
        "Male obese"      = "Male / Obese"
      )
    ) %>%
    distinct(bf_ar_m_nummer, .data[[y_var]], .keep_all = TRUE) %>%
    filter(.data[[y_var]] <= max_filter)

  # ── Guard 1: no data ──────────────────────────────────────────────────────
  if (nrow(plot_data) == 0) {
    warning("Panel '", panel, "': no data after filtering.")
    return(NULL)
  }

  # ── Guard 2: valid facet groups ───────────────────────────────────────────
  valid_groups <- plot_data %>%
    group_by(facet_group) %>%
    summarise(n_treatments = n_distinct(treatment), .groups = "drop") %>%
    filter(n_treatments == 3) %>%
    pull(facet_group)

  if (length(valid_groups) == 0) {
    warning("Panel '", panel, "': no facet group has all 3 treatments.")
    return(NULL)
  }

  plot_data <- filter(plot_data, facet_group %in% valid_groups)

  # ── 2. Statistical tests ──────────────────────────────────────────────────
  test_formula <- as.formula(paste(y_var, "~ treatment"))

  stat_test <- plot_data %>%
    group_by(facet_group) %>%
    group_split() %>%
    map(\(df) {

      fg    <- unique(df$facet_group)
      max_y <- max(df[[y_var]], na.rm = TRUE)

      tryCatch({
        df %>%
          wilcox_test(test_formula, comparisons = comparisons) %>%
          adjust_pvalue(method = "BH") %>%
          add_significance("p.adj") %>%
          # FIX 1 continued ── attach integer positions here, before bind_rows
          mutate(
            facet_group = fg,
            max_y       = max_y,
            xmin        = x_levels[group1],   # integer: 1, 2, or 3
            xmax        = x_levels[group2]    # integer: 1, 2, or 3
          )
      }, error = function(e) {
        warning("Panel '", panel, "', group '", fg, "': Wilcoxon failed – ", conditionMessage(e))
        NULL
      })
    }) %>%
    compact() %>%
    bind_rows() %>%
    filter(!is.na(group1), !is.na(group2), !is.na(xmin), !is.na(xmax))

  if (nrow(stat_test) == 0) {
    warning("Panel '", panel, "': all statistical tests failed.")
    return(NULL)
  }

  # ── 3. p-value positioning ────────────────────────────────────────────────
  sig_tests <- stat_test %>%
    group_by(facet_group) %>%
    mutate(
      y.position = first(max_y) +
        pval_steps[1] +
        (row_number() - 1L) * step_size
    ) %>%
    ungroup()

  # FIX 2 ── auto-expand y_limits so brackets are never OOB.
  # scale_y_continuous(limits=…) uses censor() by default: values outside limits
  # become NA, then seq_len(NA) crashes inside stat_pvalue_manual.
  max_annot_y  <- max(sig_tests$y.position, na.rm = TRUE)
  plot_y_max   <- if (is.finite(max_annot_y) && max_annot_y > y_limits[2]) {
    max_annot_y * 1.05   # 5% breathing room above the topmost bracket
  } else {
    y_limits[2]
  }
  plot_y_limits <- c(y_limits[1], plot_y_max)

  # ── 4. Plot ───────────────────────────────────────────────────────────────
  ggplot(plot_data, aes(x = treatment, y = .data[[y_var]], color = treatment)) +
    geom_boxplot() +
    geom_jitter(width = 0.15, alpha = 0.6, size = 2) +
    facet_wrap(~facet_group) +
    {
      if (nrow(sig_tests) > 0)
        stat_pvalue_manual(
          sig_tests,
          label    = "p {p.adj}",
          size     = 5,
          hide.ns  = FALSE     # show all comparisons incl. ns
        )
    } +
    scale_y_continuous(limits = plot_y_limits, breaks = y_breaks) +
    scale_x_discrete(labels = c(
      "Liver_Diclo" = "Liver_Diclo",
      "Liver_Ibu"   = "Liver_Ibu",
      "Liver_Para"  = "Liver_Para"
    )) +
    scale_color_manual(values = colors) +
    labs(y = y_label, title = title) +
    theme_classic() +
    theme(
      strip.text       = element_text(size = 16, face = "bold"),
      strip.background = element_blank(),
      legend.position  = "none",
      plot.title       = element_text(hjust = 0.5, size = 25, face = "bold"),
      axis.text.x      = element_text(size = 22, face = "bold"),
      axis.text.y      = element_text(size = 22, face = "bold"),
      axis.title       = element_text(size = 24, face = "bold")
    )
}
```


```{r}
library(purrr)
library(ggplot2)

#------------------------------------------------------------
# Panels
#------------------------------------------------------------


#panels <- c("got", "gpt", "ggt", "ap")

unit_map <- c(
    "got" = "AST/GOT (U/L)", "gpt" = "ALT/GPT (U/L)", "ggt" = "GGT (U/L)",
    "ap" = "Alkaline Phosphatase (U/L)", "gldh" = "GLDH (U/L)", "ldh" = "LDH (U/L)",
    "cholinesterase" = "Cholinesterase (U/L)", "bilirubin" = "Total Bilirubin (mg/dL)",
    "total_bilirubin" = "Total Bilirubin (mg/dL)", "direktes" = "Direct Bilirubin (mg/dL)",
    "direct_bilirubin" = "Direct Bilirubin (mg/dL)", "indirektes" = "Indirect Bilirubin (mg/dL)",
    "indirect_bilirubin" = "Indirect Bilirubin (mg/dL)", "ammoniak" = "Ammonia (µg/dL)",
    "ck" = "CK (U/L)", "keratinkinase" = "Creatine Kinase (U/L)", "ck_mb" = "CK-MB (U/L)", 
    "troponin" = "Troponin (ng/L)", "serummyoglobin" = "Myoglobin (µg/L)",
    "kreatinin" = "Creatinine (mg/dL)", "harnstoff" = "Urea (mg/dL)",
    "harnsaure" = "Uric Acid (mg/dL)", "gfr" = "eGFR (mL/min/1.73m²)",
    "grf" = "eGFR (mL/min/1.73m²)", "glomarulare" = "eGFR (mL/min/1.73m²)",
    "glucose" = "Glucose (mg/dL)", "lactat" = "Lactate (mmol/L)",
    "cholesterin" = "Cholesterol (mg/dL)", "triglyceride" = "Triglycerides (mg/dL)",
    "hdl" = "HDL Cholesterol (mg/dL)", "ldl" = "LDL Cholesterol (mg/dL)",
    "gesamteiweiss" = "Total Protein (g/dL)", "albumin" = "Albumin (g/dL)",
    "alpha" = "Alpha-Globulin (%)", "beta" = "Beta-Globulin (%)", "gamma" = "Gamma-Globulin (%)",
    "amylase" = "Amylase (U/L)", "lipase" = "Lipase (U/L)",
    "crp" = "CRP (mg/L)", "bsg" = "ESR (mm/h)", "leukozyten" = "Leukocytes (G/L)", "fieber" = "Temperature (°C)",
    "quick" = "Quick (%)", "inr" = "INR", "ptt" = "PTT (s)", "prothrombin" = "Prothrombin Time (s)", 
    "tz" = "Thrombin Time (s)", "antithrombin" = "Antithrombin III (%)", "antithrombin_3" = "Antithrombin III (%)",
    "fibrinogen" = "Fibrinogen (mg/dL)", "d" = "D-Dimer (mg/L)",
    "erythrozyten" = "Erythrocytes (T/L)", "hb" = "Hemoglobin (g/dL)", "hamatokrit" = "Hematocrit (%)", 
    "mcv" = "MCV (fL)", "mch" = "MCH (pg)", "mchc" = "MCHC (g/dL)", 
    "thrombozyten" = "Thrombocytes (G/L)", "trhombozyten" = "Thrombocytes (G/L)",
    "lymphozyten" = "Lymphocytes (%)", "monozyten" = "Monocytes (%)", "eosinophile" = "Eosinophils (%)", 
    "basophile" = "Basophils (%)", "neutrophile" = "Neutrophils (%)", 
    "stabkernige" = "Band Neutrophils (%)", "segmentkernige" = "Segmented Neutrophils (%)",
    "natrium" = "Sodium (mmol/L)", "kalium" = "Potassium (mmol/L)", "kalzium" = "Calcium (mmol/L)", 
    "magnesium" = "Magnesium (mmol/L)", "chlorid" = "Chloride (mmol/L)", "phosphat" = "Phosphate (mg/dL)",
    "serum_eisen" = "Serum Iron (µg/dL)", "transferrin" = "Transferrin (mg/dL)",
    "ferritin" = "Ferritin (µg/L)", "haptoglobin" = "Haptoglobin (mg/dL)",
    "total" = "Total Value", "totales" = "Total Value", "blut" = "Blood Value", "serum" = "Serum Value"
  )


panels <- all_data %>%
  dplyr::pull(panel_id) %>%
  unique() %>%
  na.omit() %>%
  trimws() %>%
  intersect(names(unit_map))

base_dir <- file.path(here::here(
  "output", "figure", "diabetes",
  "plots_all_labvalues", "BMI_treatment_gender_obese"
))
svg_dir <- file.path(base_dir, "svg")
png_dir <- file.path(base_dir, "png")
dir.create(svg_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(png_dir, recursive = TRUE, showWarnings = FALSE)

plot_list <- list()

for (panel in panels) {

  max_filter       <- 7000
  y_limits         <- c(0, max_filter)
  pval_multipliers <- c(0.20, 0.30, 0.40)

  p <- plot_liver_treatment_sex_obesity(
    all_data         = all_data,
    gender_bmi_data  = gender_bmi_data,
    panel            = panel,
    y_var            = "labreads",
    y_label          = unit_map[[panel]],
    title            = paste0(
      toupper(panel),
      " Activity by Treatment, Sex, and Obesity Status"
    ),
    max_filter       = max_filter,
    y_limits         = y_limits,
    y_breaks         = seq(0, max_filter, by = 2000),
    pval_multipliers = pval_multipliers
  )

  plot_list[[panel]] <- p

  # FIX 3 ── skip ggsave if function returned NULL (empty panel)
  if (is.null(p)) {
    message("Skipping save for panel '", panel, "' – NULL plot returned.")
    next
  }

  ggsave(
    filename = file.path(svg_dir, paste0(panel, "_BMI_treatment_gender_obese.svg")),
    plot     = p,
    width    = 12,
    height   = 8
  )
  ggsave(
    filename = file.path(png_dir, paste0(panel, "_BMI_treatment_gender_obese.png")),
    plot     = p,
    width    = 12,
    height   = 8,
    dpi      = 300
  )
}

plot_list[["got"]]
plot_list[["gpt"]]
plot_list[["ggt"]]
plot_list[["ap"]]
```


```{r}
#------------------------------------------------------------
# Output folder
#------------------------------------------------------------

base_dir <- file.path(here::here(
  "output",
  "figure",
  "diabetes",
  "plots_all_labvalues",
  "BMI_treatment_gender_obese"
))

svg_dir <- file.path(base_dir, "svg")
png_dir <- file.path(base_dir, "png")

dir.create(svg_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(png_dir, recursive = TRUE, showWarnings = FALSE)
```


```{r}
panel <- "got"

p <- plot_liver_treatment_sex_obesity(
  all_data        = all_data,
  gender_bmi_data = gender_bmi_data,
  panel           = panel,
  y_var           = "labreads",
  y_label         = unit_map[[panel]],
  title           = paste0(
    toupper(panel),
    " Activity by Treatment, Sex, and Obesity Status"
  ),
  max_filter      = 5000,
  y_limits        = c(0, 7000),
  y_breaks        = seq(0, 7000, by = 1000),
  pval_steps      = c(700, 1400, 2100)
)

p
```

```{r}
print(p)

ggsave(
  filename = file.path(
    svg_dir,
    paste0(panel, "_BMI_treatment_gender_obese.svg")
  ),
  plot   = p,
  width  = 8,
  height = 6,
  device = svglite::svglite
)

ggsave(
  filename = file.path(
    png_dir,
    paste0(panel, "_BMI_treatment_gender_obese.png")
  ),
  plot   = p,
  width  = 8,
  height = 6,
  dpi    = 600,
  bg     = "white"
)
```



```{r}
library(gg.gap)
library(plotrix)
```


```{r}
plot_data
```


```{r}
plot_data %>% 
  ggplot(aes(x = gender, y = labreads))+
  geom_boxplot()+
  geom_jitter(size = 2) +
  theme_classic() %>% 
  gg.gap::segments = list(c(0,1000))
```



```{r}
library(readxl)
```

```{r}
excel_sheets(here::here("Rawdata/rucham_rawdata.xlsx"))

```

```{r}
library(readxl)
library(purrr)
library(here)

# Excel file path
file_path <- here::here("Rawdata/rucham_rawdata.xlsx")

# Get all sheet names
sheet_names <- excel_sheets(file_path)

# Read all sheets into a named list
all_sheets <- sheet_names %>%
  set_names() %>%
  map(~ read_excel(file_path, sheet = .x))

# View names
names(all_sheets)

```

```{r}
    all_sheets[["course of ALP"]]
```



































