---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```



##### 
#####
#####
#####
#####
# all graphs new for Thrombocytes #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_thromb <- left_join(ldthromb_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_thromb %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_thromb,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 50000) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_diclo boxplot for daily dose",
       x = "dailydose in mg",
       y = "Thrombocytes cells/ul") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_diclo daily doses of Diclofenac", type = "np",
  ylab = "Thrombocytes cells/ul",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "Thrombozyten Day1", "Thrombozyten Day2", "Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5", "Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10", "Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day14","Thrombozyten Day15","Thrombozyten Day16","Thrombozyten Day17","Thrombozyten Day18","Thrombozyten Day19","Thrombozyten Day20","Thrombozyten Day21","Thrombozyten Day22","Thrombozyten Day23","Thrombozyten Day24","Thrombozyten Day25","Thrombozyten Day26","Thrombozyten Day27","Thrombozyten Day28","Thrombozyten Day29","Thrombozyten Day30","Thrombozyten Day31","Thrombozyten Day32","Thrombozyten Day33","Thrombozyten Day34","Thrombozyten Day35","Thrombozyten Day36","Thrombozyten Day37","Thrombozyten Day38","Thrombozyten Day39","Thrombozyten Day40","Thrombozyten Day41","Thrombozyten Day42","Thrombozyten Day43","Thrombozyten Day44","Thrombozyten Day45","Thrombozyten Day46","Thrombozyten Day47","Thrombozyten Day48","Thrombozyten Day49","Thrombozyten Day50","Thrombozyten Day51","Thrombozyten Day52","Thrombozyten Day53","Thrombozyten Day54","Thrombozyten Day55","Thrombozyten Day56","Thrombozyten Day57","Thrombozyten Day58","Thrombozyten Day59","Thrombozyten Day60","Thrombozyten Day61","Thrombozyten Day62","Thrombozyten Day63","Thrombozyten Day64","Thrombozyten Day65","Thrombozyten Day66","Thrombozyten Day67","Thrombozyten Day68","Thrombozyten Day69","Thrombozyten Day70","Thrombozyten Day71","Thrombozyten Day72","Thrombozyten Day73","Thrombozyten Day74","Thrombozyten Day75","Thrombozyten Day76","Thrombozyten Day77","Thrombozyten Day78","Thrombozyten Day79","Thrombozyten Day80","Thrombozyten Day81","Thrombozyten Day82","Thrombozyten Day83","Thrombozyten Day84","Thrombozyten Day85","Thrombozyten Day86","Thrombozyten Day87","Thrombozyten Day88","Thrombozyten Day89","Thrombozyten Day90","Thrombozyten Day91","Thrombozyten Day92","Thrombozyten Day93","Thrombozyten Day94","Thrombozyten Day95","Thrombozyten Day96","Thrombozyten Day97","Thrombozyten Day98","Thrombozyten Day99","Thrombozyten Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 50mg daily-dose",
       x = "Day of measurement",
       y = "Thrombocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## dose time series for 50mg####
```{r}
dd_75mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
dd_75mg$attribute <- factor(dd_75mg$attribute,levels = c( "Thrombozyten Day1", "Thrombozyten Day2", "Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5", "Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10", "Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day14","Thrombozyten Day15","Thrombozyten Day16","Thrombozyten Day17","Thrombozyten Day18","Thrombozyten Day19","Thrombozyten Day20","Thrombozyten Day21","Thrombozyten Day22","Thrombozyten Day23","Thrombozyten Day24","Thrombozyten Day25","Thrombozyten Day26","Thrombozyten Day27","Thrombozyten Day28","Thrombozyten Day29","Thrombozyten Day30","Thrombozyten Day31","Thrombozyten Day32","Thrombozyten Day33","Thrombozyten Day34","Thrombozyten Day35","Thrombozyten Day36","Thrombozyten Day37","Thrombozyten Day38","Thrombozyten Day39","Thrombozyten Day40","Thrombozyten Day41","Thrombozyten Day42","Thrombozyten Day43","Thrombozyten Day44","Thrombozyten Day45","Thrombozyten Day46","Thrombozyten Day47","Thrombozyten Day48","Thrombozyten Day49","Thrombozyten Day50","Thrombozyten Day51","Thrombozyten Day52","Thrombozyten Day53","Thrombozyten Day54","Thrombozyten Day55","Thrombozyten Day56","Thrombozyten Day57","Thrombozyten Day58","Thrombozyten Day59","Thrombozyten Day60","Thrombozyten Day61","Thrombozyten Day62","Thrombozyten Day63","Thrombozyten Day64","Thrombozyten Day65","Thrombozyten Day66","Thrombozyten Day67","Thrombozyten Day68","Thrombozyten Day69","Thrombozyten Day70","Thrombozyten Day71","Thrombozyten Day72","Thrombozyten Day73","Thrombozyten Day74","Thrombozyten Day75","Thrombozyten Day76","Thrombozyten Day77","Thrombozyten Day78","Thrombozyten Day79","Thrombozyten Day80","Thrombozyten Day81","Thrombozyten Day82","Thrombozyten Day83","Thrombozyten Day84","Thrombozyten Day85","Thrombozyten Day86","Thrombozyten Day87","Thrombozyten Day88","Thrombozyten Day89","Thrombozyten Day90","Thrombozyten Day91","Thrombozyten Day92","Thrombozyten Day93","Thrombozyten Day94","Thrombozyten Day95","Thrombozyten Day96","Thrombozyten Day97","Thrombozyten Day98","Thrombozyten Day99","Thrombozyten Day100"))

ggplot(dd_75mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 75mg daily-dose",
       x = "Day of measurement",
       y = "Thrombocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 100mg daily-dose",
       x = "Day of measurement",
       y = "Thrombocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
dd_100mg$attribute <- 
  factor(dd_100mg$attribute,levels = c( "Thrombozyten Day1", "Thrombozyten Day2", "Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5", "Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10", "Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day14","Thrombozyten Day15","Thrombozyten Day16","Thrombozyten Day17","Thrombozyten Day18","Thrombozyten Day19","Thrombozyten Day20","Thrombozyten Day21","Thrombozyten Day22","Thrombozyten Day23","Thrombozyten Day24","Thrombozyten Day25","Thrombozyten Day26","Thrombozyten Day27","Thrombozyten Day28","Thrombozyten Day29","Thrombozyten Day30","Thrombozyten Day31","Thrombozyten Day32","Thrombozyten Day33","Thrombozyten Day34","Thrombozyten Day35","Thrombozyten Day36","Thrombozyten Day37","Thrombozyten Day38","Thrombozyten Day39","Thrombozyten Day40","Thrombozyten Day41","Thrombozyten Day42","Thrombozyten Day43","Thrombozyten Day44","Thrombozyten Day45","Thrombozyten Day46","Thrombozyten Day47","Thrombozyten Day48","Thrombozyten Day49","Thrombozyten Day50","Thrombozyten Day51","Thrombozyten Day52","Thrombozyten Day53","Thrombozyten Day54","Thrombozyten Day55","Thrombozyten Day56","Thrombozyten Day57","Thrombozyten Day58","Thrombozyten Day59","Thrombozyten Day60","Thrombozyten Day61","Thrombozyten Day62","Thrombozyten Day63","Thrombozyten Day64","Thrombozyten Day65","Thrombozyten Day66","Thrombozyten Day67","Thrombozyten Day68","Thrombozyten Day69","Thrombozyten Day70","Thrombozyten Day71","Thrombozyten Day72","Thrombozyten Day73","Thrombozyten Day74","Thrombozyten Day75","Thrombozyten Day76","Thrombozyten Day77","Thrombozyten Day78","Thrombozyten Day79","Thrombozyten Day80","Thrombozyten Day81","Thrombozyten Day82","Thrombozyten Day83","Thrombozyten Day84","Thrombozyten Day85","Thrombozyten Day86","Thrombozyten Day87","Thrombozyten Day88","Thrombozyten Day89","Thrombozyten Day90","Thrombozyten Day91","Thrombozyten Day92","Thrombozyten Day93","Thrombozyten Day94","Thrombozyten Day95","Thrombozyten Day96","Thrombozyten Day97","Thrombozyten Day98","Thrombozyten Day99","Thrombozyten Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 150mg daily-dose",
       x = "Day of measurement",
       y = "Thrombocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n()) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
dd_200mg$attribute <- 
  factor(dd_200mg$attribute,levels = c( "Thrombozyten Day1", "Thrombozyten Day2", "Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5", "Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10", "Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day14","Thrombozyten Day15","Thrombozyten Day16","Thrombozyten Day17","Thrombozyten Day18","Thrombozyten Day19","Thrombozyten Day20","Thrombozyten Day21","Thrombozyten Day22","Thrombozyten Day23","Thrombozyten Day24","Thrombozyten Day25","Thrombozyten Day26","Thrombozyten Day27","Thrombozyten Day28","Thrombozyten Day29","Thrombozyten Day30","Thrombozyten Day31","Thrombozyten Day32","Thrombozyten Day33","Thrombozyten Day34","Thrombozyten Day35","Thrombozyten Day36","Thrombozyten Day37","Thrombozyten Day38","Thrombozyten Day39","Thrombozyten Day40","Thrombozyten Day41","Thrombozyten Day42","Thrombozyten Day43","Thrombozyten Day44","Thrombozyten Day45","Thrombozyten Day46","Thrombozyten Day47","Thrombozyten Day48","Thrombozyten Day49","Thrombozyten Day50","Thrombozyten Day51","Thrombozyten Day52","Thrombozyten Day53","Thrombozyten Day54","Thrombozyten Day55","Thrombozyten Day56","Thrombozyten Day57","Thrombozyten Day58","Thrombozyten Day59","Thrombozyten Day60","Thrombozyten Day61","Thrombozyten Day62","Thrombozyten Day63","Thrombozyten Day64","Thrombozyten Day65","Thrombozyten Day66","Thrombozyten Day67","Thrombozyten Day68","Thrombozyten Day69","Thrombozyten Day70","Thrombozyten Day71","Thrombozyten Day72","Thrombozyten Day73","Thrombozyten Day74","Thrombozyten Day75","Thrombozyten Day76","Thrombozyten Day77","Thrombozyten Day78","Thrombozyten Day79","Thrombozyten Day80","Thrombozyten Day81","Thrombozyten Day82","Thrombozyten Day83","Thrombozyten Day84","Thrombozyten Day85","Thrombozyten Day86","Thrombozyten Day87","Thrombozyten Day88","Thrombozyten Day89","Thrombozyten Day90","Thrombozyten Day91","Thrombozyten Day92","Thrombozyten Day93","Thrombozyten Day94","Thrombozyten Day95","Thrombozyten Day96","Thrombozyten Day97","Thrombozyten Day98","Thrombozyten Day99","Thrombozyten Day100"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 200mg daily-dose",
       x = "Day of measurement",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_diclo smooth line plot for diclofenac dose groups",        x = "daily dose (mg)",             y = "Thrombocytes cells/ul")	

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_diclo linerar regression for dayly doses",
       x = "daily dose in mg",
       y = "Thrombocytes cells/ul") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldthromb_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups",
       x = "Dose Group",
       y = "Thrombocytes cells/ul") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Natrium/Sodium #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_nat <- left_join(ldnat_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_nat %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_nat,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 20)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_diclo boxplot for daily dose",
       x = "dailydose in mg",
       y = "Sodium mmol/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(100, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_diclo daily doses of Diclofenac", type = "np",
  ylab = "Sodium mmol/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 50mg daily-dose",
       x = "Day of measurement",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 170))


```

## dose time series for 75mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 75mg daily-dose",
       x = "Day of measurement",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 170))


```



## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 100mg daily-dose",
       x = "Day of measurement",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 170))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 150mg daily-dose",
       x = "Day of measurement",
       y = "Sodium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0,170))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n()) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 200mg daily-dose",
       x = "Day of measurement",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 170))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_diclo smooth line plot for diclofenac dose groups",        x = "daily dose (mg)",             y = "sodium mmol/l")	

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_diclo linerar regression for dayly doses",
       x = "daily dose in mg",
       y = "Sodium mmol/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldnat_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups",
       x = "Dose Group",
       y = "Sodium mmol/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Kalium/Potassium #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_kal <- left_join(ldkal_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_kal %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_kal,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_diclo boxplot for daily dose",
       x = "dailydose in mg",
       y = "Potassium mmol/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_diclo daily doses of Diclofenac", type = "np",
  ylab = "Potassium mmol/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "Kalium Day1", "Kalium Day2", "Kalium Day3","Kalium Day4","Kalium Day5", "Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day10", "Kalium Day11","Kalium Day12","Kalium Day13","Kalium Day14","Kalium Day15","Kalium Day16","Kalium Day17","Kalium Day18","Kalium Day19","Kalium Day20","Kalium Day21","Kalium Day22","Kalium Day23","Kalium Day24","Kalium Day25","Kalium Day26","Kalium Day27","Kalium Day28","Kalium Day29","Kalium Day30","Kalium Day31","Kalium Day32","Kalium Day33","Kalium Day34","Kalium Day35","Kalium Day36","Kalium Day37","Kalium Day38","Kalium Day39","Kalium Day40","Kalium Day41","Kalium Day42","Kalium Day43","Kalium Day44","Kalium Day45","Kalium Day46","Kalium Day47","Kalium Day48","Kalium Day49","Kalium Day50","Kalium Day51","Kalium Day52","Kalium Day53","Kalium Day54","Kalium Day55","Kalium Day56","Kalium Day57","Kalium Day58","Kalium Day59","Kalium Day60","Kalium Day61","Kalium Day62","Kalium Day63","Kalium Day64","Kalium Day65","Kalium Day66","Kalium Day67","Kalium Day68","Kalium Day69","Kalium Day70","Kalium Day71","Kalium Day72","Kalium Day73","Kalium Day74","Kalium Day75","Kalium Day76","Kalium Day77","Kalium Day78","Kalium Day79","Kalium Day80","Kalium Day81","Kalium Day82","Kalium Day83","Kalium Day84","Kalium Day85","Kalium Day86","Kalium Day87","Kalium Day88","Kalium Day89","Kalium Day90","Kalium Day91","Kalium Day92","Kalium Day93","Kalium Day94","Kalium Day95","Kalium Day96","Kalium Day97","Kalium Day98","Kalium Day99","Kalium Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 50mg daily-dose",
       x = "Day of measurement",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 75mg####
```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "Kalium Day1", "Kalium Day2", "Kalium Day3","Kalium Day4","Kalium Day5", "Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day10", "Kalium Day11","Kalium Day12","Kalium Day13","Kalium Day14","Kalium Day15","Kalium Day16","Kalium Day17","Kalium Day18","Kalium Day19","Kalium Day20","Kalium Day21","Kalium Day22","Kalium Day23","Kalium Day24","Kalium Day25","Kalium Day26","Kalium Day27","Kalium Day28","Kalium Day29","Kalium Day30","Kalium Day31","Kalium Day32","Kalium Day33","Kalium Day34","Kalium Day35","Kalium Day36","Kalium Day37","Kalium Day38","Kalium Day39","Kalium Day40","Kalium Day41","Kalium Day42","Kalium Day43","Kalium Day44","Kalium Day45","Kalium Day46","Kalium Day47","Kalium Day48","Kalium Day49","Kalium Day50","Kalium Day51","Kalium Day52","Kalium Day53","Kalium Day54","Kalium Day55","Kalium Day56","Kalium Day57","Kalium Day58","Kalium Day59","Kalium Day60","Kalium Day61","Kalium Day62","Kalium Day63","Kalium Day64","Kalium Day65","Kalium Day66","Kalium Day67","Kalium Day68","Kalium Day69","Kalium Day70","Kalium Day71","Kalium Day72","Kalium Day73","Kalium Day74","Kalium Day75","Kalium Day76","Kalium Day77","Kalium Day78","Kalium Day79","Kalium Day80","Kalium Day81","Kalium Day82","Kalium Day83","Kalium Day84","Kalium Day85","Kalium Day86","Kalium Day87","Kalium Day88","Kalium Day89","Kalium Day90","Kalium Day91","Kalium Day92","Kalium Day93","Kalium Day94","Kalium Day95","Kalium Day96","Kalium Day97","Kalium Day98","Kalium Day99","Kalium Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 75mg daily-dose",
       x = "Day of measurement",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 100mg daily-dose",
       x = "Day of measurement",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
dd_100mg$attribute <- 
  factor(dd_100mg$attribute,levels = c( "Kalium Day1", "Kalium Day2", "Kalium Day3","Kalium Day4","Kalium Day5", "Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day10", "Kalium Day11","Kalium Day12","Kalium Day13","Kalium Day14","Kalium Day15","Kalium Day16","Kalium Day17","Kalium Day18","Kalium Day19","Kalium Day20","Kalium Day21","Kalium Day22","Kalium Day23","Kalium Day24","Kalium Day25","Kalium Day26","Kalium Day27","Kalium Day28","Kalium Day29","Kalium Day30","Kalium Day31","Kalium Day32","Kalium Day33","Kalium Day34","Kalium Day35","Kalium Day36","Kalium Day37","Kalium Day38","Kalium Day39","Kalium Day40","Kalium Day41","Kalium Day42","Kalium Day43","Kalium Day44","Kalium Day45","Kalium Day46","Kalium Day47","Kalium Day48","Kalium Day49","Kalium Day50","Kalium Day51","Kalium Day52","Kalium Day53","Kalium Day54","Kalium Day55","Kalium Day56","Kalium Day57","Kalium Day58","Kalium Day59","Kalium Day60","Kalium Day61","Kalium Day62","Kalium Day63","Kalium Day64","Kalium Day65","Kalium Day66","Kalium Day67","Kalium Day68","Kalium Day69","Kalium Day70","Kalium Day71","Kalium Day72","Kalium Day73","Kalium Day74","Kalium Day75","Kalium Day76","Kalium Day77","Kalium Day78","Kalium Day79","Kalium Day80","Kalium Day81","Kalium Day82","Kalium Day83","Kalium Day84","Kalium Day85","Kalium Day86","Kalium Day87","Kalium Day88","Kalium Day89","Kalium Day90","Kalium Day91","Kalium Day92","Kalium Day93","Kalium Day94","Kalium Day95","Kalium Day96","Kalium Day97","Kalium Day98","Kalium Day99","Kalium Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 150mg daily-dose",
       x = "Day of measurement",
       y = "Potassium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n()) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 200mg daily-dose",
       x = "Day of measurement",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 8))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_diclo smooth line plot for diclofenac dose groups",        x = "daily dose (mg)",             y = "AST U/L")	

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_diclo linerar regression for dayly doses",
       x = "daily dose in mg",
       y = "Potassium mmol/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldkal_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups",
       x = "Dose Group",
       y = "Potassium mmol/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Kalzium/Calcium #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_cal <- left_join(ldcal_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_cal %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_cal,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 1) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_diclo boxplot for daily dose",
       x = "dailydose in mg",
       y = "Calcium mmol/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_diclo daily doses of Diclofenac", type = "np",
  ylab = "Calcium mmol/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 50mg daily-dose",
       x = "Day of measurement",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 3))


```

## dose time series for 75mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 75mg daily-dose",
       x = "Day of measurement",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 3))


```


## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 100mg daily-dose",
       x = "Day of measurement",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 150mg daily-dose",
       x = "Day of measurement",
       y = "Calcium mmol/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n()) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 200mg daily-dose",
       x = "Day of measurement",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_diclo smooth line plot for diclofenac dose groups",        x = "daily dose (mg)",             y = "Calcium mmol/l")	

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_diclo linerar regression for dayly doses",
       x = "daily dose in mg",
       y = "Calcium mmol/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldcal_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups",
       x = "Dose Group",
       y = "Calcium mmol/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for Glucose #
#####
#####
#####
#####

```{r}
lvdiclo_dosedata_glu <- left_join(ldglu_data,lvdiclo_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvdiclo_dosedata_glu %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvdiclo_dosedata_glu,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Diclofenac") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 10) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_diclo boxplot for daily dose",
       x = "dailydose in mg",
       y = "Glucose mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(50, 75, 100, 150, 200)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(50,75, 100, 150,200)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_diclo daily doses of Diclofenac", type = "np",
  ylab = "Glucose mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 50mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(50)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 50mg daily-dose",
       x = "Day of measurement",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 170))


```

## dose time series for 75mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(75)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", "GPT Day6", "GPT Day11","GPT Day12", "GPT Day16", "GPT Day26"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 75mg daily-dose",
       x = "Day of measurement",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 170))


```



## line plot for 100mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(100)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 100mg daily-dose",
       x = "Day of measurement",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 150mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(150)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n())
  
### for lineplot
#dd_100mg$Attribute <- 
#  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
#                                          "GPT Day4","GPT Day5", "GPT Day6",
#                                          "GPT Day7","GPT Day8", "GPT Day9", 
#                                          "GPT Day10","GPT Day11","GPT Day12",
#                                          "GPT Day17","GPT Day20","GPT Day26",
#"GPT Day_Unknown"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 150mg daily-dose",
       x = "Day of measurement",
       y = "Glucose mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 200mg#### 
```{r}

dd_200mg <- dose_result %>% 
  filter(totaldose_mg %in% c(200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE), count= n()) #%>% 
 # filter(!is.na(mean_labread) & is.finite(mean_labread) & is.finite(sd_labread))
  
### for lineplot
#  dd_200mg$Attribute <- 
#    factor(dd_200mg$Attribute,levels = c( "GPT Day5","GPT Day11", 
#                                            "GPT Day26"))


ggplot(dd_200mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + geom_text(aes(label = count), vjust = -1.5, size = 5) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 200mg daily-dose",
       x = "Day of measurement",
       y = "Erythrocytes cells/ul",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Diclofenac") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```

```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_diclo smooth line plot for diclofenac dose groups",        x = "daily dose (mg)",             y = "Glucose mg/dl")	

```

```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_diclo linerar regression for dayly doses",
       x = "daily dose in mg",
       y = "Glucose mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 100, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 100, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liverdiclo_labreadsall <- left_join(CD_liverdiclo,ldglu_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liverdiclo_labreadsall
```


```{r}
CD_liverdiclo_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups",
       x = "Dose Group",
       y = "Glucose mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```
