---
title: "Regression_correlation_analysis"
author: "Arun Kumar"
date: "2025-09-29"
output: html_document
---

# Day... muss immer geändert werden für alle Tage die man haben will!!!!!!!!!!!!!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
library(dplyr)
library(GGally)
library(tidyr)
library(readxl)
library(Cairo)
library(ggplot2)
```





```{r}
gender_data <- read_excel("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/gender plots - bmi/gender_info_full.xlsx",
           sheet = 1, skip = 1)

gender_data1 <- gender_data %>%
  dplyr::select(1:4) %>%
  dplyr::mutate(
    Gender = dplyr::case_when(
      Male == 1 ~ "Male",
      Female == 1 ~ "Female"
    ),
    value = dplyr::case_when(
      Male == 1 ~ 1,
      Female == 1 ~ 0
    )
  ) %>% 
  dplyr::select(1,2,5,6)
gender_data1
```
```{r}
ld_gpt_dose_result1
```

### GPT ########################################################################

```{r}
gptdd_withgender <- left_join(ld_gpt_dose_result1,gender_data1, by = ("Edited_BfArM Nummer2"))
gptdd_withgender
```

  
```{r}
gpt_dd_n1 <- ld_gpt_dose_result1  %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n(),.groups = "drop") %>% 
  arrange(n) %>% 
  filter(n == 1)
gpt_dd_n1 

```


```{r}
gender_dd_for_n1 <- left_join(gpt_dd_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_dd_for_n1
```

```{r}

gptdd_withgender_n1 <- 
gptdd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_dd_for_n1$`Edited_BfArM Nummer2`)%>%
  mutate(Gender = as.factor(Gender))

gptdd_withgender_n1

```


```{r}
gptdd_withgender_n1 %>%
  dplyr::select(labreads) %>%
 dlookr::normality()


```


```{r}
library(flextable)

gptdd_withgender_n1 %>% 
  select(dailydose,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
gptdd_withgender_n1 %>% 
  select(labreads,dailydose,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```



```{r}
library(GGally)
#1setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")

liver_diclo_gpt_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue <- gptdd_withgender_n1 %>% 
  select(labreads, dailydose, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_gpt_full_correlation labvalue with daily dose by gender for patients with 1 labvalue")

liver_diclo_gpt_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_correlation daily dose by gender for patients with 1 labvalue.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  gptdd_withgender_n1$labreads,
  gptdd_withgender_n1$dailydose,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

gptdd_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, dailydose, method = "spearman"),
    p_value  = cor.test(labreads, dailydose, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ dailydose, data = gptdd_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
gpt_dd_n_morethanone <- ld_gpt_dose_result1 %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

gpt_dd_n_morethanone
```

### multiple read have to seprate based on gptday(1to N)

```{r}
gender_data_for_nmore <- left_join(gpt_dd_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

gptdd_withgender_nmore <- 
gptdd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  mutate(Gender = as.factor(Gender))

gptdd_withgender_nmore

```


1

```{r}
# Lade notwendige Pakete
library(dplyr)
library(ggplot2)
library(GGally)

# Variablen
my_gender    <- "Male"
my_attribute <- "GPT Day1"

# Normalität der Daten
norm_res <- gptdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>%
  select(dailydose, labreads) %>%
  drop_na() %>%
  normality() %>%  # Achte darauf, dass 'normality' richtig definiert ist!
  dplyr::mutate(Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender))

print(norm_res)

# Korrelation der Daten
p1 <- gptdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na() %>%
  mutate(
    labreads_log = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(
    columns = 1:2,
    aes(colour = Gender),
    lower = list(continuous = "smooth"),
    upper = list(continuous = wrap("cor", method = "spearman"))
  ) + 
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Speichern als SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_spearman labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7,
  height = 6
)

print(p1)

```


## here just need to change the gender according day
```{r}
my_gender    <- "Male"
my_attribute <- "GPT Day2"

## get normality of data ##
norm_res <- gptdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%2
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- gptdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_spearman labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)
```


```{r}
## Correlation + Gender bar plots ##
p2 <- gptdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_correlation labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- gptdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "GPT (U/L)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_Polynomial regression labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```


## here just need to change the gender according day
```{r}
my_gender    <- "Female"
my_attribute <- "GPT Day2"

## get normality of data ##
norm_res <- gptdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- gptdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_spearman labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- gptdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_correlation labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- gptdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "GPT (U/L)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_Polynomial regression labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```




#################################################################################
### cumulative dose ###############################################################
################################################################################

```{r}
gptdata_withgender <- left_join(gpt_dosedata,gender_data1, by = ("Edited_BfArM Nummer2"))
gptdata_withgender
```

  
```{r}
gpt_dose_n1 <- gpt_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n == 1)
gpt_dose_n1 

```


```{r}
gender_data_for_n1 <- left_join(gpt_dose_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_n1
```

```{r}

gptdata_withgender_n1 <- 
gptdata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_n1$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

gptdata_withgender_n1

```


### Patienten mit nur einem Laborwert ##########################################

```{r}
library(flextable)

gptdata_withgender_n1 %>% 
  select(Parameter,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
gptdata_withgender_n1 %>% 
  select(labreads,Parameter,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```


```{r}
library(GGally)

liver_diclo_gpt_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue <- gptdata_withgender_n1 %>% 
  select(labreads, Parameter, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_gpt_full_correlation labvalue with cumulative dose by gender for patients with 1 labvalue")

liver_diclo_gpt_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_correlation cumulative dose by gender for patients with 1 labvalue.svg.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  gptdata_withgender_n1$labreads,
  gptdata_withgender_n1$Parameter,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

gptdata_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, Parameter, method = "spearman"),
    p_value  = cor.test(labreads, Parameter, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ Parameter, data = gptdata_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
gpt_dosedata_n_morethanone <- gpt_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

gpt_dosedata_n_morethanone
```

### multiple read have to seprate based on gptday(1to N)

```{r}
gender_data_for_nmore <- left_join(gpt_dosedata_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

gptcd_withgender_nmore <- 
gptdata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

gptcd_withgender_nmore

```


## here just need to change the gender according day
```{r}
my_gender    <- "Male"
my_attribute <- "GPT Day2"

## get normality of data ##
norm_res <- gptcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(Parameter, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
library(GGally)
library(ggplot2)

p1 <- gptcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    Parameter_log = log1p(Parameter)
  ) %>%
  select(labreads_log, Parameter_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_spearman labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- gptcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, Parameter, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_correlation labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)


## Regression analysis ##
model_data <- gptdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation und log-log-Achsen
p_reg <- model_data %>% 
  ggplot(aes(x = Parameter, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with cumulative dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Cumulative Dose (mg) (log-scale)",
    y = "GPT (U/L) (log-scale)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_Polynomial regression labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)

```


```{r}
my_gender    <- "Female"
my_attribute <- "GPT Day2"

## get normality of data ##
norm_res <- gptcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(Parameter, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
library(GGally)
library(ggplot2)

p1 <- gptcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    Parameter_log = log1p(Parameter)
  ) %>%
  select(labreads_log, Parameter_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_spearman labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- gptcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, Parameter, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_correllation labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)


## Regression analysis ##
model_data <- gptdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation und log-log-Achsen
p_reg <- model_data %>% 
  ggplot(aes(x = Parameter, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  theme(
    plot.margin = margin(t = 20, r = 20, b = 40, l = 20)  # mehr Platz oben
  ) +
  labs(
    title = paste0("Polynomial regression with cumulative dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Cumulative Dose (mg) (log-scale)",
    y = "GPT (U/L) (log-scale)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_gpt/gender_correlation_plots/liver diclo_gpt_full_Polynomial regression labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```



################################################################################
### got ########################################################################

```{r}
gotdd_withgender <- left_join(got_ld_gpt_dose_result1,gender_data1, by = ("Edited_BfArM Nummer2"))
gotdd_withgender
```

  
```{r}
got_dd_n1 <- got_ld_gpt_dose_result1  %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n(),.groups = "drop") %>% 
  arrange(n) %>% 
  filter(n == 1)
got_dd_n1 

```


```{r}
gender_dd_for_n1 <- left_join(got_dd_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_dd_for_n1
```

```{r}

gotdd_withgender_n1 <- 
gotdd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_dd_for_n1$`Edited_BfArM Nummer2`)%>%
  mutate(Gender = as.factor(Gender))

gotdd_withgender_n1

```


```{r}
gotdd_withgender_n1 %>%
  dplyr::select(labreads) %>%
 dlookr::normality()


```


```{r}
library(flextable)

gotdd_withgender_n1 %>% 
  select(dailydose,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
gotdd_withgender_n1 %>% 
  select(labreads,dailydose,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```



```{r}
library(GGally)
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")

liver_diclo_got_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue <- gotdd_withgender_n1 %>% 
  select(labreads, dailydose, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_got_full_correlation labvalue with daily dose by gender for patients with 1 labvalue")

liver_diclo_got_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_correlation daily dose by gender for patients with 1 labvalue.svg", height = 6, width = 8)
print(liver_diclo_got_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  gotdd_withgender_n1$labreads,
  gotdd_withgender_n1$dailydose,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

gotdd_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, dailydose, method = "spearman"),
    p_value  = cor.test(labreads, dailydose, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ dailydose, data = gotdd_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
got_dd_n_morethanone <- got_ld_gpt_dose_result1 %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

got_dd_n_morethanone
```

### multiple read have to seprate based on gotday(1to N)

```{r}
gender_data_for_nmore <- left_join(got_dd_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

gotdd_withgender_nmore <- 
gotdd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  mutate(Gender = as.factor(Gender))

gotdd_withgender_nmore

```


## here just need to change the gender according day
```{r}
my_gender    <- "Male"
my_attribute <- "GOT Day2"

## get normality of data ##
norm_res <- gotdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- gotdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_spearman labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- gotdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_correlation labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- gotdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "got (U/L)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_Polynomial regression labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```


## here just need to change the gender according day
```{r}
my_gender    <- "Female"
my_attribute <- "GOT Day2"

## get normality of data ##
norm_res <- gotdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- gotdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_spearman labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- gotdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_correlation labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- gotdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "got (U/L)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_Polynomial regression labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```




#################################################################################
### cumulative dose ###############################################################
################################################################################

```{r}
gotdata_withgender <- left_join(got_dosedata,gender_data1, by = ("Edited_BfArM Nummer2"))
gotdata_withgender
```

  
```{r}
got_dose_n1 <- got_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n == 1)
got_dose_n1 

```


```{r}
gender_data_for_n1 <- left_join(got_dose_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_n1
```

```{r}

gotdata_withgender_n1 <- 
gotdata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_n1$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

gotdata_withgender_n1

```


### Patienten mit nur einem Laborwert ##########################################

```{r}
library(flextable)

gotdata_withgender_n1 %>% 
  select(Parameter,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
gotdata_withgender_n1 %>% 
  select(labreads,Parameter,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```


```{r}
library(GGally)

liver_diclo_got_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue <- gotdata_withgender_n1 %>% 
  select(labreads, Parameter, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_got_full_correlation labvalue with cumulative dose by gender for patients with 1 labvalue")

liver_diclo_got_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_correlation cumulative dose by gender for patients with 1 labvalue.svg.svg", height = 6, width = 8)
print(liver_diclo_got_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  gotdata_withgender_n1$labreads,
  gotdata_withgender_n1$Parameter,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

gotdata_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, Parameter, method = "spearman"),
    p_value  = cor.test(labreads, Parameter, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ Parameter, data = gotdata_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
got_dosedata_n_morethanone <- got_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

got_dosedata_n_morethanone
```

### multiple read have to seprate based on gotday(1to N)

```{r}
gender_data_for_nmore <- left_join(got_dosedata_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

gotcd_withgender_nmore <- 
gotdata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

gotcd_withgender_nmore

```


## here just need to change the gender according day
```{r}
my_gender    <- "Male"
my_attribute <- "GOT Day2"

## get normality of data ##
norm_res <- gotcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(Parameter, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
library(GGally)
library(ggplot2)

p1 <- gotcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    Parameter_log = log1p(Parameter)
  ) %>%
  select(labreads_log, Parameter_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_spearman labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- gotcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, Parameter, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_correlation labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)


## Regression analysis ##
model_data <- gotdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation und log-log-Achsen
p_reg <- model_data %>% 
  ggplot(aes(x = Parameter, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with cumulative dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Cumulative Dose (mg) (log-scale)",
    y = "got (U/L) (log-scale)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_Polynomial regression labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)

```


```{r}
my_gender    <- "Female"
my_attribute <- "GOT Day2"

## get normality of data ##
norm_res <- gotcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(Parameter, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
library(GGally)
library(ggplot2)

p1 <- gotcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    Parameter_log = log1p(Parameter)
  ) %>%
  select(labreads_log, Parameter_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_spearman labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- gotcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, Parameter, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_correllation labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)


## Regression analysis ##
model_data <- gotdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation und log-log-Achsen
p_reg <- model_data %>% 
  ggplot(aes(x = Parameter, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  theme(
    plot.margin = margin(t = 20, r = 20, b = 40, l = 20)  # mehr Platz oben
  ) +
  labs(
    title = paste0("Polynomial regression with cumulative dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Cumulative Dose (mg) (log-scale)",
    y = "got (U/L) (log-scale)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_got/gender_correlation_plots/liver diclo_got_full_Polynomial regression labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```



################################################################################
### ggt ########################################################################

```{r}
ggtdd_withgender <- left_join(ggt_ld_gpt_dose_result1,gender_data1, by = ("Edited_BfArM Nummer2"))
ggtdd_withgender
```

  
```{r}
ggt_dd_n1 <- ggt_ld_gpt_dose_result1  %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n(),.groups = "drop") %>% 
  arrange(n) %>% 
  filter(n == 1)
ggt_dd_n1 

```


```{r}
gender_dd_for_n1 <- left_join(ggt_dd_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_dd_for_n1
```

```{r}

ggtdd_withgender_n1 <- 
ggtdd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_dd_for_n1$`Edited_BfArM Nummer2`)%>%
  mutate(Gender = as.factor(Gender))

ggtdd_withgender_n1

```


```{r}
ggtdd_withgender_n1 %>%
  dplyr::select(labreads) %>%
 dlookr::normality()


```


```{r}
library(flextable)

ggtdd_withgender_n1 %>% 
  select(dailydose,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
ggtdd_withgender_n1 %>% 
  select(labreads,dailydose,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```



```{r}
library(GGally)
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")

liver_diclo_ggt_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue <- ggtdd_withgender_n1 %>% 
  select(labreads, dailydose, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_ggt_full_correlation labvalue with daily dose by gender for patients with 1 labvalue")

liver_diclo_ggt_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_correlation daily dose by gender for patients with 1 labvalue.svg", height = 6, width = 8)
print(liver_diclo_ggt_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  ggtdd_withgender_n1$labreads,
  ggtdd_withgender_n1$dailydose,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

ggtdd_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, dailydose, method = "spearman"),
    p_value  = cor.test(labreads, dailydose, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ dailydose, data = ggtdd_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
ggt_dd_n_morethanone <- ggt_ld_gpt_dose_result1 %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

ggt_dd_n_morethanone
```

### multiple read have to seprate based on ggtday(1to N)

```{r}
gender_data_for_nmore <- left_join(ggt_dd_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

ggtdd_withgender_nmore <- 
ggtdd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  mutate(Gender = as.factor(Gender))

ggtdd_withgender_nmore

```


## here just need to change the gender according day
```{r}
my_gender    <- "Male"
my_attribute <- "GGT Day2"

## get normality of data ##
norm_res <- ggtdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- ggtdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_spearman labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- ggtdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_correlation labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- ggtdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "ggt (U/L)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_Polynomial regression labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```


## here just need to change the gender according day
```{r}
my_gender    <- "Female"
my_attribute <- "GGT Day2"

## get normality of data ##
norm_res <- ggtdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- ggtdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_spearman labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- ggtdd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_correlation labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- ggtdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "ggt (U/L)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_Polynomial regression labvalue with daily dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```




#################################################################################
### cumulative dose ###############################################################
################################################################################

```{r}
ggtdata_withgender <- left_join(ggt_dosedata,gender_data1, by = ("Edited_BfArM Nummer2"))
ggtdata_withgender
```

  
```{r}
ggt_dose_n1 <- ggt_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n == 1)
ggt_dose_n1 

```


```{r}
gender_data_for_n1 <- left_join(ggt_dose_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_n1
```

```{r}

ggtdata_withgender_n1 <- 
ggtdata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_n1$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

ggtdata_withgender_n1

```


### Patienten mit nur einem Laborwert ##########################################

```{r}
library(flextable)

ggtdata_withgender_n1 %>% 
  select(Parameter,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
ggtdata_withgender_n1 %>% 
  select(labreads,Parameter,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```


```{r}
library(GGally)

liver_diclo_ggt_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue <- ggtdata_withgender_n1 %>% 
  select(labreads, Parameter, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_ggt_full_correlation labvalue with cumulative dose by gender for patients with 1 labvalue")

liver_diclo_ggt_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_correlation cumulative dose by gender for patients with 1 labvalue.svg.svg", height = 6, width = 8)
print(liver_diclo_ggt_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  ggtdata_withgender_n1$labreads,
  ggtdata_withgender_n1$Parameter,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

ggtdata_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, Parameter, method = "spearman"),
    p_value  = cor.test(labreads, Parameter, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ Parameter, data = ggtdata_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
ggt_dosedata_n_morethanone <- ggt_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

ggt_dosedata_n_morethanone
```

### multiple read have to seprate based on ggtday(1to N)

```{r}
gender_data_for_nmore <- left_join(ggt_dosedata_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

ggtcd_withgender_nmore <- 
ggtdata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

ggtcd_withgender_nmore

```






```{r}
my_gender    <- "Female"
my_attribute <- "GGT Day2"

## get normality of data ##
norm_res <- ggtcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(Parameter, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
library(GGally)
library(ggplot2)

p1 <- ggtcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    Parameter_log = log1p(Parameter)
  ) %>%
  select(labreads_log, Parameter_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_spearman labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- ggtcd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, Parameter, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_correllation labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)


## Regression analysis ##
model_data <- ggtdd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation und log-log-Achsen
p_reg <- model_data %>% 
  ggplot(aes(x = Parameter, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  theme(
    plot.margin = margin(t = 20, r = 20, b = 40, l = 20)  # mehr Platz oben
  ) +
  labs(
    title = paste0("Polynomial regression with cumulative dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Cumulative Dose (mg) (log-scale)",
    y = "ggt (U/L) (log-scale)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_ggt/gender_correlation_plots/liver diclo_ggt_full_Polynomial regression labvalue with cumulative dose on_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```





################################################################################
### total_bilirubin ########################################################################

```{r}
total_bilirubindd_withgender <- left_join(total_bilirubin_ld_gpt_dose_result1,gender_data1, by = ("Edited_BfArM Nummer2"))
total_bilirubindd_withgender
```

  
```{r}
total_bilirubin_dd_n1 <- total_bilirubin_ld_gpt_dose_result1  %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n(),.groups = "drop") %>% 
  arrange(n) %>% 
  filter(n == 1)
total_bilirubin_dd_n1 

```


```{r}
gender_dd_for_n1 <- left_join(total_bilirubin_dd_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_dd_for_n1
```

```{r}

total_bilirubindd_withgender_n1 <- 
total_bilirubindd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_dd_for_n1$`Edited_BfArM Nummer2`)%>%
  mutate(Gender = as.factor(Gender))

total_bilirubindd_withgender_n1

```


```{r}
total_bilirubindd_withgender_n1 %>%
  dplyr::select(labreads) %>%
 dlookr::normality()


```


```{r}
library(flextable)

total_bilirubindd_withgender_n1 %>% 
  select(dailydose,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
total_bilirubindd_withgender_n1 %>% 
  select(labreads,dailydose,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```



```{r}
library(GGally)
#setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")

liver_diclo_total_bilirubin_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue <- total_bilirubindd_withgender_n1 %>% 
  select(labreads, dailydose, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_total_bilirubin_full_correlation labvalue with daily dose by gender for patients with 1 labvalue")

liver_diclo_total_bilirubin_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_total_bilirubin_full_correlation_daily_dose_patients_with_1labvalue.svg", height = 6, width = 8)
print(liver_diclo_total_bilirubin_full_correlation__labvalue_with_daily_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  total_bilirubindd_withgender_n1$labreads,
  total_bilirubindd_withgender_n1$dailydose,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

total_bilirubindd_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, dailydose, method = "spearman"),
    p_value  = cor.test(labreads, dailydose, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ dailydose, data = total_bilirubindd_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
total_bilirubin_dd_n_morethanone <- total_bilirubin_ld_gpt_dose_result1 %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

total_bilirubin_dd_n_morethanone
```

### multiple read have to seprate based on total_bilirubinday(1to N)

```{r}
gender_data_for_nmore <- left_join(total_bilirubin_dd_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

total_bilirubindd_withgender_nmore <- 
total_bilirubindd_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  mutate(Gender = as.factor(Gender))

total_bilirubindd_withgender_nmore

```


## here just need to change the gender according day
```{r}
my_gender    <- "Male"
my_attribute <- "TotalBilirubin Day2"

## get normality of data ##
norm_res <- total_bilirubindd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- total_bilirubindd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_spearman daily dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- total_bilirubindd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_correlation daily dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- total_bilirubindd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "total_bilirubin (mg/dl)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_Poly regression daily dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```


## here just need to change the gender according day
```{r}
my_gender    <- "Female"
my_attribute <- "TotalBilirubin Day2"

## get normality of data ##
norm_res <- total_bilirubindd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(dailydose, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
p1 <- total_bilirubindd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    dailydose_log = log1p(dailydose)
  ) %>%
  select(labreads_log, dailydose_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_spearman daily dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- total_bilirubindd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, dailydose, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with daily dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_correlation daily dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)



## Regression analysis ##
model_data <- total_bilirubindd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation
p_reg <- model_data %>% 
  ggplot(aes(x = dailydose, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  labs(
    title = paste0("Polynomial regression with daily dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Daily Dose (mg)",
    y = "total_bilirubin (mg/dl)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_Poly regression daily dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```




#################################################################################
### cumulative dose ###############################################################
################################################################################

```{r}
total_bilirubindata_withgender <- left_join(total_bilirubin_dosedata,gender_data1, by = ("Edited_BfArM Nummer2"))
total_bilirubindata_withgender
```

  
```{r}
total_bilirubin_dose_n1 <- total_bilirubin_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n == 1)
total_bilirubin_dose_n1 

```


```{r}
gender_data_for_n1 <- left_join(total_bilirubin_dose_n1,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_n1
```

```{r}

total_bilirubindata_withgender_n1 <- 
total_bilirubindata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_n1$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

total_bilirubindata_withgender_n1

```


### Patienten mit nur einem Laborwert ##########################################

```{r}
library(flextable)

total_bilirubindata_withgender_n1 %>% 
  select(Parameter,labreads) %>% 
  normality()#%>% 
 #regulartable()
```




```{r}
total_bilirubindata_withgender_n1 %>% 
  select(labreads,Parameter,Gender) %>% 
ggpairs(columns = 1:3,
        aes(colour = Gender),
        lower = list(continuous = "smooth"),
        upper = list(continous = wrap ("cor", method = "pearson")))
```


```{r}
library(GGally)

liver_diclo_total_bilirubin_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue <- total_bilirubindata_withgender_n1 %>% 
  select(labreads, Parameter, Gender) %>% 
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman")))+
  labs(title = "liver diclo_total_bilirubin_full_correlation labvalue with cumulative dose by gender for patients with 1 labvalue")

liver_diclo_total_bilirubin_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue
dir.create("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_total_bilirubin_full_correlation_cum_dose_patients_with 1labv.svg.svg", height = 6, width = 8)
print(liver_diclo_total_bilirubin_full_correlation__labvalue_with_cumulative_dose_by_gender_for_patients_with_1_labvalue)
dev.off()
```



```{r}

# Overall Spearman correlation
cor.test(
  total_bilirubindata_withgender_n1$labreads,
  total_bilirubindata_withgender_n1$Parameter,
  method = "spearman"
)

# Spearman correlation by Gender
library(dplyr)

total_bilirubindata_withgender_n1 %>%
  group_by(Gender) %>%
  summarise(
    Spearman = cor(labreads, Parameter, method = "spearman"),
    p_value  = cor.test(labreads, Parameter, method = "spearman")$p.value
  )


```

#### Linear regression ###
```{r}
# Fit model
model <- lm(labreads ~ Parameter, data = total_bilirubindata_withgender_n1)
summary(model)


```



#Patients for N=2 and more ##

#################################################################################

```{r}
total_bilirubin_dosedata_n_morethanone <- total_bilirubin_dosedata %>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  group_by(`Edited_BfArM Nummer2`) %>% 
  summarize(n = n()) %>% 
  arrange(n) %>% 
  filter(n !=1)

total_bilirubin_dosedata_n_morethanone
```

### multiple read have to seprate based on total_bilirubinday(1to N)

```{r}
gender_data_for_nmore <- left_join(total_bilirubin_dosedata_n_morethanone,gender_data1, by ="Edited_BfArM Nummer2")
gender_data_for_nmore
```

```{r}

total_bilirubincd_withgender_nmore <- 
total_bilirubindata_withgender %>% 
  dplyr::filter(`Edited_BfArM Nummer2` %in% gender_data_for_nmore$`Edited_BfArM Nummer2`)%>% 
  dplyr::filter(Treatment.x == "Leber_Diclo",
                Kathegorie == "Cummulative Dosis",
                Treatment.y == "Diclofenac") %>% 
  filter(!grepl("_From Start",attribute))%>% 
  filter(!grepl("_From start",attribute)) %>% 
  filter(!grepl("DBS", attribute)) %>% 
  filter(Parameter != 0) %>% 
  mutate(Gender = as.factor(Gender))

total_bilirubincd_withgender_nmore

```





```{r}
my_gender    <- "Female"
my_attribute <- "TotalBilirubin Day2"

## get normality of data ##
norm_res <- total_bilirubincd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  select(Parameter, labreads) %>% 
  drop_na() %>% 
  normality() %>%
  dplyr::mutate(
    Condition = paste0("Attribute: ", my_attribute, ", Gender: ", my_gender)
  )

print(norm_res)


## correlation of data ##
library(GGally)
library(ggplot2)

p1 <- total_bilirubincd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  mutate(
    labreads_log  = log1p(labreads),
    Parameter_log = log1p(Parameter)
  ) %>%
  select(labreads_log, Parameter_log, Gender) %>%
  ggpairs(columns = 1:2,
          aes(colour = Gender),
          lower = list(continuous = "smooth"),
          upper = list(continuous = wrap("cor", method = "spearman"))) +
  labs(title = paste0("Spearman correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_spearman cum dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p1,
  width = 7, height = 6
)
print(p1)

## Correlation + Gender bar plots ##
p2 <- total_bilirubincd_withgender_nmore %>% 
  filter(attribute == my_attribute, Gender == my_gender) %>% 
  drop_na() %>% 
  select(labreads, Parameter, Gender) %>%
  ggpairs(columns = 1:3,
          aes(colour = Gender),
          diag = list(discrete = wrap("barDiag", position = "stack")),
          upper = list(continuous = wrap("cor", method = "spearman")),
          lower = list(continuous = "smooth")) +
  labs(title = paste0("Correlation with cumulative dose on (", my_attribute, ", ", my_gender, ")"))

# Save as SVG
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_correlation cum dose_", my_attribute, "_", my_gender, ".svg"),
  plot = p2,
  width = 8, height = 6
)


print(p2)


## Regression analysis ##
model_data <- total_bilirubindd_withgender_nmore %>%
  filter(attribute == my_attribute, Gender == my_gender) %>%
  drop_na()

# Regressionsmodell
model <- lm(labreads ~ poly(dailydose, 2, raw = TRUE), data = model_data)

# Zusammenfassung
summary_model <- summary(model)
coefs <- coef(model)
r_squared <- summary_model$r.squared
p_values <- summary_model$coefficients[, "Pr(>|t|)"]

# Hilfsfunktion zur P-Wert-Formatierung
format_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "< 0.001" else round(p, 3)
}

# Info-Text für Annotation
info_text <- paste0(
  "y = ", round(coefs[1], 2), 
  " + ", round(coefs[2], 2), "x", 
  " + ", round(coefs[3], 2), "x²\n",
  "R² = ", round(r_squared, 2), "\n",
  "p₁ = ", format_p(p_values[2]), ", p₂ = ", format_p(p_values[3]), "\n",
  "n = ", nrow(model_data)
)

# Plot mit Annotation und log-log-Achsen
p_reg <- model_data %>% 
  ggplot(aes(x = Parameter, y = labreads)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2, raw = TRUE),
              se = TRUE, 
              color = "black") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  annotate("text", x = Inf, y = Inf, 
           label = info_text, 
           hjust = 1.1, vjust = 1.2, size = 5, color = "black") +
  theme_minimal(base_size = 14) +
  theme(
    plot.margin = margin(t = 20, r = 20, b = 40, l = 20)  # mehr Platz oben
  ) +
  labs(
    title = paste0("Polynomial regression with cumulative dose on\n (", my_attribute, ", ", my_gender, ")"),
    x = "Cumulative Dose (mg) (log-scale)",
    y = "total_bilirubin (mg/dl) (log-scale)"
  )

print(p_reg)

# Speichern
ggsave(
  filename = paste0("plots_diclofenac/plots_diclofenac_total_bilirubin/gender_correlation_plots/liver diclo_totbili_full_Poly regression cum dose__", my_attribute, "_", my_gender, ".svg"),
  plot = p_reg,
  width = 7, height = 6
)


```













