---
title: "boxplot and lineplot"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r} 
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
```
### labels##
```{r}
# Create a vector with the x-axis labels in the desired order

### for lineplot
gpt_summary_data$Attribute <- factor(gpt_summary_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))

##for boxplt
gptalst_data$Attribute <- factor(gptalst_data$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3", 
              "GPT Day4", "GPT Day5", "GPT Day6", "GPT Day7", 
              "GPT Day8", "GPT Day9", "GPT Day10", "GPT Day11",
              "GPT Day12", "GPT Day16", "GPT Day17", "GPT Day20", 
              "GPT Day26","GPT Day_Unknown"))
```


## code for line plot##
## in filter choose gender either male or female to make the graph##
## choose the full joined data of gender with labreads ##
```{r}
gpt_summary_data <- libualt_data  %>% filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
# Create the line plot with rotated x-axis labels and error bars for both SD and SEM
max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

ggplot(gpt_summary_data, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  # geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "blue") +  # SD error bars in blue
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 0.5, se = TRUE) + # SEM error bars in red
  labs(title = "Line Plot of Mean ALT for Female",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))

```

##### code for boxplot ####


```{r}

library(ggplot2)
library(dplyr)

max_value <- max(gpt_summary_data$mean_labread + gpt_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)

## use the last joined data gender with labreads##
ldalt_data %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  ggplot(aes(x = Attribute, y = labreads)) +
  geom_boxplot() +
  labs(title = "liver_ibu boxplot for daily dose", # ALT for both gender",
       x = "Day of measurement",
       y = "ALT U/L") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###dose data##
```{r}

setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")

dose_data <- read_excel("Dose table.xlsx", sheet = 2)  
  
lvibu_dosedata <- dose_data %>% 
  filter(Attribut == "Leber_Ibu") %>% 
  rename( "Edited_BfArM Nummer2" ="BfArM Nummer_2" )

lvibu_dosedata
```


```{r}
lvibu_dosedata_gptalst <- left_join(libualt_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptalst %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptalst,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # ALT for both gender",
       x = "dailydose in mg",
       y = "ALT U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```


### plot##
```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "ALT U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$Attribute <- 
  factor(dd_100mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_100mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$Attribute <- 
 factor(dd_150mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- 
   factor(dd_150mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1800mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- 
   factor(dd_150mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```
###line plot for 2400mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2400)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- 
   factor(dd_150mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 2400mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```



##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "ALT U/L")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " ALT in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```


###################cumulative dose = CD #######

```{r}
CD_dose <- lvibu_dosedata_gptalst %>% 
  filter(Kathegorie == "Cummulative Dosis" & Treatment == "Ibuprofen")

num_dosetaken <- lvibu_dosedata_gptalst %>% 
  filter(Kathegorie == "Dauer der Einnahme (Tage)" & Treatment == "Ibuprofen") %>% 
  rename("daysofintake" = "Dose_mg") %>% dplyr::select(1,10)

CD_dose_weekdata <- left_join(CD_dose, num_dosetaken, by = ("Edited_BfArM Nummer2")) %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  drop_na(daysofintake)


```


```{r}
cumulativ_4week <- CD_dose_weekdata %>% 
  filter(daysofintake <= 28) %>% 
  mutate(daysofintake = as.factor(daysofintake)) %>% 
  drop_na(Dose_mg)  
  
  
  cumulativ_4week <- cumulativ_4week[cumulativ_4week$`Edited_BfArM Nummer2` != "93008468", ]
  
 cumulativ_4week %>% 
   ggplot( aes(x = daysofintake, y = Dose_mg)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(se = TRUE, color = "red", linetype = "dashed")+
     labs(title = "liver_diclo cummulative dose",
       x = "Number of day",
       y = "Cummulative dose (mg)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
   
```

### Cumulative Dose lower than 10000(mg)########
```{r}

library(dplyr)
library(readxl)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")
CD_liveribu <- read_excel("Diclo_Ibu_Para Dosis Information.xlsx", sheet = 6, skip = 1) %>%
  filter(Cumulative_Dose > 0.0 & Cumulative_Dose <= 10000 & Treatment == "Leber_Ibu")

# Summarize the counts of each Cumulative_Dose
dose_counts <- CD_liveribu %>%
  group_by(Cumulative_Dose) %>%
  summarise(count = n())

# Add the count column back into the original data frame
CD_liveribu <- CD_liveribu %>%
  left_join(dose_counts, by = "Cumulative_Dose")

# View the result
print(CD_liveribu)

  
```

```{r}
CD_liveribu %>% 
  mutate(Cumulative_Dose = as.factor(Cumulative_Dose)) %>% 
  ggplot(aes(x = Cumulative_Dose, y = count))+
  geom_point()+
  labs(title = "Cumultive Dose Ibuprofen",
       x = "cumulative Dose(mg)",
       y = "Number of Patient") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Cumulative Dose higer than 10000(mg)########
```{r}

library(dplyr)
library(readxl)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")
CD_liveribu10k <- read_excel("Diclo_Ibu_Para Dosis Information.xlsx", sheet = 6, skip = 1) %>%
  filter(Cumulative_Dose >= 10000 & Treatment == "Leber_Ibu")

dose_counts10K <-CD_liveribu10k %>%
  group_by(Cumulative_Dose) %>%
  summarise(count = n())

# View the result
#print(CD_liverdiclo1k)

  
```

```{r}
 dose_counts10K %>% 
  mutate(Cumulative_Dose = Cumulative_Dose/10000) %>% 
   mutate(Cumulative_Dose = as.factor(Cumulative_Dose)) %>% 
  ggplot(aes(x = Cumulative_Dose, y = count))+
  geom_point()+
  labs(title = "Cumultive Dose Diclofenac",
       x = "cumulative Dose(g*10)",
       y = "Number of Patient") + ### label y axis according your sample name
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  

```




```{r}
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Arun Testversionen")
read_excel("Medikamente Arun Testversion.xlsx", sheet = 5, skip = 1) %>% 
  filter(Cumulative_Dose > 0.0 & Treatment == "Leber_Ibu")



 

```



```{r}
library(dplyr)
library(readxl)
library(ggplot2)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")
CD_liverIbu <- read_excel("Diclo_Ibu_Para Dosis Information.xlsx", sheet = 6, skip = 1) %>%
  filter(Cumulative_Dose > 0.0 & Treatment == "Leber_Ibu")

# Create dose groups
CD_liveribu <- CD_liveribu %>%
  mutate(Dose_Group = cut(Cumulative_Dose,
                          breaks = c(0, 1000, 5000,20000, Inf),
                          labels = c("50mg to 1g", "1g to 5g", "5g to 20g", "20g < Higher"),
                          right = FALSE)) # right = FALSE to make intervals inclusive of lower bound and exclusive of upper bound

# View the result with dose groups
print(CD_liveribu)

# Plot frequency of each dose group
ggplot(CD_liveribu, aes(x = Dose_Group)) +
  geom_bar() +
  labs(title = "liver_ibu Frequency of Cumulative Dose Groups",
       x = "Dose Group",
       y = "Frequency") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  )

```


```{r}
library(dplyr)
library(readxl)
library(ggplot2)

# Read the Excel file and filter the data
setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/Ergebnis Vergleich dosis_labvalues")
CD_liveribu <- read_excel("Diclo_Ibu_Para Dosis Information.xlsx", sheet = 6, skip = 1) %>%
  filter(Cumulative_Dose > 0.0  & Treatment == "Leber_Ibu")

# Create dose groups
CD_liveribu <- CD_liveribu %>%
  mutate(Dose_Group = cut(Cumulative_Dose,
                          breaks = c(0, 1000, 5000, 20000, Inf),
                          labels = c("50mg to 1g", "1g to 5g", "5g to 20g", " Higher to 20"),
                          right = FALSE)) # right = FALSE to make intervals inclusive of lower bound and exclusive of upper bound

# View the result with dose groups
print(CD_liveribu)

# Plot frequency of each dose group
ggplot(CD_liveribu, aes(x = Dose_Group)) +
  geom_bar() +
  labs(title = "liver_ibu Frequency of Cumulative Dose Groups",
       x = "Dose Group",
       y = "Frequency") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(table(CD_liverdiclo$Dose_Group))))

```


```{r}
CD_liveribu_labreads <- left_join(CD_liveribu,libualt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  filter(Attribute == "GPT Day1") %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreads
```

```{r}
 
 
ggplot(CD_liveribu_labreads, aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # ALT",
       x = "Dose Group",
       y = "ALT U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liveribu_labreads$labreads)))
```



```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libualt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```


```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # ALT",
       x = "Dose Group",
       y = "ALT U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```


##### 
#####
#####
#####
#####
# all graphs new for AST #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptast <- left_join(libuast_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptast %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptast,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(Attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # AST for both gender",
       x = "dailydose in mg",
       y = "AST U/L") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "AST U/L",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$Attribute <- factor(dd_100mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_100mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```
###line plot for 1800mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 2400mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2400)) %>% 
  mutate(Attribute = as.factor(Attribute)) %>% 
  group_by(Attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = Attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 2400mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "AST U/L")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " AST in U/L") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuast_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # ALT",
       x = "Dose Group",
       y = "AST U/L") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for quick #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptquick <- left_join(libuquick_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptquick %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptquick,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # AST for both gender",
       x = "dailydose in mg",
       y = "quick %") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(                     limits = c(0, 130))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "quick %",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- factor(dd_100mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 130))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 130))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 120))


```
###line plot for 1800mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 120))


```

###line plot for 2400mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2400)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 2400mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 120))


```


##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "quick %")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " quick %") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuquick_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # quick",
       x = "Dose Group",
       y = "quick %") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for inr #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptinr <- left_join(libuinr_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptinr %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptinr,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # AST for both gender",
       x = "dailydose in mg",
       y = "inr") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, 2))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "inr",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$Attribute <- factor(dd_100mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "AST U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "ALT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "INR")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " inr") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuinr_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # quick",
       x = "Dose Group",
       y = "inr") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, 2))
```

##### 
#####
#####
#####
#####
# all graphs new for ggt #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptggt <- left_join(libuggt_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptggt %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptggt,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
#breaks_up_to_500 <- seq(0, 500, by = 100)
#additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
#all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # AST for both gender",
       x = "dailydose in mg",
       y = "ggt u/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "ggt u/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "ggt u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "GGT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "GGT U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "ggt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1800mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "ggt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```
###line plot for 2400mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2400)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 2400mg daily-dose",
       x = "Day of measurement",
       y = "ggt U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "ggt U/L")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " ggt u/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuggt_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # quick",
       x = "Dose Group",
       y = "ggt u/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for ldh #
#####
#####
#####
#####
```{r}
lvibu_dosedata_gptldh <- left_join(libuldh_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_gptldh %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_gptldh,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # AST for both gender",
       x = "dailydose in mg",
       y = "ldh u/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "ldh u/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "ldh u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1800mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "ldh U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```





##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "ldh U/L")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " ldh u/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuldh_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # quick",
       x = "Dose Group",
       y = "ldh u/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```

##### 
#####
#####
#####
#####
# all graphs new for total bilirubin #
#####
#####
#####
#####
```{r}
lvibu_dosedata_totbili <- left_join(libutotbili_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_totbili %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_totbili,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # AST for both gender",
       x = "dailydose in mg",
       y = "totbili mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "totbili mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day4","TotalBilirubin Day6","TotalBilirubin Day8","TotalBilirubin Day10","TotalBilirubin Day13" ))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day4","TotalBilirubin Day6","TotalBilirubin Day8","TotalBilirubin Day10","TotalBilirubin Day19" ))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", "TotalBilirubin Day8", "TotalBilirubin Day9", 
"TotalBilirubin Day10", "TotalBilirubin Day11","TotalBilirubin Day12","TotalBilirubin Day13","TotalBilirubin Day14","TotalBilirubin Day15","TotalBilirubin Day16","TotalBilirubin Day17","TotalBilirubin Day18","TotalBilirubin Day19","TotalBilirubin Day20","TotalBilirubin Day21","TotalBilirubin Day22","TotalBilirubin Day23","TotalBilirubin Day24","TotalBilirubin Day25","TotalBilirubin Day26","TotalBilirubin Day27","TotalBilirubin Day28","TotalBilirubin Day29","TotalBilirubin Day30","TotalBilirubin Day31","TotalBilirubin Day32","TotalBilirubin Day33","TotalBilirubin Day34","TotalBilirubin Day35","TotalBilirubin Day36","TotalBilirubin Day37","TotalBilirubin Day38","TotalBilirubin Day39","TotalBilirubin Day40","TotalBilirubin Day41","TotalBilirubin Day42","TotalBilirubin Day43","TotalBilirubin Day44","TotalBilirubin Day45","TotalBilirubin Day46","TotalBilirubin Day47","TotalBilirubin Day48","TotalBilirubin Day49","TotalBilirubin Day50","TotalBilirubin Day51","TotalBilirubin Day52","TotalBilirubin Day53","TotalBilirubin Day54","TotalBilirubin Day55","TotalBilirubin Day56","TotalBilirubin Day57","TotalBilirubin Day58","TotalBilirubin Day59","TotalBilirubin Day60"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1800mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", "TotalBilirubin Day8", "TotalBilirubin Day9", 
"TotalBilirubin Day10", "TotalBilirubin Day11","TotalBilirubin Day12","TotalBilirubin Day13","TotalBilirubin Day14","TotalBilirubin Day15","TotalBilirubin Day16","TotalBilirubin Day17","TotalBilirubin Day18","TotalBilirubin Day19","TotalBilirubin Day20","TotalBilirubin Day21","TotalBilirubin Day22","TotalBilirubin Day23","TotalBilirubin Day24","TotalBilirubin Day25","TotalBilirubin Day26","TotalBilirubin Day27","TotalBilirubin Day28","TotalBilirubin Day29","TotalBilirubin Day30","TotalBilirubin Day31","TotalBilirubin Day32","TotalBilirubin Day33","TotalBilirubin Day34","TotalBilirubin Day35","TotalBilirubin Day36","TotalBilirubin Day37","TotalBilirubin Day38","TotalBilirubin Day39","TotalBilirubin Day40","TotalBilirubin Day41","TotalBilirubin Day42","TotalBilirubin Day43","TotalBilirubin Day44","TotalBilirubin Day45","TotalBilirubin Day46","TotalBilirubin Day47","TotalBilirubin Day48","TotalBilirubin Day49","TotalBilirubin Day50","TotalBilirubin Day51","TotalBilirubin Day52","TotalBilirubin Day53","TotalBilirubin Day54","TotalBilirubin Day55","TotalBilirubin Day56","TotalBilirubin Day57","TotalBilirubin Day58","TotalBilirubin Day59","TotalBilirubin Day60"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "totbili",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


###line plot for 2400mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", "TotalBilirubin Day8", "TotalBilirubin Day9", 
"TotalBilirubin Day10", "TotalBilirubin Day11","TotalBilirubin Day12","TotalBilirubin Day13","TotalBilirubin Day14","TotalBilirubin Day15","TotalBilirubin Day16","TotalBilirubin Day17","TotalBilirubin Day18","TotalBilirubin Day19","TotalBilirubin Day20","TotalBilirubin Day21","TotalBilirubin Day22","TotalBilirubin Day23","TotalBilirubin Day24","TotalBilirubin Day25","TotalBilirubin Day26","TotalBilirubin Day27","TotalBilirubin Day28","TotalBilirubin Day29","TotalBilirubin Day30","TotalBilirubin Day31","TotalBilirubin Day32","TotalBilirubin Day33","TotalBilirubin Day34","TotalBilirubin Day35","TotalBilirubin Day36","TotalBilirubin Day37","TotalBilirubin Day38","TotalBilirubin Day39","TotalBilirubin Day40","TotalBilirubin Day41","TotalBilirubin Day42","TotalBilirubin Day43","TotalBilirubin Day44","TotalBilirubin Day45","TotalBilirubin Day46","TotalBilirubin Day47","TotalBilirubin Day48","TotalBilirubin Day49","TotalBilirubin Day50","TotalBilirubin Day51","TotalBilirubin Day52","TotalBilirubin Day53","TotalBilirubin Day54","TotalBilirubin Day55","TotalBilirubin Day56","TotalBilirubin Day57","TotalBilirubin Day58","TotalBilirubin Day59","TotalBilirubin Day60"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "totbili mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```




##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "total bilirubin mg/dl")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " totbili mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 50, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 50, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libutotbili_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # quick",
       x = "Dose Group",
       y = "totbili mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, 50))
```

##### 
#####
#####
#####
#####
# all graphs new for ap #
#####
#####
#####
#####
```{r}
lvibu_dosedata_ap <- left_join(libuap_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_ap %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_ap,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 100)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # ap for both gender",
       x = "dailydose in mg",
       y = "ap u/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "ap u/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "ap u/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c("AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1800mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1800mg daily-dose",
       x = "Day of measurement",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 2400mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(2400)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
 dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 2400mg daily-dose",
       x = "Day of measurement",
       y = "ap U/L",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "ap U/L")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " ap u/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 2500, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 2400, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libuap_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # quick",
       x = "Dose Group",
       y = "ap u/l") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```


##### 
#####
#####
#####
#####
# all graphs new for Creatinine #
#####
#####
#####
#####
```{r}
lvibu_dosedata_krea <- left_join(libukrea_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_krea %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_krea,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 1)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # ap for both gender",
       x = "dailydose in mg",
       y = "creatinine mg/dl") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "creatinine mg/dl",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$attribute <- factor(dd_50mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c( "Kreatinin Day1", "Kreatinin Day2", "Kreatinin Day3","Kreatinin Day4","Kreatinin Day5", "Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10", "Kreatinin Day11","Kreatinin Day12","Kreatinin Day13","Kreatinin Day14","Kreatinin Day15","Kreatinin Day16","Kreatinin Day17","Kreatinin Day18","Kreatinin Day19","Kreatinin Day20","Kreatinin Day21","Kreatinin Day22","Kreatinin Day23","Kreatinin Day24","Kreatinin Day25","Kreatinin Day26","Kreatinin Day27","Kreatinin Day28","Kreatinin Day29","Kreatinin Day30","Kreatinin Day31","Kreatinin Day32","Kreatinin Day33","Kreatinin Day34","Kreatinin Day35","Kreatinin Day36","Kreatinin Day37","Kreatinin Day38","Kreatinin Day39","Kreatinin Day40","Kreatinin Day41","Kreatinin Day42","Kreatinin Day43","Kreatinin Day44","Kreatinin Day45","Kreatinin Day46","Kreatinin Day47","Kreatinin Day48","Kreatinin Day49","Kreatinin Day50","Kreatinin Day51","Kreatinin Day52","Kreatinin Day53","Kreatinin Day54","Kreatinin Day55","Kreatinin Day56","Kreatinin Day57","Kreatinin Day58","Kreatinin Day59","Kreatinin Day60","Kreatinin Day61","Kreatinin Day62","Kreatinin Day63","Kreatinin Day64","Kreatinin Day65","Kreatinin Day66","Kreatinin Day67","Kreatinin Day68","Kreatinin Day69","Kreatinin Day70","Kreatinin Day71","Kreatinin Day72","Kreatinin Day73","Kreatinin Day74","Kreatinin Day75","Kreatinin Day76","Kreatinin Day77","Kreatinin Day78","Kreatinin Day79","Kreatinin Day80","Kreatinin Day81","Kreatinin Day82","Kreatinin Day83","Kreatinin Day84","Kreatinin Day85","Kreatinin Day86","Kreatinin Day87","Kreatinin Day88","Kreatinin Day89","Kreatinin Day90","Kreatinin Day91","Kreatinin Day92","Kreatinin Day93","Kreatinin Day94","Kreatinin Day95","Kreatinin Day96","Kreatinin Day97","Kreatinin Day98","Kreatinin Day99","Kreatinin Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "Kreatinin Day1", "Kreatinin Day2", "Kreatinin Day3","Kreatinin Day4","Kreatinin Day5", "Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10", "Kreatinin Day11","Kreatinin Day12","Kreatinin Day13","Kreatinin Day14","Kreatinin Day15","Kreatinin Day16","Kreatinin Day17","Kreatinin Day18","Kreatinin Day19","Kreatinin Day20","Kreatinin Day21","Kreatinin Day22","Kreatinin Day23","Kreatinin Day24","Kreatinin Day25","Kreatinin Day26","Kreatinin Day27","Kreatinin Day28","Kreatinin Day29","Kreatinin Day30","Kreatinin Day31","Kreatinin Day32","Kreatinin Day33","Kreatinin Day34","Kreatinin Day35","Kreatinin Day36","Kreatinin Day37","Kreatinin Day38","Kreatinin Day39","Kreatinin Day40","Kreatinin Day41","Kreatinin Day42","Kreatinin Day43","Kreatinin Day44","Kreatinin Day45","Kreatinin Day46","Kreatinin Day47","Kreatinin Day48","Kreatinin Day49","Kreatinin Day50","Kreatinin Day51","Kreatinin Day52","Kreatinin Day53","Kreatinin Day54","Kreatinin Day55","Kreatinin Day56","Kreatinin Day57","Kreatinin Day58","Kreatinin Day59","Kreatinin Day60","Kreatinin Day61","Kreatinin Day62","Kreatinin Day63","Kreatinin Day64","Kreatinin Day65","Kreatinin Day66","Kreatinin Day67","Kreatinin Day68","Kreatinin Day69","Kreatinin Day70","Kreatinin Day71","Kreatinin Day72","Kreatinin Day73","Kreatinin Day74","Kreatinin Day75","Kreatinin Day76","Kreatinin Day77","Kreatinin Day78","Kreatinin Day79","Kreatinin Day80","Kreatinin Day81","Kreatinin Day82","Kreatinin Day83","Kreatinin Day84","Kreatinin Day85","Kreatinin Day86","Kreatinin Day87","Kreatinin Day88","Kreatinin Day89","Kreatinin Day90","Kreatinin Day91","Kreatinin Day92","Kreatinin Day93","Kreatinin Day94","Kreatinin Day95","Kreatinin Day96","Kreatinin Day97","Kreatinin Day98","Kreatinin Day99","Kreatinin Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$attribute <- factor(dd_150mg$attribute,levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "creatinine mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "creatinine mg/dl")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " creatinine mg/dl") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 5, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 5, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libukrea_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # quick",
       x = "Dose Group",
       y = "creatinine mg/dl") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, 3))
```

##### 
#####
#####
#####
#####
# all graphs new for crp #
#####
#####
#####
#####
```{r}
lvibu_dosedata_crp <- left_join(libucrp_data,lvibu_dosedata, by = ("Edited_BfArM Nummer2")) %>% 
  dplyr::select(!7)

```

```{r}
dd_amount <- lvibu_dosedata_crp %>%
  filter(Kathegorie == "Häufigkeit der Einnahme pro Tag")%>%
  rename("numberofdose" = "Dose_mg") %>%  dplyr::select(1,8,10)

dd_amount
```

```{r}

dose_result <- left_join(lvibu_dosedata_crp,dd_amount, by = ("Edited_BfArM Nummer2")) %>%
  filter(Kathegorie.x == "Dosis (Mg/Verabreichung)" & Treatment == "Ibuprofen") %>%
  mutate(totaldose_mg = Dose_mg*numberofdose,
   Dose_mg = as.factor(Dose_mg)) %>%
  group_by(Dose_mg) %>%
  distinct()
  #drop_na(numberofdose)

dose_result1 <- dose_result[dose_result$`Edited_BfArM Nummer2` != "93008468", ]

dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 200, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 25, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 10, 50, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 175, 150, totaldose_mg))
dose_result1 <- mutate(dose_result1, totaldose_mg = ifelse(totaldose_mg == 187.5, 150, totaldose_mg))



print(dose_result1)


```

################################################################################

```{r}

dose_summary_data <- dose_result  %>% #filter(gender == "Female") %>% ## change (male and female for data to make graph)
  group_by(attribute) %>%
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE),
    sem_labread = sd(labreads, na.rm = TRUE) / sqrt(n())
  )
max_value <- max(dose_summary_data$mean_labread + dose_summary_data$sem_labread, na.rm = TRUE)
breaks_up_to_500 <- seq(0, 500, by = 10)
additional_breaks <- if (max_value > 500) seq(600, max_value, by = 300) else numeric(0)
all_breaks <- c(breaks_up_to_500, additional_breaks)
```

```{r}

dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg)) %>% 
  ggplot(aes(x = totaldose_mg, y = labreads))+
  geom_boxplot()+
  labs(title = "liver_ibu boxplot for daily dose", # crp for both gender",
       x = "dailydose in mg",
       y = "crp mg/l") +
  theme_classic() +
    theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45)
  )+
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))
  
```

####################################################

```{r}
library(dplyr)

# Filter and prepare data
filtered_data <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>%
  mutate(totaldose_mg = as.factor(totaldose_mg))

# Perform ANOVA
anova_result <- aov(labreads ~ totaldose_mg, data = filtered_data)

# Print summary of the ANOVA result
summary(anova_result)
# Perform Tukey's HSD post-hoc test
tukey_result <- TukeyHSD(anova_result)

# Print summary of the Tukey's HSD result
print(tukey_result)



```

```{r}
library(ggthemes)

dd <- dose_result %>% 
  filter(totaldose_mg %in% c(300,600,800,1200,1800,2400)) %>% 
  group_by(totaldose_mg)

pp <- ggbetweenstats(
  data = dd,
  x = totaldose_mg,
  y = labreads,
  title = "liver_ibu daily doses of Ibuprofen", type = "np",
  ylab = "crp mg/l",
  xlab = "dailydose (mg)")

extract_stats(pp)
print(pp)
```

##########################################
## dose time series for 300mg####

```{r}
dd_50mg <- dose_result %>% 
  filter(totaldose_mg %in% c(300)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
#dd_50mg$Attribute <- factor(dd_50mg$Attribute,levels = c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))

ggplot(dd_50mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 300mg daily-dose",
       x = "Day of measurement",
       y = "quick %",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```


## line plot for 600mg####
```{r}
dd_100mg <- dose_result %>% 
  filter(totaldose_mg %in% c(600)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
  
### for lineplot
dd_100mg$attribute <- factor(dd_100mg$attribute,levels = c( "CRP Day1", "CRP Day2", "CRP Day3","CRP Day4","CRP Day5", "CRP Day6","CRP Day7","CRP Day8","CRP Day9","CRP Day10", "CRP Day11","CRP Day12","CRP Day13","CRP Day14","CRP Day15","CRP Day16","CRP Day17","CRP Day18","CRP Day19","CRP Day20","CRP Day21","CRP Day22","CRP Day23","CRP Day24","CRP Day25","CRP Day26","CRP Day27","CRP Day28","CRP Day29","CRP Day30","CRP Day31","CRP Day32","CRP Day33","CRP Day34","CRP Day35","CRP Day36","CRP Day37","CRP Day38","CRP Day39","CRP Day40","CRP Day41","CRP Day42","CRP Day43","CRP Day44","CRP Day45","CRP Day46","CRP Day47","CRP Day48","CRP Day49","CRP Day50","CRP Day51","CRP Day52","CRP Day53","CRP Day54","CRP Day55","CRP Day56","CRP Day57","CRP Day58","CRP Day59","CRP Day60","CRP Day61","CRP Day62","CRP Day63","CRP Day64","CRP Day65","CRP Day66","CRP Day67","CRP Day68","CRP Day69","CRP Day70","CRP Day71","CRP Day72","CRP Day73","CRP Day74","CRP Day75","CRP Day76","CRP Day77","CRP Day78","CRP Day79","CRP Day80","CRP Day81","CRP Day82","CRP Day83","CRP Day84","CRP Day85","CRP Day86","CRP Day87","CRP Day88","CRP Day89","CRP Day90","CRP Day91","CRP Day92","CRP Day93","CRP Day94","CRP Day95","CRP Day96","CRP Day97","CRP Day98","CRP Day99","CRP Day100"))


ggplot(dd_100mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 600mg daily-dose",
       x = "Day of measurement",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

## line plot for 800mg####
```{r}
dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(800)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE))
#  lab read(!is.na(mean_labread) & is.finite(mean_labread))
  
  
### for lineplot
#dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 800mg daily-dose",
       x = "Day of measurement",
       y = "crp mg/l",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

###line plot for 1200mg#### 
```{r}

dd_150mg <- dose_result %>% 
  filter(totaldose_mg %in% c(1200)) %>% 
  mutate(attribute = as.factor(attribute)) %>% 
  group_by(attribute) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    sd_labread = sd(labreads, na.rm = TRUE)) %>% 
  filter(!is.na(mean_labread) & is.finite(mean_labread))
  
### for lineplot
# dd_150mg$Attribute <- factor(dd_150mg$Attribute,levels = c( "GOT Day1", "GOT Day2", "GOT Day3","GOT Day4","GOT Day5", "GOT Day6","GOT Day7","GOT Day8","GOT Day9","GOT Day10", "GOT Day11","GOT Day12","GOT Day13","GOT Day14","GOT Day15","GOT Day16","GOT Day17","GOT Day18","GOT Day19","GOT Day20","GOT Day21","GOT Day22","GOT Day23","GOT Day24","GOT Day25","GOT Day26","GOT Day27","GOT Day28","GOT Day29","GOT Day30","GOT Day31","GOT Day32","GOT Day33","GOT Day34","GOT Day35","GOT Day36","GOT Day37","GOT Day38","GOT Day39","GOT Day40","GOT Day41","GOT Day42","GOT Day43","GOT Day44","GOT Day45","GOT Day46","GOT Day47","GOT Day48","GOT Day49","GOT Day50","GOT Day51","GOT Day52","GOT Day53","GOT Day54","GOT Day55","GOT Day56","GOT Day57","GOT Day58","GOT Day59","GOT Day60","GOT Day61","GOT Day62","GOT Day63","GOT Day64","GOT Day65","GOT Day66","GOT Day67","GOT Day68","GOT Day69","GOT Day70","GOT Day71","GOT Day72","GOT Day73","GOT Day74","GOT Day75","GOT Day76","GOT Day77","GOT Day78","GOT Day79","GOT Day80","GOT Day81","GOT Day82","GOT Day83","GOT Day84","GOT Day85","GOT Day86","GOT Day87","GOT Day88","GOT Day89","GOT Day90","GOT Day91","GOT Day92","GOT Day93","GOT Day94","GOT Day95","GOT Day96","GOT Day97","GOT Day98","GOT Day99","GOT Day100"))


ggplot(dd_150mg, aes(x = attribute, y = mean_labread, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_labread, ymax = mean_labread + sd_labread), width = 0.2, color = "red") +
  geom_smooth(method = "loess", color = "lightgrey", size = 1, se = FALSE) + # SEM error bars in red
  labs(title = "liver_diclo labvalues for 1200mg daily-dose",
       x = "Day of measurement",
       y = "crp mg/dl",
       caption = "Red error bars: SD") +
  theme_classic() +
  theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = all_breaks,
                     limits = c(0, max_value))


```

##### linear regression###

```{r}
ww <- dose_result %>% 
  filter(Treatment == "Ibuprofen") %>% 
  distinct(`Edited_BfArM Nummer2`, .keep_all = TRUE) %>% 
  group_by(totaldose_mg)

ww
```



```{r}
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth() + labs(title = "liver_ibu smooth line plot for ibuprofen dose groups",        x = "daily dose (mg)",             y = "crp mg/l")

```


```{r}
library(performance)
library(ggplot2)

library(ggplot2)

# Fit the linear model
lm_model <- lm(labreads ~ totaldose_mg, data = dose_result1)

#check_model(lm_model)

# Extract the coefficients
intercept <- coef(lm_model)[1]
slope <- coef(lm_model)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model)$r.squared


```

```{r}
# Create the scatter plot with linear regression line, R-squared, and equation
ggplot(dose_result1, aes(x = totaldose_mg, y = labreads)) +
  geom_point(color = "blue", size = 2) +    # Scatter plot points
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed")+
  labs(title = "liver_ibu linerar regression for dayly doses",
       x = "daily dose in mg",
       y = " crp mg/l") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotate("text", x = 150, y = 50, label = paste("R² =", round(r_squared, 2)), 
           hjust = 1.1, vjust = 2, size = 5, color = "black") +
  annotate("text", x = 150, y = 50, label = equation, 
           hjust = 1.1, vjust = 3.5, size = 5, color = "black")
```

```{r}
CD_liveribu_labreadsall <- left_join(CD_liveribu,libucrp_data, by = "Edited_BfArM Nummer2") %>% 
  drop_na(count) %>% 
  dplyr::select(1,2,3,7,8,9,11,12,13)

CD_liveribu_labreadsall
```

```{r}
CD_liveribu_labreadsall %>% 
  mutate(Dose_Group = as.factor(Dose_Group)) %>% 
  ggplot(aes(x = Dose_Group, y = labreads)) +
  geom_boxplot() +
  geom_jitter()+
  labs(title = "liver_diclo boxplot for cumulative dose groups", # crp",
       x = "Dose Group",
       y = "crp") +
  theme_classic() +
  theme(
    plot.title = element_text(margin = margin(b = 10), color = "black", face = "bold", hjust = 0.5),
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1)
  ) +
  scale_y_continuous(limits = c(0, max(CD_liverdiclo_labreadsall$labreads)))
```