---
title: "Untitled"
output: html_document
date: "2026-04-25"
---

```{r}
library(GGally)
library(dplyr)
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggstatsplot)
library(ggplot2)
library(performance)
library(car)
```

```{r}

setwd("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/hospitalisation")

hospitalisation_data <- read_excel("hospitalisation rawdata.xlsx", sheet = 1)  

#lvdiclo_dosedata <- dose_data %>% 
#  filter(Attribut == "Leber_Diclo") %>% 
#  rename( "Edited_BfArM Nummer2" ="BfArM Nummer_2" )

#lvdiclo_dosedata
hospitalisation_data
```

### gpt #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

gpt_hosp <- left_join(hospitalisation_data_filter, gpt_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
gpt_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- gpt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = gpt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_gpt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_gpt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(gpt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

all_groups_gpt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_gpt_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_gpt_comparison_stat_amb)
dev.off()
```

```{r}
ld_gpt_hosp <- gpt_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_gpt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_gpt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_gpt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_gpt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_gpt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

ld_gpt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_gpt_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_gpt_comparison_stat_amb)
dev.off()
```

```{r}
li_gpt_hosp <- gpt_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_gpt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_gpt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_gpt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_gpt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_gpt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

li_gpt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_gpt_comparison_stat_amb.svg", height = 6, width = 8)
print(li_gpt_comparison_stat_amb)
dev.off()
```

```{r}
lp_gpt_hosp <- gpt_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_gpt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_gpt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_gpt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_gpt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_gpt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

lp_gpt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_gpt_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_gpt_comparison_stat_amb)
dev.off()
```


### gpt peak #####

```{r}
gpt_hosp_peak <- gpt_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_gpt_peak_comparison_stat_amb <- ggbetweenstats(
  data = gpt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_gpt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

all_groups_gpt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_gpt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_gpt_peak_comparison_stat_amb)
dev.off()
```


```{r}
ld_gpt_hosp_peak <- gpt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_gpt_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_gpt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_gpt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

ld_gpt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_gpt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_gpt_peak_comparison_stat_amb)
dev.off()
```


```{r}
li_gpt_hosp_peak <- gpt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_gpt_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_gpt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_gpt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

li_gpt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_gpt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_gpt_peak_comparison_stat_amb)
dev.off()
```


```{r}
lp_gpt_hosp_peak <- gpt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_gpt_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_gpt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_gpt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gpt (u/l)",
  messages = FALSE
)

lp_gpt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_gpt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_gpt_peak_comparison_stat_amb)
dev.off()
```


### got #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

got_hosp <- left_join(hospitalisation_data_filter, got_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
got_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- got_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = got_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_got_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_got_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(got_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_got_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_got_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_got_comparison_stat_amb)
dev.off()
```

```{r}
ld_got_hosp <- got_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_got_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_got_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_got_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_got_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_got_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_got_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_got_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_got_comparison_stat_amb)
dev.off()
```

```{r}
li_got_hosp <- got_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_got_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_got_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_got_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_got_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_got_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_got_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_got_comparison_stat_amb.svg", height = 6, width = 8)
print(li_got_comparison_stat_amb)
dev.off()
```

```{r}
lp_got_hosp <- got_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_got_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_got_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_got_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_got_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_got_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_got_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_got_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_got_comparison_stat_amb)
dev.off()
```


### got peak #####

```{r}
got_hosp_peak <- got_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_got_peak_comparison_stat_amb <- ggbetweenstats(
  data = got_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_got_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

#all_groups_got_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_got_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_got_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_got_hosp_peak <- got_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_got_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_got_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_got_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

#ld_got_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_got_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_got_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_got_hosp_peak <- got_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_got_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_got_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_got_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

#li_got_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_got_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_got_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_got_hosp_peak <- got_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_got_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_got_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_got_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "got (u/l)",
  messages = FALSE
)

#lp_got_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_got_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_got_peak_comparison_stat_amb)
dev.off()
```


### ggt #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

ggt_hosp <- left_join(hospitalisation_data_filter, ggt_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
ggt_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ggt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ggt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ggt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_ggt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ggt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_ggt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_ggt_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ggt_comparison_stat_amb)
dev.off()
```

```{r}
ld_ggt_hosp <- ggt_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_ggt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_ggt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ggt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_ggt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_ggt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_ggt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_ggt_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ggt_comparison_stat_amb)
dev.off()
```

```{r}
li_ggt_hosp <- ggt_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_ggt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_ggt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ggt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_ggt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_ggt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_ggt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_ggt_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ggt_comparison_stat_amb)
dev.off()
```

```{r}
lp_ggt_hosp <- ggt_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_ggt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_ggt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ggt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_ggt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_ggt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_ggt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_ggt_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ggt_comparison_stat_amb)
dev.off()
```


### ggt peak #####

```{r}
ggt_hosp_peak <- ggt_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_ggt_peak_comparison_stat_amb <- ggbetweenstats(
  data = ggt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ggt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

#all_groups_ggt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_ggt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ggt_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_ggt_hosp_peak <- ggt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_ggt_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_ggt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ggt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

#ld_ggt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_ggt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ggt_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_ggt_hosp_peak <- ggt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_ggt_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_ggt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ggt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

#li_ggt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_ggt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ggt_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_ggt_hosp_peak <- ggt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_ggt_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_ggt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ggt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ggt (u/l)",
  messages = FALSE
)

#lp_ggt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_ggt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ggt_peak_comparison_stat_amb)
dev.off()
```



### ldh #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

ldh_hosp <- left_join(hospitalisation_data_filter, ldh_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
ldh_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ldh_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ldh_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ldh_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_ldh_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ldh_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_ldh_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_ldh_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ldh_comparison_stat_amb)
dev.off()
```

```{r}
ld_ldh_hosp <- ldh_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_ldh_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_ldh_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ldh_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_ldh_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_ldh_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_ldh_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_ldh_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ldh_comparison_stat_amb)
dev.off()
```

```{r}
li_ldh_hosp <- ldh_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_ldh_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_ldh_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ldh_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_ldh_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_ldh_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_ldh_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_ldh_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ldh_comparison_stat_amb)
dev.off()
```

```{r}
lp_ldh_hosp <- ldh_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_ldh_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_ldh_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ldh_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_ldh_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_ldh_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_ldh_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_ldh_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ldh_comparison_stat_amb)
dev.off()
```


### ldh peak #####

```{r}
ldh_hosp_peak <- ldh_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_ldh_peak_comparison_stat_amb <- ggbetweenstats(
  data = ldh_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ldh_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

#all_groups_ldh_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_ldh_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ldh_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_ldh_hosp_peak <- ldh_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_ldh_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_ldh_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ldh_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

#ld_ldh_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_ldh_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ldh_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_ldh_hosp_peak <- ldh_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_ldh_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_ldh_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ldh_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

#li_ldh_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_ldh_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ldh_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_ldh_hosp_peak <- ldh_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_ldh_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_ldh_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ldh_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ldh (u/l)",
  messages = FALSE
)

#lp_ldh_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_ldh_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ldh_peak_comparison_stat_amb)
dev.off()
```



### ap #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

ap_hosp <- left_join(hospitalisation_data_filter, ap_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
ap_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ap_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ap_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ap_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_ap_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ap_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_ap_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_ap_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ap_comparison_stat_amb)
dev.off()
```

```{r}
ld_ap_hosp <- ap_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_ap_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_ap_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ap_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_ap_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_ap_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_ap_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_ap_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ap_comparison_stat_amb)
dev.off()
```

```{r}
li_ap_hosp <- ap_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_ap_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_ap_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ap_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_ap_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_ap_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_ap_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_ap_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ap_comparison_stat_amb)
dev.off()
```

```{r}
lp_ap_hosp <- ap_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_ap_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_ap_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ap_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_ap_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_ap_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_ap_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_ap_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ap_comparison_stat_amb)
dev.off()
```


### ap peak #####

```{r}
ap_hosp_peak <- ap_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_ap_peak_comparison_stat_amb <- ggbetweenstats(
  data = ap_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ap_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

#all_groups_ap_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_ap_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ap_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_ap_hosp_peak <- ap_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_ap_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_ap_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ap_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

#ld_ap_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_ap_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ap_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_ap_hosp_peak <- ap_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_ap_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_ap_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ap_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

#li_ap_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_ap_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ap_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_ap_hosp_peak <- ap_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_ap_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_ap_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ap_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ap (u/l)",
  messages = FALSE
)

#lp_ap_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_ap_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ap_peak_comparison_stat_amb)
dev.off()
```



### ck #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

ck_hosp <- left_join(hospitalisation_data_filter, ck_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
ck_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ck_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ck_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ck_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_ck_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ck_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_ck_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_ck_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ck_comparison_stat_amb)
dev.off()
```

```{r}
ld_ck_hosp <- ck_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_ck_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_ck_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ck_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_ck_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_ck_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_ck_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_ck_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ck_comparison_stat_amb)
dev.off()
```

```{r}
li_ck_hosp <- ck_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_ck_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_ck_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ck_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_ck_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_ck_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_ck_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_ck_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ck_comparison_stat_amb)
dev.off()
```

```{r}
lp_ck_hosp <- ck_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_ck_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_ck_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ck_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_ck_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_ck_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_ck_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_ck_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ck_comparison_stat_amb)
dev.off()
```


### ck peak #####

```{r}
ck_hosp_peak <- ck_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_ck_peak_comparison_stat_amb <- ggbetweenstats(
  data = ck_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ck_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

#all_groups_ck_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_ck_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ck_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_ck_hosp_peak <- ck_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_ck_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_ck_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ck_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

#ld_ck_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_ck_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ck_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_ck_hosp_peak <- ck_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_ck_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_ck_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ck_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

#li_ck_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_ck_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ck_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_ck_hosp_peak <- ck_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_ck_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_ck_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ck_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ck (u/l)",
  messages = FALSE
)

#lp_ck_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_ck_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ck_peak_comparison_stat_amb)
dev.off()
```



### quick #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

quick_hosp <- left_join(hospitalisation_data_filter, quick_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
quick_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- quick_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = quick_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_quick_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_quick_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(quick_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_quick_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_quick_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_quick_comparison_stat_amb)
dev.off()
```

```{r}
ld_quick_hosp <- quick_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_quick_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_quick_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_quick_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_quick_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_quick_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_quick_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_quick_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_quick_comparison_stat_amb)
dev.off()
```

```{r}
li_quick_hosp <- quick_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_quick_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_quick_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_quick_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_quick_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_quick_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_quick_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_quick_comparison_stat_amb.svg", height = 6, width = 8)
print(li_quick_comparison_stat_amb)
dev.off()
```

```{r}
lp_quick_hosp <- quick_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_quick_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_quick_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_quick_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_quick_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_quick_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_quick_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_quick_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_quick_comparison_stat_amb)
dev.off()
```


### quick peak #####

```{r}
quick_hosp_peak <- quick_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_quick_peak_comparison_stat_amb <- ggbetweenstats(
  data = quick_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_quick_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

#all_groups_quick_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_quick_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_quick_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_quick_hosp_peak <- quick_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_quick_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_quick_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_quick_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

#ld_quick_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_quick_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_quick_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_quick_hosp_peak <- quick_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_quick_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_quick_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_quick_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

#li_quick_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_quick_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_quick_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_quick_hosp_peak <- quick_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_quick_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_quick_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_quick_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

#lp_quick_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_quick_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_quick_peak_comparison_stat_amb)
dev.off()
```



### hämatokrit #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

hämatokrit_hosp <- left_join(hospitalisation_data_filter, hämatokrit_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
hämatokrit_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hämatokrit_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hämatokrit_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_hämatokrit_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_hämatokrit_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(hämatokrit_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_hämatokrit_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_hämatokrit_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_hämatokrit_comparison_stat_amb)
dev.off()
```

```{r}
ld_hämatokrit_hosp <- hämatokrit_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_hämatokrit_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_hämatokrit_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_hämatokrit_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_hämatokrit_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_hämatokrit_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_hämatokrit_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_hämatokrit_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_hämatokrit_comparison_stat_amb)
dev.off()
```

```{r}
li_hämatokrit_hosp <- hämatokrit_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_hämatokrit_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_hämatokrit_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_hämatokrit_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_hämatokrit_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_hämatokrit_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_hämatokrit_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_hämatokrit_comparison_stat_amb.svg", height = 6, width = 8)
print(li_hämatokrit_comparison_stat_amb)
dev.off()
```

```{r}
lp_hämatokrit_hosp <- hämatokrit_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_hämatokrit_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_hämatokrit_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_hämatokrit_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_hämatokrit_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_hämatokrit_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_hämatokrit_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_hämatokrit_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_hämatokrit_comparison_stat_amb)
dev.off()
```


### hämatokrit peak #####

```{r}
hämatokrit_hosp_peak <- hämatokrit_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_hämatokrit_peak_comparison_stat_amb <- ggbetweenstats(
  data = hämatokrit_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_hämatokrit_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

#all_groups_hämatokrit_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_hämatokrit_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_hämatokrit_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_hämatokrit_hosp_peak <- hämatokrit_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_hämatokrit_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_hämatokrit_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_hämatokrit_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

#ld_hämatokrit_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_hämatokrit_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_hämatokrit_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_hämatokrit_hosp_peak <- hämatokrit_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_hämatokrit_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_hämatokrit_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_hämatokrit_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

#li_hämatokrit_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_hämatokrit_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_hämatokrit_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_hämatokrit_hosp_peak <- hämatokrit_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_hämatokrit_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_hämatokrit_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_hämatokrit_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

#lp_hämatokrit_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_hämatokrit_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_hämatokrit_peak_comparison_stat_amb)
dev.off()
```



### ptt #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

ptt_hosp <- left_join(hospitalisation_data_filter, ptt_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
ptt_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ptt_comparison_stat_amb)
dev.off()
```

```{r}
ld_ptt_hosp <- ptt_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ptt_comparison_stat_amb)
dev.off()
```

```{r}
li_ptt_hosp <- ptt_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ptt_comparison_stat_amb)
dev.off()
```

```{r}
lp_ptt_hosp <- ptt_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ptt_comparison_stat_amb)
dev.off()
```


### ptt peak #####

```{r}
ptt_hosp_peak <- ptt_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#all_groups_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ptt_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_ptt_hosp_peak <- ptt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#ld_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ptt_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_ptt_hosp_peak <- ptt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#li_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ptt_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_ptt_hosp_peak <- ptt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#lp_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ptt_peak_comparison_stat_amb)
dev.off()
```



### ptt #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

ptt_hosp <- left_join(hospitalisation_data_filter, ptt_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
ptt_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ptt_comparison_stat_amb)
dev.off()
```

```{r}
ld_ptt_hosp <- ptt_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ptt_comparison_stat_amb)
dev.off()
```

```{r}
li_ptt_hosp <- ptt_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ptt_comparison_stat_amb)
dev.off()
```

```{r}
lp_ptt_hosp <- ptt_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_ptt_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_ptt_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ptt_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_ptt_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_ptt_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_ptt_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_ptt_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ptt_comparison_stat_amb)
dev.off()
```


### ptt peak #####

```{r}
ptt_hosp_peak <- ptt_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#all_groups_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_ptt_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_ptt_hosp_peak <- ptt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#ld_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_ptt_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_ptt_hosp_peak <- ptt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#li_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_ptt_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_ptt_hosp_peak <- ptt_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_ptt_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_ptt_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_ptt_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

#lp_ptt_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_ptt_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_ptt_peak_comparison_stat_amb)
dev.off()
```



### leukozyten #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

leukozyten_hosp <- left_join(hospitalisation_data_filter, leukozyten_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
leukozyten_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leukozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leukozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_leukozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_leukozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(leukozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_leukozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_leukozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_leukozyten_comparison_stat_amb)
dev.off()
```

```{r}
ld_leukozyten_hosp <- leukozyten_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_leukozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_leukozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_leukozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_leukozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_leukozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_leukozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_leukozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_leukozyten_comparison_stat_amb)
dev.off()
```

```{r}
li_leukozyten_hosp <- leukozyten_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_leukozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_leukozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_leukozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_leukozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_leukozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_leukozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_leukozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(li_leukozyten_comparison_stat_amb)
dev.off()
```

```{r}
lp_leukozyten_hosp <- leukozyten_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_leukozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_leukozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_leukozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_leukozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_leukozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_leukozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_leukozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_leukozyten_comparison_stat_amb)
dev.off()
```


### leukozyten peak #####

```{r}
leukozyten_hosp_peak <- leukozyten_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_leukozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = leukozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_leukozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

#all_groups_leukozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_leukozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_leukozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_leukozyten_hosp_peak <- leukozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_leukozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_leukozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_leukozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

#ld_leukozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_leukozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_leukozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_leukozyten_hosp_peak <- leukozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_leukozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_leukozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_leukozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

#li_leukozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_leukozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_leukozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_leukozyten_hosp_peak <- leukozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_leukozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_leukozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_leukozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

#lp_leukozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_leukozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_leukozyten_peak_comparison_stat_amb)
dev.off()
```



### erythrozyten #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

erythrozyten_hosp <- left_join(hospitalisation_data_filter, erythrozyten_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
erythrozyten_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- erythrozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = erythrozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_erythrozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_erythrozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(erythrozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_erythrozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_erythrozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_erythrozyten_comparison_stat_amb)
dev.off()
```

```{r}
ld_erythrozyten_hosp <- erythrozyten_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_erythrozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_erythrozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_erythrozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_erythrozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_erythrozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_erythrozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_erythrozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_erythrozyten_comparison_stat_amb)
dev.off()
```

```{r}
li_erythrozyten_hosp <- erythrozyten_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_erythrozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_erythrozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_erythrozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_erythrozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_erythrozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_erythrozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_erythrozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(li_erythrozyten_comparison_stat_amb)
dev.off()
```

```{r}
lp_erythrozyten_hosp <- erythrozyten_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_erythrozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_erythrozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_erythrozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_erythrozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_erythrozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_erythrozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_erythrozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_erythrozyten_comparison_stat_amb)
dev.off()
```


### erythrozyten peak #####

```{r}
erythrozyten_hosp_peak <- erythrozyten_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_erythrozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = erythrozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_erythrozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

#all_groups_erythrozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_erythrozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_erythrozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_erythrozyten_hosp_peak <- erythrozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_erythrozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_erythrozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_erythrozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

#ld_erythrozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_erythrozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_erythrozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_erythrozyten_hosp_peak <- erythrozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_erythrozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_erythrozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_erythrozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

#li_erythrozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_erythrozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_erythrozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_erythrozyten_hosp_peak <- erythrozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_erythrozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_erythrozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_erythrozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

#lp_erythrozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_erythrozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_erythrozyten_peak_comparison_stat_amb)
dev.off()
```



### thrombozyten #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

thrombozyten_hosp <- left_join(hospitalisation_data_filter, thrombozyten_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
thrombozyten_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- thrombozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = thrombozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_thrombozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_thrombozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(thrombozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_thrombozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_thrombozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_thrombozyten_comparison_stat_amb)
dev.off()
```

```{r}
ld_thrombozyten_hosp <- thrombozyten_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_thrombozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_thrombozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_thrombozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_thrombozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_thrombozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_thrombozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_thrombozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_thrombozyten_comparison_stat_amb)
dev.off()
```

```{r}
li_thrombozyten_hosp <- thrombozyten_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_thrombozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_thrombozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_thrombozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_thrombozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_thrombozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_thrombozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_thrombozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(li_thrombozyten_comparison_stat_amb)
dev.off()
```

```{r}
lp_thrombozyten_hosp <- thrombozyten_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_thrombozyten_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_thrombozyten_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_thrombozyten_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_thrombozyten_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_thrombozyten_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_thrombozyten_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_thrombozyten_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_thrombozyten_comparison_stat_amb)
dev.off()
```


### thrombozyten peak #####

```{r}
thrombozyten_hosp_peak <- thrombozyten_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_thrombozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = thrombozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_thrombozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

#all_groups_thrombozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_thrombozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_thrombozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_thrombozyten_hosp_peak <- thrombozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_thrombozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_thrombozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_thrombozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

#ld_thrombozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_thrombozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_thrombozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_thrombozyten_hosp_peak <- thrombozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_thrombozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_thrombozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_thrombozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

#li_thrombozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_thrombozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_thrombozyten_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_thrombozyten_hosp_peak <- thrombozyten_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_thrombozyten_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_thrombozyten_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_thrombozyten_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

#lp_thrombozyten_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_thrombozyten_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_thrombozyten_peak_comparison_stat_amb)
dev.off()
```



### hb #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

hb_hosp <- left_join(hospitalisation_data_filter, hb_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
hb_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hb_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hb_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_hb_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_hb_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(hb_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_hb_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_hb_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_hb_comparison_stat_amb)
dev.off()
```

```{r}
ld_hb_hosp <- hb_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_hb_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_hb_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_hb_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_hb_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_hb_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_hb_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_hb_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_hb_comparison_stat_amb)
dev.off()
```

```{r}
li_hb_hosp <- hb_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_hb_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_hb_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_hb_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_hb_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_hb_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_hb_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_hb_comparison_stat_amb.svg", height = 6, width = 8)
print(li_hb_comparison_stat_amb)
dev.off()
```

```{r}
lp_hb_hosp <- hb_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_hb_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_hb_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_hb_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_hb_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_hb_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_hb_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_hb_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_hb_comparison_stat_amb)
dev.off()
```


### hb peak #####

```{r}
hb_hosp_peak <- hb_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_hb_peak_comparison_stat_amb <- ggbetweenstats(
  data = hb_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_hb_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

#all_groups_hb_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_hb_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_hb_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_hb_hosp_peak <- hb_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_hb_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_hb_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_hb_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

#ld_hb_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_hb_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_hb_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_hb_hosp_peak <- hb_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_hb_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_hb_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_hb_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

#li_hb_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_hb_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_hb_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_hb_hosp_peak <- hb_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_hb_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_hb_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_hb_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

#lp_hb_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_hb_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_hb_peak_comparison_stat_amb)
dev.off()
```



### gesamteiweiß #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

gesamteiweiß_hosp <- left_join(hospitalisation_data_filter, gesamteiweiß_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
gesamteiweiß_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- gesamteiweiß_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = gesamteiweiß_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_gesamteiweiß_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_gesamteiweiß_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(gesamteiweiß_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_gesamteiweiß_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_gesamteiweiß_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_gesamteiweiß_comparison_stat_amb)
dev.off()
```

```{r}
ld_gesamteiweiß_hosp <- gesamteiweiß_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_gesamteiweiß_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_gesamteiweiß_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_gesamteiweiß_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_gesamteiweiß_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_gesamteiweiß_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_gesamteiweiß_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_gesamteiweiß_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_gesamteiweiß_comparison_stat_amb)
dev.off()
```

```{r}
li_gesamteiweiß_hosp <- gesamteiweiß_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_gesamteiweiß_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_gesamteiweiß_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_gesamteiweiß_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_gesamteiweiß_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_gesamteiweiß_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_gesamteiweiß_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_gesamteiweiß_comparison_stat_amb.svg", height = 6, width = 8)
print(li_gesamteiweiß_comparison_stat_amb)
dev.off()
```

```{r}
lp_gesamteiweiß_hosp <- gesamteiweiß_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_gesamteiweiß_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_gesamteiweiß_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_gesamteiweiß_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_gesamteiweiß_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_gesamteiweiß_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_gesamteiweiß_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_gesamteiweiß_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_gesamteiweiß_comparison_stat_amb)
dev.off()
```


### gesamteiweiß peak #####

```{r}
gesamteiweiß_hosp_peak <- gesamteiweiß_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_gesamteiweiß_peak_comparison_stat_amb <- ggbetweenstats(
  data = gesamteiweiß_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_gesamteiweiß_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

#all_groups_gesamteiweiß_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_gesamteiweiß_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_gesamteiweiß_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_gesamteiweiß_hosp_peak <- gesamteiweiß_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_gesamteiweiß_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_gesamteiweiß_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_gesamteiweiß_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

#ld_gesamteiweiß_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_gesamteiweiß_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_gesamteiweiß_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_gesamteiweiß_hosp_peak <- gesamteiweiß_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_gesamteiweiß_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_gesamteiweiß_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_gesamteiweiß_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

#li_gesamteiweiß_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_gesamteiweiß_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_gesamteiweiß_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_gesamteiweiß_hosp_peak <- gesamteiweiß_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_gesamteiweiß_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_gesamteiweiß_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_gesamteiweiß_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

#lp_gesamteiweiß_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_gesamteiweiß_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_gesamteiweiß_peak_comparison_stat_amb)
dev.off()
```



### total_bilirubin #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

total_bilirubin_hosp <- left_join(hospitalisation_data_filter, total_bilirubin_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
total_bilirubin_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- total_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = total_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_total_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_total_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(total_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_total_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_total_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_total_bilirubin_comparison_stat_amb)
dev.off()
```

```{r}
ld_total_bilirubin_hosp <- total_bilirubin_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_total_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_total_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_total_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_total_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_total_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_total_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_total_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_total_bilirubin_comparison_stat_amb)
dev.off()
```

```{r}
li_total_bilirubin_hosp <- total_bilirubin_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_total_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_total_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_total_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_total_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_total_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_total_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_total_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(li_total_bilirubin_comparison_stat_amb)
dev.off()
```

```{r}
lp_total_bilirubin_hosp <- total_bilirubin_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_total_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_total_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_total_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_total_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_total_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_total_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_total_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_total_bilirubin_comparison_stat_amb)
dev.off()
```


### total_bilirubin peak #####

```{r}
total_bilirubin_hosp_peak <- total_bilirubin_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_total_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = total_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_total_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

#all_groups_total_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_total_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_total_bilirubin_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_total_bilirubin_hosp_peak <- total_bilirubin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_total_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_total_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_total_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

#ld_total_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_total_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_total_bilirubin_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_total_bilirubin_hosp_peak <- total_bilirubin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_total_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_total_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_total_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

#li_total_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_total_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_total_bilirubin_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_total_bilirubin_hosp_peak <- total_bilirubin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_total_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_total_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_total_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

#lp_total_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_total_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_total_bilirubin_peak_comparison_stat_amb)
dev.off()
```



### direct_bilirubin #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

direct_bilirubin_hosp <- left_join(hospitalisation_data_filter, direct_bilirubin_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
direct_bilirubin_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- direct_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = direct_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_direct_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_direct_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(direct_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_direct_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_direct_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_direct_bilirubin_comparison_stat_amb)
dev.off()
```

```{r}
ld_direct_bilirubin_hosp <- direct_bilirubin_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_direct_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_direct_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_direct_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_direct_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_direct_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_direct_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_direct_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_direct_bilirubin_comparison_stat_amb)
dev.off()
```

```{r}
li_direct_bilirubin_hosp <- direct_bilirubin_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_direct_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_direct_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_direct_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_direct_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_direct_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_direct_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_direct_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(li_direct_bilirubin_comparison_stat_amb)
dev.off()
```

```{r}
lp_direct_bilirubin_hosp <- direct_bilirubin_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_direct_bilirubin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_direct_bilirubin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_direct_bilirubin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_direct_bilirubin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_direct_bilirubin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_direct_bilirubin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_direct_bilirubin_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_direct_bilirubin_comparison_stat_amb)
dev.off()
```


### direct_bilirubin peak #####

```{r}
direct_bilirubin_hosp_peak <- direct_bilirubin_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_direct_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = direct_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_direct_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

#all_groups_direct_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_direct_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_direct_bilirubin_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_direct_bilirubin_hosp_peak <- direct_bilirubin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_direct_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_direct_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_direct_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

#ld_direct_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_direct_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_direct_bilirubin_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_direct_bilirubin_hosp_peak <- direct_bilirubin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_direct_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_direct_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_direct_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

#li_direct_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_direct_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_direct_bilirubin_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_direct_bilirubin_hosp_peak <- direct_bilirubin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_direct_bilirubin_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_direct_bilirubin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_direct_bilirubin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

#lp_direct_bilirubin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_direct_bilirubin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_direct_bilirubin_peak_comparison_stat_amb)
dev.off()
```



### kreatinin #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

kreatinin_hosp <- left_join(hospitalisation_data_filter, kreatinin_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
kreatinin_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kreatinin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kreatinin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_kreatinin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_kreatinin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(kreatinin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_kreatinin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_kreatinin_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_kreatinin_comparison_stat_amb)
dev.off()
```

```{r}
ld_kreatinin_hosp <- kreatinin_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_kreatinin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_kreatinin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_kreatinin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_kreatinin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_kreatinin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_kreatinin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_kreatinin_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_kreatinin_comparison_stat_amb)
dev.off()
```

```{r}
li_kreatinin_hosp <- kreatinin_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_kreatinin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_kreatinin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_kreatinin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_kreatinin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_kreatinin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_kreatinin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_kreatinin_comparison_stat_amb.svg", height = 6, width = 8)
print(li_kreatinin_comparison_stat_amb)
dev.off()
```

```{r}
lp_kreatinin_hosp <- kreatinin_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_kreatinin_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_kreatinin_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_kreatinin_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_kreatinin_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_kreatinin_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_kreatinin_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_kreatinin_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_kreatinin_comparison_stat_amb)
dev.off()
```


### kreatinin peak #####

```{r}
kreatinin_hosp_peak <- kreatinin_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_kreatinin_peak_comparison_stat_amb <- ggbetweenstats(
  data = kreatinin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_kreatinin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

#all_groups_kreatinin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_kreatinin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_kreatinin_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_kreatinin_hosp_peak <- kreatinin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_kreatinin_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_kreatinin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_kreatinin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

#ld_kreatinin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_kreatinin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_kreatinin_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_kreatinin_hosp_peak <- kreatinin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_kreatinin_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_kreatinin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_kreatinin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

#li_kreatinin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_kreatinin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_kreatinin_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_kreatinin_hosp_peak <- kreatinin_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_kreatinin_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_kreatinin_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_kreatinin_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

#lp_kreatinin_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_kreatinin_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_kreatinin_peak_comparison_stat_amb)
dev.off()
```



### harnstoff #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

harnstoff_hosp <- left_join(hospitalisation_data_filter, harnstoff_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
harnstoff_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- harnstoff_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = harnstoff_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_harnstoff_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_harnstoff_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(harnstoff_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_harnstoff_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_harnstoff_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_harnstoff_comparison_stat_amb)
dev.off()
```

```{r}
ld_harnstoff_hosp <- harnstoff_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_harnstoff_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_harnstoff_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_harnstoff_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_harnstoff_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_harnstoff_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_harnstoff_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_harnstoff_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_harnstoff_comparison_stat_amb)
dev.off()
```

```{r}
li_harnstoff_hosp <- harnstoff_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_harnstoff_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_harnstoff_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_harnstoff_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_harnstoff_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_harnstoff_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_harnstoff_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_harnstoff_comparison_stat_amb.svg", height = 6, width = 8)
print(li_harnstoff_comparison_stat_amb)
dev.off()
```

```{r}
lp_harnstoff_hosp <- harnstoff_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_harnstoff_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_harnstoff_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_harnstoff_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_harnstoff_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_harnstoff_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_harnstoff_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_harnstoff_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_harnstoff_comparison_stat_amb)
dev.off()
```


### harnstoff peak #####

```{r}
harnstoff_hosp_peak <- harnstoff_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_harnstoff_peak_comparison_stat_amb <- ggbetweenstats(
  data = harnstoff_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_harnstoff_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

#all_groups_harnstoff_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_harnstoff_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_harnstoff_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_harnstoff_hosp_peak <- harnstoff_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_harnstoff_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_harnstoff_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_harnstoff_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

#ld_harnstoff_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_harnstoff_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_harnstoff_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_harnstoff_hosp_peak <- harnstoff_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_harnstoff_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_harnstoff_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_harnstoff_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

#li_harnstoff_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_harnstoff_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_harnstoff_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_harnstoff_hosp_peak <- harnstoff_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_harnstoff_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_harnstoff_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_harnstoff_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

#lp_harnstoff_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_harnstoff_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_harnstoff_peak_comparison_stat_amb)
dev.off()
```



### crp #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

crp_hosp <- left_join(hospitalisation_data_filter, crp_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
crp_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- crp_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = crp_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_crp_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_crp_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(crp_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_crp_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_crp_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_crp_comparison_stat_amb)
dev.off()
```

```{r}
ld_crp_hosp <- crp_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_crp_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_crp_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_crp_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_crp_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_crp_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_crp_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_crp_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_crp_comparison_stat_amb)
dev.off()
```

```{r}
li_crp_hosp <- crp_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_crp_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_crp_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_crp_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_crp_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_crp_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_crp_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_crp_comparison_stat_amb.svg", height = 6, width = 8)
print(li_crp_comparison_stat_amb)
dev.off()
```

```{r}
lp_crp_hosp <- crp_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_crp_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_crp_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_crp_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_crp_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_crp_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_crp_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_crp_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_crp_comparison_stat_amb)
dev.off()
```


### crp peak #####

```{r}
crp_hosp_peak <- crp_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_crp_peak_comparison_stat_amb <- ggbetweenstats(
  data = crp_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_crp_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

#all_groups_crp_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_crp_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_crp_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_crp_hosp_peak <- crp_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_crp_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_crp_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_crp_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

#ld_crp_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_crp_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_crp_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_crp_hosp_peak <- crp_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_crp_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_crp_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_crp_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

#li_crp_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_crp_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_crp_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_crp_hosp_peak <- crp_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_crp_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_crp_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_crp_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

#lp_crp_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_crp_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_crp_peak_comparison_stat_amb)
dev.off()
```



### natrium #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

natrium_hosp <- left_join(hospitalisation_data_filter, natrium_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
natrium_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- natrium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = natrium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_natrium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_natrium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(natrium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_natrium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_natrium_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_natrium_comparison_stat_amb)
dev.off()
```

```{r}
ld_natrium_hosp <- natrium_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_natrium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_natrium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_natrium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_natrium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_natrium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_natrium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_natrium_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_natrium_comparison_stat_amb)
dev.off()
```

```{r}
li_natrium_hosp <- natrium_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_natrium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_natrium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_natrium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_natrium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_natrium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_natrium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_natrium_comparison_stat_amb.svg", height = 6, width = 8)
print(li_natrium_comparison_stat_amb)
dev.off()
```

```{r}
lp_natrium_hosp <- natrium_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_natrium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_natrium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_natrium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_natrium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_natrium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_natrium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_natrium_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_natrium_comparison_stat_amb)
dev.off()
```


### natrium peak #####

```{r}
natrium_hosp_peak <- natrium_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_natrium_peak_comparison_stat_amb <- ggbetweenstats(
  data = natrium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_natrium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

#all_groups_natrium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_natrium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_natrium_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_natrium_hosp_peak <- natrium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_natrium_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_natrium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_natrium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

#ld_natrium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_natrium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_natrium_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_natrium_hosp_peak <- natrium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_natrium_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_natrium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_natrium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

#li_natrium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_natrium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_natrium_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_natrium_hosp_peak <- natrium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_natrium_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_natrium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_natrium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

#lp_natrium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_natrium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_natrium_peak_comparison_stat_amb)
dev.off()
```



### kalium #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

kalium_hosp <- left_join(hospitalisation_data_filter, kalium_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
kalium_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_kalium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_kalium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(kalium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_kalium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_kalium_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_kalium_comparison_stat_amb)
dev.off()
```

```{r}
ld_kalium_hosp <- kalium_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_kalium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_kalium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_kalium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_kalium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_kalium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_kalium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_kalium_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_kalium_comparison_stat_amb)
dev.off()
```

```{r}
li_kalium_hosp <- kalium_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_kalium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_kalium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_kalium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_kalium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_kalium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_kalium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_kalium_comparison_stat_amb.svg", height = 6, width = 8)
print(li_kalium_comparison_stat_amb)
dev.off()
```

```{r}
lp_kalium_hosp <- kalium_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_kalium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_kalium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_kalium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_kalium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_kalium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_kalium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_kalium_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_kalium_comparison_stat_amb)
dev.off()
```


### kalium peak #####

```{r}
kalium_hosp_peak <- kalium_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_kalium_peak_comparison_stat_amb <- ggbetweenstats(
  data = kalium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_kalium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

#all_groups_kalium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_kalium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_kalium_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_kalium_hosp_peak <- kalium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_kalium_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_kalium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_kalium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

#ld_kalium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_kalium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_kalium_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_kalium_hosp_peak <- kalium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_kalium_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_kalium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_kalium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

#li_kalium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_kalium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_kalium_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_kalium_hosp_peak <- kalium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_kalium_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_kalium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_kalium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

#lp_kalium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_kalium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_kalium_peak_comparison_stat_amb)
dev.off()
```



### kalzium #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

kalzium_hosp <- left_join(hospitalisation_data_filter, kalzium_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
kalzium_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalzium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalzium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_kalzium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_kalzium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(kalzium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_kalzium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_kalzium_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_kalzium_comparison_stat_amb)
dev.off()
```

```{r}
ld_kalzium_hosp <- kalzium_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_kalzium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_kalzium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_kalzium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_kalzium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_kalzium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_kalzium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_kalzium_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_kalzium_comparison_stat_amb)
dev.off()
```

```{r}
li_kalzium_hosp <- kalzium_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_kalzium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_kalzium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_kalzium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_kalzium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_kalzium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_kalzium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_kalzium_comparison_stat_amb.svg", height = 6, width = 8)
print(li_kalzium_comparison_stat_amb)
dev.off()
```

```{r}
lp_kalzium_hosp <- kalzium_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_kalzium_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_kalzium_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_kalzium_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_kalzium_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_kalzium_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_kalzium_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_kalzium_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_kalzium_comparison_stat_amb)
dev.off()
```


### inr #########
```{r}
hospitalisation_data_filter <- hospitalisation_data %>%
  filter(!(hospitalisation == "unknown")) %>%
  dplyr::select(1,4)
hospitalisation_data_filter

inr_hosp <- left_join(hospitalisation_data_filter, inr_full, by = ("Edited_BfArM Nummer2")) %>% 
  drop_na() %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute))
inr_hosp
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- inr_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = inr_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_inr_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
all_groups_inr_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(inr_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#all_groups_inr_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/all_inr_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_inr_comparison_stat_amb)
dev.off()
```

```{r}
ld_inr_hosp <- inr_hosp  %>%
  filter(!(Treatment == "Leber_Diclo"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ld_inr_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ld_inr_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_inr_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
ld_inr_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(ld_inr_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#ld_inr_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/ld_inr_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_inr_comparison_stat_amb)
dev.off()
```

```{r}
li_inr_hosp <- inr_hosp  %>%
  filter(!(Treatment == "Leber_Ibu"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- li_inr_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = li_inr_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_inr_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
li_inr_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(li_inr_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#li_inr_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/li_inr_comparison_stat_amb.svg", height = 6, width = 8)
print(li_inr_comparison_stat_amb)
dev.off()
```

```{r}
lp_inr_hosp <- inr_hosp  %>%
  filter(!(Treatment == "Leber_Para"))
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- lp_inr_hosp %>%
  distinct(`Edited_BfArM Nummer2`, hospitalisation) %>%  # nur einzigartige Patienten
  count(hospitalisation, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = lp_inr_hosp,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_inr_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
lp_inr_comparison_stat_amb <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = hospitalisation, 
        y = max(lp_inr_hosp$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

#lp_inr_comparison_stat_amb
dir.create("plots hosp/all labv", showWarnings = FALSE)
svg("plots hosp/all labv/lp_inr_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_inr_comparison_stat_amb)
dev.off()
```

### kalzium peak #####

```{r}
kalzium_hosp_peak <- kalzium_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_kalzium_peak_comparison_stat_amb <- ggbetweenstats(
  data = kalzium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_kalzium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

#all_groups_kalzium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_kalzium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_kalzium_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_kalzium_hosp_peak <- kalzium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_kalzium_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_kalzium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_kalzium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

#ld_kalzium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_kalzium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_kalzium_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_kalzium_hosp_peak <- kalzium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_kalzium_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_kalzium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_kalzium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

#li_kalzium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_kalzium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_kalzium_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_kalzium_hosp_peak <- kalzium_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_kalzium_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_kalzium_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_kalzium_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

#lp_kalzium_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_kalzium_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_kalzium_peak_comparison_stat_amb)
dev.off()
```


### inr peak #####

```{r}
inr_hosp_peak <- inr_hosp %>% 
  drop_na() %>% 
  group_by(hospitalisation) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()
```

```{r}
all_groups_inr_peak_comparison_stat_amb <- ggbetweenstats(
  data = inr_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_inr_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

#all_groups_inr_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/all_inr_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(all_groups_inr_peak_comparison_stat_amb)
dev.off()
```

```{r}
ld_inr_hosp_peak <- inr_hosp_peak  %>%
  filter(!(Treatment == "Leber_Diclo"))

ld_inr_peak_comparison_stat_amb <- ggbetweenstats(
  data = ld_inr_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo_inr_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

#ld_inr_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/ld_inr_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(ld_inr_peak_comparison_stat_amb)
dev.off()
```

```{r}
li_inr_hosp_peak <- inr_hosp_peak  %>%
  filter(!(Treatment == "Leber_Ibu"))

li_inr_peak_comparison_stat_amb <- ggbetweenstats(
  data = li_inr_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu_inr_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

#li_inr_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/li_inr_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(li_inr_peak_comparison_stat_amb)
dev.off()
```

```{r}
lp_inr_hosp_peak <- inr_hosp_peak  %>%
  filter(!(Treatment == "Leber_Para"))

lp_inr_peak_comparison_stat_amb <- ggbetweenstats(
  data = lp_inr_hosp_peak,
  x = "hospitalisation",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para_inr_peak_comparison ambulant vs. stationary treated patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

#lp_inr_peak_comparison_stat_amb
dir.create("plots hosp/peak labv", showWarnings = FALSE)
svg("plots hosp/peak labv/lp_inr_peak_comparison_stat_amb.svg", height = 6, width = 8)
print(lp_inr_peak_comparison_stat_amb)
dev.off()
```



