---
title: "Untitled"
output: html_document
date: "2026-04-26"
---

# run first: "comparison stat. vs. ambulant.Rmd"


### All groups ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  gpt_hosp = gpt_hosp,
  got_hosp = got_hosp,
  ggt_hosp = ggt_hosp,
  ap_hosp = ap_hosp,
  total_bilirubin_hosp = total_bilirubin_hosp,
  direct_bilirubin_hosp = direct_bilirubin_hosp,
  ldh_hosp = ldh_hosp,
  ck_hosp = ck_hosp,
  quick_hosp = quick_hosp,
  inr_hosp = inr_hosp,
  ptt_hosp = ptt_hosp,
  leukozyten_hosp = leukozyten_hosp,
  erythrozyten_hosp = erythrozyten_hosp,
  thrombozyten_hosp = thrombozyten_hosp,
  hb_hosp = hb_hosp,
  hämatokrit_hosp = hämatokrit_hosp,
  gesamteiweiß_hosp = gesamteiweiß_hosp,
  crp_hosp = crp_hosp,
  kreatinin_hosp = kreatinin_hosp,
  harnstoff_hosp = harnstoff_hosp,
  natrium_hosp = natrium_hosp,
  kalium_hosp = kalium_hosp,
  kalzium_hosp = kalzium_hosp
)

sink("plots hosp/all groups_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```


### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  gpt_hosp = gpt_hosp,
  got_hosp = got_hosp,
  ggt_hosp = ggt_hosp,
  ap_hosp = ap_hosp,
  total_bilirubin_hosp = total_bilirubin_hosp,
  direct_bilirubin_hosp = direct_bilirubin_hosp,
  ldh_hosp = ldh_hosp,
  ck_hosp = ck_hosp,
  quick_hosp = quick_hosp,
  inr_hosp = inr_hosp,
  ptt_hosp = ptt_hosp,
  leukozyten_hosp = leukozyten_hosp,
  erythrozyten_hosp = erythrozyten_hosp,
  thrombozyten_hosp = thrombozyten_hosp,
  hb_hosp = hb_hosp,
  hämatokrit_hosp = hämatokrit_hosp,
  gesamteiweiß_hosp = gesamteiweiß_hosp,
  crp_hosp = crp_hosp,
  kreatinin_hosp = kreatinin_hosp,
  harnstoff_hosp = harnstoff_hosp,
  natrium_hosp = natrium_hosp,
  kalium_hosp = kalium_hosp,
  kalzium_hosp = kalzium_hosp
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "all groups_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```



### Liver diclo ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  ld_gpt_hosp = ld_gpt_hosp,
  ld_got_hosp = ld_got_hosp,
  ld_ggt_hosp = ld_ggt_hosp,
  ld_ap_hosp = ld_ap_hosp,
  ld_total_bilirubin_hosp = ld_total_bilirubin_hosp,
  ld_direct_bilirubin_hosp = ld_direct_bilirubin_hosp,
  ld_ldh_hosp = ld_ldh_hosp,
  ld_ck_hosp = ld_ck_hosp,
  ld_quick_hosp = ld_quick_hosp,
  ld_inr_hosp = ld_inr_hosp,
  ld_ptt_hosp = ld_ptt_hosp,
  ld_leukozyten_hosp = ld_leukozyten_hosp,
  ld_erythrozyten_hosp = ld_erythrozyten_hosp,
  ld_thrombozyten_hosp = ld_thrombozyten_hosp,
  ld_hb_hosp = ld_hb_hosp,
  ld_hämatokrit_hosp = ld_hämatokrit_hosp,
  ld_gesamteiweiß_hosp = ld_gesamteiweiß_hosp,
  ld_crp_hosp = ld_crp_hosp,
  ld_kreatinin_hosp = ld_kreatinin_hosp,
  ld_harnstoff_hosp = ld_harnstoff_hosp,
  ld_natrium_hosp = ld_natrium_hosp,
  ld_kalium_hosp = ld_kalium_hosp,
  ld_kalzium_hosp = ld_kalzium_hosp
)

sink("plots hosp/liver diclo_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```



### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  ld_gpt_hosp = ld_gpt_hosp,
  ld_got_hosp = ld_got_hosp,
  ld_ggt_hosp = ld_ggt_hosp,
  ld_ap_hosp = ld_ap_hosp,
  ld_total_bilirubin_hosp = ld_total_bilirubin_hosp,
  ld_direct_bilirubin_hosp = ld_direct_bilirubin_hosp,
  ld_ldh_hosp = ld_ldh_hosp,
  ld_ck_hosp = ld_ck_hosp,
  ld_quick_hosp = ld_quick_hosp,
  ld_inr_hosp = ld_inr_hosp,
  ld_ptt_hosp = ld_ptt_hosp,
  ld_leukozyten_hosp = ld_leukozyten_hosp,
  ld_erythrozyten_hosp = ld_erythrozyten_hosp,
  ld_thrombozyten_hosp = ld_thrombozyten_hosp,
  ld_hb_hosp = ld_hb_hosp,
  ld_hämatokrit_hosp = ld_hämatokrit_hosp,
  ld_gesamteiweiß_hosp = ld_gesamteiweiß_hosp,
  ld_crp_hosp = ld_crp_hosp,
  ld_kreatinin_hosp = ld_kreatinin_hosp,
  ld_harnstoff_hosp = ld_harnstoff_hosp,
  ld_natrium_hosp = ld_natrium_hosp,
  ld_kalium_hosp = ld_kalium_hosp,
  ld_kalzium_hosp = ld_kalzium_hosp
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "liver diclo_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```


### Liver ibu ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  li_gpt_hosp = li_gpt_hosp,
  li_got_hosp = li_got_hosp,
  li_ggt_hosp = li_ggt_hosp,
  li_ap_hosp = li_ap_hosp,
  li_total_bilirubin_hosp = li_total_bilirubin_hosp,
  li_direct_bilirubin_hosp = li_direct_bilirubin_hosp,
  li_ldh_hosp = li_ldh_hosp,
  li_ck_hosp = li_ck_hosp,
  li_quick_hosp = li_quick_hosp,
  li_inr_hosp = li_inr_hosp,
  li_ptt_hosp = li_ptt_hosp,
  li_leukozyten_hosp = li_leukozyten_hosp,
  li_erythrozyten_hosp = li_erythrozyten_hosp,
  li_thrombozyten_hosp = li_thrombozyten_hosp,
  li_hb_hosp = li_hb_hosp,
  li_hämatokrit_hosp = li_hämatokrit_hosp,
  li_gesamteiweiß_hosp = li_gesamteiweiß_hosp,
  li_crp_hosp = li_crp_hosp,
  li_kreatinin_hosp = li_kreatinin_hosp,
  li_harnstoff_hosp = li_harnstoff_hosp,
  li_natrium_hosp = li_natrium_hosp,
  li_kalium_hosp = li_kalium_hosp,
  li_kalzium_hosp = li_kalzium_hosp
)

sink("plots hosp/liver ibu_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```


### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  li_gpt_hosp = li_gpt_hosp,
  li_got_hosp = li_got_hosp,
  li_ggt_hosp = li_ggt_hosp,
  li_ap_hosp = li_ap_hosp,
  li_total_bilirubin_hosp = li_total_bilirubin_hosp,
  li_direct_bilirubin_hosp = li_direct_bilirubin_hosp,
  li_ldh_hosp = li_ldh_hosp,
  li_ck_hosp = li_ck_hosp,
  li_quick_hosp = li_quick_hosp,
  li_inr_hosp = li_inr_hosp,
  li_ptt_hosp = li_ptt_hosp,
  li_leukozyten_hosp = li_leukozyten_hosp,
  li_erythrozyten_hosp = li_erythrozyten_hosp,
  li_thrombozyten_hosp = li_thrombozyten_hosp,
  li_hb_hosp = li_hb_hosp,
  li_hämatokrit_hosp = li_hämatokrit_hosp,
  li_gesamteiweiß_hosp = li_gesamteiweiß_hosp,
  li_crp_hosp = li_crp_hosp,
  li_kreatinin_hosp = li_kreatinin_hosp,
  li_harnstoff_hosp = li_harnstoff_hosp,
  li_natrium_hosp = li_natrium_hosp,
  li_kalium_hosp = li_kalium_hosp,
  li_kalzium_hosp = li_kalzium_hosp
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "liver ibu_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```


### Liver para ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  lp_gpt_hosp = lp_gpt_hosp,
  lp_got_hosp = lp_got_hosp,
  lp_ggt_hosp = lp_ggt_hosp,
  lp_ap_hosp = lp_ap_hosp,
  lp_total_bilirubin_hosp = lp_total_bilirubin_hosp,
  lp_direct_bilirubin_hosp = lp_direct_bilirubin_hosp,
  lp_ldh_hosp = lp_ldh_hosp,
  lp_ck_hosp = lp_ck_hosp,
  lp_quick_hosp = lp_quick_hosp,
  lp_inr_hosp = lp_inr_hosp,
  lp_ptt_hosp = lp_ptt_hosp,
  lp_leukozyten_hosp = lp_leukozyten_hosp,
  lp_erythrozyten_hosp = lp_erythrozyten_hosp,
  lp_thrombozyten_hosp = lp_thrombozyten_hosp,
  lp_hb_hosp = lp_hb_hosp,
  lp_hämatokrit_hosp = lp_hämatokrit_hosp,
  lp_gesamteiweiß_hosp = lp_gesamteiweiß_hosp,
  lp_crp_hosp = lp_crp_hosp,
  lp_kreatinin_hosp = lp_kreatinin_hosp,
  lp_harnstoff_hosp = lp_harnstoff_hosp,
  lp_natrium_hosp = lp_natrium_hosp,
  lp_kalium_hosp = lp_kalium_hosp,
  lp_kalzium_hosp = lp_kalzium_hosp
)

sink("plots hosp/liver para_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```


### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  lp_gpt_hosp = lp_gpt_hosp,
  lp_got_hosp = lp_got_hosp,
  lp_ggt_hosp = lp_ggt_hosp,
  lp_ap_hosp = lp_ap_hosp,
  lp_total_bilirubin_hosp = lp_total_bilirubin_hosp,
  lp_direct_bilirubin_hosp = lp_direct_bilirubin_hosp,
  lp_ldh_hosp = lp_ldh_hosp,
  lp_ck_hosp = lp_ck_hosp,
  lp_quick_hosp = lp_quick_hosp,
  lp_inr_hosp = lp_inr_hosp,
  lp_ptt_hosp = lp_ptt_hosp,
  lp_leukozyten_hosp = lp_leukozyten_hosp,
  lp_erythrozyten_hosp = lp_erythrozyten_hosp,
  lp_thrombozyten_hosp = lp_thrombozyten_hosp,
  lp_hb_hosp = lp_hb_hosp,
  lp_hämatokrit_hosp = lp_hämatokrit_hosp,
  lp_gesamteiweiß_hosp = lp_gesamteiweiß_hosp,
  lp_crp_hosp = lp_crp_hosp,
  lp_kreatinin_hosp = lp_kreatinin_hosp,
  lp_harnstoff_hosp = lp_harnstoff_hosp,
  lp_natrium_hosp = lp_natrium_hosp,
  lp_kalium_hosp = lp_kalium_hosp,
  lp_kalzium_hosp = lp_kalzium_hosp
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "liver para_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```


### All groups_peak ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  gpt_hosp_peak = gpt_hosp_peak,
  got_hosp_peak = got_hosp_peak,
  ggt_hosp_peak = ggt_hosp_peak,
  ap_hosp_peak = ap_hosp_peak,
  total_bilirubin_hosp_peak = total_bilirubin_hosp_peak,
  direct_bilirubin_hosp_peak = direct_bilirubin_hosp_peak,
  ldh_hosp_peak = ldh_hosp_peak,
  ck_hosp_peak = ck_hosp_peak,
  quick_hosp_peak = quick_hosp_peak,
  inr_hosp_peak = inr_hosp_peak,
  ptt_hosp_peak = ptt_hosp_peak,
  leukozyten_hosp_peak = leukozyten_hosp_peak,
  erythrozyten_hosp_peak = erythrozyten_hosp_peak,
  thrombozyten_hosp_peak = thrombozyten_hosp_peak,
  hb_hosp_peak = hb_hosp_peak,
  hämatokrit_hosp_peak = hämatokrit_hosp_peak,
  gesamteiweiß_hosp_peak = gesamteiweiß_hosp_peak,
  crp_hosp_peak = crp_hosp_peak,
  kreatinin_hosp_peak = kreatinin_hosp_peak,
  harnstoff_hosp_peak = harnstoff_hosp_peak,
  natrium_hosp_peak = natrium_hosp_peak,
  kalium_hosp_peak = kalium_hosp_peak,
  kalzium_hosp_peak = kalzium_hosp_peak
)

sink("plots hosp/all groups_peak_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```


### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  gpt_hosp_peak = gpt_hosp_peak,
  got_hosp_peak = got_hosp_peak,
  ggt_hosp_peak = ggt_hosp_peak,
  ap_hosp_peak = ap_hosp_peak,
  total_bilirubin_hosp_peak = total_bilirubin_hosp_peak,
  direct_bilirubin_hosp_peak = direct_bilirubin_hosp_peak,
  ldh_hosp_peak = ldh_hosp_peak,
  ck_hosp_peak = ck_hosp_peak,
  quick_hosp_peak = quick_hosp_peak,
  inr_hosp_peak = inr_hosp_peak,
  ptt_hosp_peak = ptt_hosp_peak,
  leukozyten_hosp_peak = leukozyten_hosp_peak,
  erythrozyten_hosp_peak = erythrozyten_hosp_peak,
  thrombozyten_hosp_peak = thrombozyten_hosp_peak,
  hb_hosp_peak = hb_hosp_peak,
  hämatokrit_hosp_peak = hämatokrit_hosp_peak,
  gesamteiweiß_hosp_peak = gesamteiweiß_hosp_peak,
  crp_hosp_peak = crp_hosp_peak,
  kreatinin_hosp_peak = kreatinin_hosp_peak,
  harnstoff_hosp_peak = harnstoff_hosp_peak,
  natrium_hosp_peak = natrium_hosp_peak,
  kalium_hosp_peak = kalium_hosp_peak,
  kalzium_hosp_peak = kalzium_hosp_peak
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "all groups_peak_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```


### Liver diclo ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  ld_gpt_hosp_peak = ld_gpt_hosp_peak,
  ld_got_hosp_peak = ld_got_hosp_peak,
  ld_ggt_hosp_peak = ld_ggt_hosp_peak,
  ld_ap_hosp_peak = ld_ap_hosp_peak,
  ld_total_bilirubin_hosp_peak = ld_total_bilirubin_hosp_peak,
  ld_direct_bilirubin_hosp_peak = ld_direct_bilirubin_hosp_peak,
  ld_ldh_hosp_peak = ld_ldh_hosp_peak,
  ld_ck_hosp_peak = ld_ck_hosp_peak,
  ld_quick_hosp_peak = ld_quick_hosp_peak,
  ld_inr_hosp_peak = ld_inr_hosp_peak,
  ld_ptt_hosp_peak = ld_ptt_hosp_peak,
  ld_leukozyten_hosp_peak = ld_leukozyten_hosp_peak,
  ld_erythrozyten_hosp_peak = ld_erythrozyten_hosp_peak,
  ld_thrombozyten_hosp_peak = ld_thrombozyten_hosp_peak,
  ld_hb_hosp_peak = ld_hb_hosp_peak,
  ld_hämatokrit_hosp_peak = ld_hämatokrit_hosp_peak,
  ld_gesamteiweiß_hosp_peak = ld_gesamteiweiß_hosp_peak,
  ld_crp_hosp_peak = ld_crp_hosp_peak,
  ld_kreatinin_hosp_peak = ld_kreatinin_hosp_peak,
  ld_harnstoff_hosp_peak = ld_harnstoff_hosp_peak,
  ld_natrium_hosp_peak = ld_natrium_hosp_peak,
  ld_kalium_hosp_peak = ld_kalium_hosp_peak,
  ld_kalzium_hosp_peak = ld_kalzium_hosp_peak
)

sink("plots hosp/liver diclo_peak_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```


### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  ld_gpt_hosp_peak = ld_gpt_hosp_peak,
  ld_got_hosp_peak = ld_got_hosp_peak,
  ld_ggt_hosp_peak = ld_ggt_hosp_peak,
  ld_ap_hosp_peak = ld_ap_hosp_peak,
  ld_total_bilirubin_hosp_peak = ld_total_bilirubin_hosp_peak,
  ld_direct_bilirubin_hosp_peak = ld_direct_bilirubin_hosp_peak,
  ld_ldh_hosp_peak = ld_ldh_hosp_peak,
  ld_ck_hosp_peak = ld_ck_hosp_peak,
  ld_quick_hosp_peak = ld_quick_hosp_peak,
  ld_inr_hosp_peak = ld_inr_hosp_peak,
  ld_ptt_hosp_peak = ld_ptt_hosp_peak,
  ld_leukozyten_hosp_peak = ld_leukozyten_hosp_peak,
  ld_erythrozyten_hosp_peak = ld_erythrozyten_hosp_peak,
  ld_thrombozyten_hosp_peak = ld_thrombozyten_hosp_peak,
  ld_hb_hosp_peak = ld_hb_hosp_peak,
  ld_hämatokrit_hosp_peak = ld_hämatokrit_hosp_peak,
  ld_gesamteiweiß_hosp_peak = ld_gesamteiweiß_hosp_peak,
  ld_crp_hosp_peak = ld_crp_hosp_peak,
  ld_kreatinin_hosp_peak = ld_kreatinin_hosp_peak,
  ld_harnstoff_hosp_peak = ld_harnstoff_hosp_peak,
  ld_natrium_hosp_peak = ld_natrium_hosp_peak,
  ld_kalium_hosp_peak = ld_kalium_hosp_peak,
  ld_kalzium_hosp_peak = ld_kalzium_hosp_peak
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "liver diclo_peak_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```


### Liver ibu ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  li_gpt_hosp_peak = li_gpt_hosp_peak,
  li_got_hosp_peak = li_got_hosp_peak,
  li_ggt_hosp_peak = li_ggt_hosp_peak,
  li_ap_hosp_peak = li_ap_hosp_peak,
  li_total_bilirubin_hosp_peak = li_total_bilirubin_hosp_peak,
  li_direct_bilirubin_hosp_peak = li_direct_bilirubin_hosp_peak,
  li_ldh_hosp_peak = li_ldh_hosp_peak,
  li_ck_hosp_peak = li_ck_hosp_peak,
  li_quick_hosp_peak = li_quick_hosp_peak,
  li_inr_hosp_peak = li_inr_hosp_peak,
  li_ptt_hosp_peak = li_ptt_hosp_peak,
  li_leukozyten_hosp_peak = li_leukozyten_hosp_peak,
  li_erythrozyten_hosp_peak = li_erythrozyten_hosp_peak,
  li_thrombozyten_hosp_peak = li_thrombozyten_hosp_peak,
  li_hb_hosp_peak = li_hb_hosp_peak,
  li_hämatokrit_hosp_peak = li_hämatokrit_hosp_peak,
  li_gesamteiweiß_hosp_peak = li_gesamteiweiß_hosp_peak,
  li_crp_hosp_peak = li_crp_hosp_peak,
  li_kreatinin_hosp_peak = li_kreatinin_hosp_peak,
  li_harnstoff_hosp_peak = li_harnstoff_hosp_peak,
  li_natrium_hosp_peak = li_natrium_hosp_peak,
  li_kalium_hosp_peak = li_kalium_hosp_peak,
  li_kalzium_hosp_peak = li_kalzium_hosp_peak
)

sink("plots hosp/liver ibu_peak_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```


### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  li_gpt_hosp_peak = li_gpt_hosp_peak,
  li_got_hosp_peak = li_got_hosp_peak,
  li_ggt_hosp_peak = li_ggt_hosp_peak,
  li_ap_hosp_peak = li_ap_hosp_peak,
  li_total_bilirubin_hosp_peak = li_total_bilirubin_hosp_peak,
  li_direct_bilirubin_hosp_peak = li_direct_bilirubin_hosp_peak,
  li_ldh_hosp_peak = li_ldh_hosp_peak,
  li_ck_hosp_peak = li_ck_hosp_peak,
  li_quick_hosp_peak = li_quick_hosp_peak,
  li_inr_hosp_peak = li_inr_hosp_peak,
  li_ptt_hosp_peak = li_ptt_hosp_peak,
  li_leukozyten_hosp_peak = li_leukozyten_hosp_peak,
  li_erythrozyten_hosp_peak = li_erythrozyten_hosp_peak,
  li_thrombozyten_hosp_peak = li_thrombozyten_hosp_peak,
  li_hb_hosp_peak = li_hb_hosp_peak,
  li_hämatokrit_hosp_peak = li_hämatokrit_hosp_peak,
  li_gesamteiweiß_hosp_peak = li_gesamteiweiß_hosp_peak,
  li_crp_hosp_peak = li_crp_hosp_peak,
  li_kreatinin_hosp_peak = li_kreatinin_hosp_peak,
  li_harnstoff_hosp_peak = li_harnstoff_hosp_peak,
  li_natrium_hosp_peak = li_natrium_hosp_peak,
  li_kalium_hosp_peak = li_kalium_hosp_peak,
  li_kalzium_hosp_peak = li_kalzium_hosp_peak
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "liver ibu_peak_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```


### Liver para ##########################################

### normality, variance, levene, welch summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  lp_gpt_hosp_peak = lp_gpt_hosp_peak,
  lp_got_hosp_peak = lp_got_hosp_peak,
  lp_ggt_hosp_peak = lp_ggt_hosp_peak,
  lp_ap_hosp_peak = lp_ap_hosp_peak,
  lp_total_bilirubin_hosp_peak = lp_total_bilirubin_hosp_peak,
  lp_direct_bilirubin_hosp_peak = lp_direct_bilirubin_hosp_peak,
  lp_ldh_hosp_peak = lp_ldh_hosp_peak,
  lp_ck_hosp_peak = lp_ck_hosp_peak,
  lp_quick_hosp_peak = lp_quick_hosp_peak,
  lp_inr_hosp_peak = lp_inr_hosp_peak,
  lp_ptt_hosp_peak = lp_ptt_hosp_peak,
  lp_leukozyten_hosp_peak = lp_leukozyten_hosp_peak,
  lp_erythrozyten_hosp_peak = lp_erythrozyten_hosp_peak,
  lp_thrombozyten_hosp_peak = lp_thrombozyten_hosp_peak,
  lp_hb_hosp_peak = lp_hb_hosp_peak,
  lp_hämatokrit_hosp_peak = lp_hämatokrit_hosp_peak,
  lp_gesamteiweiß_hosp_peak = lp_gesamteiweiß_hosp_peak,
  lp_crp_hosp_peak = lp_crp_hosp_peak,
  lp_kreatinin_hosp_peak = lp_kreatinin_hosp_peak,
  lp_harnstoff_hosp_peak = lp_harnstoff_hosp_peak,
  lp_natrium_hosp_peak = lp_natrium_hosp_peak,
  lp_kalium_hosp_peak = lp_kalium_hosp_peak,
  lp_kalzium_hosp_peak = lp_kalzium_hosp_peak
)

sink("plots hosp/liver para_peak_results normality, variance, levene, welch.txt")

for (name in names(files)) {
  
  data <- files[[name]]
 
  data <- data[!is.na(data$hospitalisation), ]
  
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    cat("\n============================\n")
    cat("Datensatz:", name, "\n")
    cat("============================\n")
    cat("➡️ skipped: fewer than 2 groups available\n\n")
    next
  }
  
  cat("\n============================\n")
  cat("Datensatz:", name, "\n")
  cat("============================\n\n")
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  cat("Normality Test (Shapiro-Wilk, abgesichert):\n")
  
  norm_res <- by(data[[var]], data$hospitalisation, function(x) {
    if (length(x) >= 3) {
      shapiro.test(x)
    } else {
      list(W = NA, p.value = NA)
    }
  })
  
  print(norm_res)
  
  cat("\nVarianz pro Gruppe:\n")
  print(tapply(data[[var]], data$hospitalisation, FUN = stats::var))
  
  cat("\nLevene-Test:\n")
  print(leveneTest(formula, data = data))
  
  group_sizes <- table(data$hospitalisation)
  valid_groups <- names(group_sizes[group_sizes >= 3])
  
  if (length(valid_groups) < 2) {
    cat("\nWelch ANOVA could not be performed due to an insufficient number of observations per group.\n")
  } else {
    filtered_data <- data[data$hospitalisation %in% valid_groups, ]
    cat("\nWelch ANOVA:\n")
    print(oneway.test(formula, data = filtered_data))
  }
}

sink()
while (sink.number() > 0) sink()
```


### Kruskal-Wallis-Test summary ###
```{r}
while (sink.number() > 0) sink()

files <- list(
  lp_gpt_hosp_peak = lp_gpt_hosp_peak,
  lp_got_hosp_peak = lp_got_hosp_peak,
  lp_ggt_hosp_peak = lp_ggt_hosp_peak,
  lp_ap_hosp_peak = lp_ap_hosp_peak,
  lp_total_bilirubin_hosp_peak = lp_total_bilirubin_hosp_peak,
  lp_direct_bilirubin_hosp_peak = lp_direct_bilirubin_hosp_peak,
  lp_ldh_hosp_peak = lp_ldh_hosp_peak,
  lp_ck_hosp_peak = lp_ck_hosp_peak,
  lp_quick_hosp_peak = lp_quick_hosp_peak,
  lp_inr_hosp_peak = lp_inr_hosp_peak,
  lp_ptt_hosp_peak = lp_ptt_hosp_peak,
  lp_leukozyten_hosp_peak = lp_leukozyten_hosp_peak,
  lp_erythrozyten_hosp_peak = lp_erythrozyten_hosp_peak,
  lp_thrombozyten_hosp_peak = lp_thrombozyten_hosp_peak,
  lp_hb_hosp_peak = lp_hb_hosp_peak,
  lp_hämatokrit_hosp_peak = lp_hämatokrit_hosp_peak,
  lp_gesamteiweiß_hosp_peak = lp_gesamteiweiß_hosp_peak,
  lp_crp_hosp_peak = lp_crp_hosp_peak,
  lp_kreatinin_hosp_peak = lp_kreatinin_hosp_peak,
  lp_harnstoff_hosp_peak = lp_harnstoff_hosp_peak,
  lp_natrium_hosp_peak = lp_natrium_hosp_peak,
  lp_kalium_hosp_peak = lp_kalium_hosp_peak,
  lp_kalzium_hosp_peak = lp_kalzium_hosp_peak
)

results <- data.frame()

for (name in names(files)) {
  
  data <- files[[name]]
  
  var <- "labreads"
  formula <- as.formula(paste(var, "~ hospitalisation"))
  
  data <- data[!is.na(data$hospitalisation), ]
  n_groups <- length(unique(data$hospitalisation))
  
  if (n_groups < 2) {
    results <- rbind(
      results,
      data.frame(
        Dataset = name,
        Variable = var,
        W_statistic = NA,
        p_value = NA,
        Note = "skipped: fewer than 2 groups available"
      )
    )
    next
  }
  
  mw <- wilcox.test(formula, data = data)
  
  group_sizes <- table(data$hospitalisation)
  
  note <- if (any(group_sizes < 3)) {
    "warning: at least one group has < 3 observations"
  } else {
    ""
  }
  
  # Ergebnis speichern
  results <- rbind(
    results,
    data.frame(
      Dataset = name,
      Variable = var,
      W_statistic = unname(mw$statistic),
      p_value = mw$p.value,
      Note = note
    )
  )
}

results

setwd("plots hosp/")
write.table(results,
            file = "liver para_peak_mann whitney results.txt",
            sep = "\t",
            row.names = FALSE,
            quote = FALSE)

while (sink.number() > 0) sink()
```