---
title: "Untitled"
output: html_document
date: "2025-09-29"
---


```{r}
library(dplyr)
library(ggplot2)
library(performance)

```




####regression plots ################################################################################
### Daily dose ####################################################################################
####################################################################################
### polynomial regression for daily doses for all labvalues #########
```{r}
# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_poly_plot <- ggplot(dose_result1, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily doses for all labvalues",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day1
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily doses for all labvalues.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day1)
dev.off()
```



```{r}
dose_result1_count <- dose_result1 %>%
  group_by(`Edited_BfArM Nummer2`) %>%
  mutate(
    labvalue_count = n(),  # Anzahl der Messwerte pro Patient
  ) %>%
  ungroup()
dose_result1_count
```


### polynomial regression for patients with 1 labvalue #########
```{r}
# Filter nur Patienten mit labvalue_count == 1
dose_result1_count_filtered <- dose_result1_count %>%
  filter(labvalue_count == 1)

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_poly_plot <- ggplot(dose_result1_count_filtered, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily doses for patients with 1 labvalue",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

#liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
#dir.create("plots_diclofenac", showWarnings = FALSE)
#svg("plots_diclofenac/liver diclo_gpt_full_linear regression for daily doses of diclofenac.svg", height = 6, width = 8)
#print(liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac)
#dev.off()
```



################################################################################
#### count patients per day for the time course group ##########################
```{r}
dose_result1_count %>% 
  filter(labvalue_count != 1) %>% 
  group_by(attribute) %>% 
  summarize(n = n(), .groups = "drop") %>% 
  arrange(n) #%>% 
  #filter(attribute == "GPT Day3")
  
```


###polynomial regression for time course patients for day1 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day1")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day1 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day1",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day1
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day1.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day1)
dev.off()
```



###polynomial regression for time course patients for day2 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day2")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day2 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day2",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day2
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day2.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day2)
dev.off()
```


###polynomial regression for time course patients for day3 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day3")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day3 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day3",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day3
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day3.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day3)
dev.off()
```


###polynomial regression for time course patients for day4 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day4")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day4 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day4",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day4
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day4.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day4)
dev.off()
```


###polynomial regression for time course patients for day5 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day5")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day5 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day5",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day5
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day5.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day5)
dev.off()
```


###polynomial regression for time course patients for day6 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day6")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day6 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day6",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day6
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day6.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day6)
dev.off()
```


###polynomial regression for time course patients for day8 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day8")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day8 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day8",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day8
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day8.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day8)
dev.off()
```


###polynomial regression for time course patients for day10 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day10")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day10 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day10",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day10
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day10.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day10)
dev.off()
```

###polynomial regression for time course patients for day11 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day11")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day11 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day11",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day11
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day11.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day11)
dev.off()
```

###polynomial regression for time course patients for day12 (=TCP)############
```{r}
# Filter 
dose_result1_count_filtered1 <- dose_result1_count %>%
  filter(labvalue_count != 1)
dose_result1_count_filtered2 <- dose_result1_count_filtered1 %>%
  filter(attribute == "GPT Day12")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = dose_result1_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day12 <- ggplot(dose_result1_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily dose for TCP at day12",
    x = "Daily dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day12
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for daily dose for TCP at day12.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_daily_doses_for_TCP_day12)
dev.off()
```









####regression plots ################################################################################
### Cumulative Dose ##################################################################
####################################################################################

### polynomial regression for cumulative doses for all labvalues #########
```{r}
# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_poly_plot <- ggplot(ld_gpt_cd, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for all labvalues",
    x = "Cumulative dose (mg) (log-scale)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

#liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
#dir.create("plots_diclofenac", showWarnings = FALSE)
#svg("plots_diclofenac/liver diclo_gpt_full_linear regression for daily doses of diclofenac.svg", height = 6, width = 8)
#print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day11)
#dev.off()
```


```{r}
library(dplyr)

ld_gpt_cd_count <- ld_gpt_cd %>%
  group_by(`Edited_BfArM Nummer2`) %>%
  mutate(
    labvalue_count = n(),  # Anzahl der Messwerte pro Patient
  ) %>%
  ungroup()
ld_gpt_cd_count
```




```{} 
wird nicht gebraucht


# Logarithmische Skala: x-Achse log10
ld_gpt_cd_count_filtered <- ld_gpt_cd_count %>%
  filter(labvalue_count == 1)

library(dplyr)
library(scales)
liver_diclo_gpt_full_smooth_line_plot_for_cumulative_doses_of_diclofenac_1 <- ggplot(ld_gpt_cd_count_filtered, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +           # Scatter plot
  geom_smooth() +                                  # Glättungslinie (loess oder lm)
  scale_x_log10() +                                # <-- hier die Log-Skala
  labs(
    title = "liver_diclo smooth line plot for cumulative doses of diclofenac with log scale",        
    x = "Cumulative dose in mg (log scale)",             
    y = "GPT U/L"
  ) +
  theme_classic()
liver_diclo_gpt_full_smooth_line_plot_for_cumulative_doses_of_diclofenac_1
#liver_diclo_gpt_full_smooth_line_plot_for_cumulative_doses_of_diclofenac
#dir.create("plots_diclofenac", showWarnings = FALSE)
#svg("plots_diclofenac/liver_diclo_gpt_full_smooth line plot for cumulative doses of diclofenac.svg", height = 6, width = 8)
#print(liver_diclo_gpt_full_smooth_line_plot_for_cumulative_doses_of_diclofenac)
#dev.off()
```

```{}
#alte Grafik mit log scale an der falschen stelle und nicht so sophisticated

ld_gpt_cd_count_filtered <- ld_gpt_cd_count %>%
  filter(labvalue_count == 1)
# Fit the linear model
lm_model_cd <- lm(labreads  ~ Parameter , data = ld_gpt_cd_count_filtered)

#check_model(lm_model_cd)

# Extract the coefficients
intercept <- coef(lm_model_cd)[1]
slope <- coef(lm_model_cd)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model_cd)$r.squared


```

```{}
ld_gpt_cd_count_filtered <- ld_gpt_cd_count %>%
  filter(labvalue_count == 1)

liver_diclo_gpt_full_linear_regression_for_cumulative_doses_of_diclofenac1 <- ggplot(ld_gpt_cd_count_filtered, aes(x= Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_linear regression for CD of diclo for labvaluecount 1",   
    x = "Cumulative dose in mg (log-scale)",
    y = "GPT (U/L)"
  ) +
  coord_cartesian(clip = "off") +  # erlaubt Text außerhalb des Plotbereichs
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)  # etwas mehr Rand rechts
  )
liver_diclo_gpt_full_linear_regression_for_cumulative_doses_of_diclofenac1
#dir.create("plots_diclofenac", showWarnings = FALSE)
#svg("plots_diclofenac/liver diclo_gpt_full_linear regression for cumulative doses of diclofenac.svg", height = 6, width = 8)
#print(liver_diclo_gpt_full_linear_regression_for_cumulative_doses_of_diclofenac)
#dev.off()
```

### polynomial regression for patients with 1 labvalue #########
```{r}
# Filter nur Patienten mit labvalue_count == 1
ld_gpt_cd_count_filtered <- ld_gpt_cd_count %>%
  filter(labvalue_count == 1)

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_poly_plot <- ggplot(ld_gpt_cd_count_filtered, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
   scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for daily doses for patients with 1 labvalue",
    x = "Cumulative dose (mg) (log-scale)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

#liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
#dir.create("plots_diclofenac", showWarnings = FALSE)
#svg("plots_diclofenac/liver diclo_gpt_full_linear regression for daily doses of diclofenac.svg", height = 6, width = 8)
#print(liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac)
#dev.off()
```


### polynomial regression with patients with 1 labvalue #########
```{}
library(dplyr)
library(ggplot2)

# Filter nur Patienten mit labvalue_count == 1
ld_gpt_cd_count_filtered <- ld_gpt_cd_count %>%
  filter(labvalue_count == 1)

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_poly_plot <- ggplot(ld_gpt_cd_count_filtered, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "Liver Diclofenac: Polynomial Regression (2nd order) for Cumulative Dose",
    x = "Cumulative dose in mg (log-scale)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

```


################################################################################
#### count patients per day for the time course group ##########################
```{r}
ld_gpt_cd_count %>% 
  filter(labvalue_count != 1) %>% 
  group_by(attribute) %>% 
  summarize(n = n(), .groups = "drop") %>% 
  arrange(n) #%>% 
  #filter(attribute == "GPT Day3")
  
```

### linear regression with patients with more than one labvalue for day 1 ############
# lineare Regression hat sich zu niedriges R2, daher soll nur polynomiale Regression verwendet werden!!!!!!!!!!!
```{}
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day1")

# Fit the linear model
lm_model_cd <- lm(labreads ~ Parameter, data = ld_gpt_cd_count_filtered2)

#check_model(lm_model_cd)

# Extract the coefficients
intercept <- coef(lm_model_cd)[1]
slope <- coef(lm_model_cd)[2]

# Create the equation string
equation <- paste("y = ", round(intercept, 2), " + ", round(slope, 2), "x", sep = "")
r_squared <- summary(lm_model_cd)$r.squared


```

```{}
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day1")

liver_diclo_gpt_full_linear_regression_for_cumulative_doses_of_diclofenac2 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", se = TRUE, color = "red", linetype = "dashed") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_linear regression for cumulative doses of diclofenac with log scale",   
    x = "Cumulative dose in mg (log-scale)",
    y = "GPT (U/L)"
  ) +
  coord_cartesian(clip = "off") +  # erlaubt Text außerhalb des Plotbereichs
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)  # etwas mehr Rand rechts
  )
liver_diclo_gpt_full_linear_regression_for_cumulative_doses_of_diclofenac2
#dir.create("plots_diclofenac", showWarnings = FALSE)
#svg("plots_diclofenac/liver diclo_gpt_full_linear regression for cumulative doses of diclofenac.svg", height = 6, width = 8)
#print(liver_diclo_gpt_full_linear_regression_for_cumulative_doses_of_diclofenac)
#dev.off()
```

###polynomial regression for time course patients for day 1 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day1")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day1 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative dose for TCP at day1",
    x = "Cumulative dose (mg) (log-scale)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day1
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative dose for TCP at day1.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day1)
dev.off()
```

###polynomial regression with patients with more than one labvalue for day 1 ############
```{}
# logscale an der falschen stelle und nicht so sophisticated
library(dplyr)
library(ggplot2)

ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day1")

# Filter nur Patienten mit labvalue_count == 1
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count %>%
  filter(labvalue_count == 1)

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_poly_plot <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "Liver Diclofenac: Polynomial Regression (2nd order) for Cumulative Dose",
    x = "Cumulative dose in mg (log-scale)",
    y = "GPT (U/L)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

```


###polynomial regression for time course patients for day2 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day2")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day2 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative dose for TCP at day2",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day2
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day2.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day2)
dev.off()
```


###polynomial regression for time course patients for day3 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day3")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day3 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day3",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day3.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day3)
dev.off()
```


###polynomial regression for time course patients for day4 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day4")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day4 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day4",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day4.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day4)
dev.off()
```


###polynomial regression for time course patients for day5 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day5")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day5 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day5",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day5.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day5)
dev.off()
```


###polynomial regression for time course patients for day6 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day6")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day6 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day6",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day6.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day6)
dev.off()
```


###polynomial regression for time course patients for day8 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day8")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day8 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day8",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day8.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day8)
dev.off()
```


###polynomial regression for time course patients for day10 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day10")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day10 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day10",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day10.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day10)
dev.off()
```



###polynomial regression for time course patients for day11 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day11")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day11 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day11",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day11.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day11)
dev.off()
```


###polynomial regression for time course patients for day11 (=TCP)############
```{r}
# Filter 
ld_gpt_cd_count_filtered1 <- ld_gpt_cd_count %>%
  filter(labvalue_count != 1)
ld_gpt_cd_count_filtered2 <- ld_gpt_cd_count_filtered1 %>%
  filter(attribute == "GPT Day12")

# Polynomiale Regression 2. Ordnung (quadratisch)
lm_model_cd_poly <- lm(labreads ~ poly(Parameter, 2, raw = TRUE), data = ld_gpt_cd_count_filtered2)

# Koeffizienten extrahieren
coefs <- coef(lm_model_cd_poly)
intercept <- coefs[1]
slope1 <- coefs[2]
slope2 <- coefs[3]

# Gleichung und R²
equation <- paste0("y = ", round(intercept, 2), 
                   " + ", round(slope1, 2), "x", 
                   " + ", round(slope2, 2), "x²")
r_squared <- summary(lm_model_cd_poly)$r.squared

# Plot
liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day11 <- ggplot(ld_gpt_cd_count_filtered2, aes(x = Parameter, y = labreads)) +
  geom_point(color = "blue", size = 2) +    
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = TRUE, 
              color = "red", linetype = "dashed") +
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 20000),
    labels = scales::label_number(big.mark = ".", decimal.mark = ",")
  ) +
  labs(
    title = "liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day11",
    x = "Cumulative dose (mg)",
    y = "GPT (U/L) (log-scale)"
  ) +
  coord_cartesian(clip = "off") +
  annotate("text", x = Inf, y = Inf, label = paste("R² =", round(r_squared, 2)),
           hjust = 1.05, vjust = 2.2, size = 5, color = "black") +
  annotate("text", x = Inf, y = Inf, label = equation,
           hjust = 1.05, vjust = 3.8, size = 5, color = "black") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 30, r = 30, b = 20, l = 20)
  )

# Plot anzeigen
liver_diclo_gpt_poly_plot

liver_diclo_gpt_full_linear_regression_for_daily_doses_of_diclofenac
dir.create("plots_diclofenac/plots_diclofenac_gpt", showWarnings = FALSE)
svg("plots_diclofenac/plots_diclofenac_gpt/liver diclo_gpt_full_polynomial regression for cumulative doses for TCP at day11.svg", height = 6, width = 8)
print(liver_diclo_gpt_full_polynomial_regression_for_cumulative_doses_for_TCP_day11)
dev.off()
```








