---
title: "boxplots_20may2026"
author: "Arun Kumar"
date: "2026-05-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(rstatix)
```

```{r}
source(here::here("R/make_boxplot_with_stats.R"))
source(here::here("R/export_plot.R"))
source(here::here("R/pretty_boxplot.R"))
source(here::here("R/clean_data.R"))
source(here::here("R/comedication.R"))
```


##===================
## Raw data from Excel
##===================

```{r}
sheets <- excel_sheets(here::here(
  "RawData/new_raw_data/ubersicht_Laborwerte_laborwerte_fertig_aktuell_new.xlsx"
))

sheets <- sheets[
  sheets %in% c(
    "Fallberichte")]
sheets


all_data <- map_dfr(
  sheets,
  ~ process_sheet(file = here::here("RawData/new_raw_data/ubersicht_Laborwerte_laborwerte_fertig_aktuell_new.xlsx"), .x)
  )
all_data
```

## Note:: please open the diabetes_graphs_may2026 file to work together ##


##================
## Diabetic case
##================
```{r}
gpt_full <- all_data %>% 
       filter(panel_id == "gpt")
gpt_full
```


```{r}

diabetic_data <- read_excel(here::here("RawData/Diabetes rawdata.xlsx"), 
                            sheet = 2) %>% 
                            drop_na() %>% 
  janitor::clean_names() %>% 
  dplyr::rename("bf_ar_m_nummer"  = "edited_bf_ar_m_nummer2")

diabetic_data
```


```{r}
p1_diabetic_plot <- left_join(gpt_full, 
                          diabetic_data, 
                          by = ("bf_ar_m_nummer"),
                          relationship = "many-to-many") %>% 
            mutate(labreads = as.numeric(labreads)) %>% 
  drop_na() %>% 
  filter(diabetes == "Diabetic") %>% 
#  filter(!attribute == "GPT Day_Unknown") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  mutate(treatment = recode(treatment,
    "Leber_Diclo" = "Liver_Diclo",
    "Leber_Ibu"   = "Liver_Ibu",
    "Leber_Para"  = "Liver_Para"
  )) %>% 
  group_by(treatment)
  
p1_diabetic_plot
```

```{r}
df_test <- p1_diabetic_plot %>%
  ungroup() %>%
  mutate(
    labreads  = as.numeric(labreads),
    treatment = factor(treatment)
  ) %>%
  drop_na(treatment, labreads)

stat_test_debug <- df_test %>%
  pairwise_wilcox_test(
    formula         = labreads ~ treatment,
    p.adjust.method = "BH"
  ) %>%
  add_significance("p.adj") %>%
  add_xy_position(x = "treatment")

# Check group1/group2 values and y.position
print(stat_test_debug)
```



```{r}
comparisons_diabetes <- list(
  c("Leber_Diclo", "Leber_Ibu"),
  c("Leber_Diclo", "Leber_Para"),
  c("Leber_Ibu", "Leber_Para")
)
```

```{r}
diabetic_case <- make_boxplot_with_stats(
  data = p1_diabetic_plot,
  x = treatment,
  y = labreads,
  title = "Comparison of Diabetic Cases",
  ylab = "ALT (u/l)",
  comparisons = comparisons_diabetes
  
)
diabetic_case
```




##================
## Non Diabetic case
##================

```{r}
p2_nondiabetic_plot <- left_join(gpt_full, 
                          diabetic_data, 
                          by = ("bf_ar_m_nummer"),
                          relationship = "many-to-many") %>% 
            mutate(labreads = as.numeric(labreads)) %>% 
  drop_na() %>% 
  filter(diabetes == "Non_Diabetic") %>% 
#  filter(!attribute == "GPT Day_Unknown") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  filter(grepl("Leber_", treatment)) %>% 
  mutate(treatment = recode(treatment,
    "Leber_Diclo" = "Liver_Diclo",
    "Leber_Ibu"   = "Liver_Ibu",
    "Leber_Para"  = "Liver_Para"
  )) %>% 
  group_by(treatment)
  
p2_nondiabetic_plot
```




```{r}
non_diabetic_case <- make_boxplot_with_stats(
  data = p2_nondiabetic_plot,
  x = treatment,
  y = labreads,
  title = "Comparison of nonDiabetic Cases",
  ylab = "ALT (u/l)",
  comparisons = comparisons_diabetes,
  
)
non_diabetic_case
```


```{r}
save_plots(
  plots = list(diabetic_case,non_diabetic_case),
  names = c("ALT_diabetic", "ALT_non_diabetic"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##====================================
## liver_diclo_diabetic vs nondiabetic
##====================================


```{r}
# Anzahl einzigartiger Patienten pro Gruppe
leber_diabetic_diclo <- gpt_diabetic %>% 
  filter(treatment == "Leber_Diclo")

label_df <- leber_diabetic_diclo %>%
  group_by(diabetes) %>%
  summarise(
    n_patients = n_distinct(bf_ar_m_nummer),
    n_labreads = n()
  ) %>%
  mutate(label = paste0("N = ", n_patients,
                        "\nLab = ", n_labreads))
label_df

label_df_top <- label_df %>%
  mutate(label = paste0("N = ", n_patients))
label_df_bottom <- label_df %>%
  mutate(label = paste0("n = ", n_labreads))



# y positions
y_max    <- max(leber_diabetic_diclo$labreads, na.rm = TRUE)
y_top    <- y_max * 1.30
y_bottom <- y_max * -0.40 



leber_diclo_diabetic_vs_nondiabetic <- ggplot(leber_diabetic_diclo,
             aes(x = diabetes, y = labreads, fill = diabetes)) +
  geom_violin(trim = TRUE, alpha = 0.5, color = "black") +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.8, color = "black") +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = median, geom = "point",
               shape = 23, size = 4, fill = "yellow") +
  geom_text(
    data = label_df_top,
    aes(x = diabetes, y = y_top, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 5
  ) +
  geom_text(
    data = label_df_bottom,
    aes(x = diabetes, y = y_bottom, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 4
  ) +
  stat_compare_means(
    comparisons = list(c("Diabetic", "Non_Diabetic")),
    method = "wilcox.test", label = "p.format",
    label.y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.08,
    bracket.size = 1, tip.length = 0.02, size = 4
  ) +
  labs(
    title = "Comparsion ofliver_diclo ALT for \nDiabetic vs. Non-Diabetic Patients",
    x = NULL, y = "ALT (U/l)"
  ) +
  coord_cartesian(ylim = c(0, y_max * 1.50),
                  clip = "off") +          # ✅ Separate layer — NOT inside theme()
  theme_classic() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold",
                              margin = margin(b = 10), lineheight = 1.2),
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold"),
    axis.title  = element_text(size = 15, face = "bold"),
    axis.line   = element_line(linewidth = 1),
    plot.margin = margin(t = 10, r = 10, b = 40, l = 10)  # bottom margin for labels
  )
leber_diclo_diabetic_vs_nondiabetic
```


##======================================
## Boxplots for diabetic_non_diabetic
##======================================



```{r}
dibetic_nondiabetic_full <- plot_lab_comparison(
  data           = gpt_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of \nALT for Diabetic vs. Non-Diabetic Patients",
  y_label        = "ALT (U/l)"
)
dibetic_nondiabetic_full
```


```{r}
gpt_liver_diclo <- gpt_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_alt_diclo <- plot_lab_comparison(
  data           = gpt_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of liver diclo \nALT for Diabetic vs. Non-Diabetic Patients",
  y_label        = "ALT (U/l)"
)
p1_alt_diclo
```

```{r}
gpt_liver_Ibu <- gpt_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_alt_ibu <-plot_lab_comparison(
  data           = gpt_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of liver ibu \nALT for Diabetic vs. Non-Diabetic Patients",
  y_label        = "ALT (U/l)"
)
p2_alt_ibu
```

```{r}
gpt_liver_para <- gpt_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_alt_para <-plot_lab_comparison(
  data           = gpt_liver_para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of liver para \nALT for Diabetic vs. Non-Diabetic Patients",
  y_label        = "ALT (U/l)"
)
p3_alt_para
```
```{r}
save_plots(
  plots = list(dibetic_nondiabetic_full, p1_alt_diclo, p2_alt_ibu, p3_alt_para),
  names = c("dibetic_nondiabetic_full", "p1_alt_diclo", "p2_alt_ibu", "p3_alt_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```



##=======================
## GOT Diabetic data
========================

```{r}
# plot_lab_comparison <- function(
#     data,
#     group_var,
#     y_var,
#     patient_id_var,
#     comparisons,
#     plot_title   = "Comparison of Lab Values",
#     x_label      = NULL,
#     y_label      = "Lab Value",
#     jitter_width = 0.15,
#     jitter_alpha = 0.5,
#     jitter_size  = 2,
#     text_size    = 4,
#     n_breaks     = 10
# ) {
# 
#   group_col <- deparse(substitute(group_var))
#   y_col     <- deparse(substitute(y_var))
#   id_col    <- deparse(substitute(patient_id_var))
# 
#   # ── Validation ---------------------------------------------------------------
#   missing_cols <- setdiff(c(group_col, y_col, id_col), names(data))
#   if (length(missing_cols) > 0) {
#     stop("Column(s) not found in data: ", paste(missing_cols, collapse = ", "))
#   }
# 
#   if (!is.numeric(data[[y_col]])) {
#     message("Note: Converting '", y_col, "' from ", class(data[[y_col]]), " to numeric.")
#     data[[y_col]] <- as.numeric(data[[y_col]])
# 
#     n_lost <- sum(is.na(data[[y_col]]))
#     if (n_lost > 0) {
#       message("Warning: ", n_lost, " value(s) became NA after conversion — check raw data.")
#     }
#   }
# 
#   if (all(is.na(data[[y_col]]))) {
#     stop("y_var '", y_col, "' is all NA after conversion — check for non-numeric values.")
#   }
# 
#   # ── Label data frames --------------------------------------------------------
#   labels <- make_label_dfs(data, {{ group_var }}, {{ patient_id_var }})
#   label_df_top    <- labels$top
#   label_df_bottom <- labels$bottom
# 
#   # ── Y-axis positions ---------------------------------------------------------
#   y_max    <- max(data[[y_col]], na.rm = TRUE)
#   y_top    <- y_max * 1.15
#   y_bottom <- y_max * -0.25
# 
#   # ── rest of your ggplot code unchanged ──────────────────────────────────────
#   ggplot(data,
#          aes(x = .data[[group_col]],
#              y = .data[[y_col]],
#              fill = .data[[group_col]])) +
# 
#     # geom_violin(trim = FALSE, alpha = 0.5, color = "black") +
# 
#     geom_boxplot(width = 0.15, outlier.shape = NA,
#                  alpha = 0.5, color = "black") +
#     geom_jitter(width = jitter_width, alpha = jitter_alpha,
#                 size  = jitter_size,
#                 color = "#CC79A7")  +
#     stat_summary(fun = median, geom = "point",
#                  shape = 23, size = 4, fill = "brown") +
#     geom_text(
#       data        = label_df_top,
#       aes(x = .data[[group_col]], y = y_top, label = label),
#       inherit.aes = FALSE, fontface = "plain", size = text_size
#     ) +
#     geom_text(
#       data        = label_df_bottom,
#       aes(x = .data[[group_col]], y = y_bottom, label = label),
#       inherit.aes = FALSE, fontface = "plain", size = text_size
#     ) +
#     stat_compare_means(
#       comparisons  = comparisons,
#       method       = "wilcox.test",
#       label        = "p.format",
#       label.y      = y_max * 1.02,
#       bracket.size = 1, tip.length = 0.02, size = text_size
#     ) +
#     labs(title = plot_title, x = x_label, y = y_label) +
#     coord_cartesian(ylim = c(0, y_max * 1.20), clip = "off") +
#     scale_y_continuous(breaks = scales::breaks_pretty(n = n_breaks)) +
#     theme_classic() +
#     theme(
#       legend.position  = "none",
#       plot.title       = element_text(hjust = 0.5, face = "bold",
#                                       margin = margin(b = 10),
#                                       lineheight = 1.2),
#       axis.text.x      = element_text(size = 12, face = "bold"),
#       axis.text.y      = element_text(size = 12, face = "bold"),
#       axis.title       = element_text(size = 15, face = "bold"),
#       axis.line        = element_line(linewidth = 1),
#       plot.margin      = margin(t = 10, r = 10, b = 30, l = 10)
#     )
# }
```


```{r}
dibetic_nondiabetic_ASTfull <- plot_lab_comparison(
  data           = got_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of AST \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AST (U/l)"
)
dibetic_nondiabetic_ASTfull
```


```{r}

got_liver_diclo <- got_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_ast_diclo <- plot_lab_comparison(
  data           = got_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of AST liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AST (U/l)"
)
p1_ast_diclo
```


```{r}

got_liver_Ibu <- got_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_ast_ibu <- plot_lab_comparison(
  data           = got_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of AST liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AST (U/l)"
)
p2_ast_ibu
```


```{r}

got_liver_para <- got_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_ast_para <- plot_lab_comparison(
  data           = got_liver_para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of AST liver_para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AST (U/l)"
)
p3_ast_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_ASTfull, p1_ast_diclo, p2_ast_ibu, p3_ast_para),
  names = c("dibetic_nondiabetic_ASTfull", "p1_ast_diclo", "p2_ast_ibu", "p3_ast_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##==========================
## GGT
##=========================

```{r}

dibetic_nondiabetic_GGTfull <- plot_lab_comparison(
  data           = ggt_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of GGT \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "GGT (U/l)"
)
dibetic_nondiabetic_GGTfull
```


```{r}

ggt_liver_diclo <- ggt_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_ggt_diclo <- plot_lab_comparison(
  data           = ggt_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of GGT liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "GGT (U/l)"
)
p1_ggt_diclo
```


```{r}

ggt_liver_Ibu <- ggt_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_ggt_ibu <- plot_lab_comparison(
  data           = ggt_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of GGT liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "GGT (U/l)"
)
p2_ggt_ibu
```


```{r}

ggt_liver_Para <- ggt_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_ggt_para <- plot_lab_comparison(
  data           = ggt_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of GGT liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "GGT (U/l)"
)
p3_ggt_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_GGTfull, p1_ggt_diclo, p2_ggt_ibu, p3_ggt_para),
  names = c("dibetic_nondiabetic_GGTfull", "p1_ggt_diclo", "p2_ggt_ibu", "p3_ggt_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##=================
## LDH
##================

```{r}

dibetic_nondiabetic_LDHfull <- plot_lab_comparison(
  data           = ldh_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of LDH \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "LDH (U/l)"
)
dibetic_nondiabetic_LDHfull
```


```{r}

ldh_liver_diclo <- ldh_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_ldh_diclo <- plot_lab_comparison(
  data           = ldh_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of LDH liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "LDH (U/l)"
)
p1_ldh_diclo
```



```{r}

ldh_liver_Ibu <- ldh_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_ldh_ibu <- plot_lab_comparison(
  data           = ldh_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of LDH liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "LDH (U/l)"
)
p2_ldh_ibu
```


```{r}

ldh_liver_Para <- ldh_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_ldh_para <- plot_lab_comparison(
  data           = ldh_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of LDH liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "LDH (U/l)"
)
p3_ldh_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_LDHfull, p1_ldh_diclo, p2_ldh_ibu, p3_ldh_para),
  names = c("dibetic_nondiabetic_LDHfull", "p1_ldh_diclo", "p2_ldh_ibu", "p3_ldh_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##=================
## CK
##================

```{r}

dibetic_nondiabetic_CKfull <- plot_lab_comparison(
  data           = ck_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of CK \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CK (U/l)"
)
dibetic_nondiabetic_CKfull
```




```{r}

ck_liver_diclo <- ck_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_ck_diclo <- plot_lab_comparison(
  data           = ck_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of LDH liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CK (U/l)"
)
p1_ck_diclo
```

```{r}

ck_liver_Ibu <- ck_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_ck_ibu <- plot_lab_comparison(
  data           = ck_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of LDH liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CK (U/l)"
)
p2_ck_ibu
```

```{r}

ck_liver_Para <- ck_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_ck_para <- plot_lab_comparison(
  data           = ck_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of LDH liver_para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CK (U/l)"
)
p3_ck_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_CKfull, p1_ck_diclo, p2_ck_ibu, p3_ck_para),
  names = c("dibetic_nondiabetic_CKfull", "p1_ck_diclo", "p2_ck_ibu", "p3_ck_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##==============
## AP
##==============

```{r}

dibetic_nondiabetic_APfull <- plot_lab_comparison(
  data           = ap_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of AP \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AP (U/l)"
)
dibetic_nondiabetic_APfull
```


```{r}

ap_liver_diclo <- ap_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_ap_diclo <- plot_lab_comparison(
  data           = ap_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of AP liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AP (U/l)"
)
p1_ap_diclo
```

```{r}

ap_liver_Ibu <- ap_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_ap_ibu <- plot_lab_comparison(
  data           = ap_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of AP liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AP (U/l)"
)
p2_ap_ibu
```


```{r}

ap_liver_Para <- ap_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_ap_para <- plot_lab_comparison(
  data           = ap_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of AP liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "AP (U/l)"
)
p3_ap_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_APfull, p1_ap_diclo, p2_ap_ibu, p3_ap_para),
  names = c("dibetic_nondiabetic_APfull", "p1_ap_diclo", "p2_ap_ibu", "p3_ap_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##==========
##ptt
##==========

```{r}

dibetic_nondiabetic_PTTfull <- plot_lab_comparison(
  data           = ptt_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of PTT \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "PTT (U/l)"
)
dibetic_nondiabetic_PTTfull
```


```{r}

ptt_liver_diclo <- ptt_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_ptt_diclo <- plot_lab_comparison(
  data           = ptt_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of PTT liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "PTT (U/l)"
)
p1_ptt_diclo
```

```{r}

ptt_liver_Ibu <- ptt_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_ptt_ibu <- plot_lab_comparison(
  data           = ptt_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of PTT liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "PTT (U/l)"
)
p2_ptt_ibu
```

```{r}

ptt_liver_Para <- ptt_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_ptt_para <- plot_lab_comparison(
  data           = ptt_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of PTT liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "PTT (U/l)"
)
p3_ptt_para 
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_PTTfull, p1_ptt_diclo, p2_ptt_ibu, p3_ptt_para),
  names = c("dibetic_nondiabetic_PTTfull", "p1_ptt_diclo", "p2_ptt_ibu", "p3_ptt_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##==============
## leukocytes
##==============

```{r}

dibetic_nondiabetic_leucoytefull <- plot_lab_comparison(
  data           = Leukozyten_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of leukocytes \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "leukocytes (U/l)"
)
dibetic_nondiabetic_leucoytefull
```


```{r}

Leukozyten_liver_diclo <- Leukozyten_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_leucocyte_diclo <- plot_lab_comparison(
  data           = Leukozyten_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of leukocytes liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "leukocytes (U/l)"
)
p1_leucocyte_diclo
```

```{r}

Leukozyten_liver_Ibu <- Leukozyten_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_leucocyte_ibu <- plot_lab_comparison(
  data           = Leukozyten_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of leukocytes liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "leukocytes (U/l)"
)
p2_leucocyte_ibu
```


```{r}

Leukozyten_liver_Para <- Leukozyten_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_leucocyte_para <- plot_lab_comparison(
  data           = Leukozyten_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of leukocytes liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "leukocytes (U/l)"
)
p3_leucocyte_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_leucoytefull, 
               p1_leucocyte_diclo, 
               p2_leucocyte_ibu, 
               p3_leucocyte_para),
  names = c("dibetic_nondiabetic_leucoytefull", 
            "p1_leucocyte_diclo", 
            "p2_leucocyte_ibu", 
            "p3_leucocyte_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##=================
## Erythrocytes erythrocytes
##=================

```{r}

dibetic_nondiabetic_erythrocytesfull <- plot_lab_comparison(
  data           = erythrozyten_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of erythrocytes \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Erythrocytes (cells/ul)"
)
dibetic_nondiabetic_erythrocytesfull
```


```{r}

Erythorcytes_liver_diclo <- erythrozyten_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_erythrocytes_diclo <- plot_lab_comparison(
  data           = Erythorcytes_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of erythorcytes liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Erythorcytes (Cell/Ul)"
)
p1_erythrocytes_diclo
```


```{r}

Erythorcytes_liver_Ibu <- erythrozyten_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_erythrocytes_ibu <- plot_lab_comparison(
  data           = Erythorcytes_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of erythorcytes liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Erythorcytes (Cell/Ul)"
)
p2_erythrocytes_ibu
```


```{r}

Erythorcytes_liver_Para <- erythrozyten_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_erythrocytes_para <- plot_lab_comparison(
  data           = Erythorcytes_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of erythorcytes liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Erythorcytes (Cell/Ul)"
)
p3_erythrocytes_para
```



```{r}
save_plots(
  plots = list(dibetic_nondiabetic_erythrocytesfull, 
               p1_erythrocytes_diclo, 
               p2_erythrocytes_ibu, 
               p3_erythrocytes_para),
  names = c("dibetic_nondiabetic_erythrocytesfull", 
            "p1_erythrocytes_diclo", 
            "p2_erythrocytes_ibu", 
            "p3_erythrocytes_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##======================
## Thrombozyten_diabetic
##======================

```{r}

dibetic_nondiabetic_thrombocytesfull <- plot_lab_comparison(
  data           = Thrombozyten_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of thrombocytes \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Thrombocytes (cells/ul)"
)
dibetic_nondiabetic_thrombocytesfull
```

```{r}

Thrombocytes_liver_diclo <- Thrombozyten_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_thrombocytes_diclo <- plot_lab_comparison(
  data           = Thrombocytes_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of thrombocytes liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Thrombocytes (Cell/Ul)"
)
p1_thrombocytes_diclo
```

```{r}

Thrombocytes_liver_Ibu <- Thrombozyten_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_thrombocytes_ibu <- plot_lab_comparison(
  data           = Thrombocytes_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of thrombocytes liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Thrombocytes (Cell/Ul)"
)
p2_thrombocytes_ibu
```

```{r}

Thrombocytes_liver_Para <- Thrombozyten_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_thrombocytes_para <- plot_lab_comparison(
  data           = Thrombocytes_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of thrombocytes liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Thrombocytes (Cell/Ul)"
)
p3_thrombocytes_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_thrombocytesfull, 
               p1_thrombocytes_diclo, 
               p2_thrombocytes_ibu, 
               p3_thrombocytes_para),
  names = c("dibetic_nondiabetic_thrombocytesfull", 
            "p1_thrombocytes_diclo", 
            "p2_thrombocytes_ibu", 
            "p3_thrombocytes_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##===============
## hb_diabetic
##===============

```{r}

dibetic_nondiabetic_hbfull <- plot_lab_comparison(
  data           = hb_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of hb \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "hb (g/dl)"
)
dibetic_nondiabetic_hbfull
```


```{r}

hb_liver_diclo <- hb_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_hb_diclo <- plot_lab_comparison(
  data           = hb_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of hb liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "hb (g/dl)"
)
p1_hb_diclo
```

```{r}

hb_liver_Ibu <- hb_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_hb_ibu <- plot_lab_comparison(
  data           = hb_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of hb liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "hb (g/dl)"
)
p2_hb_ibu
```

```{r}

hb_liver_Para <- hb_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_hb_para <- plot_lab_comparison(
  data           = hb_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of hb liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "hb (g/dl)"
)
p3_hb_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_hbfull, 
               p1_hb_diclo, 
               p2_hb_ibu, 
               p3_hb_para),
  names = c("dibetic_nondiabetic_hbfull", 
            "p1_hb_diclo", 
            "p2_hb_ibu", 
            "p3_hb_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##=======================
## gesamteiweiß_diabetic
## Total Protein
##=======================


```{r}

dibetic_nondiabetic_totalproteinfull <- plot_lab_comparison(
  data           = gesamteiweiß_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of Total protein \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Total Protein (g/dl)"
)
dibetic_nondiabetic_totalproteinfull
```


```{r}

TP_liver_diclo <- gesamteiweiß_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_totalprotein_diclo <- plot_lab_comparison(
  data           = TP_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of Total protein liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Total Protein (g/dl)"
)
p1_totalprotein_diclo
```

```{r}

TP_liver_Ibu <- gesamteiweiß_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_totalprotein_ibu <- plot_lab_comparison(
  data           = TP_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of Total protein liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Total Protein (g/dl)"
)
p2_totalprotein_ibu
```

```{r}

TP_liver_Para <- gesamteiweiß_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_totalprotein_para <- plot_lab_comparison(
  data           = TP_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of Total protein liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Total Protein (g/dl)"
)
p3_totalprotein_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_totalproteinfull, 
               p1_totalprotein_diclo, 
               p2_totalprotein_ibu, 
               p3_totalprotein_para),
  names = c("dibetic_nondiabetic_totalproteinfull", 
            "p1_totalprotein_diclo", 
            "p2_totalprotein_ibu", 
            "p3_totalprotein_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##====================
## kreatinin_diabetic
##====================

```{r}

dibetic_nondiabetic_kreatininfull <- plot_lab_comparison(
  data           = kreatinin_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of kreatinin \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "kreatinin (mg/dl)"
)
dibetic_nondiabetic_kreatininfull

```

```{r}

kreatinin_liver_diclo <- kreatinin_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_kreatinin_diclo <- plot_lab_comparison(
  data           = kreatinin_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of kreatinin liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "kreatinin (mg/dl)"
)
p1_kreatinin_diclo
```


```{r}

kreatinin_liver_Ibu <- kreatinin_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_kreatinin_ibu <- plot_lab_comparison(
  data           = kreatinin_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of kreatinin liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "kreatinin (mg/dl)"
)
p2_kreatinin_ibu
```

```{r}

kreatinin_liver_Para <- kreatinin_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_kreatinin_para <- plot_lab_comparison(
  data           = kreatinin_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of kreatinin liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "kreatinin (mg/dl)"
)
p3_kreatinin_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_kreatininfull, 
               p1_kreatinin_diclo, 
               p2_kreatinin_ibu, 
               p3_kreatinin_para),
  names = c("dibetic_nondiabetic_kreatininfull", 
            "p1_kreatinin_diclo", 
            "p2_kreatinin_ibu", 
            "p3_kreatinin_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##===========================
## harnstoff_diabetic
##===========================

```{r}

dibetic_nondiabetic_ureafull <- plot_lab_comparison(
  data           = harnstoff_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of Urea \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Urea (mg/dl)"
)
dibetic_nondiabetic_ureafull
```


```{r}

urea_liver_diclo <- harnstoff_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_urea_diclo <- plot_lab_comparison(
  data           = urea_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of urea liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Urea (mg/dl)"
)
p1_urea_diclo
```


```{r}

urea_liver_Ibu <- harnstoff_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_urea_ibu <- plot_lab_comparison(
  data           = urea_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of urea liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Urea (mg/dl)"
)
p2_urea_ibu
```

```{r}

urea_liver_Para <- harnstoff_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_urea_para <- plot_lab_comparison(
  data           = urea_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of urea liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Urea (mg/dl)"
)
p3_urea_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_ureafull, 
               p1_urea_diclo, 
               p2_urea_ibu, 
               p3_urea_para),
  names = c("dibetic_nondiabetic_ureafull", 
            "p1_urea_diclo", 
            "p2_urea_ibu", 
            "p3_urea_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##================
## crp_diabetic
##================

```{r}

dibetic_nondiabetic_crpfull <- plot_lab_comparison(
  data           = crp_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of CRP \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CRP (mg/l)"
)
dibetic_nondiabetic_crpfull
```


```{r}
crp_liver_diclo <- crp_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_crp_diclo <- plot_lab_comparison(
  data           = crp_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of CRP liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CRP (mg/l)"
)
p1_crp_diclo
```


```{r}
crp_liver_Ibu <- crp_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_crp_ibu <- plot_lab_comparison(
  data           = crp_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of CRP liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CRP (mg/l)"
)
p2_crp_ibu
```


```{r}
crp_liver_Para <- crp_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_crp_para <- plot_lab_comparison(
  data           = crp_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of CRP liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "CRP (mg/l)"
)
p3_crp_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_crpfull, 
               p1_crp_diclo, 
               p2_crp_ibu, 
               p3_crp_para),
  names = c("dibetic_nondiabetic_crpfull", 
            "p1_crp_diclo", 
            "p2_crp_ibu", 
            "p3_crp_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##============================
## natrium_diabetic
##============================

```{r}

dibetic_nondiabetic_sodiumfull <- plot_lab_comparison(
  data           = natrium_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of Sodium \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Sodium (mmol/l)"
)
dibetic_nondiabetic_sodiumfull
```

```{r}
sodium_liver_diclo <- natrium_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_sodium_diclo <- plot_lab_comparison(
  data           = sodium_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of sodium liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Sodium (mmol/l)"
)
p1_sodium_diclo
```


```{r}
sodium_liver_Ibu <- natrium_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_sodium_ibu <- plot_lab_comparison(
  data           = sodium_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of sodium liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Sodium (mmol/l)"
)
p2_sodium_ibu
```

```{r}
sodium_liver_Para <- natrium_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_sodium_para <- plot_lab_comparison(
  data           = sodium_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of sodium liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Sodium (mmol/l)"
)
p3_sodium_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_sodiumfull, 
               p1_sodium_diclo, 
               p2_sodium_ibu, 
               p3_sodium_para),
  names = c("dibetic_nondiabetic_sodiumfull", 
            "p1_sodium_diclo", 
            "p2_sodium_ibu", 
            "p3_sodium_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##====================
## kalium_diabetic potassium
##====================

```{r}

dibetic_nondiabetic_potassiumfull <- plot_lab_comparison(
  data           = kalium_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of potassium \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Potassium (mmol/l)"
)
dibetic_nondiabetic_potassiumfull
```


```{r}
potassium_liver_diclo <- kalium_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_potassium_diclo <- plot_lab_comparison(
  data           = potassium_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of potassium liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Potassium (mmol/l)"
)
p1_potassium_diclo
```

```{r}
potassium_liver_Ibu <- kalium_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_potassium_ibu <- plot_lab_comparison(
  data           = potassium_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of potassium liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Potassium (mmol/l)"
)
p2_potassium_ibu
```


```{r}
potassium_liver_Para <- kalium_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_potassium_para <- plot_lab_comparison(
  data           = potassium_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of potassium liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Potassium (mmol/l)"
)
p3_potassium_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_potassiumfull, 
               p1_potassium_diclo, 
               p2_potassium_ibu, 
               p3_potassium_para),
  names = c("dibetic_nondiabetic_potassiumfull", 
            "p1_potassium_diclo", 
            "p2_potassium_ibu", 
            "p3_potassium_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##========================
## kalzium_diabetic
##========================


```{r}

dibetic_nondiabetic_calciumfull <- plot_lab_comparison(
  data           = kalzium_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of calcium \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Calcium (mmol/l)"
)
dibetic_nondiabetic_calciumfull
```

```{r}
calcium_liver_diclo <- kalzium_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_calcium_diclo <- plot_lab_comparison(
  data           = calcium_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of calcium liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Calcium (mmol/l)"
)
p1_calcium_diclo
```


```{r}
calcium_liver_Ibu <- kalzium_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_calcium_ibu <- plot_lab_comparison(
  data           = calcium_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of calcium liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Calcium (mmol/l)"
)
p2_calcium_ibu
```

```{r}
calcium_liver_Para <- kalzium_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_calcium_para <- plot_lab_comparison(
  data           = calcium_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of calcium liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Calcium (mmol/l)"
)
p3_calcium_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_calciumfull, 
               p1_calcium_diclo, 
               p2_calcium_ibu, 
               p3_calcium_para),
  names = c("dibetic_nondiabetic_calciumfull", 
            "p1_calcium_diclo", 
            "p2_calcium_ibu", 
            "p3_calcium_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##=====================
##  quick_diabetic
##=====================

```{r}

dibetic_nondiabetic_quickfull <- plot_lab_comparison(
  data           = quick_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of quick \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Quick (%)"
)
dibetic_nondiabetic_quickfull
```


```{r}
quick_liver_diclo <- quick_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_quick_diclo <- plot_lab_comparison(
  data           = quick_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of quick liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Quick (%)"
)
p1_quick_diclo
```


```{r}
quick_liver_Ibu <- quick_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_quick_ibu <- plot_lab_comparison(
  data           = quick_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of quick liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Quick (%)"
)
p2_quick_ibu
```


```{r}
quick_liver_Para <- quick_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_quick_para <- plot_lab_comparison(
  data           = quick_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of quick liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "Quick (%)"
)
p3_quick_para
```

```{r}
save_plots(
  plots = list(dibetic_nondiabetic_quickfull, 
               p1_quick_diclo, 
               p2_quick_ibu, 
               p3_quick_para),
  names = c("dibetic_nondiabetic_quickfull", 
            "p1_quick_diclo", 
            "p2_quick_ibu", 
            "p3_quick_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```

##==================
## inr_diabetic
##==================

```{r}

dibetic_nondiabetic_inrfull <- plot_lab_comparison(
  data           = inr_diabetic,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "All groups_Comparison of INR \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "INR (%)"
)
dibetic_nondiabetic_inrfull
```


```{r}
inr_liver_diclo <- inr_diabetic %>% 
  filter(treatment == "Leber_Diclo")

p1_inr_diclo <- plot_lab_comparison(
  data           = inr_liver_diclo,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of INR liver_diclo \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "INR (%)"
)
p1_inr_diclo
```

```{r}
inr_liver_Ibu <- inr_diabetic %>% 
  filter(treatment == "Leber_Ibu")

p2_inr_ibu <- plot_lab_comparison(
  data           = inr_liver_Ibu,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of INR liver_Ibu \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "INR (%)"
)
p2_inr_ibu
```


```{r}
inr_liver_Para <- inr_diabetic %>% 
  filter(treatment == "Leber_Para")

p3_inr_para <- plot_lab_comparison(
  data           = inr_liver_Para,
  group_var      = diabetes,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = list(c("Diabetic", "Non_Diabetic")),
  plot_title     = "Comparison of INR liver_Para \n for Diabetic vs. Non-Diabetic Patients",
  y_label        = "INR (%)"
)
p3_inr_para
```


```{r}
save_plots(
  plots = list(dibetic_nondiabetic_inrfull, 
               p1_inr_diclo, 
               p2_inr_ibu, 
               p3_inr_para),
  names = c("dibetic_nondiabetic_inrfull", 
            "p1_inr_diclo", 
            "p2_inr_ibu", 
            "p3_inr_para"),
  dataset_name = "diabetic",
  subfolder    = "diabetic"
)
```


##==============================================================================
##==============================================================================
##==============================================================================

```{r}
# ══════════════════════════════════════════════════════════════════════════════
# Helper: filter panel and join with diabetic data
# ══════════════════════════════════════════════════════════════════════════════

prepare_panel_data <- function(
    all_data,
    diabetic_data,
    panel_id_value,                          # e.g. "got", "crp", "alt"
    all_data_id_col      = "bf_ar_m_nummer", # join key in all_data
    diabetic_id_col      = "edited_bf_ar_m_nummer2", # join key in diabetic_data
    exclude_pattern      = "_From Start|_From start|DBS", # regex to exclude
    group_col            = "diabetes"
) {

  library(dplyr)

  # ── Validation ---------------------------------------------------------------
  if (!panel_id_value %in% unique(all_data$panel_id)) {
    stop("panel_id '", panel_id_value, "' not found in all_data. ",
         "Available: ", paste(unique(all_data$panel_id), collapse = ", "))
  }

  # ── Step 1: Filter panel and convert labreads to numeric --------------------
  panel_filtered <- all_data %>%
    filter(panel_id == panel_id_value) %>%
    mutate(labreads = as.numeric(labreads))

  n_lost <- sum(is.na(panel_filtered$labreads))
  if (n_lost > 0) {
    message("Warning: ", n_lost, " value(s) in 'labreads' became NA after conversion.")
  }

  # ── Step 2: Join with diabetic data -----------------------------------------
  panel_diabetic <- left_join(
    panel_filtered,
    diabetic_data,
    by           = setNames(diabetic_id_col, all_data_id_col),
    relationship = "many-to-many"
  ) %>%
    drop_na() %>%
    filter(!grepl(exclude_pattern, attribute)) %>%
    group_by(.data[[group_col]])

  message("✔ '", panel_id_value, "' ready — ",
          nrow(panel_diabetic), " rows | ",
          n_distinct(panel_diabetic[[all_data_id_col]]), " patients")

  return(panel_diabetic)
}
```



```{r}
got_diabetic <- prepare_panel_data(
  all_data      = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "got"
)
got_diabetic 
```




































































































