---
title: "Diabetes_plots_gender"
output: html_document
date: "2025-10-02"
---

```{r}
library(here)
library(dplyr)
library(stringr)
library(tidyverse)
```
```{r}
source(here::here("R/clean_data.R"))
source(here::here("R/filter_panel_data.R"))
source(here::here("R/pretty_boxplot.R"))
source(here::here("R/gender_boxplot.R"))
source(here::here("R/export_plot.R"))
source(here::here("R/make_boxplot_with_stats.R"))
source(here::here("R/diabetes_wrapper.R"))

```


##===================
## Raw data from Excel
##===================

```{r}
sheets <- excel_sheets(here::here(
  "RawData/new_raw_data/ubersicht_Laborwerte_laborwerte_fertig_aktuell_new.xlsx"
))

sheets <- sheets[
  sheets %in% c(
    "Fallberichte")]
sheets


all_data <- map_dfr(
  sheets,
  ~ process_sheet(file = here::here("RawData/new_raw_data/ubersicht_Laborwerte_laborwerte_fertig_aktuell_new.xlsx"), .x)
  )
all_data
```


```{r}
diabetic_data <- read_excel(here::here("RawData/Diabetes rawdata.xlsx"), 
                            sheet = 2) %>% 
                            drop_na() %>% 
  janitor::clean_names() %>% 
  dplyr::rename("bf_ar_m_nummer" = "edited_bf_ar_m_nummer2")

diabetic_data
```

```{r}
gender_data <- read_excel(here::here("RawData/gender_info_full.xlsx"),
           sheet = 1, skip = 1)

gender_data1 <- gender_data %>%
    dplyr::select(1:4) %>%
    dplyr::mutate(
    Gender = dplyr::case_when(
    Male == 1 ~ "Male",
    Female == 1 ~ "Female"),
    value = dplyr::case_when(
    Male == 1 ~ 1,
    Female == 1 ~ 0
    )) %>% 
    dplyr::select(1,2,5,6)%>% 
    drop_na() %>% 
    janitor::clean_names() %>% 
  dplyr::rename("bf_ar_m_nummer" = "edited_bf_ar_m_nummer2")
gender_data1
```

##===========================
### gpt 
##===========================

```{r}
gpt_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "gpt"
)
gpt_diabetic
```

```{r}

gpt_diabetic_gender <- left_join(gender_data1,
                                 gpt_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

gpt_diabetic_gender
```
 
```{r}
gpt_diabetic_gender %>% 
  group_by(treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ treatment.x, data = gpt_diabetic_gender)
```

##=================================
# nsaid comparison peak labvlues 
##=================================

```{r}
gpt_diabetic_gender_peak <- gpt_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  #slice(1) %>% 
  ungroup()

gpt_diabetic_gender_peak
```

```{r}
gpt_diabetic_gender_peak %>% 
  group_by(treatment.x) %>% 
  normality(labreads)
```


##===============
## gpt Female
##===============

```{r}
gpt_diabetic_female <- gpt_diabetic_gender %>% 
  dplyr::filter(gender == "Female") 

gpt_diabetic_female
```
```{r}
comparisons_diabetes_gender <- list(
  c("Leber_Diclo", "Leber_Ibu"),
  c("Leber_Diclo", "Leber_Para"),
  c("Leber_Ibu", "Leber_Para")
)
```


```{r}
alt_diabetic_female_case <- make_boxplot_with_stats(
  data = gpt_diabetic_female,
  x = treatment.x,
  y = labreads,
  title = "Comparison of ALT Diabetic females",
  ylab = "ALT (u/l)",
  comparisons = comparisons_diabetes_gender
  
)
alt_diabetic_female_case
```


```{r}
alt_diabetic_female_case <- gender_plot_lab_comparison(
  data           = gpt_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of ALT Diabetic females",
  y_label        = "ALT (U/l)"
)
alt_diabetic_female_case
```

##============
## gpt_Male 
##===========

```{r}
gpt_diabetic_male <- gpt_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

gpt_diabetic_male
```
```{r}
alt_diabetic_male_case <- gender_plot_lab_comparison(
  data           = gpt_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of ALT Diabetic females",
  y_label        = "ALT (U/l)"
)
alt_diabetic_male_case
```

##===============
## Female 
##===============

```{r}
gpt_diabetic_female_peak <- gpt_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

gpt_diabetic_female_peak
```

```{r}
alt_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = gpt_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of ALT peak nsaid \n Diabetic females",
  y_label        = "Peak-ALT (U/l)"
)
alt_diabetic_female_peak_case
```

##=============
## Male peak
##============

```{r}
gpt_diabetic_male_peak <- gpt_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

gpt_diabetic_male_peak
```

```{r}
alt_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = gpt_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of ALT peak nsaid \n Diabetic males",
  y_label        = "Peak-ALT (U/l)"
)
alt_diabetic_male_peak_case
```



##==============
## got 
##==============

```{r}

got_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "got"
)
got_diabetic
```


```{r}

got_diabetic_gender <- left_join(gender_data1,
                                 got_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

got_diabetic_gender
```
 
##==================================
## nsaid comparison peak labvlues 
##==================================

```{r}
got_diabetic_gender_peak <- got_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

got_diabetic_gender_peak
```

##===============
## got Female ##
##===============

```{r}
got_diabetic_female <- got_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

got_diabetic_female
```

```{r}
ast_diabetic_female_case <- gender_plot_lab_comparison(
  data           = got_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AST Diabetic females",
  y_label        = "AST (U/l)"
)
ast_diabetic_female_case
```


##==============
## got Male ##
##==============

```{r}
got_diabetic_male <- got_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

got_diabetic_male
```

```{r}
ast_diabetic_male_case <- gender_plot_lab_comparison(
  data           = got_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AST Diabetic males",
  y_label        = "AST (U/l)"
)
ast_diabetic_male_case
```

##====================
## got Female peak ##
##====================

```{r}
got_diabetic_female_peak <- got_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

got_diabetic_female_peak
```

```{r}
ast_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = got_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AST nsaid Diabetic females",
  y_label        = "AST (U/l)"
)
ast_diabetic_female_peak_case
```


##====================
## got male peak ##
##====================

```{r}
got_diabetic_male_peak <- got_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")
got_diabetic_male_peak
```

```{r}
ast_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = got_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AST nsaid Diabetic males",
  y_label        = "AST (U/l)"
)
ast_diabetic_male_peak_case
```

##===================
## ggt 
##===================
```{r}
ggt_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "ggt"
)
ggt_diabetic
```

```{r}

ggt_diabetic_gender <- left_join(gender_data1,
                                 ggt_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

ggt_diabetic_gender
```

##==================================
## nsaid comparison peak labvlues 
##==================================

```{r}
ggt_diabetic_gender_peak <- ggt_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

ggt_diabetic_gender_peak
```
##===========
## Female 
##===========


```{r}
ggt_diabetic_female <- ggt_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

ggt_diabetic_female
```

```{r}
ggt_diabetic_female_case <- gender_plot_lab_comparison(
  data           = got_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT Diabetic females",
  y_label        = "AST (U/l)"
)
ggt_diabetic_female_case
```

##==============
## Male 
##==============

```{r}
ggt_diabetic_male <- ggt_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

ggt_diabetic_male
```
```{r}
ggt_diabetic_male_case <- gender_plot_lab_comparison(
  data           = got_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT Diabetic males",
  y_label        = "AST (U/l)"
)
ggt_diabetic_male_case
```


##===============
## Female 
##===============


```{r}
ggt_diabetic_female_peak <- ggt_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

ggt_diabetic_female_peak
```
```{r}
ggt_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = got_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT nasid \n Diabetic females",
  y_label        = "AST (U/l)"
)
ggt_diabetic_female_peak_case
```


##==========
## Male 
##==========

```{r}
ggt_diabetic_male_peak <- ggt_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

ggt_diabetic_male_peak
```

```{r}
ggt_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = got_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT nasid \n Diabetic males",
  y_label        = "AST (U/l)"
)
ggt_diabetic_male_peak_case
```

##===================
## ldh 
##===================

```{r}
ldh_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "ldh"
)
ldh_diabetic
```

```{r}

ldh_diabetic_gender <- left_join(gender_data1,
                                 ldh_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

ldh_diabetic_gender
```
##=====================================
# nsaid comparison peak labvlues 
##=====================================

```{r}
ldh_diabetic_gender_peak <- ldh_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  #slice(1) %>% 
  ungroup()

ldh_diabetic_gender_peak
```
##============
## Female ldh
##===========

```{r}
ldh_diabetic_female <- ldh_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

ldh_diabetic_female
```

```{r}
ldh_diabetic_female_case <- gender_plot_lab_comparison(
  data           = ldh_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT nasid \n Diabetic females",
  y_label        = "LDH (U/l)"
)
ldh_diabetic_female_case
```


##===========
## Male ldh
##===========


```{r}
ldh_diabetic_male <- ldh_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

ldh_diabetic_male
```

```{r}
ldh_diabetic_male_case <- gender_plot_lab_comparison(
  data           = ldh_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT nasid \n Diabetic males",
  y_label        = "LDH (U/l)"
)
ldh_diabetic_male_case
```

##================
## Female 
##================

```{r}
ldh_diabetic_female_peak <- ldh_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

ldh_diabetic_female_peak
```

```{r}
ldh_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = ldh_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT nasid \n Diabetic females",
  y_label        = "LDH (U/l)"
)
ldh_diabetic_female_peak_case
```


##===============
## Male ldh_peak
##===============

```{r}
ldh_diabetic_male_peak <- ldh_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

ldh_diabetic_male_peak
```
```{r}
ldh_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = ldh_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of GGT nasid \n Diabetic males",
  y_label        = "LDH (U/l)"
)
ldh_diabetic_male_peak_case
```
##===================
## ck 
##===================


```{r}
ck_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "ck"
)
ck_diabetic
```

```{r}

ck_diabetic_gender <- left_join(gender_data1,
                                 ck_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

ck_diabetic_gender
```

 
# nsaid comparison peak labvlues #
```{r}
ck_diabetic_gender_peak <- ck_diabetic_gender %>% 
    group_by(treatment.x) %>%  
    group_by(bf_ar_m_nummer) %>%   
    filter(labreads == max(labreads, na.rm = TRUE)) %>%  
    #slice(1) %>% 
    ungroup()

ck_diabetic_gender_peak
```

##==========
## Female 
##==========

```{r}
ck_diabetic_female <- ck_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

ck_diabetic_female
```

```{r}
ck_diabetic_female_case <- gender_plot_lab_comparison(
  data           = ck_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of CK Diabetic females",
  y_label        = "CK (U/l)"
)
ck_diabetic_female_case
```

##=========
## Male 
##=========

```{r}
ck_diabetic_male <- ck_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

ck_diabetic_male
```




##===============
## Female ck peak
##===============

```{r}
ck_diabetic_female_peak <- ck_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

ck_diabetic_female_peak
```

```{r}
ck_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = ck_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of CK nsaid\n  Diabetic females",
  y_label        = "CK (U/l)"
)
ck_diabetic_female_peak_case
```

##===========
## Male ##
##===========

```{r}
ck_diabetic_male_peak <- ck_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

ck_diabetic_male_peak
```

##=============
## AP
##=============

```{r}
ap_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "ap"
)
ap_diabetic
```

```{r}

ap_diabetic_gender <- left_join(gender_data1,
                                 ap_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

ap_diabetic_gender
```

##==================================
# nsaid comparison peak labvlues #
##=================================

```{r}
ap_diabetic_gender_peak <- ap_diabetic_gender %>% 
    group_by(treatment.x) %>%  
    group_by(bf_ar_m_nummer) %>%   
    filter(labreads == max(labreads, na.rm = TRUE)) %>%  
    slice(1) %>% 
    ungroup()
ap_diabetic_gender_peak
```

##===========
## Female 
##===========

```{r}
ap_diabetic_female <- ap_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

ap_diabetic_female
```

```{r}
ap_diabetic_female_case <- gender_plot_lab_comparison(
  data           = ap_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AP Diabetic females",
  y_label        = "AP (U/l)"
)
ap_diabetic_female_case
```


##===========
## Male AP
##===========

```{r}
ap_diabetic_male <- ap_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

ap_diabetic_male
```

```{r}
ap_diabetic_male_case <- gender_plot_lab_comparison(
  data           = ap_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AP Diabetic males",
  y_label        = "AP (U/l)"
)
ap_diabetic_male_case
```

##==============
## Female AP peak
##===============

```{r}
ap_diabetic_female_peak <- ap_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

ap_diabetic_female_peak
```

```{r}
ap_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = ap_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AP nsaid Diabetic females",
  y_label        = "AP (U/l)"
)
ap_diabetic_female_peak_case
```

##=============
## Male AP peak
##=============

```{r}
ap_diabetic_male_peak <- ap_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

ap_diabetic_male_peak
```

```{r}
ap_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = ap_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of AP Diabetic males",
  y_label        = "AP (U/l)"
)
ap_diabetic_male_peak_case
```

##============
## ptt 
##===========


```{r}
ptt_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "ptt"
)
ptt_diabetic
```

```{r}

ptt_diabetic_gender <- left_join(gender_data1,
                                 ptt_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

ptt_diabetic_gender
```

##==================================
# nsaid comparison peak labvlues 
##==================================

```{r}
ptt_diabetic_gender_peak <- ptt_diabetic_gender %>% 
   group_by(treatment.x) %>%  
   group_by(bf_ar_m_nummer) %>%   
   filter(labreads == max(labreads, na.rm = TRUE)) %>%  
   slice(1) %>% 
   ungroup()

ptt_diabetic_gender_peak
```

##============
## Female ptt
##=============

```{r}
ptt_diabetic_female <- ptt_diabetic_gender %>% 
  dplyr::filter(gender == "Female")
ptt_diabetic_female
```

```{r}
ptt_diabetic_female_case <- gender_plot_lab_comparison(
  data           = ptt_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of PTT Diabetic females",
  y_label        = "ptt (Sec.)"
)
ptt_diabetic_female_case
```

##===============
## Male ptt
##===============

```{r}
ptt_diabetic_male <- ptt_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

ptt_diabetic_male
```

```{r}
ptt_diabetic_male_case <- gender_plot_lab_comparison(
  data           = ptt_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of PTT Diabetic males",
  y_label        = "ptt (Sec.)"
)
ptt_diabetic_male_case
```

##================
## Female ptt peak
##================

```{r}
ptt_diabetic_female_peak <- ptt_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

ptt_diabetic_female_peak
```

```{r}
ptt_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = ptt_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of PTT nsaid Diabetic females",
  y_label        = "ptt (Sec.)"
)
ptt_diabetic_female_peak_case
```

##==============
## Male ptt peak
##==============

```{r}
ptt_diabetic_male_peak <- ptt_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

ptt_diabetic_male_peak
```

```{r}
ptt_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = ptt_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of PTT nsaid Diabetic males",
  y_label        = "ptt (Sec.)"
)
ptt_diabetic_male_peak_case
```

##===============
### leukozyten 
##===============

```{r}
leukozyten_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "leukozyten"
)
leukozyten_diabetic
```

```{r}

leukozyten_diabetic_gender <- left_join(gender_data1,
                                 leukozyten_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

leukozyten_diabetic_gender
```

##=================================
## nsaid comparison peak labvlues 
##=================================

```{r}
leukozyten_diabetic_gender_peak <- leukozyten_diabetic_gender %>% 
   group_by(treatment.x) %>%  
   group_by(bf_ar_m_nummer) %>%   
   filter(labreads == max(labreads, na.rm = TRUE)) %>%  
   slice(1) %>% 
   ungroup()

leukozyten_diabetic_gender_peak
```

##============
## Female leukozyten
##============

```{r}
leukozyten_diabetic_female <- leukozyten_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

leukozyten_diabetic_female
```

```{r}
leukozyten_diabetic_female_case <- gender_plot_lab_comparison(
  data           = leukozyten_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of leukocytes Diabetic females",
  y_label        = "Leucocytes (cells/ul)"
)
leukozyten_diabetic_female_case
```

##===========
## Male ##
##============

```{r}
leukozyten_diabetic_male <- leukozyten_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

leukozyten_diabetic_male
```
```{r}
leukozyten_diabetic_male_case <- gender_plot_lab_comparison(
  data           = leukozyten_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of leukocytes Diabetic males",
  y_label        = "Leucocytes (cells/ul)"
)
leukozyten_diabetic_male_case
```


##========================
## Female leukocytes_peak
##========================

```{r}
leukozyten_diabetic_female_peak <- leukozyten_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

leukozyten_diabetic_female_peak
```

```{r}
leukozyten_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = leukozyten_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of leukocytes nsaid \nDiabetic females",
  y_label        = "Leucocytes (cells/ul)"
)
leukozyten_diabetic_female_peak_case
```


##=====================
## Male leucocytes_peak
##=====================

```{r}
leukozyten_diabetic_male_peak <- leukozyten_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

leukozyten_diabetic_male_peak
```

```{r}
leukozyten_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = leukozyten_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of leukocytes nsaid \nDiabetic males",
  y_label        = "Leucocytes (cells/ul)"
)
leukozyten_diabetic_male_peak_case
```

##=================
### erythrozyten 
##=================

```{r}
erythrocytes_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "erythrozyten"
)
erythrocytes_diabetic
```

```{r}

erythrocytes_diabetic_gender <- left_join(gender_data1,
                                 erythrocytes_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

erythrocytes_diabetic_gender
```

##==================================
## nsaid comparison peak labvlues 
##==================================

```{r}

erythrozyten_diabetic_gender_peak <- erythrocytes_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

erythrozyten_diabetic_gender_peak
```

##============
## Female erythrocytes
##============

```{r}
erythrozyten_diabetic_female <- erythrocytes_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

erythrozyten_diabetic_female
```

```{r}
erythrozyten_diabetic_female_case <- gender_plot_lab_comparison(
  data           = erythrozyten_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of erythrocytes Diabetic females",
  y_label        = "Erythrocytes (cells/ul)"
)
erythrozyten_diabetic_female_case
```


## Male ##

```{r}
erythrozyten_diabetic_male <- erythrocytes_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

erythrozyten_diabetic_male
```

```{r}
erythrozyten_diabetic_male_case <- gender_plot_lab_comparison(
  data           = erythrozyten_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of erythrocytes Diabetic males",
  y_label        = "Erythrocytes (cells/ul)"
)
erythrozyten_diabetic_male_case
```


 
##=========================
## Female erythocytes peak
##=========================

```{r}
erythrozyten_diabetic_female_peak <- erythrozyten_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

erythrozyten_diabetic_female_peak
```

```{r}
erythrozyten_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = erythrozyten_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of erythrocytes nsaid \n Diabetic females",
  y_label        = "Erythrocytes (cells/ul)"
)
erythrozyten_diabetic_female_peak_case
```




## Male ##

```{r}
erythrozyten_diabetic_male_peak <- erythrozyten_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

erythrozyten_diabetic_male_peak
```

```{r}
erythrozyten_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = erythrozyten_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of erythrocytes nsaid \n Diabetic males",
  y_label        = "Erythrocytes (cells/ul)"
)
erythrozyten_diabetic_male_peak_case
```




##====================
## thrombozyten 
##====================
```{r}
thrombocytes_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "thrombozyten"
)
thrombocytes_diabetic
```

```{r}

thrombocytes_diabetic_gender <- left_join(gender_data1,
                                 thrombocytes_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

thrombocytes_diabetic_gender
```

##======================================
# nsaid comparison peak labvlues #
##======================================

```{r}
thrombozyten_diabetic_gender_peak <- thrombocytes_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

thrombozyten_diabetic_gender_peak
```
##================
## Female thrombocytes
##===============

```{r}
thrombozyten_diabetic_female <- thrombocytes_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

thrombozyten_diabetic_female
```


```{r}
thrombozyten_diabetic_female_case <- gender_plot_lab_comparison(
  data           = thrombozyten_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of thrombocytes Diabetic females",
  y_label        = "Thrombocytes (cells/ul)"
)
thrombozyten_diabetic_female_case
```

##==================
## Male Thrombocytes
##==================

```{r}
thrombozyten_diabetic_male <- thrombocytes_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

thrombozyten_diabetic_male
```

```{r}
thrombozyten_diabetic_male_case <- gender_plot_lab_comparison(
  data           = thrombozyten_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of thrombocytes \n Diabetic males",
  y_label        = "Thrombocytes (cells/ul)"
)
thrombozyten_diabetic_male_case
```



##=========================
## Female thrombocytes peak
##=========================

```{r}
thrombozyten_diabetic_female_peak <- thrombozyten_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

thrombozyten_diabetic_female_peak
```

```{r}
thrombozyten_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = thrombozyten_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of thrombocytes nsaid \nDiabetic females",
  y_label        = "Thrombocytes (cells/ul)"
)
thrombozyten_diabetic_female_peak_case
```

##=======================
## Male thrombocytes peak
##=======================

```{r}
thrombozyten_diabetic_male_peak <- thrombozyten_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

thrombozyten_diabetic_male_peak
```

```{r}
thrombozyten_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = thrombozyten_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of thrombocytes nsaid \nDiabetic males",
  y_label        = "Thrombocytes (cells/ul)"
)
thrombozyten_diabetic_male_peak_case
```

##================
## hb 
##===============
```{r}
hb_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "hb"
)
hb_diabetic
```

```{r}

hb_diabetic_gender <- left_join(gender_data1,
                                 hb_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

hb_diabetic_gender
```

##=================================
# nsaid comparison peak labvlues #
##=================================

```{r}
hb_diabetic_gender_peak <- hb_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

hb_diabetic_gender_peak
```

##===========
## Female HB
##===========

```{r}
hb_diabetic_female <- hb_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

hb_diabetic_female
```
```{r}
hb_diabetic_female_case <- gender_plot_lab_comparison(
  data           = hb_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of Hb Diabetic females",
  y_label        = "hb (g/dl)"
)
hb_diabetic_female_case
```


##==========
## Male hb
##==========

```{r}
hb_diabetic_male <- hb_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

hb_diabetic_male
```

```{r}
hb_diabetic_male_case <- gender_plot_lab_comparison(
  data           = hb_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of Hb Diabetic males",
  y_label        = "hb (g/dl)"
)
hb_diabetic_male_case
```


##=================
## Female hb peak
##================

```{r}
hb_diabetic_female_peak <- hb_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

hb_diabetic_female_peak
```

```{r}
hb_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = hb_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of Hb nsaid \nDiabetic females",
  y_label        = "hb (g/dl)"
)
hb_diabetic_female_peak_case
```

##===============
## Male HB peak
##===============

```{r}
hb_diabetic_male_peak <- hb_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

hb_diabetic_male_peak
```

```{r}
hb_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = hb_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of Hb nsaid \nDiabetic males",
  y_label        = "hb (g/dl)"
)
hb_diabetic_male_peak_case
```

##==========================
## gesamteiweiß totalprotein
##===========================
```{r}
gesamteiweiss_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "gesamteiweiss"
)
gesamteiweiss_diabetic
```

```{r}

gesamteiweiss_diabetic_gender <- left_join(gender_data1,
                                gesamteiweiss_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

gesamteiweiss_diabetic_gender
```

 
# nsaid comparison peak labvlues #
```{r}
gesamteiweiss_diabetic_gender_peak <- gesamteiweiss_diabetic_gender %>% 
  group_by(treatment.x) %>%  
  group_by(bf_ar_m_nummer) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

gesamteiweiss_diabetic_gender_peak
```

##===============
## Female totalprotein
##=====================

```{r}
gesamteiweiß_diabetic_female <- gesamteiweiss_diabetic_gender %>% 
  dplyr::filter(gender == "Female")

gesamteiweiß_diabetic_female
```

```{r}
gesamteiweiß_diabetic_female_case <- gender_plot_lab_comparison(
  data           = gesamteiweiß_diabetic_female,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of totalprotein Diabetic females",
  y_label        = "Total Protein (g/dl)"
)
gesamteiweiß_diabetic_female_case
```

##===================
## Male totalprotein
##===================

```{r}
gesamteiweiß_diabetic_male <- gesamteiweiss_diabetic_gender %>% 
  dplyr::filter(gender == "Male")

gesamteiweiß_diabetic_male
```

```{r}
gesamteiweiß_diabetic_male_case <- gender_plot_lab_comparison(
  data           = gesamteiweiß_diabetic_male,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of totalprotein Diabetic males",
  y_label        = "Total Protein (g/dl)"
)
gesamteiweiß_diabetic_male_case
```

##=========================
## Female totalprotein peak
##=========================

```{r}
gesamteiweiß_diabetic_female_peak <- gesamteiweiss_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Female")

gesamteiweiß_diabetic_female_peak
```


```{r}
gesamteiweiß_diabetic_female_peak_case <- gender_plot_lab_comparison(
  data           = gesamteiweiß_diabetic_female_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of totalprotein nsaid \n Diabetic females",
  y_label        = "Total Protein (g/dl)"
)
gesamteiweiß_diabetic_female_peak_case
```
##==================
## Male totalprotein
##===================

```{r}
gesamteiweiß_diabetic_male_peak <- gesamteiweiss_diabetic_gender_peak %>% 
  dplyr::filter(gender == "Male")

gesamteiweiß_diabetic_male_peak
```


```{r}
gesamteiweiß_diabetic_male_peak_case <- gender_plot_lab_comparison(
  data           = gesamteiweiß_diabetic_male_peak,
  group_var      = treatment.x,
  y_var          = labreads,
  patient_id_var = bf_ar_m_nummer,
  comparisons    = comparisons_diabetes_gender,
  plot_title     = "Comparison of totalprotein nsaid \n Diabetic males",
  y_label        = "Total Protein (g/dl)"
)
gesamteiweiß_diabetic_male_peak_case
```

##======================
## total_bilirubin 
##=======================

```{r}
bilirubin_diabetic <- prepare_panel_data(
  all_data = all_data,
  diabetic_data = diabetic_data,
  panel_id_value = "bilirubin"
)
bilirubin_diabetic
```

```{r}

bilirubin_diabetic_gender <- left_join(gender_data1,
                                bilirubin_diabetic,
                                 by = "bf_ar_m_nummer") %>% 
       filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
       filter(diabetes == "Diabetic") %>%
       drop_na() %>% 
      filter(str_starts(treatment.x, "Leber_")) %>% 
      mutate(treatment.x = as.factor(treatment.x),
         gender = as.factor(gender))

bilirubin_diabetic_gender
```
```{r}

total_bilirubin_diabetic_gender <- left_join(gender_data1,total_bilirubin_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% filter(Diabetes == "Diabetic") %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Treatment.x = as.factor(Treatment.x),
         Gender = as.factor(Gender))

total_bilirubin_diabetic_gender
```
 
```{r}
total_bilirubin_diabetic_gender %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = total_bilirubin_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
total_bilirubin_diabetic_gender_peak <- total_bilirubin_diabetic_gender %>% 
  group_by(Treatment.x) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

total_bilirubin_diabetic_gender_peak
```

```{r}
total_bilirubin_diabetic_gender_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = total_bilirubin_diabetic_gender_peak)
```




## Female ##

```{r}
total_bilirubin_diabetic_female <- total_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

total_bilirubin_diabetic_female
```

```{r}
total_bilirubin_diabetic_female %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = total_bilirubin_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- total_bilirubin_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = total_bilirubin_diabetic_female,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_total_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(total_bilirubin_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison female/liver_total_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
total_bilirubin_diabetic_male <- total_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

total_bilirubin_diabetic_male
```

```{r}
total_bilirubin_diabetic_male %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = total_bilirubin_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- total_bilirubin_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = total_bilirubin_diabetic_male,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_total_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(total_bilirubin_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison male/liver_total_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```
 

## Female ##

```{r}
total_bilirubin_diabetic_female_peak <- total_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

total_bilirubin_diabetic_female_peak
```

```{r}
total_bilirubin_diabetic_female_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = total_bilirubin_diabetic_female_peak)
```

```{r}
liver_total_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_female <- ggbetweenstats(
  data = total_bilirubin_diabetic_female_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "Peak-total_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison female", showWarnings = FALSE)
svg("plots_peak/nsaid comparison female/liver_total_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
total_bilirubin_diabetic_male_peak <- total_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

total_bilirubin_diabetic_male_peak
```

```{r}
total_bilirubin_diabetic_male_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = total_bilirubin_diabetic_male_peak)
```

```{r}
liver_total_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_male <- ggbetweenstats(
  data = total_bilirubin_diabetic_male_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "Peak-total_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison male", showWarnings = FALSE)
svg("plots_peak/nsaid comparison male/liver_total_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```



### direct_bilirubin ##########################################################################

```{r}

direct_bilirubin_diabetic_gender <- left_join(gender_data1,direct_bilirubin_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% filter(Diabetes == "Diabetic") %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Treatment.x = as.factor(Treatment.x),
         Gender = as.factor(Gender))

direct_bilirubin_diabetic_gender
```
 
```{r}
direct_bilirubin_diabetic_gender %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = direct_bilirubin_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
direct_bilirubin_diabetic_gender_peak <- direct_bilirubin_diabetic_gender %>% 
  group_by(Treatment.x) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

direct_bilirubin_diabetic_gender_peak
```

```{r}
direct_bilirubin_diabetic_gender_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = direct_bilirubin_diabetic_gender_peak)
```




## Female ##

```{r}
direct_bilirubin_diabetic_female <- direct_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

direct_bilirubin_diabetic_female
```

```{r}
direct_bilirubin_diabetic_female %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = direct_bilirubin_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- direct_bilirubin_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = direct_bilirubin_diabetic_female,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_direct_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(direct_bilirubin_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison female/liver_direct_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
direct_bilirubin_diabetic_male <- direct_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

direct_bilirubin_diabetic_male
```

```{r}
direct_bilirubin_diabetic_male %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = direct_bilirubin_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- direct_bilirubin_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = direct_bilirubin_diabetic_male,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_direct_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(direct_bilirubin_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison male/liver_direct_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_all_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```
 

## Female ##

```{r}
direct_bilirubin_diabetic_female_peak <- direct_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

direct_bilirubin_diabetic_female_peak
```

```{r}
direct_bilirubin_diabetic_female_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = direct_bilirubin_diabetic_female_peak)
```

```{r}
liver_direct_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_female <- ggbetweenstats(
  data = direct_bilirubin_diabetic_female_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "Peak-direct_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison female", showWarnings = FALSE)
svg("plots_peak/nsaid comparison female/liver_direct_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
direct_bilirubin_diabetic_male_peak <- direct_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

direct_bilirubin_diabetic_male_peak
```

```{r}
direct_bilirubin_diabetic_male_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = direct_bilirubin_diabetic_male_peak)
```

```{r}
liver_direct_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_male <- ggbetweenstats(
  data = direct_bilirubin_diabetic_male_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "Peak-direct_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison male", showWarnings = FALSE)
svg("plots_peak/nsaid comparison male/liver_direct_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_peak_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```



### kreatinin ##########################################################################

```{r}

kreatinin_diabetic_gender <- left_join(gender_data1,kreatinin_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% filter(Diabetes == "Diabetic") %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Treatment.x = as.factor(Treatment.x),
         Gender = as.factor(Gender))

kreatinin_diabetic_gender
```
 
```{r}
kreatinin_diabetic_gender %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = kreatinin_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
kreatinin_diabetic_gender_peak <- kreatinin_diabetic_gender %>% 
  group_by(Treatment.x) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

kreatinin_diabetic_gender_peak
```

```{r}
kreatinin_diabetic_gender_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = kreatinin_diabetic_gender_peak)
```




## Female ##

```{r}
kreatinin_diabetic_female <- kreatinin_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

kreatinin_diabetic_female
```

```{r}
kreatinin_diabetic_female %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = kreatinin_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kreatinin_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kreatinin_diabetic_female,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kreatinin_all_labvalues_comparison_nsaid_in_diabetic_group_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(kreatinin_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison female/liver_kreatinin_all_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_kreatinin_all_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
kreatinin_diabetic_male <- kreatinin_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

kreatinin_diabetic_male
```

```{r}
kreatinin_diabetic_male %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = kreatinin_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kreatinin_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kreatinin_diabetic_male,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kreatinin_all_labvalues_comparison_nsaid_in_diabetic_group_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(kreatinin_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison male/liver_kreatinin_all_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_kreatinin_all_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```
 

## Female ##

```{r}
kreatinin_diabetic_female_peak <- kreatinin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

kreatinin_diabetic_female_peak
```

```{r}
kreatinin_diabetic_female_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Treatment.x, data = kreatinin_diabetic_female_peak)
```

```{r}
liver_kreatinin_peak_labvalues_comparison_nsaid_in_diabetic_group_female <- ggbetweenstats(
  data = kreatinin_diabetic_female_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "Peak-kreatinin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison female", showWarnings = FALSE)
svg("plots_peak/nsaid comparison female/liver_kreatinin_peak_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_kreatinin_peak_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
kreatinin_diabetic_male_peak <- kreatinin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

kreatinin_diabetic_male_peak
```

```{r}
kreatinin_diabetic_male_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = kreatinin_diabetic_male_peak)
```

```{r}
liver_kreatinin_peak_labvalues_comparison_nsaid_in_diabetic_group_male <- ggbetweenstats(
  data = kreatinin_diabetic_male_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "Peak-kreatinin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison male", showWarnings = FALSE)
svg("plots_peak/nsaid comparison male/liver_kreatinin_peak_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_kreatinin_peak_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```



### harnstoff ##########################################################################

```{r}

harnstoff_diabetic_gender <- left_join(gender_data1,harnstoff_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% filter(Diabetes == "Diabetic") %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Treatment.x = as.factor(Treatment.x),
         Gender = as.factor(Gender))

harnstoff_diabetic_gender
```
 
```{r}
harnstoff_diabetic_gender %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = harnstoff_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
harnstoff_diabetic_gender_peak <- harnstoff_diabetic_gender %>% 
  group_by(Treatment.x) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

harnstoff_diabetic_gender_peak
```

```{r}
harnstoff_diabetic_gender_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = harnstoff_diabetic_gender_peak)
```




## Female ##

```{r}
harnstoff_diabetic_female <- harnstoff_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

harnstoff_diabetic_female
```

```{r}
harnstoff_diabetic_female %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = harnstoff_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- harnstoff_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = harnstoff_diabetic_female,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_harnstoff_all_labvalues_comparison_nsaid_in_diabetic_group_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(harnstoff_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison female/liver_harnstoff_all_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_harnstoff_all_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
harnstoff_diabetic_male <- harnstoff_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

harnstoff_diabetic_male
```

```{r}
harnstoff_diabetic_male %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = harnstoff_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- harnstoff_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Treatment.x) %>%  # nur einzigartige Patienten
  count(Treatment.x, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = harnstoff_diabetic_male,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_harnstoff_all_labvalues_comparison_nsaid_in_diabetic_group_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Treatment.x, 
        y = max(harnstoff_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison male/liver_harnstoff_all_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_harnstoff_all_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```
 

## Female ##

```{r}
harnstoff_diabetic_female_peak <- harnstoff_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

harnstoff_diabetic_female_peak
```

```{r}
harnstoff_diabetic_female_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = harnstoff_diabetic_female_peak)
```

```{r}
liver_harnstoff_peak_labvalues_comparison_nsaid_in_diabetic_group_female <- ggbetweenstats(
  data = harnstoff_diabetic_female_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for female",
  xlab = "Patient group",
  ylab = "Peak-harnstoff (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison female", showWarnings = FALSE)
svg("plots_peak/nsaid comparison female/liver_harnstoff_peak_labvalues_comparison_nsaid_in_diabetic_group_female.svg", height = 8, width = 6.5)
print(liver_harnstoff_peak_labvalues_comparison_nsaid_in_diabetic_group_female)
dev.off()
```


## Male ##

```{r}
harnstoff_diabetic_male_peak <- harnstoff_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

harnstoff_diabetic_male_peak
```

```{r}
harnstoff_diabetic_male_peak %>% 
  group_by(Treatment.x) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Treatment.x, data = harnstoff_diabetic_male_peak)
```

```{r}
liver_harnstoff_peak_labvalues_comparison_nsaid_in_diabetic_group_male <- ggbetweenstats(
  data = harnstoff_diabetic_male_peak,
  x = "Treatment.x",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group for male",
  xlab = "Patient group",
  ylab = "Peak-harnstoff (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison male", showWarnings = FALSE)
svg("plots_peak/nsaid comparison male/liver_harnstoff_peak_labvalues_comparison_nsaid_in_diabetic_group_male.svg", height = 8, width = 6.5)
print(liver_harnstoff_peak_labvalues_comparison_nsaid_in_diabetic_group_male)
dev.off()
```



#############################################################################

```{r}
ap_diabetic_male_peak_case <- make_condition_plot(
  
  all_data = all_data,
  diabetic_data = diabetic_data,
  gender_data = gender_data1,
  
  panel_id_value = "hb",
  
  diabetes_status = "Diabetic",
  
  gender_filter = "Female",
  
  comparisons = comparisons_diabetes_gender,
  
  plot_title = "Comparison of PTT Diabetic males",
  
  y_label = "PTT (U/L)"
)

ap_diabetic_male_peak_case
```


















