---
title: "Diabetes"
output: html_notebook
---

```{r}
library(here)
library(readxl)
library(tidyr)
library(dplyr)
library(ggstatsplot)
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
library(ggprism)
library(ggpubr)
```

```{r}
source(here::here("R/boxplot_stat_summary.R"))
```


```{r}
diabetic_data <- read_excel(here::here("RawData/Diabetes rawdata.xlsx"), 
                            sheet = 2) %>% 
                            drop_na() %>% 
  janitor::clean_names()

diabetic_data
```

```{r}
gpt_full <- all_data %>% 
  filter(panel_id == "gpt")
gpt_full
```


```{r}
gpt_diabetic <- left_join(gpt_full, 
                          diabetic_data, 
                          by = c ("bf_ar_m_nummer"  = "edited_bf_ar_m_nummer2" ),
                          relationship = "many-to-many") %>% 
            mutate(labreads = as.numeric(labreads)) %>% 
  drop_na() %>% 
#  filter(Diabetes == "Diabetic") %>% 
#  filter(!attribute == "GPT Day_Unknown") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  group_by(diabetes) 
#%>% 
  #summarise(mean_labread = mean(labreads),
            #(sd_labread = sd(labreads)))
gpt_diabetic 
```


### Based on Patient number ###


```{r}
diabetic_patient_number <- gpt_diabetic %>% 
  filter(diabetes == "Diabetic") %>% 
  filter(treatment == "Leber_Diclo") %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  group_by(bf_ar_m_nummer) %>% 
  summarise( mean_labread = mean(labreads, na.rm = TRUE)) %>% 
  ggplot(aes(x = bf_ar_m_nummer, y = mean_labread, fill= bf_ar_m_nummer))+
  geom_col()+
  scale_y_continuous(expand = expansion(mult = c(0, 0)))+
  theme_classic()+
  labs(title = "Liver_Diclo_Diabetic cases labvalues",
       x = "Patients",
       y = "ALT (u/l)"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12, face = "bold"),
    axis.text.y = element_text(angle = 0, hjust = 1, size = 12,face = "bold"),
    axis.title = element_text(size = 15, face = "bold"),
    plot.title = element_text(size =  18, face = "bold", hjust = 0.5),
    legend.position = "none",
    axis.line = element_line(linewidth = 1)
   
  )

print(diabetic_patient_number)
ggsave(
  filename = here::here("output/figure/diabetes/diabetic_patient_number.png"),
  plot = diabetic_patient_number,
  width = 4,
  height = 2,
  dpi = 300
)

ggsave(
  filename = here::here("output/figure/diabetes/diabetic_patient_number.svg"),
  plot = diabetic_patient_number,
  width = 4,
  height = 2
)

```

##================================
### Based on Patient number ###
##================================

```{r}
gpt_diabetic1 <- 
  left_join(gpt_full, 
            diabetic_data, 
            by = c ("bf_ar_m_nummer"  = "edited_bf_ar_m_nummer2" ),
                          relationship = "many-to-many") %>% 
  drop_na() %>% 
  filter(diabetes == "Diabetic") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  group_by(bf_ar_m_nummer) %>% 
  summarise(mean_labread = mean(labreads))
  
liver_gpt_full_diabetic_cases_labvalues <-  ggplot(
  data = gpt_diabetic1,
  aes(x = bf_ar_m_nummer, y = mean_labread)) +
  geom_col()+
  scale_y_continuous(expand = expansion(mult = c(0, 0)))+
  labs(title = "All groups_Diabetic cases mean ALT",
      x = "Patients",
      y = "ALT u/l")+
  theme_classic()+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12, face = "bold"),
    axis.text.y = element_text(angle = 0, hjust = 1, size = 12,face = "bold"),
    axis.title = element_text(size = 15, face = "bold"),
    plot.title = element_text(size =  18, face = "bold", hjust = 0.5),
    legend.position = "none",
    axis.line = element_line(linewidth = 1)
   
  )
liver_gpt_full_diabetic_cases_labvalues
dir.create(here::here("output/figure/diabetes/plots_all_labvalues"), 
           showWarnings = FALSE)




ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/all_gpt_diabetic cases labvalues.png"),
  plot = liver_gpt_full_diabetic_cases_labvalues,
  width = 6,
  height = 4,
  dpi = 300
)

ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/all_gpt_diabetic cases labvalues.svg"),
  plot = liver_gpt_full_diabetic_cases_labvalues,
  width = 6,
  height = 4
)
print(liver_gpt_full_diabetic_cases_labvalues)
dev.off()
```



```{r}
gpt_diabetic2 <- gpt_diabetic %>% 
  filter(diabetes == "Diabetic") %>% 
  #filter(!grepl("_", attribute))

#gpt_diabetic2_counts <- gpt_diabetic2 %>% 
  group_by(days) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
gpt_diabetic2
```

```{r}
library(glue)
gptday = as.factor(glue("ALT Day {1:28}"))
gptday
```

```{r}
 # c( "GPT Day1", "GPT Day2", "GPT Day3","GPT Day4","GPT Day5", "GPT Day6","GPT Day7","GPT Day8","GPT Day9","GPT Day10", "GPT Day11","GPT Day12","GPT Day13","GPT Day14","GPT Day15","GPT Day16","GPT Day17","GPT Day18","GPT Day19","GPT Day20","GPT Day21","GPT Day22","GPT Day23","GPT Day24","GPT Day25","GPT Day26","GPT Day27","GPT Day28","GPT Day29","GPT Day30","GPT Day31","GPT Day32","GPT Day33","GPT Day34","GPT Day35","GPT Day36","GPT Day37","GPT Day38","GPT Day39","GPT Day40","GPT Day41","GPT Day42","GPT Day43","GPT Day44","GPT Day45","GPT Day46","GPT Day47","GPT Day48","GPT Day49","GPT Day50","GPT Day51","GPT Day52","GPT Day53","GPT Day54","GPT Day55","GPT Day56","GPT Day57","GPT Day58","GPT Day59","GPT Day60","GPT Day61","GPT Day62","GPT Day63","GPT Day64","GPT Day65","GPT Day66","GPT Day67","GPT Day68","GPT Day69","GPT Day70","GPT Day71","GPT Day72","GPT Day73","GPT Day74","GPT Day75","GPT Day76","GPT Day77","GPT Day78","GPT Day79","GPT Day80","GPT Day81","GPT Day82","GPT Day83","GPT Day84","GPT Day85","GPT Day86","GPT Day87","GPT Day88","GPT Day89","GPT Day90","GPT Day91","GPT Day92","GPT Day93","GPT Day94","GPT Day95","GPT Day96","GPT Day97","GPT Day98","GPT Day99","GPT Day100"))
```



```{r}
library(tidyverse)
library(glue)

# Prepare data
gpt_diabetic2 <- gpt_diabetic %>% 
  filter(diabetes == "Diabetic") %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  group_by(days) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

# Convert days to ordered factor with labels
gpt_diabetic2$days <- factor(
  gpt_diabetic2$days,
  levels = 1:28,
  labels = glue("ALT Day {1:28}")
)

# Plot
liver_gpt_full_diabetic_cases_labvalues_time <- gpt_diabetic2 %>%
  ggplot(aes(x = days, y = mean_labread)) +
  geom_col() +
    geom_text(
    aes(label = paste0("N = ", n)),
    vjust = -1.0,
    size = 5,
    color = "black"
  ) +
  
  labs(
    title = "All groups Diabetic cases mean ALT",
    x = "Day of measurement",
    y = "ALT (U/L)"
  ) +
  
  theme_classic() +
  
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 12,
      face = "bold"
    ),
    
    axis.text.y = element_text(
      size = 12,
      face = "bold"
    ),
    
    axis.title = element_text(
      size = 15,
      face = "bold"
    ),
    
    plot.title = element_text(
      size = 18,
      face = "bold",
      hjust = 0.5
    ),
    
    axis.line = element_line(linewidth = 1),
    
    legend.position = "none"
  )

# Show plot
liver_gpt_full_diabetic_cases_labvalues_time
ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/liver_gpt_full_diabetic_cases_labvalues_time.png"),
  plot = liver_gpt_full_diabetic_cases_labvalues_time,
  width = 6,
  height = 4,
  dpi = 300
)

ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/liver_gpt_full_diabetic_cases_labvalues_time.svg"),
  plot = liver_gpt_full_diabetic_cases_labvalues_time,
  width = 10,
  height = 6
)
print(liver_gpt_full_diabetic_cases_labvalues_time)
dev.off()
```



```{r}
gpt_nondiabetic <- 
  left_join(gpt_full, 
            diabetic_data, 
            by = c ("bf_ar_m_nummer"  = "edited_bf_ar_m_nummer2" ),
                          relationship = "many-to-many") %>% 
            mutate(labreads = as.numeric(labreads)) %>% 
  drop_na() %>% 
  filter(diabetes == "Non_Diabetic") %>% 
#  filter(!attribute == "GPT Day_Unknown") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  group_by(diabetes) 
#%>% 
  #summarise(mean_labread_non = mean(labreads),
            #sd_labread_non = sd(labreads))
gpt_nondiabetic
```

```{r}
gpt_nondiabetic %>% 
  filter(treatment == "Leber_Diclo") %>% 
  group_by(bf_ar_m_nummer) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = bf_ar_m_nummer, y = mean_labread))+
  geom_col()+
  labs(title = "Liver_Diclo_Nondiabetic labvalues", hjust = 0.5,
       x = "Patient",
       y = "ALT (u/l)"
       )+
  theme_classic()+
    theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 12,
      face = "bold"
    ),
    
    axis.text.y = element_text(
      size = 12,
      face = "bold"
    ),
    
    axis.title = element_text(
      size = 15,
      face = "bold"
    ),
    
    plot.title = element_text(
      size = 18,
      face = "bold",
      hjust = 0.5
    ),
    
    axis.line = element_line(linewidth = 1),
    
    legend.position = "none"
  )

```


```{r}
gpt_nondiabetic %>% 
  filter(treatment == "Leber_Ibu") %>% 
  group_by(bf_ar_m_nummer) %>% 
  mutate(labreads = as.numeric(labreads)) %>%
  summarise(mean_labread = mean(labreads)) %>% 
  ggplot(aes(x = bf_ar_m_nummer, y = mean_labread))+
  geom_col()+
  scale_y_continuous(expand = expansion(mult = c(0,0)))+
  theme_classic()+
  labs(title = "Leber_Ibu_Non_Diabetic",
       x = NULL)+
  theme_classic()+
    theme(
    axis.text.x = element_text(
      angle = 90,
      hjust = 1,
      size = 12,
      face = "bold"
    ),
    
    axis.text.y = element_text(
      size = 12,
      face = "bold"
    ),
    
    axis.title = element_text(
      size = 15,
      face = "bold"
    ),
    
    plot.title = element_text(
      size = 18,
      face = "bold",
      hjust = 0.5
    ),
    
    axis.line = element_line(linewidth = 1),
    
    legend.position = "none"
  )
```

```{r}
gpt_diabetic <- gpt_diabetic %>% 
  mutate(labreads = as.numeric(labreads))
gpt_diabetic
```

```{r}

gpt_diabitic_yes <- data.frame(
  diabetes = "Diabetes",
  labread = gpt_diabetic$labreads
)

gpt_diabitic_no <- data.frame(
  diabetes = "Non_Diabetes",
  labread = gpt_nondiabetic$labreads
)

combined_diabetic <- rbind(
  gpt_diabitic_yes,
  gpt_diabitic_no
)

combined_diabetic
```



```{r}
#gpt_nondiabetic[!(gpt_nondiabetic$`Edited_BfArM Nummer2` %in% gpt_diabetic$`Edited_BfArM Nummer2`),]

```

```{r}
#filter(gpt_nondiabetic, !Diabetes %in% "1")
```




```{r}

 
combined_diabetic %>% 
  ggplot(aes(x= diabetes, y = labread))+
  geom_boxplot(width = 0.6)+
  geom_jitter(color = "red", alpha = 0.3)+
  scale_y_continuous(breaks = seq(0, 12500, by = 1000),
                     expand = expansion(mult = c(0,0)))+
  theme_classic()+
  labs(title = "All cases_mean of diabetic and non-diabetic", # ALT for labvalue and daily dose",
       x = "Patient group",
       y = "Mean ALT u/l") +
     theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)
  )
  
```

##=========================================
## Diabetes Boxplots_ whole data
##=========================================

```{r}
P1_diabetic <- left_join(gpt_full, 
                          diabetic_data, 
                          by = c ("bf_ar_m_nummer"  = "edited_bf_ar_m_nummer2" ),
                          relationship = "many-to-many") %>% 
            mutate(labreads = as.numeric(labreads)) %>% 
  drop_na() %>% 
  filter(diabetes == "Diabetic") %>% 
#  filter(!attribute == "GPT Day_Unknown") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  group_by(treatment) %>% 
  ggplot(aes(x = treatment, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(title = "Comparsion of Diabetic Cases", # ALT for labvalue and daily dose",
       x = "Patient group",
       y = "ALT (u/l)") +
  theme_classic()+
     theme(
     #plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1),
     axis.text.y = element_text(size = 12,face = "bold"),
    axis.title = element_text(size = 15,face = "bold"),
    plot.title = element_text(size = 18,face = "bold",hjust = 0.5),
    axis.line = element_line(linewidth = 1),
    legend.position = "none"
  )
P1_diabetic
```

```{r}
P2_nondiabitic <- left_join(gpt_full, 
                          diabetic_data, 
                          by = c ("bf_ar_m_nummer"  = "edited_bf_ar_m_nummer2" ),
                          relationship = "many-to-many") %>% 
  filter(diabetes == "Non_Diabetic") %>% 
#  filter(!attribute == "GPT Day_Unknown") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  filter(grepl("Leber_", treatment)) %>% 
  group_by(treatment) %>% 
  ggplot(aes(x = treatment, y = labreads))+
  geom_boxplot()+
  #geom_jitter(colour = "red")+
  theme_classic()+
  labs(title = "Comparsion of Non Diabetic Cases", # ALT for labvalue and daily dose",
       x = "Patient group",
       y = "ALT u/l") +
     theme(
     plot.title = element_text(margin = margin(b=10), color="black", face="bold", hjust = 0.5),
     axis.text.x = element_text(face="bold", angle = 45, hjust = 1)
  )

P2_nondiabitic
```

```{r}
leber_diabitic <- P1_diabetic+ P2_nondiabitic

print(leber_diabitic)
```

```{r}
library(dlookr)
gpt_diabetic %>% 
  group_by(diabetes) %>% 
  normality(labreads)
```

```{r}
t.test(
   labreads ~ diabetes,
  data = gpt_diabetic
)
```

##==============================
## Diabetic vs non-diabetic
##==============================

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
# n_patients <- gpt_diabetic %>%
#   distinct(bf_ar_m_nummer, diabetes) %>%  # nur einzigartige Patienten
#   count(diabetes, name = "n") %>%
#   mutate(label = paste0("N = ", n))
# 
# #Schritt 2: ggbetweenstats-Plot erstellen
# plot_without_count <- ggbetweenstats(
#   data = gpt_diabetic,
#   x = "diabetes",
#   y = "labreads",
#   type = "np",  # non-parametrisch
#   title = "All groups_Comparison of \n ALT for Diabetic vs. Non-Diabetic Patients",
#   xlab = "Patient group",
#   ylab = "ALT (U/l)",
#   messages = FALSE
# )
# p1 <- plot_without_count+theme_classic()+
#   theme(
#     legend.position = "none",
#     plot.title = element_text(margin = margin(b=10),hjust = 0.5, face = "bold"),
#     axis.text.x = element_text(size = 12 , face = "bold"),
#     axis.text.y = element_text(size = 12 , face = "bold"),
#     axis.title = element_text(size = 15 , face = "bold"),
#     axis.line = element_line(linewidth = 1))
# 
# # Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
# liver_gpt_full_comparison_diabetic_vs_nondiabetic <- p1+ 
#   geom_text(
#     data = n_patients,
#     aes(x = diabetes, 
#         y = max(gpt_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
#         label = label),
#     inherit.aes = FALSE,
#     size = 5,
#     fontface = "bold"
#   )

#dir.create("plots_all_labvalues", showWarnings = FALSE)
#svg("plots_all_labvalues/all_gpt_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
#print(liver_gpt_full_comparison_diabetic_vs_nondiabetic)
#dev.off()
```


```{r}
label_df <- gpt_diabetic %>%
  group_by(diabetes) %>%
  summarise(
    n_patients = n_distinct(bf_ar_m_nummer),
    n_labreads = n()
  ) %>%
  mutate(label = paste0("N = ", n_patients,
                        "\nLab = ", n_labreads))
label_df

label_df_top <- label_df %>%
  mutate(label = paste0("N = ", n_patients))
label_df_bottom <- label_df %>%
  mutate(label = paste0("n = ", n_labreads))
```

```{r}
library(ggplot2)
library(dplyr)

# Anzahl einzigartiger Patienten pro Gruppe
# y positions
y_max    <- max(gpt_diabetic$labreads, na.rm = TRUE)
y_top    <- y_max * 1.15
y_bottom <- y_max * -0.25 



liver_gpt_full_comparison_diabetic_vs_nondiabetic <- ggplot(gpt_diabetic,
             aes(x = diabetes, y = labreads, fill = diabetes)) +
  geom_violin(trim = FALSE, alpha = 0.5, color = "black") +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.8, color = "black") +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = median, geom = "point",
               shape = 23, size = 4, fill = "yellow") +
  geom_text(
    data = label_df_top,
    aes(x = diabetes, y = y_top, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 4
  ) +
  geom_text(
    data = label_df_bottom,
    aes(x = diabetes, y = y_bottom, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 4
  ) +
  stat_compare_means(
    comparisons = list(c("Diabetic", "Non_Diabetic")),
    method = "wilcox.test", label = "p.format",
    label.y = max(gpt_diabetic$labreads, na.rm = TRUE) * 1.02,
    bracket.size = 1, tip.length = 0.02, size = 4
  ) +
  labs(
    title = "All groups_Comparison of \nALT for Diabetic vs. Non-Diabetic Patients",
    x = NULL, y = "ALT (U/l)"
  ) +
  coord_cartesian(ylim = c(0, y_max * 1.20),
                  clip = "off") +          # ✅ Separate layer — NOT inside theme()
  theme_classic() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold",
                              margin = margin(b = 10), lineheight = 1.2),
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold"),
    axis.title  = element_text(size = 15, face = "bold"),
    axis.line   = element_line(linewidth = 1),
    plot.margin = margin(t = 10, r = 10, b = 30, l = 10)  # bottom margin for labels
  )


liver_gpt_full_comparison_diabetic_vs_nondiabetic
```

```{r}
ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/liver_gpt_full_comparison_diabetic_vs_nondiabetic.png"),
  plot = liver_gpt_full_comparison_diabetic_vs_nondiabetic,
  width = 6,
  height = 4,
  dpi = 300
)

ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/liver_gpt_full_comparison_diabetic_vs_nondiabetic.svg"),
  plot = liver_gpt_full_comparison_diabetic_vs_nondiabetic,
  width = 10,
  height = 6
)
```


##==================================
## Liver diclo_ diabetic_nondiabetic
##==================================


```{r}
# library(ggstatsplot)
# 
# leber_diabetic_diclo <- gpt_diabetic%>% 
#   filter(treatment == "Leber_Diclo")
# 
# 
# # Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
# n_patients <- leber_diabetic_diclo %>%
#   distinct(bf_ar_m_nummer, diabetes) %>%  # nur einzigartige Patienten
#   count(diabetes, name = "n") %>%
#   mutate(label = paste0("N = ", n))
# 
# # Schritt 2: ggbetweenstats-Plot erstellen
# plot_without_count <- ggbetweenstats(
#   data = leber_diabetic_diclo,
#   x = "diabetes",
#   y = "labreads",
#   type = "np",  # non-parametrisch
#   title = "liver_diclo Comparison of ALT for Diabetic vs. Non-Diabetic Patients",
#   xlab = "Patient group",
#   ylab = "ALT (U/l)",
#   messages = FALSE,
#   bf.message = FALSE,
#   result.sutitle = FALSE,
#   pairwise.display = "none"
# )
# 
# # Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
# liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
#   geom_text(
#     data = n_patients,
#     aes(x = diabetes, 
#         y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
#         label = label),
#     inherit.aes = FALSE,
#     size = 4
#   )
# 
# #dir.create("plots_all_labvalues", showWarnings = FALSE)
# #svg("plots_all_labvalues/all_gpt_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
# print(liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic)
# #dev.off()


```



```{r}

# Anzahl einzigartiger Patienten pro Gruppe
leber_diabetic_diclo <- gpt_diabetic %>% 
  filter(treatment == "Leber_Diclo")

label_df <- leber_diabetic_diclo %>%
  group_by(diabetes) %>%
  summarise(
    n_patients = n_distinct(bf_ar_m_nummer),
    n_labreads = n()
  ) %>%
  mutate(label = paste0("N = ", n_patients,
                        "\nLab = ", n_labreads))
label_df

label_df_top <- label_df %>%
  mutate(label = paste0("N = ", n_patients))
label_df_bottom <- label_df %>%
  mutate(label = paste0("n = ", n_labreads))



# y positions
y_max    <- max(leber_diabetic_diclo$labreads, na.rm = TRUE)
y_top    <- y_max * 1.20
y_bottom <- y_max * -0.25 



leber_diclo_diabetic_vs_nondiabetic <- ggplot(leber_diabetic_diclo,
             aes(x = diabetes, y = labreads, fill = diabetes)) +
  geom_violin(trim = TRUE, alpha = 0.5, color = "black") +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.8, color = "black") +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = median, geom = "point",
               shape = 23, size = 4, fill = "yellow") +
  geom_text(
    data = label_df_top,
    aes(x = diabetes, y = y_top, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 5
  ) +
  geom_text(
    data = label_df_bottom,
    aes(x = diabetes, y = y_bottom, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 4
  ) +
  stat_compare_means(
    comparisons = list(c("Diabetic", "Non_Diabetic")),
    method = "wilcox.test", label = "p.format",
    label.y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,
    bracket.size = 1, tip.length = 0.02, size = 4
  ) +
  labs(
    title = "Comparsion of liver_diclo ALT for \nDiabetic vs. Non-Diabetic Patients",
    x = NULL, y = "ALT (U/l)"
  ) +
  coord_cartesian(ylim = c(0, y_max * 1.20),
                  clip = "off") +          # ✅ Separate layer — NOT inside theme()
  theme_classic() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold",
                              margin = margin(b = 10), lineheight = 1.15),
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold"),
    axis.title  = element_text(size = 15, face = "bold"),
    axis.line   = element_line(linewidth = 1),
    plot.margin = margin(t = 10, r = 10, b = 40, l = 10)  # bottom margin for labels
  )
leber_diclo_diabetic_vs_nondiabetic
```
```{r}
ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/leber_diclo_diabetic_vs_nondiabetic.png"),
  plot = leber_diclo_diabetic_vs_nondiabetic,
  width = 6,
  height = 4,
  dpi = 300
)

ggsave(
  filename = here::here("output/figure/diabetes/plots_all_labvalues/leber_diclo_diabetic_vs_nondiabetic.svg"),
  plot = leber_diclo_diabetic_vs_nondiabetic,
  width = 10,
  height = 6
)
```

##==================================
## Liver IBU_ diabetic_nondiabetic
##==================================

```{r}
# library(ggstatsplot)
# 
# leber_diabetic_ibu <- gpt_diabetic%>% 
#   filter(Treatment == "Leber_Ibu")
# 
# 
# # Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
# n_patients <- leber_diabetic_ibu %>%
#   distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
#   count(Diabetes, name = "n") %>%
#   mutate(label = paste0("N = ", n))
# 
# # Schritt 2: ggbetweenstats-Plot erstellen
# plot_without_count <- ggbetweenstats(
#   data = leber_diabetic_ibu,
#   x = "Diabetes",
#   y = "labreads",
#   type = "np",  # non-parametrisch
#   title = "liver_ibu Comparison of ALT for Diabetic vs. Non-Diabetic Patients",
#   xlab = "Patient group",
#   ylab = "ALT (U/l)",
#   messages = FALSE
# )
# 
# # Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
# liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
#   geom_text(
#     data = n_patients,
#     aes(x = Diabetes, 
#         y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
#         label = label),
#     inherit.aes = FALSE,
#     size = 4
#   )
# 
# dir.create("plots_all_labvalues", showWarnings = FALSE)
# svg("plots_all_labvalues/all_gpt_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
# print(liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic)
# dev.off()


```



```{r}
# Anzahl einzigartiger Patienten pro Gruppe
leber_diabetic_ibu <- gpt_diabetic %>% 
  filter(treatment == "Leber_Ibu")

label_df <- leber_diabetic_ibu %>%
  group_by(diabetes) %>%
  summarise(
    n_patients = n_distinct(bf_ar_m_nummer),
    n_labreads = n()
  ) %>%
  mutate(label = paste0("N = ", n_patients,
                        "\nLab = ", n_labreads))
label_df

label_df_top <- label_df %>%
  mutate(label = paste0("N = ", n_patients))
label_df_bottom <- label_df %>%
  mutate(label = paste0("n = ", n_labreads))



# y positions
y_max    <- max(leber_diabetic_ibu$labreads, na.rm = TRUE)
y_top    <- y_max * 1.20
y_bottom <- y_max * -0.25 



leber_ibu_diabetic_vs_nondiabetic <- ggplot(leber_diabetic_ibu,
             aes(x = diabetes, y = labreads, fill = diabetes)) +
  geom_violin(trim = TRUE, alpha = 0.5, color = "black") +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.8, color = "black") +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = median, geom = "point",
               shape = 23, size = 4, fill = "yellow") +
  geom_text(
    data = label_df_top,
    aes(x = diabetes, y = y_top, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 5
  ) +
  geom_text(
    data = label_df_bottom,
    aes(x = diabetes, y = y_bottom, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 4
  ) +
  stat_compare_means(
    comparisons = list(c("Diabetic", "Non_Diabetic")),
    method = "wilcox.test", label = "p.format",
    label.y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,
    bracket.size = 1, tip.length = 0.02, size = 4
  ) +
  labs(
    title = "Comparsion of liver_ibu ALT for \nDiabetic vs. Non-Diabetic Patients",
    x = NULL, y = "ALT (U/l)"
  ) +
  coord_cartesian(ylim = c(0, y_max * 1.20),
                  clip = "off") +          # ✅ Separate layer — NOT inside theme()
  theme_classic() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold",
                              margin = margin(b = 10), lineheight = 1.15),
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold"),
    axis.title  = element_text(size = 15, face = "bold"),
    axis.line   = element_line(linewidth = 1),
    plot.margin = margin(t = 10, r = 10, b = 40, l = 10)  # bottom margin for labels
  )

leber_ibu_diabetic_vs_nondiabetic

```

```{r}
# library(ggstatsplot)
# 
# leber_diabetic_para <- gpt_diabetic%>%
#   filter(treatment == "Leber_Para")
# 
# 
# # Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
# n_patients <- leber_diabetic_para %>%
#   distinct(bf_ar_m_nummer, diabetes) %>%  # nur einzigartige Patienten
#   count(diabetes, name = "n") %>%
#   mutate(label = paste0("N = ", n))
# 
# # Schritt 2: ggbetweenstats-Plot erstellen
# plot_without_count <- ggbetweenstats(
#   data = leber_diabetic_para,
#   x = "diabetes",
#   y = "labreads",
#   type = "np",  # non-parametrisch
#   title = "liver_para Comparison of ALT for Diabetic vs. Non-Diabetic Patients",
#   xlab = "Patient group",
#   ylab = "ALT (U/l)",
#   messages = FALSE
# )
# 
# # Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
# liver_gpt_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+
#   geom_text(
#     data = n_patients,
#     aes(x = diabetes,
#         y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
#         label = label),
#     inherit.aes = FALSE,
#     size = 4
#   )
# # 
# # dir.create("plots_all_labvalues", showWarnings = FALSE)
# # svg("plots_all_labvalues/all_gpt_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
#  print(liver_gpt_full_para_comparison_diabetic_vs_nondiabetic)
# # dev.off()


```


```{r}
# Anzahl einzigartiger Patienten pro Gruppe
leber_diabetic_para <- gpt_diabetic %>% 
  filter(treatment == "Leber_Para")

label_df <- leber_diabetic_para %>%
  group_by(diabetes) %>%
  summarise(
    n_patients = n_distinct(bf_ar_m_nummer),
    n_labreads = n()
  ) %>%
  mutate(label = paste0("N = ", n_patients,
                        "\nLab = ", n_labreads))
label_df

label_df_top <- label_df %>%
  mutate(label = paste0("N = ", n_patients))
label_df_bottom <- label_df %>%
  mutate(label = paste0("n = ", n_labreads))



# y positions
y_max    <- max(leber_diabetic_para$labreads, na.rm = TRUE)
y_top    <- y_max * 1.20
y_bottom <- y_max * -0.25 



leber_para_diabetic_vs_nondiabetic <- ggplot(leber_diabetic_para,
             aes(x = diabetes, y = labreads, fill = diabetes)) +
  geom_violin(trim = TRUE, alpha = 0.5, color = "black") +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.8, color = "black") +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = median, geom = "point",
               shape = 23, size = 4, fill = "yellow") +
  geom_text(
    data = label_df_top,
    aes(x = diabetes, y = y_top, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 5
  ) +
  geom_text(
    data = label_df_bottom,
    aes(x = diabetes, y = y_bottom, label = label),
    inherit.aes = FALSE, fontface = "plain", size = 4
  ) +
  stat_compare_means(
    comparisons = list(c("Diabetic", "Non_Diabetic")),
    method = "wilcox.test", label = "p.format",
    label.y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,
    bracket.size = 1, tip.length = 0.02, size = 4
  ) +
  labs(
    title = "Comparsion of liver_para ALT for \nDiabetic vs. Non-Diabetic Patients",
    x = NULL, y = "ALT (U/l)"
  ) +
  coord_cartesian(ylim = c(0, y_max * 1.50),
                  clip = "off") +          # ✅ Separate layer — NOT inside theme()
  theme_classic() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold",
                              margin = margin(b = 10), lineheight = 1.15),
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold"),
    axis.title  = element_text(size = 15, face = "bold"),
    axis.line   = element_line(linewidth = 1),
    plot.margin = margin(t = 10, r = 10, b = 40, l = 10)  # bottom margin for labels
  )

leber_para_diabetic_vs_nondiabetic
```


##===========================================================================
## Boxplots_for diabetic data
##============================================================================

```{r}
# gpt_diabetic %>% 
#   ggplot(aes( x =diabetes, y = labreads))+
#   geom_boxplot()+
#   geom_jitter(colour = "#CC79A7")+
#     stat_compare_means(
#     comparisons = list(c("Diabetic", "Non_Diabetic")),
#     method = "wilcox.test", label = "p.format",
#     #label.y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,
#     bracket.size = 1, tip.length = 0.02, size = 4
#   )+
#   labs(
#     x = "Patient group",
#     y = "ALT U/L",
#     title = "all groups_Comaprsion of\n diabetic and non-diabetic cases" )+
#   theme_classic()+
#     theme(
#     axis.text.x = element_text(
#     angle = 0,hjust = 1,size = 12,face = "bold" ),
#     axis.text.y = element_text(size = 12,face = "bold"),
#     axis.title = element_text(size = 15,face = "bold"),
#     plot.title = element_text(size = 18,face = "bold",hjust = 0.5),
#     axis.line = element_line(linewidth = 1),
#     legend.position = "none"
#   )
```

```{r}
box_jitter_plot(
  data = gpt_diabetic,
  x_var = "diabetes",
  y_var = "labreads",
  group1 = "Diabetic",
  group2 = "Non_Diabetic",
  x_label = "Patient",
  y_label = "ALT (u/L)",
  title_text = "all_groups_Comaprsion of \n diabetic and non-diabetic cases")



```

```{r}
p1_diclo <- gpt_diabetic %>% 
  filter(treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ALT U/L",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    axis.text.x = element_text(
      angle = 0,hjust = 1,size = 12,face = "bold" ),
    axis.text.y = element_text(size = 12,face = "bold"),
    axis.title = element_text(size = 15,face = "bold"),
    plot.title = element_text(size = 18,face = "bold",hjust = 0.5),
    axis.line = element_line(linewidth = 1),
    legend.position = "none"
  )
print(p1_diclo)
```
```{r}
gpt_liver_diclo <- gpt_diabetic %>% 
  filter(treatment == "Leber_Diclo")


box_jitter_plot(
  data = gpt_liver_diclo,
  x_var = "diabetes",
  y_var = "labreads",
  group1 = "Diabetic",
  group2 = "Non_Diabetic",
  x_label = "Patient",
  y_label = "ALT (u/L)",
  title_text = "Comaprsion of liver diclo \n diabetic and non-diabetic cases")

```


```{r}
p2_ibu <- gpt_diabetic %>% 
  filter(treatment == "Leber_Ibu") %>% 
  ggplot(aes( x = diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ALT U/L",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    axis.text.x = element_text(
      angle = 0,hjust = 1,size = 12,face = "bold" ),
    axis.text.y = element_text(size = 12,face = "bold"),
    axis.title = element_text(size = 15,face = "bold"),
    plot.title = element_text(size = 18,face = "bold",hjust = 0.5),
    axis.line = element_line(linewidth = 1),
    legend.position = "none"
  )
print(p2_ibu)
```
```{r}
gpt_liver_Ibu <- gpt_diabetic %>% 
  filter(treatment == "Leber_Ibu")


box_jitter_plot(
  data = gpt_liver_Ibu,
  x_var = "diabetes",
  y_var = "labreads",
  group1 = "Diabetic",
  group2 = "Non_Diabetic",
  x_label = "Patient",
  y_label = "ALT (u/L)",
  title_text = "Comaprsion of liver Ibu \n diabetic and non-diabetic cases")
```


```{r}
p3_para <- gpt_diabetic %>% 
  filter(treatment == "Leber_Para") %>% 
  ggplot(aes( x =diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ALT U/L",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
print(p3_para)
```

```{r}
liver_gpt_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_gpt_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_gpt_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##============================
## GOT
##==========================
```{r}
got_full <- all_data %>% 
  filter(panel_id == "got") %>% 
  mutate(labreads = as.numeric(labreads))
got_full
```


```{r}
got_diabetic <- left_join(got_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

got_diabetic
```

### Based on Patient number ###


```{r}
liver_got_full_diabetic_cases_labvalues <- got_diabetic %>% 
  filter(diabetes == "Diabetic") %>%   
  group_by(bf_ar_m_nummer) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = bf_ar_m_nummer, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean GOT", hjust = 0.5,
       x = "Patients",
       y = "GOT u/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

#dir.create("plots_all_labvalues", showWarnings = FALSE)
#svg("plots_all_labvalues/all_got_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_got_full_diabetic_cases_labvalues)
#dev.off()
```



```{r}
got_diabetic2 <- got_diabetic %>% 
  filter(diabetes == "Diabetic") 

got_diabetic2_counts <- got_diabetic2 %>% 
  group_by(days) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
got_diabetic2_counts
```





```{r}
library(tidyverse)
library(glue)

# Prepare data
got_diabetic2 <- got_diabetic %>% 
  filter(diabetes == "Diabetic") %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  group_by(days) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

# Convert days to ordered factor with labels
got_diabetic2$days <- factor(
  got_diabetic2$days,
  levels = 1:28,
  labels = glue("GOT Day {1:28}")
)

# Plot
liver_got_full_diabetic_cases_labvalues_time <- got_diabetic2 %>%
  ggplot(aes(x = days, y = mean_labread)) +
  geom_col() +
    geom_text(
    aes(label = paste0("N = ", n)),
    vjust = -1.0,
    size = 5,
    color = "black"
  ) +
  
  labs(
    title = "All groups Diabetic cases mean AST",
    x = "Day of measurement",
    y = "ALT (U/L)"
  ) +
  
  theme_classic() +
  
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 12,
      face = "bold"
    ),
    
    axis.text.y = element_text(
      size = 12,
      face = "bold"
    ),
    
    axis.title = element_text(
      size = 15,
      face = "bold"
    ),
    
    plot.title = element_text(
      size = 18,
      face = "bold",
      hjust = 0.5
    ),
    
    axis.line = element_line(linewidth = 1),
    
    legend.position = "none"
  )

liver_got_full_diabetic_cases_labvalues_time
#dir.create("plots_all_labvalues", showWarnings = FALSE)
#svg("plots_all_labvalues/all_got_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_got_full_diabetic_cases_labvalues_time)
#dev.off()
```


##=============
##
#==============


```{r}
library(dlookr)
got_diabetic %>% 
  group_by(diabetes) %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  normality(labreads)
```


```{r}
got_diabetic %>% 
  group_by(diabetes) %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
t.test(
   labreads ~ diabetes,
  data = .)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- got_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = got_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of GOT for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "GOT (U/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_got_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(got_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_got_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_got_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- got_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "GOT U/L",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- got_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "GOT U/L",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- got_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "GOT U/L",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_got_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_got_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_got_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##==========================
## GGT
##=========================
```{r}
ggt_full <- all_data %>% 
  filter(panel_id == "ggt")
ggt_full
```

```{r}
ggt_diabetic <- left_join(ggt_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

ggt_diabetic
```

### Based on Patient number ###


```{r}
liver_ggt_full_diabetic_cases_labvalues <- ggt_diabetic %>% 
  filter(diabetes == "Diabetic") %>%   
  group_by(bf_ar_m_nummer) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = bf_ar_m_nummer, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean GGT", hjust = 0.5,
       x = "Patients",
       y = "GOT u/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

#dir.create("plots_all_labvalues", showWarnings = FALSE)
#svg("plots_all_labvalues/all_ggt_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_ggt_full_diabetic_cases_labvalues)
#dev.off()
```


```{r}
ggt_diabetic2 <- ggt_diabetic %>% 
  filter(diabetes == "Diabetic") 

ggt_diabetic2_counts <- ggt_diabetic2 %>% 
  group_by(days) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
ggt_diabetic2_counts
```


```{r}
# ggt_diabetic2_counts$attribute <-  factor(ggt_diabetic2_counts$attribute, 
#                                    levels = c( "GGT Day1", "GGT Day2", "GGT Day3","GGT Day4","GGT Day5", "GGT Day6","GGT Day7","GGT Day8","GGT Day9","GGT Day10", "GGT Day11","GGT Day12","GGT Day13","GGT Day14","GGT Day15","GGT Day16","GGT Day17","GGT Day18","GGT Day19","GGT Day20","GGT Day21","GGT Day22","GGT Day23","GGT Day24","GGT Day25","GGT Day26","GGT Day27","GGT Day28","GGT Day29","GGT Day30","GGT Day31","GGT Day32","GGT Day33","GGT Day34","GGT Day35","GGT Day36","GGT Day37","GGT Day38","GGT Day39","GGT Day40","GGT Day41","GGT Day42","GGT Day43","GGT Day44","GGT Day45","GGT Day46","GGT Day47","GGT Day48","GGT Day49","GGT Day50","GGT Day51","GGT Day52","GGT Day53","GGT Day54","GGT Day55","GGT Day56","GGT Day57","GGT Day58","GGT Day59","GGT Day60","GGT Day61","GGT Day62","GGT Day63","GGT Day64","GGT Day65","GGT Day66","GGT Day67","GGT Day68","GGT Day69","GGT Day70","GGT Day71","GGT Day72","GGT Day73","GGT Day74","GGT Day75","GGT Day76","GGT Day77","GGT Day78","GGT Day79","GGT Day80","GGT Day81","GGT Day82","GGT Day83","GGT Day84","GGT Day85","GGT Day86","GGT Day87","GGT Day88","GGT Day89","GGT Day90","GGT Day91","GGT Day92","GGT Day93","GGT Day94","GGT Day95","GGT Day96","GGT Day97","GGT Day98","GGT Day99","GGT Day100"))
# liver_ggt_full_diabetic_cases_labvalues_time <- ggt_diabetic2_counts %>%
#   ggplot(aes(x = attribute, y = mean_labread))+
#   geom_col()+
#   theme_classic()+
#   geom_text(data = ggt_diabetic2_counts, 
#             aes(label = paste0("N = ", n)),
#             vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
#             size = 3)+       # Optional: kleinere Schriftgröße
#   labs(title = "All groups_Diabetic cases mean ggt", hjust = 0.5,
#        x = "Day of measurement",
#        y = "ggt u/l"
#        )+
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1)
#   ) 
# liver_ggt_full_diabetic_cases_labvalues_time
# dir.create("plots_all_labvalues", showWarnings = FALSE)
# svg("plots_all_labvalues/all_ggt_diabetic cases labvalues time.svg", height = 7, width = 10)
# print(liver_ggt_full_diabetic_cases_labvalues_time)
# dev.off()
```

```{r}

library(tidyverse)
library(glue)

# Prepare data
ggt_diabetic2 <- ggt_diabetic %>% 
  filter(diabetes == "Diabetic") %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  group_by(days) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

# Convert days to ordered factor with labels
ggt_diabetic2$days <- factor(
  ggt_diabetic2$days,
  levels = 1:28,
  labels = glue("GGT Day {1:28}")
)

# Plot
liver_ggt_full_diabetic_cases_labvalues_time <- ggt_diabetic2 %>%
  ggplot(aes(x = days, y = mean_labread)) +
  geom_col() +
    geom_text(
    aes(label = paste0("N = ", n)),
    vjust = -1.0,
    size = 5,
    color = "black"
  ) +
  
  labs(
    title = "All groups Diabetic cases mean GGT",
    x = "Day of measurement",
    y = "GGT (U/L)"
  ) +
  
  theme_classic() +
  
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 12,
      face = "bold"
    ),
    
    axis.text.y = element_text(
      size = 12,
      face = "bold"
    ),
    
    axis.title = element_text(
      size = 15,
      face = "bold"
    ),
    
    plot.title = element_text(
      size = 18,
      face = "bold",
      hjust = 0.5
    ),
    
    axis.line = element_line(linewidth = 1),
    
    legend.position = "none"
  )

liver_ggt_full_diabetic_cases_labvalues_time
#dir.create("plots_all_labvalues", showWarnings = FALSE)
#svg("plots_all_labvalues/all_got_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_ggt_full_diabetic_cases_labvalues_time)
#dev.off()
```


###########################################################################


```{r}
library(dlookr)
ggt_diabetic %>% 
  group_by(diabetes) %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  normality(labreads)
```


```{r}
ggt_diabetic %>% 
  group_by(diabetes) %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
t.test(
   labreads ~ diabetes,
  data = .
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ggt_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ggt_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of ggt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ggt (U/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ggt_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ggt_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ggt_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ggt_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- ggt_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ggt U/L",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- ggt_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ggt U/L",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- ggt_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ggt U/L",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_ggt_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_ggt_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ggt_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##===================
## ldh 
##===================

```{r}
ldh_full <- all_data %>% 
  filter(panel_id == "ldh")
ldh_full
```



```{r}
ldh_diabetic <- left_join(ldh_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 
ldh_diabetic  
```

### Based on Patient number ###


```{r}
liver_ldh_full_diabetic_cases_labvalues <- ldh_diabetic %>% 
  filter(diabetes == "Diabetic") %>%   
  group_by(bf_ar_m_nummer) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = bf_ar_m_nummer, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean GGT", hjust = 0.5,
       x = "Patients",
       y = "GOT u/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

#dir.create("plots_all_labvalues", showWarnings = FALSE)
#svg("plots_all_labvalues/all_ldh_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_ldh_full_diabetic_cases_labvalues)
#dev.off()
```


```{r}
ldh_diabetic2 <- ldh_diabetic %>% 
  filter(diabetes == "Diabetic") 

ldh_diabetic2_counts <- ldh_diabetic2 %>% 
  group_by(days) %>%
  mutate(labreads = as.numeric(labreads)) %>% 
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
ldh_diabetic2_counts
```


```{r}
# ldh_diabetic2_counts$attribute <-  factor(ldh_diabetic2_counts$attribute, 
#                                    levels = c( "LDH Day1", "LDH Day2", "LDH Day3","LDH Day4","LDH Day5", "LDH Day6","LDH Day7","LDH Day8","LDH Day9","LDH Day10", "LDH Day11","LDH Day12","LDH Day13","LDH Day14","LDH Day15","LDH Day16","LDH Day17","LDH Day18","LDH Day19","LDH Day20","LDH Day21","LDH Day22","LDH Day23","LDH Day24","LDH Day25","LDH Day26","LDH Day27","LDH Day28","LDH Day29","LDH Day30","LDH Day31","LDH Day32","LDH Day33","LDH Day34","LDH Day35","LDH Day36","LDH Day37","LDH Day38","LDH Day39","LDH Day40","LDH Day41","LDH Day42","LDH Day43","LDH Day44","LDH Day45","LDH Day46","LDH Day47","LDH Day48","LDH Day49","LDH Day50","LDH Day51","LDH Day52","LDH Day53","LDH Day54","LDH Day55","LDH Day56","LDH Day57","LDH Day58","LDH Day59","LDH Day60","LDH Day61","LDH Day62","LDH Day63","LDH Day64","LDH Day65","LDH Day66","LDH Day67","LDH Day68","LDH Day69","LDH Day70","LDH Day71","LDH Day72","LDH Day73","LDH Day74","LDH Day75","LDH Day76","LDH Day77","LDH Day78","LDH Day79","LDH Day80","LDH Day81","LDH Day82","LDH Day83","LDH Day84","LDH Day85","LDH Day86","LDH Day87","LDH Day88","LDH Day89","LDH Day90","LDH Day91","LDH Day92","LDH Day93","LDH Day94","LDH Day95","LDH Day96","LDH Day97","LDH Day98","LDH Day99","LDH Day100"))
# liver_ldh_full_diabetic_cases_labvalues_time <- ldh_diabetic2_counts %>%
#   ggplot(aes(x = attribute, y = mean_labread))+
#   geom_col()+
#   theme_classic()+
#   geom_text(data = ldh_diabetic2_counts, 
#             aes(label = paste0("N = ", n)),
#             vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
#             size = 3)+       # Optional: kleinere Schriftgröße
#   labs(title = "All groups_Diabetic cases mean ldh", hjust = 0.5,
#        x = "Day of measurement",
#        y = "ldh u/l"
#        )+
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1)
#   ) 
# 
# dir.create("plots_all_labvalues", showWarnings = FALSE)
# svg("plots_all_labvalues/all_ldh_diabetic cases labvalues time.svg", height = 7, width = 10)
# print(liver_ldh_full_diabetic_cases_labvalues_time)
# dev.off()
```


```{r}

library(tidyverse)
library(glue)

# Prepare data
ldh_diabetic2 <- ldh_diabetic %>% 
  filter(diabetes == "Diabetic") %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  group_by(days) %>% 
  summarize(
    mean_labread = mean(labreads, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

# Convert days to ordered factor with labels
ldh_diabetic2$days <- factor(
  ldh_diabetic2$days,
  levels = 1:28,
  labels = glue("LDH Day {1:28}")
)

# Plot
liver_ldh_full_diabetic_cases_labvalues_time <- ldh_diabetic2 %>%
  ggplot(aes(x = days, y = mean_labread)) +
  geom_col() +
    geom_text(
    aes(label = paste0("N = ", n)),
    vjust = -1.0,
    size = 5,
    color = "black"
  ) +
  
  labs(
    title = "All groups Diabetic cases mean LDH",
    x = "Day of measurement",
    y = "LDJ (U/L)"
  ) +
  
  theme_classic() +
  
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 12,
      face = "bold"
    ),
    
    axis.text.y = element_text(
      size = 12,
      face = "bold"
    ),
    
    axis.title = element_text(
      size = 15,
      face = "bold"
    ),
    
    plot.title = element_text(
      size = 18,
      face = "bold",
      hjust = 0.5
    ),
    
    axis.line = element_line(linewidth = 1),
    
    legend.position = "none"
  )

liver_ldh_full_diabetic_cases_labvalues_time
#dir.create("plots_all_labvalues", showWarnings = FALSE)
#svg("plots_all_labvalues/all_got_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_ldh_full_diabetic_cases_labvalues_time)
#dev.off()
```
###########################################################################


```{r}
library(dlookr)
ldh_diabetic %>% 
  group_by(diabetes) %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
  normality(labreads)
```


```{r}
ldh_diabetic %>% 
  group_by(diabetes) %>% 
  mutate(labreads = as.numeric(labreads)) %>% 
t.test(
   labreads ~ diabetes,
  data = .
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ldh_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ldh_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of ldh for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ldh (U/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ldh_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ldh_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ldh_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ldh_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- ldh_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ldh U/L",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- ldh_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ldh U/L",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- ldh_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ldh U/L",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_ldh_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_ldh_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ldh_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##========================
## ck 
##========================
```{r}
ck_full <- all_data %>% 
         filter(panel_id == "ck")
ck_full
```


```{r}
ck_diabetic <- left_join(ck_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

ck_diabetic
```

### Based on Patient number ###


```{r}
liver_ck_full_diabetic_cases_labvalues <- ck_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean ck", hjust = 0.5,
       x = "Patients",
       y = "ck u/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ck_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_ck_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
ck_diabetic2 <- ck_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

ck_diabetic2_counts <- ck_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
ck_diabetic2_counts$attribute <-  factor(ck_diabetic2_counts$attribute, 
                                   levels = c( "CK Day1", "CK Day2", "CK Day3","CK Day4","CK Day5", "CK Day6","CK Day7","CK Day8","CK Day9","CK Day10", "CK Day11","CK Day12","CK Day13","CK Day14","CK Day15","CK Day16","CK Day17","CK Day18","CK Day19","CK Day20","CK Day21","CK Day22","CK Day23","CK Day24","CK Day25","CK Day26","CK Day27","CK Day28","CK Day29","CK Day30","CK Day31","CK Day32","CK Day33","CK Day34","CK Day35","CK Day36","CK Day37","CK Day38","CK Day39","CK Day40","CK Day41","CK Day42","CK Day43","CK Day44","CK Day45","CK Day46","CK Day47","CK Day48","CK Day49","CK Day50","CK Day51","CK Day52","CK Day53","CK Day54","CK Day55","CK Day56","CK Day57","CK Day58","CK Day59","CK Day60","CK Day61","CK Day62","CK Day63","CK Day64","CK Day65","CK Day66","CK Day67","CK Day68","CK Day69","CK Day70","CK Day71","CK Day72","CK Day73","CK Day74","CK Day75","CK Day76","CK Day77","CK Day78","CK Day79","CK Day80","CK Day81","CK Day82","CK Day83","CK Day84","CK Day85","CK Day86","CK Day87","CK Day88","CK Day89","CK Day90","CK Day91","CK Day92","CK Day93","CK Day94","CK Day95","CK Day96","CK Day97","CK Day98","CK Day99","CK Day100"))
liver_ck_full_diabetic_cases_labvalues_time <- ck_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = ck_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean ck", hjust = 0.5,
       x = "Day of measurement",
       y = "ck u/l"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_ck_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ck_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_ck_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
ck_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = ck_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ck_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ck_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of ck for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ck (U/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ck_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ck_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ck_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ck_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- ck_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ck U/L",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- ck_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ck U/L",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- ck_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ck U/L",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_ck_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_ck_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ck_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##============================
## AP 
##============================
```{r}
ap_full <- all_data %>% 
  filter(panel_id == "ap")
ap_full
```


```{r}
ap_diabetic <- left_join(ap_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

ap_diabetic
```

### Based on Patient number ###


```{r}
liver_ap_full_diabetic_cases_labvalues <- ap_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean ap", hjust = 0.5,
       x = "Patients",
       y = "ap u/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ap_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_ap_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
ap_diabetic2 <- ap_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

ap_diabetic2_counts <- ap_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
ap_diabetic2_counts$attribute <-  factor(ap_diabetic2_counts$attribute, 
                                   levels = c( "AP Day1", "AP Day2", "AP Day3","AP Day4","AP Day5", "AP Day6","AP Day7","AP Day8","AP Day9","AP Day10", "AP Day11","AP Day12","AP Day13","AP Day14","AP Day15","AP Day16","AP Day17","AP Day18","AP Day19","AP Day20","AP Day21","AP Day22","AP Day23","AP Day24","AP Day25","AP Day26","AP Day27","AP Day28","AP Day29","AP Day30","AP Day31","AP Day32","AP Day33","AP Day34","AP Day35","AP Day36","AP Day37","AP Day38","AP Day39","AP Day40","AP Day41","AP Day42","AP Day43","AP Day44","AP Day45","AP Day46","AP Day47","AP Day48","AP Day49","AP Day50","AP Day51","AP Day52","AP Day53","AP Day54","AP Day55","AP Day56","AP Day57","AP Day58","AP Day59","AP Day60","AP Day61","AP Day62","AP Day63","AP Day64","AP Day65","AP Day66","AP Day67","AP Day68","AP Day69","AP Day70","AP Day71","AP Day72","AP Day73","AP Day74","AP Day75","AP Day76","AP Day77","AP Day78","AP Day79","AP Day80","AP Day81","AP Day82","AP Day83","AP Day84","AP Day85","AP Day86","AP Day87","AP Day88","AP Day89","AP Day90","AP Day91","AP Day92","AP Day93","AP Day94","AP Day95","AP Day96","AP Day97","AP Day98","AP Day99","AP Day100"))
liver_ap_full_diabetic_cases_labvalues_time <- ap_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = ap_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean ap", hjust = 0.5,
       x = "Day of measurement",
       y = "ap u/l"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_ap_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ap_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_ap_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
ap_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = ap_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ap_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ap_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of ap for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ap (U/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ap_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ap_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ap_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ap_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- ap_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ap U/L",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- ap_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ap U/L",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- ap_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ap U/L",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_ap_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_ap_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ap_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##=======================
## ptt 
##=======================

```{r}
ptt_full <- all_data %>% 
  filter(panel_id == "ptt")
ptt_full
```



```{r}
ptt_diabetic <- left_join(ptt_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes)

ptt_diabetic
```

### Based on Patient number ###


```{r}
liver_ptt_full_diabetic_cases_labvalues <- ptt_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean ptt", hjust = 0.5,
       x = "Patients",
       y = "ptt sec.")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ptt_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_ptt_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
ptt_diabetic2 <- ptt_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

ptt_diabetic2_counts <- ptt_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
ptt_diabetic2_counts$attribute <-  factor(ptt_diabetic2_counts$attribute, 
                                   levels = c( "ptt Day1", "ptt Day2", "ptt Day3","ptt Day4","ptt Day5", "ptt Day6","ptt Day7","ptt Day8","ptt Day9","ptt Day10", "ptt Day11","ptt Day12","ptt Day13","ptt Day14","ptt Day15","ptt Day16","ptt Day17","ptt Day18","ptt Day19","ptt Day20","ptt Day21","ptt Day22","ptt Day23","ptt Day24","ptt Day25","ptt Day26","ptt Day27","ptt Day28","ptt Day29","ptt Day30","ptt Day31","ptt Day32","ptt Day33","ptt Day34","ptt Day35","ptt Day36","ptt Day37","ptt Day38","ptt Day39","ptt Day40","ptt Day41","ptt Day42","ptt Day43","ptt Day44","ptt Day45","ptt Day46","ptt Day47","ptt Day48","ptt Day49","ptt Day50","ptt Day51","ptt Day52","ptt Day53","ptt Day54","ptt Day55","ptt Day56","ptt Day57","ptt Day58","ptt Day59","ptt Day60","ptt Day61","ptt Day62","ptt Day63","ptt Day64","ptt Day65","ptt Day66","ptt Day67","ptt Day68","ptt Day69","ptt Day70","ptt Day71","ptt Day72","ptt Day73","ptt Day74","ptt Day75","ptt Day76","ptt Day77","ptt Day78","ptt Day79","ptt Day80","ptt Day81","ptt Day82","ptt Day83","ptt Day84","ptt Day85","ptt Day86","ptt Day87","ptt Day88","ptt Day89","ptt Day90","ptt Day91","ptt Day92","ptt Day93","ptt Day94","ptt Day95","ptt Day96","ptt Day97","ptt Day98","ptt Day99","ptt Day100"))
liver_ptt_full_diabetic_cases_labvalues_time <- ptt_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = ptt_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean ptt", hjust = 0.5,
       x = "Day of measurement",
       y = "ptt sec."
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_ptt_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ptt_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_ptt_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
ptt_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = ptt_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ptt_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ptt_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of ptt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ptt (sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ptt_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ptt_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_ptt_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ptt_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- ptt_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ptt sec.",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- ptt_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ptt sec.",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- ptt_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "ptt sec.",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_ptt_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_ptt_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ptt_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##===================
## Leukozyten 
##===================

```{r}
leukozyten_full <- all_data %>% 
  filter(panel_id == "leukozyten")
leukozyten_full
```

```{r}
Leukozyten_diabetic <- left_join(leukozyten_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

Leukozyten_diabetic
```

### Based on Patient number ###


```{r}
liver_Leukozyten_full_diabetic_cases_labvalues <- Leukozyten_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean Leukozyten", hjust = 0.5,
       x = "Patients",
       y = "Leukozyten cells/ul")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Leukozyten_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_Leukozyten_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
Leukozyten_diabetic2 <- Leukozyten_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

Leukozyten_diabetic2_counts <- Leukozyten_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
Leukozyten_diabetic2_counts$attribute <-  factor(Leukozyten_diabetic2_counts$attribute, 
                                   levels = c( "Leukozyten Day1", "Leukozyten Day2", "Leukozyten Day3","Leukozyten Day4","Leukozyten Day5", "Leukozyten Day6","Leukozyten Day7","Leukozyten Day8","Leukozyten Day9","Leukozyten Day10", "Leukozyten Day11","Leukozyten Day12","Leukozyten Day13","Leukozyten Day14","Leukozyten Day15","Leukozyten Day16","Leukozyten Day17","Leukozyten Day18","Leukozyten Day19","Leukozyten Day20","Leukozyten Day21","Leukozyten Day22","Leukozyten Day23","Leukozyten Day24","Leukozyten Day25","Leukozyten Day26","Leukozyten Day27","Leukozyten Day28","Leukozyten Day29","Leukozyten Day30","Leukozyten Day31","Leukozyten Day32","Leukozyten Day33","Leukozyten Day34","Leukozyten Day35","Leukozyten Day36","Leukozyten Day37","Leukozyten Day38","Leukozyten Day39","Leukozyten Day40","Leukozyten Day41","Leukozyten Day42","Leukozyten Day43","Leukozyten Day44","Leukozyten Day45","Leukozyten Day46","Leukozyten Day47","Leukozyten Day48","Leukozyten Day49","Leukozyten Day50","Leukozyten Day51","Leukozyten Day52","Leukozyten Day53","Leukozyten Day54","Leukozyten Day55","Leukozyten Day56","Leukozyten Day57","Leukozyten Day58","Leukozyten Day59","Leukozyten Day60","Leukozyten Day61","Leukozyten Day62","Leukozyten Day63","Leukozyten Day64","Leukozyten Day65","Leukozyten Day66","Leukozyten Day67","Leukozyten Day68","Leukozyten Day69","Leukozyten Day70","Leukozyten Day71","Leukozyten Day72","Leukozyten Day73","Leukozyten Day74","Leukozyten Day75","Leukozyten Day76","Leukozyten Day77","Leukozyten Day78","Leukozyten Day79","Leukozyten Day80","Leukozyten Day81","Leukozyten Day82","Leukozyten Day83","Leukozyten Day84","Leukozyten Day85","Leukozyten Day86","Leukozyten Day87","Leukozyten Day88","Leukozyten Day89","Leukozyten Day90","Leukozyten Day91","Leukozyten Day92","Leukozyten Day93","Leukozyten Day94","Leukozyten Day95","Leukozyten Day96","Leukozyten Day97","Leukozyten Day98","Leukozyten Day99","Leukozyten Day100"))
liver_Leukozyten_full_diabetic_cases_labvalues_time <- Leukozyten_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = Leukozyten_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean Leukozyten", hjust = 0.5,
       x = "Day of measurement",
       y = "Leukozyten cells/ul"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_Leukozyten_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Leukozyten_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_Leukozyten_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
Leukozyten_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = Leukozyten_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- Leukozyten_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = Leukozyten_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of Leukozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_Leukozyten_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(Leukozyten_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Leukozyten_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Leukozyten_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- Leukozyten_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Leukozyten cells/ul",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- Leukozyten_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Leukozyten cells/ul",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- Leukozyten_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Leukozyten cells/ul",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_Leukozyten_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_Leukozyten_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_Leukozyten_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##====================
## Erythrozyten 
##====================
```{r}
erythrozyten_full <- all_data %>% 
  filter(panel_id == "erythrozyten")
erythrozyten_full
```

```{r}
erythrozyten_diabetic <- left_join(erythrozyten_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes)

erythrozyten_diabetic
```

### Based on Patient number ###


```{r}
liver_Erythrozyten_full_diabetic_cases_labvalues <- Erythrozyten_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean Erythrozyten", hjust = 0.5,
       x = "Patients",
       y = "Erythrozyten cells/ul")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Erythrozyten_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_Erythrozyten_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
Erythrozyten_diabetic2 <- Erythrozyten_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

Erythrozyten_diabetic2_counts <- Erythrozyten_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
Erythrozyten_diabetic2_counts$attribute <-  factor(Erythrozyten_diabetic2_counts$attribute, 
                                   levels = c( "Erythrozyten Day1", "Erythrozyten Day2", "Erythrozyten Day3","Erythrozyten Day4","Erythrozyten Day5", "Erythrozyten Day6","Erythrozyten Day7","Erythrozyten Day8","Erythrozyten Day9","Erythrozyten Day10", "Erythrozyten Day11","Erythrozyten Day12","Erythrozyten Day13","Erythrozyten Day14","Erythrozyten Day15","Erythrozyten Day16","Erythrozyten Day17","Erythrozyten Day18","Erythrozyten Day19","Erythrozyten Day20","Erythrozyten Day21","Erythrozyten Day22","Erythrozyten Day23","Erythrozyten Day24","Erythrozyten Day25","Erythrozyten Day26","Erythrozyten Day27","Erythrozyten Day28","Erythrozyten Day29","Erythrozyten Day30","Erythrozyten Day31","Erythrozyten Day32","Erythrozyten Day33","Erythrozyten Day34","Erythrozyten Day35","Erythrozyten Day36","Erythrozyten Day37","Erythrozyten Day38","Erythrozyten Day39","Erythrozyten Day40","Erythrozyten Day41","Erythrozyten Day42","Erythrozyten Day43","Erythrozyten Day44","Erythrozyten Day45","Erythrozyten Day46","Erythrozyten Day47","Erythrozyten Day48","Erythrozyten Day49","Erythrozyten Day50","Erythrozyten Day51","Erythrozyten Day52","Erythrozyten Day53","Erythrozyten Day54","Erythrozyten Day55","Erythrozyten Day56","Erythrozyten Day57","Erythrozyten Day58","Erythrozyten Day59","Erythrozyten Day60","Erythrozyten Day61","Erythrozyten Day62","Erythrozyten Day63","Erythrozyten Day64","Erythrozyten Day65","Erythrozyten Day66","Erythrozyten Day67","Erythrozyten Day68","Erythrozyten Day69","Erythrozyten Day70","Erythrozyten Day71","Erythrozyten Day72","Erythrozyten Day73","Erythrozyten Day74","Erythrozyten Day75","Erythrozyten Day76","Erythrozyten Day77","Erythrozyten Day78","Erythrozyten Day79","Erythrozyten Day80","Erythrozyten Day81","Erythrozyten Day82","Erythrozyten Day83","Erythrozyten Day84","Erythrozyten Day85","Erythrozyten Day86","Erythrozyten Day87","Erythrozyten Day88","Erythrozyten Day89","Erythrozyten Day90","Erythrozyten Day91","Erythrozyten Day92","Erythrozyten Day93","Erythrozyten Day94","Erythrozyten Day95","Erythrozyten Day96","Erythrozyten Day97","Erythrozyten Day98","Erythrozyten Day99","Erythrozyten Day100"))
liver_Erythrozyten_full_diabetic_cases_labvalues_time <- Erythrozyten_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = Erythrozyten_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean Erythrozyten", hjust = 0.5,
       x = "Day of measurement",
       y = "Erythrozyten cells/ul"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_Erythrozyten_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Erythrozyten_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_Erythrozyten_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
Erythrozyten_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = Erythrozyten_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- Erythrozyten_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = Erythrozyten_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of Erythrozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_Erythrozyten_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(Erythrozyten_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Erythrozyten_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Erythrozyten_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- Erythrozyten_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Erythrozyten cells/ul",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- Erythrozyten_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Erythrozyten cells/ul",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- Erythrozyten_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Erythrozyten cells/ul",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_Erythrozyten_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_Erythrozyten_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_Erythrozyten_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##================
## Thrombozyten 
##================

```{r}
thrombozyten_full <- all_data %>% 
  filter(panel_id == "thrombozyten")
thrombozyten_full
```

```{r}
Thrombozyten_diabetic <- left_join(thrombozyten_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes)

Thrombozyten_diabetic
```

### Based on Patient number ###


```{r}
liver_Thrombozyten_full_diabetic_cases_labvalues <- Thrombozyten_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean Thrombozyten", hjust = 0.5,
       x = "Patients",
       y = "Thrombozyten cells/ul")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Thrombozyten_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_Thrombozyten_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
Thrombozyten_diabetic2 <- Thrombozyten_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

Thrombozyten_diabetic2_counts <- Thrombozyten_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
Thrombozyten_diabetic2_counts$attribute <-  factor(Thrombozyten_diabetic2_counts$attribute, 
                                   levels = c( "Thrombozyten Day1", "Thrombozyten Day2", "Thrombozyten Day3","Thrombozyten Day4","Thrombozyten Day5", "Thrombozyten Day6","Thrombozyten Day7","Thrombozyten Day8","Thrombozyten Day9","Thrombozyten Day10", "Thrombozyten Day11","Thrombozyten Day12","Thrombozyten Day13","Thrombozyten Day14","Thrombozyten Day15","Thrombozyten Day16","Thrombozyten Day17","Thrombozyten Day18","Thrombozyten Day19","Thrombozyten Day20","Thrombozyten Day21","Thrombozyten Day22","Thrombozyten Day23","Thrombozyten Day24","Thrombozyten Day25","Thrombozyten Day26","Thrombozyten Day27","Thrombozyten Day28","Thrombozyten Day29","Thrombozyten Day30","Thrombozyten Day31","Thrombozyten Day32","Thrombozyten Day33","Thrombozyten Day34","Thrombozyten Day35","Thrombozyten Day36","Thrombozyten Day37","Thrombozyten Day38","Thrombozyten Day39","Thrombozyten Day40","Thrombozyten Day41","Thrombozyten Day42","Thrombozyten Day43","Thrombozyten Day44","Thrombozyten Day45","Thrombozyten Day46","Thrombozyten Day47","Thrombozyten Day48","Thrombozyten Day49","Thrombozyten Day50","Thrombozyten Day51","Thrombozyten Day52","Thrombozyten Day53","Thrombozyten Day54","Thrombozyten Day55","Thrombozyten Day56","Thrombozyten Day57","Thrombozyten Day58","Thrombozyten Day59","Thrombozyten Day60","Thrombozyten Day61","Thrombozyten Day62","Thrombozyten Day63","Thrombozyten Day64","Thrombozyten Day65","Thrombozyten Day66","Thrombozyten Day67","Thrombozyten Day68","Thrombozyten Day69","Thrombozyten Day70","Thrombozyten Day71","Thrombozyten Day72","Thrombozyten Day73","Thrombozyten Day74","Thrombozyten Day75","Thrombozyten Day76","Thrombozyten Day77","Thrombozyten Day78","Thrombozyten Day79","Thrombozyten Day80","Thrombozyten Day81","Thrombozyten Day82","Thrombozyten Day83","Thrombozyten Day84","Thrombozyten Day85","Thrombozyten Day86","Thrombozyten Day87","Thrombozyten Day88","Thrombozyten Day89","Thrombozyten Day90","Thrombozyten Day91","Thrombozyten Day92","Thrombozyten Day93","Thrombozyten Day94","Thrombozyten Day95","Thrombozyten Day96","Thrombozyten Day97","Thrombozyten Day98","Thrombozyten Day99","Thrombozyten Day100"))
liver_Thrombozyten_full_diabetic_cases_labvalues_time <- Thrombozyten_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = Thrombozyten_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean Thrombozyten", hjust = 0.5,
       x = "Day of measurement",
       y = "Thrombozyten cells/ul"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_Thrombozyten_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Thrombozyten_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_Thrombozyten_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
Thrombozyten_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = Thrombozyten_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- Thrombozyten_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = Thrombozyten_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of Thrombozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_Thrombozyten_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(Thrombozyten_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Thrombozyten_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Thrombozyten_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- Thrombozyten_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  filter(!grepl("_1|_2|_3|_4|_d", attribute)) %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Thrombozyten cells/ul",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- Thrombozyten_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Thrombozyten cells/ul",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- Thrombozyten_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Thrombozyten cells/ul",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_Thrombozyten_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_Thrombozyten_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_Thrombozyten_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##============================
## hb 
##============================

```{r}
hb_full <- all_data %>% 
  filter(panel_id == "hb")
hb_full
```
```{r}
hb_diabetic <- left_join(hb_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

hb_diabetic
```

### Based on Patient number ###


```{r}
liver_hb_full_diabetic_cases_labvalues <- hb_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean hb", hjust = 0.5,
       x = "Patients",
       y = "hb g/dl")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_hb_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_hb_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
hb_diabetic2 <- hb_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

hb_diabetic2_counts <- hb_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
hb_diabetic2_counts$attribute <-  factor(hb_diabetic2_counts$attribute, 
                                   levels = c( "HB Day1", "HB Day2", "HB Day3","HB Day4","HB Day5", "HB Day6","HB Day7","HB Day8","HB Day9","HB Day10", "HB Day11","HB Day12","HB Day13","HB Day14","HB Day15","HB Day16","HB Day17","HB Day18","HB Day19","HB Day20","HB Day21","HB Day22","HB Day23","HB Day24","HB Day25","HB Day26","HB Day27","HB Day28","HB Day29","HB Day30","HB Day31","HB Day32","HB Day33","HB Day34","HB Day35","HB Day36","HB Day37","HB Day38","HB Day39","HB Day40","HB Day41","HB Day42","HB Day43","HB Day44","HB Day45","HB Day46","HB Day47","HB Day48","HB Day49","HB Day50","HB Day51","HB Day52","HB Day53","HB Day54","HB Day55","HB Day56","HB Day57","HB Day58","HB Day59","HB Day60","HB Day61","HB Day62","HB Day63","HB Day64","HB Day65","HB Day66","HB Day67","HB Day68","HB Day69","HB Day70","HB Day71","HB Day72","HB Day73","HB Day74","HB Day75","HB Day76","HB Day77","HB Day78","HB Day79","HB Day80","HB Day81","HB Day82","HB Day83","HB Day84","HB Day85","HB Day86","HB Day87","HB Day88","HB Day89","HB Day90","HB Day91","HB Day92","HB Day93","HB Day94","HB Day95","HB Day96","HB Day97","HB Day98","HB Day99","HB Day100"))
liver_hb_full_diabetic_cases_labvalues_time <- hb_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = hb_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean hb", hjust = 0.5,
       x = "Day of measurement",
       y = "hb g/dl"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_hb_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_hb_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_hb_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
hb_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = hb_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hb_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hb_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of hb for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_hb_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(hb_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_hb_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hb_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- hb_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "hb g/dl",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- hb_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "hb g/dl",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- hb_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "hb g/dl",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_hb_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_hb_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_hb_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##=========================
## Gesamteiweiß or eggwhite
##=========================

```{r}
gesamteiweiß_full <- all_data %>% 
  filter(panel_id == "gesamteiweiss")
gesamteiweiß_full
```
```{r}
gesamteiweiß_diabetic <- left_join(gesamteiweiß_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

gesamteiweiß_diabetic
```

### Based on Patient number ###


```{r}
liver_Gesamteiweiß_full_diabetic_cases_labvalues <- Gesamteiweiß_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean Gesamteiweiß", hjust = 0.5,
       x = "Patients",
       y = "Gesamteiweiß g/dl")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Gesamteiweiß_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_Gesamteiweiß_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
Gesamteiweiß_diabetic2 <- Gesamteiweiß_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

Gesamteiweiß_diabetic2_counts <- Gesamteiweiß_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
Gesamteiweiß_diabetic2_counts$attribute <-  factor(Gesamteiweiß_diabetic2_counts$attribute, 
                                   levels = c( "Gesamteiweiß Day1", "Gesamteiweiß Day2", "Gesamteiweiß Day3","Gesamteiweiß Day4","Gesamteiweiß Day5", "Gesamteiweiß Day6","Gesamteiweiß Day7","Gesamteiweiß Day8","Gesamteiweiß Day9","Gesamteiweiß Day10", "Gesamteiweiß Day11","Gesamteiweiß Day12","Gesamteiweiß Day13","Gesamteiweiß Day14","Gesamteiweiß Day15","Gesamteiweiß Day16","Gesamteiweiß Day17","Gesamteiweiß Day18","Gesamteiweiß Day19","Gesamteiweiß Day20","Gesamteiweiß Day21","Gesamteiweiß Day22","Gesamteiweiß Day23","Gesamteiweiß Day24","Gesamteiweiß Day25","Gesamteiweiß Day26","Gesamteiweiß Day27","Gesamteiweiß Day28","Gesamteiweiß Day29","Gesamteiweiß Day30","Gesamteiweiß Day31","Gesamteiweiß Day32","Gesamteiweiß Day33","Gesamteiweiß Day34","Gesamteiweiß Day35","Gesamteiweiß Day36","Gesamteiweiß Day37","Gesamteiweiß Day38","Gesamteiweiß Day39","Gesamteiweiß Day40","Gesamteiweiß Day41","Gesamteiweiß Day42","Gesamteiweiß Day43","Gesamteiweiß Day44","Gesamteiweiß Day45","Gesamteiweiß Day46","Gesamteiweiß Day47","Gesamteiweiß Day48","Gesamteiweiß Day49","Gesamteiweiß Day50","Gesamteiweiß Day51","Gesamteiweiß Day52","Gesamteiweiß Day53","Gesamteiweiß Day54","Gesamteiweiß Day55","Gesamteiweiß Day56","Gesamteiweiß Day57","Gesamteiweiß Day58","Gesamteiweiß Day59","Gesamteiweiß Day60","Gesamteiweiß Day61","Gesamteiweiß Day62","Gesamteiweiß Day63","Gesamteiweiß Day64","Gesamteiweiß Day65","Gesamteiweiß Day66","Gesamteiweiß Day67","Gesamteiweiß Day68","Gesamteiweiß Day69","Gesamteiweiß Day70","Gesamteiweiß Day71","Gesamteiweiß Day72","Gesamteiweiß Day73","Gesamteiweiß Day74","Gesamteiweiß Day75","Gesamteiweiß Day76","Gesamteiweiß Day77","Gesamteiweiß Day78","Gesamteiweiß Day79","Gesamteiweiß Day80","Gesamteiweiß Day81","Gesamteiweiß Day82","Gesamteiweiß Day83","Gesamteiweiß Day84","Gesamteiweiß Day85","Gesamteiweiß Day86","Gesamteiweiß Day87","Gesamteiweiß Day88","Gesamteiweiß Day89","Gesamteiweiß Day90","Gesamteiweiß Day91","Gesamteiweiß Day92","Gesamteiweiß Day93","Gesamteiweiß Day94","Gesamteiweiß Day95","Gesamteiweiß Day96","Gesamteiweiß Day97","Gesamteiweiß Day98","Gesamteiweiß Day99","Gesamteiweiß Day100"))
liver_Gesamteiweiß_full_diabetic_cases_labvalues_time <- Gesamteiweiß_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = Gesamteiweiß_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean Gesamteiweiß", hjust = 0.5,
       x = "Day of measurement",
       y = "Gesamteiweiß g/dl"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_Gesamteiweiß_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Gesamteiweiß_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_Gesamteiweiß_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
Gesamteiweiß_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = Gesamteiweiß_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- Gesamteiweiß_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = Gesamteiweiß_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of Gesamteiweiß for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_Gesamteiweiß_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(Gesamteiweiß_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_Gesamteiweiß_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Gesamteiweiß_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- Gesamteiweiß_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Gesamteiweiß g/dl",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- Gesamteiweiß_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Gesamteiweiß g/dl",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- Gesamteiweiß_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  filter(!grepl("_1|_2|_3|_4|_d", attribute)) %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "Gesamteiweiß g/dl",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_Gesamteiweiß_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_Gesamteiweiß_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_Gesamteiweiß_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##==========================
## total_bilirubin 
##==========================



```{r}
total_bilirubin_diabetic <- left_join(total_bilirubin_full, diabetic_data, c = "Edited_BfArM Nummer2") %>% 
  drop_na() %>% 
 # filter(Diabetes == "Diabetic") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  group_by(Diabetes) 

total_bilirubin_diabetic
```

### Based on Patient number ###


```{r}
liver_total_bilirubin_full_diabetic_cases_labvalues <- total_bilirubin_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean total_bilirubin", hjust = 0.5,
       x = "Patients",
       y = "total_bilirubin mg/dl")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_total_bilirubin_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_total_bilirubin_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
total_bilirubin_diabetic2 <- total_bilirubin_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

total_bilirubin_diabetic2_counts <- total_bilirubin_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
total_bilirubin_diabetic2_counts$attribute <-  factor(total_bilirubin_diabetic2_counts$attribute, 
                                   levels = c( "TotalBilirubin Day1", "TotalBilirubin Day2", "TotalBilirubin Day3", "TotalBilirubin Day4", "TotalBilirubin Day5", "TotalBilirubin Day6", "TotalBilirubin Day7", "TotalBilirubin Day8", "TotalBilirubin Day9", 
"TotalBilirubin Day10", "TotalBilirubin Day11","TotalBilirubin Day12","TotalBilirubin Day13","TotalBilirubin Day14","TotalBilirubin Day15","TotalBilirubin Day16","TotalBilirubin Day17","TotalBilirubin Day18","TotalBilirubin Day19","TotalBilirubin Day20","TotalBilirubin Day21","TotalBilirubin Day22","TotalBilirubin Day23","TotalBilirubin Day24","TotalBilirubin Day25","TotalBilirubin Day26","TotalBilirubin Day27","TotalBilirubin Day28","TotalBilirubin Day29","TotalBilirubin Day30","TotalBilirubin Day31","TotalBilirubin Day32","TotalBilirubin Day33","TotalBilirubin Day34","TotalBilirubin Day35","TotalBilirubin Day36","TotalBilirubin Day37","TotalBilirubin Day38","TotalBilirubin Day39","TotalBilirubin Day40","TotalBilirubin Day41","TotalBilirubin Day42","TotalBilirubin Day43","TotalBilirubin Day44","TotalBilirubin Day45","TotalBilirubin Day46","TotalBilirubin Day47","TotalBilirubin Day48","TotalBilirubin Day49","TotalBilirubin Day50","TotalBilirubin Day51","TotalBilirubin Day52","TotalBilirubin Day53","TotalBilirubin Day54","TotalBilirubin Day55","TotalBilirubin Day56","TotalBilirubin Day57","TotalBilirubin Day58","TotalBilirubin Day59","TotalBilirubin Day60","TotalBilirubin Day61", "TotalBilirubin Day62","TotalBilirubin Day63","TotalBilirubin Day64","TotalBilirubin Day65","TotalBilirubin Day66","TotalBilirubin Day67","TotalBilirubin Day68","TotalBilirubin Day69","TotalBilirubin Day70","TotalBilirubin Day71","TotalBilirubin Day72","TotalBilirubin Day73","TotalBilirubin Day74","TotalBilirubin Day75","TotalBilirubin Day76","TotalBilirubin Day77","TotalBilirubin Day78","TotalBilirubin Day79","TotalBilirubin Day80","TotalBilirubin Day81","TotalBilirubin Day82","TotalBilirubin Day83","TotalBilirubin Day84","TotalBilirubin Day85","TotalBilirubin Day86","TotalBilirubin Day87","TotalBilirubin Day88","TotalBilirubin Day89","TotalBilirubin Day90","TotalBilirubin Day91","TotalBilirubin Day92","TotalBilirubin Day93","TotalBilirubin Day94","TotalBilirubin Day95","TotalBilirubin Day96","TotalBilirubin Day97","TotalBilirubin Day98","TotalBilirubin Day99","TotalBilirubin Day100"
))
liver_total_bilirubin_full_diabetic_cases_labvalues_time <- total_bilirubin_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = total_bilirubin_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean total_bilirubin", hjust = 0.5,
       x = "Day of measurement",
       y = "total_bilirubin mg/dl"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_total_bilirubin_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_total_bilirubin_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_total_bilirubin_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
total_bilirubin_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = total_bilirubin_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- total_bilirubin_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = total_bilirubin_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of total_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_total_bilirubin_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(total_bilirubin_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_total_bilirubin_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- total_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "total_bilirubin mg/dl",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- total_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "total_bilirubin mg/dl",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- total_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "total_bilirubin mg/dl",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_total_bilirubin_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_total_bilirubin_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_total_bilirubin_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##===================================
## direct_bilirubin 
##=========================================


```{r}
direct_bilirubin_diabetic <- left_join(direct_bilirubin_full, diabetic_data, c = "Edited_BfArM Nummer2") %>% 
  drop_na() %>% 
 # filter(Diabetes == "Diabetic") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  group_by(Diabetes) 

direct_bilirubin_diabetic
```

### Based on Patient number ###


```{r}
liver_direct_bilirubin_full_diabetic_cases_labvalues <- direct_bilirubin_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean direct_bilirubin", hjust = 0.5,
       x = "Patients",
       y = "direct_bilirubin mg/dl")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_direct_bilirubin_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_direct_bilirubin_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
direct_bilirubin_diabetic2 <- direct_bilirubin_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

direct_bilirubin_diabetic2_counts <- direct_bilirubin_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
direct_bilirubin_diabetic2_counts$attribute <-  factor(direct_bilirubin_diabetic2_counts$attribute, 
                                   levels = c( "DirectBilirubin Day1", "DirectBilirubin Day2", "DirectBilirubin Day3", "DirectBilirubin Day4", "DirectBilirubin Day5", "DirectBilirubin Day6", "DirectBilirubin Day7", "DirectBilirubin Day8", "DirectBilirubin Day9", 
"DirectBilirubin Day10", "DirectBilirubin Day11","DirectBilirubin Day12","DirectBilirubin Day13","DirectBilirubin Day14","DirectBilirubin Day15","DirectBilirubin Day16","DirectBilirubin Day17","DirectBilirubin Day18","DirectBilirubin Day19","DirectBilirubin Day20","DirectBilirubin Day21","DirectBilirubin Day22","DirectBilirubin Day23","DirectBilirubin Day24","DirectBilirubin Day25","DirectBilirubin Day26","DirectBilirubin Day27","DirectBilirubin Day28","DirectBilirubin Day29","DirectBilirubin Day30","DirectBilirubin Day31","DirectBilirubin Day32","DirectBilirubin Day33","DirectBilirubin Day34","DirectBilirubin Day35","DirectBilirubin Day36","DirectBilirubin Day37","DirectBilirubin Day38","DirectBilirubin Day39","DirectBilirubin Day40","DirectBilirubin Day41","DirectBilirubin Day42","DirectBilirubin Day43","DirectBilirubin Day44","DirectBilirubin Day45","DirectBilirubin Day46","DirectBilirubin Day47","DirectBilirubin Day48","DirectBilirubin Day49","DirectBilirubin Day50","DirectBilirubin Day51","DirectBilirubin Day52","DirectBilirubin Day53","DirectBilirubin Day54","DirectBilirubin Day55","DirectBilirubin Day56","DirectBilirubin Day57","DirectBilirubin Day58","DirectBilirubin Day59","DirectBilirubin Day60","DirectBilirubin Day61", "DirectBilirubin Day62","DirectBilirubin Day63","DirectBilirubin Day64","DirectBilirubin Day65","DirectBilirubin Day66","DirectBilirubin Day67","DirectBilirubin Day68","DirectBilirubin Day69","DirectBilirubin Day70","DirectBilirubin Day71","DirectBilirubin Day72","DirectBilirubin Day73","DirectBilirubin Day74","DirectBilirubin Day75","DirectBilirubin Day76","DirectBilirubin Day77","DirectBilirubin Day78","DirectBilirubin Day79","DirectBilirubin Day80","DirectBilirubin Day81","DirectBilirubin Day82","DirectBilirubin Day83","DirectBilirubin Day84","DirectBilirubin Day85","DirectBilirubin Day86","DirectBilirubin Day87","DirectBilirubin Day88","DirectBilirubin Day89","DirectBilirubin Day90","DirectBilirubin Day91","DirectBilirubin Day92","DirectBilirubin Day93","DirectBilirubin Day94","DirectBilirubin Day95","DirectBilirubin Day96","DirectBilirubin Day97","DirectBilirubin Day98","DirectBilirubin Day99","DirectBilirubin Day100"))
liver_direct_bilirubin_full_diabetic_cases_labvalues_time <- direct_bilirubin_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = direct_bilirubin_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean direct_bilirubin", hjust = 0.5,
       x = "Day of measurement",
       y = "direct_bilirubin mg/dl"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_direct_bilirubin_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_direct_bilirubin_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_direct_bilirubin_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
direct_bilirubin_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = direct_bilirubin_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- direct_bilirubin_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = direct_bilirubin_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of direct_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_direct_bilirubin_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(direct_bilirubin_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_direct_bilirubin_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- direct_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "direct_bilirubin mg/dl",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- direct_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "direct_bilirubin mg/dl",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- direct_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "direct_bilirubin mg/dl",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_direct_bilirubin_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_direct_bilirubin_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_direct_bilirubin_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##================================
## kreatinin 
##================================

```{r}
kreatinin_full <- all_data %>% 
  filter(panel_id == "kreatinin")
kreatinin_full
```
```{r}
kreatinin_diabetic <- left_join(kreatinin_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

kreatinin_diabetic
```


```{r}
kreatinin_diabetic <- left_join(kreatinin_full, diabetic_data, c = "Edited_BfArM Nummer2") %>% 
  drop_na() %>% 
 # filter(Diabetes == "Diabetic") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  group_by(Diabetes) 

kreatinin_diabetic
```

### Based on Patient number ###


```{r}
liver_kreatinin_full_diabetic_cases_labvalues <- kreatinin_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean kreatinin", hjust = 0.5,
       x = "Patients",
       y = "kreatinin mg/dl")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kreatinin_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_kreatinin_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
kreatinin_diabetic2 <- kreatinin_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

kreatinin_diabetic2_counts <- kreatinin_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
kreatinin_diabetic2_counts$attribute <-  factor(kreatinin_diabetic2_counts$attribute, 
                                   levels = c( "Kreatinin Day1", "Kreatinin Day2", "Kreatinin Day3","Kreatinin Day4","Kreatinin Day5", "Kreatinin Day6","Kreatinin Day7","Kreatinin Day8","Kreatinin Day9","Kreatinin Day10", "Kreatinin Day11","Kreatinin Day12","Kreatinin Day13","Kreatinin Day14","Kreatinin Day15","Kreatinin Day16","Kreatinin Day17","Kreatinin Day18","Kreatinin Day19","Kreatinin Day20","Kreatinin Day21","Kreatinin Day22","Kreatinin Day23","Kreatinin Day24","Kreatinin Day25","Kreatinin Day26","Kreatinin Day27","Kreatinin Day28","Kreatinin Day29","Kreatinin Day30","Kreatinin Day31","Kreatinin Day32","Kreatinin Day33","Kreatinin Day34","Kreatinin Day35","Kreatinin Day36","Kreatinin Day37","Kreatinin Day38","Kreatinin Day39","Kreatinin Day40","Kreatinin Day41","Kreatinin Day42","Kreatinin Day43","Kreatinin Day44","Kreatinin Day45","Kreatinin Day46","Kreatinin Day47","Kreatinin Day48","Kreatinin Day49","Kreatinin Day50","Kreatinin Day51","Kreatinin Day52","Kreatinin Day53","Kreatinin Day54","Kreatinin Day55","Kreatinin Day56","Kreatinin Day57","Kreatinin Day58","Kreatinin Day59","Kreatinin Day60","Kreatinin Day61","Kreatinin Day62","Kreatinin Day63","Kreatinin Day64","Kreatinin Day65","Kreatinin Day66","Kreatinin Day67","Kreatinin Day68","Kreatinin Day69","Kreatinin Day70","Kreatinin Day71","Kreatinin Day72","Kreatinin Day73","Kreatinin Day74","Kreatinin Day75","Kreatinin Day76","Kreatinin Day77","Kreatinin Day78","Kreatinin Day79","Kreatinin Day80","Kreatinin Day81","Kreatinin Day82","Kreatinin Day83","Kreatinin Day84","Kreatinin Day85","Kreatinin Day86","Kreatinin Day87","Kreatinin Day88","Kreatinin Day89","Kreatinin Day90","Kreatinin Day91","Kreatinin Day92","Kreatinin Day93","Kreatinin Day94","Kreatinin Day95","Kreatinin Day96","Kreatinin Day97","Kreatinin Day98","Kreatinin Day99","Kreatinin Day100"))
liver_kreatinin_full_diabetic_cases_labvalues_time <- kreatinin_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = kreatinin_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean kreatinin", hjust = 0.5,
       x = "Day of measurement",
       y = "kreatinin mg/dl"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_kreatinin_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kreatinin_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_kreatinin_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
kreatinin_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = kreatinin_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kreatinin_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kreatinin_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of kreatinin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kreatinin_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kreatinin_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kreatinin_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kreatinin_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- kreatinin_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kreatinin mg/dl",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- kreatinin_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kreatinin mg/dl",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- kreatinin_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kreatinin mg/dl",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_kreatinin_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_kreatinin_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_kreatinin_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##=====================
## harnstoff (Urea)
##=====================

```{r}
harnstoff_full <- all_data %>% 
  filter(panel_id == "harnstoff")
harnstoff_full
```
```{r}
harnstoff_diabetic <- left_join(harnstoff_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

harnstoff_diabetic
```


### Based on Patient number ###


```{r}
liver_harnstoff_full_diabetic_cases_labvalues <- harnstoff_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean harnstoff", hjust = 0.5,
       x = "Patients",
       y = "harnstoff mg/dl")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_harnstoff_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_harnstoff_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
harnstoff_diabetic2 <- harnstoff_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

harnstoff_diabetic2_counts <- harnstoff_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
harnstoff_diabetic2_counts$attribute <-  factor(harnstoff_diabetic2_counts$attribute, 
                                   levels = c(  "Harnstoff Day1", "Harnstoff Day2", "Harnstoff Day3","Harnstoff Day4","Harnstoff Day5", "Harnstoff Day6","Harnstoff Day7","Harnstoff Day8","Harnstoff Day9","Harnstoff Day10", "Harnstoff Day11","Harnstoff Day12","Harnstoff Day13","Harnstoff Day14","Harnstoff Day15","Harnstoff Day16","Harnstoff Day17","Harnstoff Day18","Harnstoff Day19","Harnstoff Day20","Harnstoff Day21","Harnstoff Day22","Harnstoff Day23","Harnstoff Day24","Harnstoff Day25","Harnstoff Day26","Harnstoff Day27","Harnstoff Day28","Harnstoff Day29","Harnstoff Day30","Harnstoff Day31","Harnstoff Day32","Harnstoff Day33","Harnstoff Day34","Harnstoff Day35","Harnstoff Day36","Harnstoff Day37","Harnstoff Day38","Harnstoff Day39","Harnstoff Day40","Harnstoff Day41","Harnstoff Day42","Harnstoff Day43","Harnstoff Day44","Harnstoff Day45","Harnstoff Day46","Harnstoff Day47","Harnstoff Day48","Harnstoff Day49","Harnstoff Day50","Harnstoff Day51","Harnstoff Day52","Harnstoff Day53","Harnstoff Day54","Harnstoff Day55","Harnstoff Day56","Harnstoff Day57","Harnstoff Day58","Harnstoff Day59","Harnstoff Day60","Harnstoff Day61","Harnstoff Day62","Harnstoff Day63","Harnstoff Day64","Harnstoff Day65","Harnstoff Day66","Harnstoff Day67","Harnstoff Day68","Harnstoff Day69","Harnstoff Day70","Harnstoff Day71","Harnstoff Day72","Harnstoff Day73","Harnstoff Day74","Harnstoff Day75","Harnstoff Day76","Harnstoff Day77","Harnstoff Day78","Harnstoff Day79","Harnstoff Day80","Harnstoff Day81","Harnstoff Day82","Harnstoff Day83","Harnstoff Day84","Harnstoff Day85","Harnstoff Day86","Harnstoff Day87","Harnstoff Day88","Harnstoff Day89","Harnstoff Day90","Harnstoff Day91","Harnstoff Day92","Harnstoff Day93","Harnstoff Day94","Harnstoff Day95","Harnstoff Day96","Harnstoff Day97","Harnstoff Day98","Harnstoff Day99","Harnstoff Day100"))
liver_harnstoff_full_diabetic_cases_labvalues_time <- harnstoff_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = harnstoff_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean harnstoff", hjust = 0.5,
       x = "Day of measurement",
       y = "harnstoff mg/dl"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_harnstoff_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_harnstoff_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_harnstoff_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
harnstoff_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = harnstoff_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- harnstoff_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = harnstoff_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of harnstoff for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_harnstoff_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(harnstoff_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_harnstoff_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_harnstoff_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- harnstoff_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "harnstoff mg/dl",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- harnstoff_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "harnstoff mg/dl",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- harnstoff_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "harnstoff mg/dl",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_harnstoff_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_harnstoff_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_harnstoff_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##===========================
## crp 
##==========================

```{r}
crp_full <- all_data %>% 
  filter(panel_id == "crp")
crp_full
```
```{r}
crp_diabetic <- left_join(crp_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

crp_diabetic
```


### Based on Patient number ###


```{r}
liver_crp_full_diabetic_cases_labvalues <- crp_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean crp", hjust = 0.5,
       x = "Patients",
       y = "crp mg/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_crp_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_crp_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
crp_diabetic2 <- crp_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

crp_diabetic2_counts <- crp_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
crp_diabetic2_counts$attribute <-  factor(crp_diabetic2_counts$attribute, 
                                   levels = c(  "CRP Day1", "CRP Day2", "CRP Day3","CRP Day4","CRP Day5", "CRP Day6","CRP Day7","CRP Day8","CRP Day9","CRP Day10", "CRP Day11","CRP Day12","CRP Day13","CRP Day14","CRP Day15","CRP Day16","CRP Day17","CRP Day18","CRP Day19","CRP Day20","CRP Day21","CRP Day22","CRP Day23","CRP Day24","CRP Day25","CRP Day26","CRP Day27","CRP Day28","CRP Day29","CRP Day30","CRP Day31","CRP Day32","CRP Day33","CRP Day34","CRP Day35","CRP Day36","CRP Day37","CRP Day38","CRP Day39","CRP Day40","CRP Day41","CRP Day42","CRP Day43","CRP Day44","CRP Day45","CRP Day46","CRP Day47","CRP Day48","CRP Day49","CRP Day50","CRP Day51","CRP Day52","CRP Day53","CRP Day54","CRP Day55","CRP Day56","CRP Day57","CRP Day58","CRP Day59","CRP Day60","CRP Day61","CRP Day62","CRP Day63","CRP Day64","CRP Day65","CRP Day66","CRP Day67","CRP Day68","CRP Day69","CRP Day70","CRP Day71","CRP Day72","CRP Day73","CRP Day74","CRP Day75","CRP Day76","CRP Day77","CRP Day78","CRP Day79","CRP Day80","CRP Day81","CRP Day82","CRP Day83","CRP Day84","CRP Day85","CRP Day86","CRP Day87","CRP Day88","CRP Day89","CRP Day90","CRP Day91","CRP Day92","CRP Day93","CRP Day94","CRP Day95","CRP Day96","CRP Day97","CRP Day98","CRP Day99","CRP Day100"))
liver_crp_full_diabetic_cases_labvalues_time <- crp_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = crp_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean crp", hjust = 0.5,
       x = "Day of measurement",
       y = "crp mg/l"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_crp_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_crp_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_crp_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
crp_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = crp_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- crp_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = crp_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of crp for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_crp_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(crp_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_crp_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_crp_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- crp_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "crp mg/l",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- crp_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "crp mg/l",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- crp_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "crp mg/l",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_crp_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_crp_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_crp_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##================================
## natrium 
##================================

```{r}
natrium_full <- all_data %>% 
  filter(panel_id == "natrium")
natrium_full
```

```{r}
natrium_diabetic <- left_join(natrium_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

natrium_diabetic
```

### Based on Patient number ###


```{r}
liver_natrium_full_diabetic_cases_labvalues <- natrium_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean natrium", hjust = 0.5,
       x = "Patients",
       y = "natrium mmol/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_natrium_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_natrium_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
natrium_diabetic2 <- natrium_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

natrium_diabetic2_counts <- natrium_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
natrium_diabetic2_counts$attribute <-  factor(natrium_diabetic2_counts$attribute, 
                                   levels = c( "Natrium Day1", "Natrium Day2", "Natrium Day3","Natrium Day4","Natrium Day5", "Natrium Day6","Natrium Day7","Natrium Day8","Natrium Day9","Natrium Day10", "Natrium Day11","Natrium Day12","Natrium Day13","Natrium Day14","Natrium Day15","Natrium Day16","Natrium Day17","Natrium Day18","Natrium Day19","Natrium Day20","Natrium Day21","Natrium Day22","Natrium Day23","Natrium Day24","Natrium Day25","Natrium Day26","Natrium Day27","Natrium Day28","Natrium Day29","Natrium Day30","Natrium Day31","Natrium Day32","Natrium Day33","Natrium Day34","Natrium Day35","Natrium Day36","Natrium Day37","Natrium Day38","Natrium Day39","Natrium Day40","Natrium Day41","Natrium Day42","Natrium Day43","Natrium Day44","Natrium Day45","Natrium Day46","Natrium Day47","Natrium Day48","Natrium Day49","Natrium Day50","Natrium Day51","Natrium Day52","Natrium Day53","Natrium Day54","Natrium Day55","Natrium Day56","Natrium Day57","Natrium Day58","Natrium Day59","Natrium Day60","Natrium Day61","Natrium Day62","Natrium Day63","Natrium Day64","Natrium Day65","Natrium Day66","Natrium Day67","Natrium Day68","Natrium Day69","Natrium Day70","Natrium Day71","Natrium Day72","Natrium Day73","Natrium Day74","Natrium Day75","Natrium Day76","Natrium Day77","Natrium Day78","Natrium Day79","Natrium Day80","Natrium Day81","Natrium Day82","Natrium Day83","Natrium Day84","Natrium Day85","Natrium Day86","Natrium Day87","Natrium Day88","Natrium Day89","Natrium Day90","Natrium Day91","Natrium Day92","Natrium Day93","Natrium Day94","Natrium Day95","Natrium Day96","Natrium Day97","Natrium Day98","Natrium Day99","Natrium Day100"))
liver_natrium_full_diabetic_cases_labvalues_time <- natrium_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = natrium_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean natrium", hjust = 0.5,
       x = "Day of measurement",
       y = "natrium mmol/l"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_natrium_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_natrium_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_natrium_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
natrium_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = natrium_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- natrium_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = natrium_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of natrium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_natrium_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(natrium_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_natrium_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_natrium_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- natrium_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  filter(!grepl("_1|_2|_3|_4|_d", attribute)) %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "natrium mmol/l",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- natrium_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "natrium mmol/l",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- natrium_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "natrium mmol/l",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_natrium_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_natrium_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_natrium_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##=========================
## kalium 
##===========================
```{r}
kalium_full <- all_data %>% 
  filter(panel_id == "kalium")
kalium_full
```

```{r}
kalium_diabetic <- left_join(natrium_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

kalium_diabetic
```


### Based on Patient number ###


```{r}
liver_kalium_full_diabetic_cases_labvalues <- kalium_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean kalium", hjust = 0.5,
       x = "Patients",
       y = "kalium mmol/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kalium_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_kalium_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
kalium_diabetic2 <- kalium_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

kalium_diabetic2_counts <- kalium_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
kalium_diabetic2_counts$attribute <-  factor(kalium_diabetic2_counts$attribute, 
                                   levels = c( "Kalium Day1", "Kalium Day2", "Kalium Day3","Kalium Day4","Kalium Day5", "Kalium Day6","Kalium Day7","Kalium Day8","Kalium Day9","Kalium Day10", "Kalium Day11","Kalium Day12","Kalium Day13","Kalium Day14","Kalium Day15","Kalium Day16","Kalium Day17","Kalium Day18","Kalium Day19","Kalium Day20","Kalium Day21","Kalium Day22","Kalium Day23","Kalium Day24","Kalium Day25","Kalium Day26","Kalium Day27","Kalium Day28","Kalium Day29","Kalium Day30","Kalium Day31","Kalium Day32","Kalium Day33","Kalium Day34","Kalium Day35","Kalium Day36","Kalium Day37","Kalium Day38","Kalium Day39","Kalium Day40","Kalium Day41","Kalium Day42","Kalium Day43","Kalium Day44","Kalium Day45","Kalium Day46","Kalium Day47","Kalium Day48","Kalium Day49","Kalium Day50","Kalium Day51","Kalium Day52","Kalium Day53","Kalium Day54","Kalium Day55","Kalium Day56","Kalium Day57","Kalium Day58","Kalium Day59","Kalium Day60","Kalium Day61","Kalium Day62","Kalium Day63","Kalium Day64","Kalium Day65","Kalium Day66","Kalium Day67","Kalium Day68","Kalium Day69","Kalium Day70","Kalium Day71","Kalium Day72","Kalium Day73","Kalium Day74","Kalium Day75","Kalium Day76","Kalium Day77","Kalium Day78","Kalium Day79","Kalium Day80","Kalium Day81","Kalium Day82","Kalium Day83","Kalium Day84","Kalium Day85","Kalium Day86","Kalium Day87","Kalium Day88","Kalium Day89","Kalium Day90","Kalium Day91","Kalium Day92","Kalium Day93","Kalium Day94","Kalium Day95","Kalium Day96","Kalium Day97","Kalium Day98","Kalium Day99","Kalium Day100"))
liver_kalium_full_diabetic_cases_labvalues_time <- kalium_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = kalium_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean kalium", hjust = 0.5,
       x = "Day of measurement",
       y = "kalium mmol/l"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_kalium_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kalium_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_kalium_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
kalium_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = kalium_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalium_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalium_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of kalium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kalium_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kalium_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kalium_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalium_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- kalium_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kalium mmol/l",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- kalium_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kalium mmol/l",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- kalium_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kalium mmol/l",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_kalium_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_kalium_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_kalium_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##===============================
## kalzium 
##================================
```{r}
kalzium_full <- all_data %>% 
  filter(panel_id == "kalzium")
kalzium_full
```

```{r}
kalzium_diabetic <- left_join(kalzium_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

kalzium_diabetic
```



### Based on Patient number ###


```{r}
liver_kalzium_full_diabetic_cases_labvalues <- kalzium_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean kalzium", hjust = 0.5,
       x = "Patients",
       y = "kalzium mmol/l")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kalzium_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_kalzium_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
kalzium_diabetic2 <- kalzium_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

kalzium_diabetic2_counts <- kalzium_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
kalzium_diabetic2_counts$attribute <-  factor(kalzium_diabetic2_counts$attribute, 
                                   levels = c( "Kalzium Day1", "Kalzium Day2", "Kalzium Day3","Kalzium Day4","Kalzium Day5", "Kalzium Day6","Kalzium Day7","Kalzium Day8","Kalzium Day9","Kalzium Day10", "Kalzium Day11","Kalzium Day12","Kalzium Day13","Kalzium Day14","Kalzium Day15","Kalzium Day16","Kalzium Day17","Kalzium Day18","Kalzium Day19","Kalzium Day20","Kalzium Day21","Kalzium Day22","Kalzium Day23","Kalzium Day24","Kalzium Day25","Kalzium Day26","Kalzium Day27","Kalzium Day28","Kalzium Day29","Kalzium Day30","Kalzium Day31","Kalzium Day32","Kalzium Day33","Kalzium Day34","Kalzium Day35","Kalzium Day36","Kalzium Day37","Kalzium Day38","Kalzium Day39","Kalzium Day40","Kalzium Day41","Kalzium Day42","Kalzium Day43","Kalzium Day44","Kalzium Day45","Kalzium Day46","Kalzium Day47","Kalzium Day48","Kalzium Day49","Kalzium Day50","Kalzium Day51","Kalzium Day52","Kalzium Day53","Kalzium Day54","Kalzium Day55","Kalzium Day56","Kalzium Day57","Kalzium Day58","Kalzium Day59","Kalzium Day60","Kalzium Day61","Kalzium Day62","Kalzium Day63","Kalzium Day64","Kalzium Day65","Kalzium Day66","Kalzium Day67","Kalzium Day68","Kalzium Day69","Kalzium Day70","Kalzium Day71","Kalzium Day72","Kalzium Day73","Kalzium Day74","Kalzium Day75","Kalzium Day76","Kalzium Day77","Kalzium Day78","Kalzium Day79","Kalzium Day80","Kalzium Day81","Kalzium Day82","Kalzium Day83","Kalzium Day84","Kalzium Day85","Kalzium Day86","Kalzium Day87","Kalzium Day88","Kalzium Day89","Kalzium Day90","Kalzium Day91","Kalzium Day92","Kalzium Day93","Kalzium Day94","Kalzium Day95","Kalzium Day96","Kalzium Day97","Kalzium Day98","Kalzium Day99","Kalzium Day100"))
liver_kalzium_full_diabetic_cases_labvalues_time <- kalzium_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = kalzium_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean kalzium", hjust = 0.5,
       x = "Day of measurement",
       y = "kalzium mmol/l"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_kalzium_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kalzium_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_kalzium_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
kalzium_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = kalzium_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalzium_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalzium_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of kalzium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kalzium_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kalzium_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_kalzium_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalzium_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- kalzium_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kalzium mmol/l",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- kalzium_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kalzium mmol/l",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- kalzium_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "kalzium mmol/l",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_kalzium_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_kalzium_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_kalzium_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```

##====================================
## hämatokrit 
##====================================


```{r}
hämatokrit_diabetic <- left_join(hämatokrit_full, diabetic_data, c = "Edited_BfArM Nummer2") %>% 
  drop_na() %>% 
 # filter(Diabetes == "Diabetic") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  group_by(Diabetes) 

hämatokrit_diabetic
```

### Based on Patient number ###


```{r}
liver_hämatokrit_full_diabetic_cases_labvalues <- hämatokrit_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean hämatokrit", hjust = 0.5,
       x = "Patients",
       y = "hämatokrit %")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_hämatokrit_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_hämatokrit_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
hämatokrit_diabetic2 <- hämatokrit_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

hämatokrit_diabetic2_counts <- hämatokrit_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
hämatokrit_diabetic2_counts$attribute <-  factor(hämatokrit_diabetic2_counts$attribute, 
                                   levels = c(  "Hämatokrit Day1", "Hämatokrit Day2", "Hämatokrit Day3","Hämatokrit Day4","Hämatokrit Day5", "Hämatokrit Day6","Hämatokrit Day7","Hämatokrit Day8","Hämatokrit Day9","Hämatokrit Day10", "Hämatokrit Day11","Hämatokrit Day12","Hämatokrit Day13","Hämatokrit Day14","Hämatokrit Day15","Hämatokrit Day16","Hämatokrit Day17","Hämatokrit Day18","Hämatokrit Day19","Hämatokrit Day20","Hämatokrit Day21","Hämatokrit Day22","Hämatokrit Day23","Hämatokrit Day24","Hämatokrit Day25","Hämatokrit Day26","Hämatokrit Day27","Hämatokrit Day28","Hämatokrit Day29","Hämatokrit Day30","Hämatokrit Day31","Hämatokrit Day32","Hämatokrit Day33","Hämatokrit Day34","Hämatokrit Day35","Hämatokrit Day36","Hämatokrit Day37","Hämatokrit Day38","Hämatokrit Day39","Hämatokrit Day40","Hämatokrit Day41","Hämatokrit Day42","Hämatokrit Day43","Hämatokrit Day44","Hämatokrit Day45","Hämatokrit Day46","Hämatokrit Day47","Hämatokrit Day48","Hämatokrit Day49","Hämatokrit Day50","Hämatokrit Day51","Hämatokrit Day52","Hämatokrit Day53","Hämatokrit Day54","Hämatokrit Day55","Hämatokrit Day56","Hämatokrit Day57","Hämatokrit Day58","Hämatokrit Day59","Hämatokrit Day60","Hämatokrit Day61","Hämatokrit Day62","Hämatokrit Day63","Hämatokrit Day64","Hämatokrit Day65","Hämatokrit Day66","Hämatokrit Day67","Hämatokrit Day68","Hämatokrit Day69","Hämatokrit Day70","Hämatokrit Day71","Hämatokrit Day72","Hämatokrit Day73","Hämatokrit Day74","Hämatokrit Day75","Hämatokrit Day76","Hämatokrit Day77","Hämatokrit Day78","Hämatokrit Day79","Hämatokrit Day80","Hämatokrit Day81","Hämatokrit Day82","Hämatokrit Day83","Hämatokrit Day84","Hämatokrit Day85","Hämatokrit Day86","Hämatokrit Day87","Hämatokrit Day88","Hämatokrit Day89","Hämatokrit Day90","Hämatokrit Day91","Hämatokrit Day92","Hämatokrit Day93","Hämatokrit Day94","Hämatokrit Day95","Hämatokrit Day96","Hämatokrit Day97","Hämatokrit Day98","Hämatokrit Day99","Hämatokrit Day100"))
liver_hämatokrit_full_diabetic_cases_labvalues_time <- hämatokrit_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = hämatokrit_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean hämatokrit", hjust = 0.5,
       x = "Day of measurement",
       y = "hämatokrit %"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_hämatokrit_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_hämatokrit_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_hämatokrit_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
hämatokrit_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = hämatokrit_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hämatokrit_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hämatokrit_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of hämatokrit for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_hämatokrit_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(hämatokrit_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_hämatokrit_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hämatokrit_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- hämatokrit_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "hämatokrit %",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- hämatokrit_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "hämatokrit %",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- hämatokrit_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "hämatokrit %",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_hämatokrit_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_hämatokrit_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_hämatokrit_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##===============================
## quick 
##===============================

```{r}
quick_full <- all_data %>% 
  filter(panel_id == "quick")
quick_full
```

```{r}
quick_diabetic <- left_join(quick_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

quick_diabetic
```



### Based on Patient number ###


```{r}
liver_quick_full_diabetic_cases_labvalues <- quick_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean quick", hjust = 0.5,
       x = "Patients",
       y = "quick %")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_quick_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_quick_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
quick_diabetic2 <- quick_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

quick_diabetic2_counts <- quick_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
quick_diabetic2_counts$attribute <-  factor(quick_diabetic2_counts$attribute, 
                                   levels = c(  "Quick Day1", "Quick Day2", "Quick Day3","Quick Day4","Quick Day5", "Quick Day6","Quick Day7","Quick Day8","Quick Day9","Quick Day10", "Quick Day11","Quick Day12","Quick Day13","Quick Day14","Quick Day15","Quick Day16","Quick Day17","Quick Day18","Quick Day19","Quick Day20","Quick Day21","Quick Day22","Quick Day23","Quick Day24","Quick Day25","Quick Day26","Quick Day27","Quick Day28","Quick Day29","Quick Day30","Quick Day31","Quick Day32","Quick Day33","Quick Day34","Quick Day35","Quick Day36","Quick Day37","Quick Day38","Quick Day39","Quick Day40","Quick Day41","Quick Day42","Quick Day43","Quick Day44","Quick Day45","Quick Day46","Quick Day47","Quick Day48","Quick Day49","Quick Day50","Quick Day51","Quick Day52","Quick Day53","Quick Day54","Quick Day55","Quick Day56","Quick Day57","Quick Day58","Quick Day59","Quick Day60","Quick Day61","Quick Day62","Quick Day63","Quick Day64","Quick Day65","Quick Day66","Quick Day67","Quick Day68","Quick Day69","Quick Day70","Quick Day71","Quick Day72","Quick Day73","Quick Day74","Quick Day75","Quick Day76","Quick Day77","Quick Day78","Quick Day79","Quick Day80","Quick Day81","Quick Day82","Quick Day83","Quick Day84","Quick Day85","Quick Day86","Quick Day87","Quick Day88","Quick Day89","Quick Day90","Quick Day91","Quick Day92","Quick Day93","Quick Day94","Quick Day95","Quick Day96","Quick Day97","Quick Day98","Quick Day99","Quick Day100"))
liver_quick_full_diabetic_cases_labvalues_time <- quick_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = quick_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean quick", hjust = 0.5,
       x = "Day of measurement",
       y = "quick %"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_quick_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_quick_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_quick_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
quick_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = quick_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- quick_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = quick_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of quick for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_quick_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(quick_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_quick_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_quick_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- quick_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "quick %",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- quick_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "quick %",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- quick_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "quick %",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_quick_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_quick_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_quick_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


##=========================
## inr 
##=========================
```{r}
inr_full <- all_data %>% 
  filter(panel_id == "inr")
inr_full
```

```{r}
inr_diabetic <- left_join(inr_full, 
                          diabetic_data, 
                  by = c( "bf_ar_m_nummer" = "edited_bf_ar_m_nummer2"),
                  relationship = "many-to-many") %>% 
                 drop_na() %>% 
         filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
         group_by(diabetes) 

inr_diabetic
```

### Based on Patient number ###


```{r}
liver_inr_full_diabetic_cases_labvalues <- inr_diabetic %>% 
  filter(Diabetes == "Diabetic") %>%   group_by(`Edited_BfArM Nummer2`) %>%
  summarise(mean_labread = mean(labreads)) %>%
  ggplot(aes(x = `Edited_BfArM Nummer2`, y = mean_labread))+
  geom_col()+
  theme_classic()+
  labs(title = "All groups_Diabetic cases mean inr", hjust = 0.5,
       x = "Patients",
       y = "INR")+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_inr_diabetic cases labvalues.svg", height = 7, width = 10)
print(liver_inr_full_diabetic_cases_labvalues)
dev.off()
```


```{r}
inr_diabetic2 <- inr_diabetic %>% 
  filter(Diabetes == "Diabetic")     %>%   filter(!grepl("_", attribute))

inr_diabetic2_counts <- inr_diabetic2 %>% 
  group_by(attribute) %>%
  summarize(mean_labread = mean(labreads),n = n(), .groups = "drop")
```


```{r}
inr_diabetic2_counts$attribute <-  factor(inr_diabetic2_counts$attribute, 
                                   levels = c(  "INR Day1", "INR Day2", "INR Day3","INR Day4","INR Day5", "INR Day6","INR Day7","INR Day8","INR Day9","INR Day10", "INR Day11","INR Day12","INR Day13","INR Day14","INR Day15","INR Day16","INR Day17","INR Day18","INR Day19","INR Day20","INR Day21","INR Day22","INR Day23","INR Day24","INR Day25","INR Day26","INR Day27","INR Day28","INR Day29","INR Day30","INR Day31","INR Day32","INR Day33","INR Day34","INR Day35","INR Day36","INR Day37","INR Day38","INR Day39","INR Day40","INR Day41","INR Day42","INR Day43","INR Day44","INR Day45","INR Day46","INR Day47","INR Day48","INR Day49","INR Day50","INR Day51","INR Day52","INR Day53","INR Day54","INR Day55","INR Day56","INR Day57","INR Day58","INR Day59","INR Day60","INR Day61","INR Day62","INR Day63","INR Day64","INR Day65","INR Day66","INR Day67","INR Day68","INR Day69","INR Day70","INR Day71","INR Day72","INR Day73","INR Day74","INR Day75","INR Day76","INR Day77","INR Day78","INR Day79","INR Day80","INR Day81","INR Day82","INR Day83","INR Day84","INR Day85","INR Day86","INR Day87","INR Day88","INR Day89","INR Day90","INR Day91","INR Day92","INR Day93","INR Day94","INR Day95","INR Day96","INR Day97","INR Day98","INR Day99","INR Day100"))
liver_inr_full_diabetic_cases_labvalues_time <- inr_diabetic2_counts %>%
  ggplot(aes(x = attribute, y = mean_labread))+
  geom_col()+
  theme_classic()+
  geom_text(data = inr_diabetic2_counts, 
            aes(label = paste0("N = ", n)),
            vjust = -0.3,  # Positionierung leicht oberhalb des Balkens
            size = 3)+       # Optional: kleinere Schriftgröße
  labs(title = "All groups_Diabetic cases mean inr", hjust = 0.5,
       x = "Day of measurement",
       y = "INR"
       )+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 
liver_inr_full_diabetic_cases_labvalues_time
dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_inr_diabetic cases labvalues time.svg", height = 7, width = 10)
print(liver_inr_full_diabetic_cases_labvalues_time)
dev.off()
```


###########################################################################


```{r}
library(dlookr)
inr_diabetic %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```


```{r}
t.test(
   labreads ~ Diabetes,
  data = inr_diabetic
)
```


```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- inr_diabetic %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = inr_diabetic,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "All groups_Comparison of inr for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "inr (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_inr_full_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(inr_diabetic$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/all_inr_full_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_inr_full_comparison_diabetic_vs_nondiabetic)
dev.off()
```


```{r}
p1_diclo <- inr_diabetic %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "INR",
    title = "Leber_Diclo" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p2_ibu <- inr_diabetic %>% 
  filter(Treatment == "Leber_Ibu") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "INR",
    title = "Leber_Ibu" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
p3_para <- inr_diabetic %>% 
  filter(Treatment == "Leber_Para") %>% 
  ggplot(aes( x =Diabetes, y = labreads))+
  geom_boxplot()+
  geom_jitter(colour = "red")+
  labs(
    x = "Patient group",
    y = "INR",
    title = "Leber_Para" )+
  theme_classic()+
  theme(
    plot.title = element_text(size = 10, hjust =0.5)
  )
```


```{r}
liver_inr_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo+p2_ibu+p3_para

dir.create("plots_all_labvalues", showWarnings = FALSE)
svg("plots_all_labvalues/liver_inr_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_inr_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```





























