---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readxl)
library(tidyr)
library(dplyr)
library(ggstatsplot)
library(tidyverse)
library(readxl)
library(dlookr)
library(reshape2)
```


### run code "diabetes graphs" first for rawdata!!!!!!!!!!!!!!!!


### GPT ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- gpt_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of ALT for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ALT (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- gpt_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of ALT for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ALT (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- gpt_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of ALT for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ALT (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_gpt_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_gpt_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_gpt_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- gpt_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "GPT (U/L)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- gpt_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "GPT (U/L)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- gpt_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "GPT (U/L)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_gpt_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_gpt_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_gpt_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### got ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- got_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of got for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "got (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_got_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_got_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_got_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- got_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of got for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "got (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_got_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_got_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_got_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- got_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of got for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "got (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_got_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_got_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_got_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- got_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "got (U/L)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- got_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "got (U/L)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- got_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "got (U/L)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_got_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_got_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_got_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### gpt ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- gpt_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of gpt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "gpt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_gpt_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- gpt_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of gpt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "gpt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_gpt_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- gpt_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of gpt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "gpt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_gpt_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_gpt_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_gpt_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- gpt_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "gpt (U/L)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- gpt_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "gpt (U/L)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- gpt_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "gpt (U/L)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_gpt_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_gpt_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_gpt_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### ldh ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- ldh_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of ldh for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ldh (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ldh_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ldh_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ldh_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- ldh_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of ldh for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ldh (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ldh_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ldh_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ldh_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- ldh_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of ldh for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ldh (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ldh_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ldh_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ldh_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- ldh_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ldh (U/L)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- ldh_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ldh (U/L)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- ldh_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ldh (U/L)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_ldh_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_ldh_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ldh_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### ck ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- ck_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of ck for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ck (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ck_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ck_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ck_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- ck_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of ck for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ck (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ck_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ck_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ck_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- ck_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of ck for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ck (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ck_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ck_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ck_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- ck_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ck (U/L)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- ck_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ck (U/L)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- ck_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ck (U/L)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_ck_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_ck_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ck_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### ap ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- ap_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of ap for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ap (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ap_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ap_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ap_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- ap_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of ap for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ap (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ap_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ap_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ap_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- ap_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of ap for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ap (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ap_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ap_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ap_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- ap_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ap (U/L)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- ap_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ap (U/L)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- ap_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ap (U/L)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_ap_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_ap_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ap_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### ptt ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- ptt_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of ptt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ptt_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ptt_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ptt_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- ptt_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of ptt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ptt_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ptt_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ptt_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- ptt_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of ptt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ptt_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ptt_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ptt_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- ptt_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ptt (Sec.)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- ptt_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ptt (Sec.)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- ptt_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ptt (Sec.)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_ptt_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_ptt_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ptt_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### leukozyten ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- Leukozyten_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of leukozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_leukozyten_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_leukozyten_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_leukozyten_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{}
library(ggstatsplot)

leber_diabetic_ibu <- Leukozyten_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of leukozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_leukozyten_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_leukozyten_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_leukozyten_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- Leukozyten_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of leukozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_leukozyten_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_leukozyten_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_leukozyten_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- Leukozyten_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "leukozyten (cells/ul)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- Leukozyten_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "leukozyten (cells/ul)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- Leukozyten_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "leukozyten (cells/ul)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_leukozyten_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_leukozyten_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_leukozyten_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### Erythrozyten ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- Erythrozyten_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of Erythrozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Erythrozyten_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Erythrozyten_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Erythrozyten_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- Erythrozyten_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of Erythrozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Erythrozyten_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Erythrozyten_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Erythrozyten_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- Erythrozyten_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of Erythrozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Erythrozyten_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Erythrozyten_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Erythrozyten_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- Erythrozyten_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Erythrozyten (cells/ul)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- Erythrozyten_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Erythrozyten (cells/ul)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- Erythrozyten_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Erythrozyten (cells/ul)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_Erythrozyten_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_Erythrozyten_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_Erythrozyten_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### Thrombozyten ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- Thrombozyten_diabetic%>% 
  filter(Treatment == "Leber_Diclo") %>% filter(!grepl("_1|_2|_3|_4|_d", attribute)) 


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of Thrombozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Thrombozyten_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Thrombozyten_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Thrombozyten_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- Thrombozyten_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of Thrombozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Thrombozyten_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Thrombozyten_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Thrombozyten_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- Thrombozyten_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of Thrombozyten for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Thrombozyten_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Thrombozyten_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Thrombozyten_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- Thrombozyten_diabetic %>% 
  filter(Treatment == "Leber_Diclo")%>% filter(!grepl("_1|_2|_3|_4|_d", attribute)) 

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Thrombozyten (cells/ul)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- Thrombozyten_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Thrombozyten (cells/ul)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- Thrombozyten_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Thrombozyten (cells/ul)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_Thrombozyten_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_Thrombozyten_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_Thrombozyten_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### hb ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- hb_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of hb for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_hb_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_hb_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hb_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- hb_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of hb for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_hb_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_hb_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hb_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- hb_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of hb for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_hb_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_hb_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hb_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- hb_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "hb (g/dl)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- hb_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "hb (g/dl)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- hb_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "hb (g/dl)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_hb_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_hb_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_hb_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### Gesamteiweiß ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- Gesamteiweiß_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of Gesamteiweiß for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Gesamteiweiß_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Gesamteiweiß_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Gesamteiweiß_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- Gesamteiweiß_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of Gesamteiweiß for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Gesamteiweiß_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Gesamteiweiß_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Gesamteiweiß_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- Gesamteiweiß_diabetic%>% 
  filter(Treatment == "Leber_Para")%>% filter(!grepl("_1|_2|_3|_4|_d", attribute)) 


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of Gesamteiweiß for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "Gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_Gesamteiweiß_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_Gesamteiweiß_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_Gesamteiweiß_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- Gesamteiweiß_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Gesamteiweiß (g/dl)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- Gesamteiweiß_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Gesamteiweiß (g/dl)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- Gesamteiweiß_diabetic %>% 
  filter(Treatment == "Leber_Para")%>% filter(!grepl("_1|_2|_3|_4|_d", attribute)) 

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "Gesamteiweiß (g/dl)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_Gesamteiweiß_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_Gesamteiweiß_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_Gesamteiweiß_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### total_bilirubin ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- total_bilirubin_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of total_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_total_bilirubin_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_total_bilirubin_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- total_bilirubin_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of total_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_total_bilirubin_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_total_bilirubin_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- total_bilirubin_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of total_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_total_bilirubin_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_total_bilirubin_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_total_bilirubin_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- total_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "total_bilirubin (mg/dl)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- total_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "total_bilirubin (mg/dl)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- total_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "total_bilirubin (mg/dl)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_total_bilirubin_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_total_bilirubin_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_total_bilirubin_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### direct_bilirubin ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- direct_bilirubin_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of direct_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_direct_bilirubin_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_direct_bilirubin_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- direct_bilirubin_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of direct_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_direct_bilirubin_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_direct_bilirubin_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- direct_bilirubin_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of direct_bilirubin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_direct_bilirubin_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_direct_bilirubin_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_direct_bilirubin_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- direct_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "direct_bilirubin (mg/dl)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- direct_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "direct_bilirubin (mg/dl)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- direct_bilirubin_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "direct_bilirubin (mg/dl)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_direct_bilirubin_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_direct_bilirubin_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_direct_bilirubin_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### kreatinin ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- kreatinin_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of kreatinin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kreatinin_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kreatinin_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kreatinin_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- kreatinin_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of kreatinin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kreatinin_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kreatinin_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kreatinin_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- kreatinin_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of kreatinin for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kreatinin_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kreatinin_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kreatinin_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- kreatinin_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kreatinin (mg/dl)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- kreatinin_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kreatinin (mg/dl)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- kreatinin_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kreatinin (mg/dl)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_kreatinin_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_kreatinin_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_kreatinin_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### harnstoff ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- harnstoff_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of harnstoff for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_harnstoff_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_harnstoff_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_harnstoff_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- harnstoff_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of harnstoff for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_harnstoff_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_harnstoff_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_harnstoff_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- harnstoff_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of harnstoff for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_harnstoff_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_harnstoff_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_harnstoff_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- harnstoff_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "harnstoff (mg/dl)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- harnstoff_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "harnstoff (mg/dl)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- harnstoff_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "harnstoff (mg/dl)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_harnstoff_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_harnstoff_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_harnstoff_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### crp ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- crp_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of crp for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "crp (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_crp_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_crp_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_crp_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- crp_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of crp for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "crp (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_crp_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_crp_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_crp_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- crp_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of crp for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "crp (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_crp_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_crp_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_crp_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- crp_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "crp (mg/dl)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- crp_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "crp (mg/dl)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- crp_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "crp (mg/dl)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_crp_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_crp_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_crp_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### crp ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- crp_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of crp for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_crp_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_crp_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_crp_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- crp_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of crp for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_crp_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_crp_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_crp_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- crp_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of crp for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_crp_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_crp_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_crp_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- crp_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "crp (mg/l)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- crp_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "crp (mg/l)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- crp_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "crp (mg/l)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_crp_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_crp_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_crp_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### natrium ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- natrium_diabetic%>% 
  filter(Treatment == "Leber_Diclo")%>% filter(!grepl("_1|_2|_3|_4|_d", attribute)) 


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of natrium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_natrium_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_natrium_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_natrium_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- natrium_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of natrium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_natrium_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_natrium_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_natrium_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- natrium_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of natrium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_natrium_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_natrium_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_natrium_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- natrium_diabetic %>% 
  filter(Treatment == "Leber_Diclo")%>% filter(!grepl("_1|_2|_3|_4|_d", attribute)) 

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "natrium (mmol/l)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- natrium_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "natrium (mmol/l)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- natrium_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "natrium (mmol/l)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_natrium_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_natrium_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_natrium_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### kalium ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- kalium_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of kalium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kalium_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kalium_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalium_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- kalium_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of kalium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kalium_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kalium_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalium_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- kalium_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of kalium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kalium_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kalium_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalium_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- kalium_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kalium (mmol/l)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- kalium_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kalium (mmol/l)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- kalium_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kalium (mmol/l)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_kalium_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_kalium_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_kalium_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### kalzium ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- kalzium_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of kalzium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kalzium_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kalzium_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalzium_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- kalzium_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of kalzium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kalzium_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kalzium_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalzium_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- kalzium_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of kalzium for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_kalzium_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_kalzium_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_kalzium_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- kalzium_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kalzium (mmol/l)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- kalzium_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kalzium (mmol/l)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- kalzium_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "kalzium (mmol/l)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_kalzium_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_kalzium_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_kalzium_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```


### inr ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- inr_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of inr for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_inr_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_inr_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_inr_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- inr_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of inr for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_inr_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_inr_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_inr_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- inr_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of inr for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_inr_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_inr_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_inr_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- inr_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "inr ",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- inr_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "inr ",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- inr_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "inr ",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_inr_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_inr_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_inr_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### quick ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- quick_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of quick for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_quick_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_quick_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_quick_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- quick_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of quick for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_quick_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_quick_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_quick_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- quick_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of quick for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_quick_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_quick_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_quick_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- quick_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "quick (%)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- quick_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "quick (%)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- quick_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "quick (%)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_quick_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_quick_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_quick_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```



### hämatokrit ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- hämatokrit_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of hämatokrit for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_hämatokrit_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_hämatokrit_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hämatokrit_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- hämatokrit_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of hämatokrit for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_hämatokrit_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_hämatokrit_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hämatokrit_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- hämatokrit_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of hämatokrit for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_hämatokrit_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_hämatokrit_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_hämatokrit_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- hämatokrit_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "hämatokrit (%)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- hämatokrit_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "hämatokrit (%)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- hämatokrit_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "hämatokrit (%)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_hämatokrit_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_hämatokrit_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_hämatokrit_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```




### ggt ########################################################################
### violin plot ###

```{r}
library(ggstatsplot)

leber_diabetic_diclo <- ggt_diabetic%>% 
  filter(Treatment == "Leber_Diclo")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_diclo %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_diclo,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_diclo Comparison of ggt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ggt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ggt_full_diclo_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_diclo$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ggt_full_diclo_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ggt_full_diclo_comparison_diabetic_vs_nondiabetic)
dev.off()


```


```{r}
library(ggstatsplot)

leber_diabetic_ibu <- ggt_diabetic%>% 
  filter(Treatment == "Leber_Ibu")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_ibu %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_ibu,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_ibu Comparison of ggt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ggt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ggt_full_ibu_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_ibu$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ggt_full_ibu_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ggt_full_ibu_comparison_diabetic_vs_nondiabetic)
dev.off()


```



```{r}
library(ggstatsplot)

leber_diabetic_para <- ggt_diabetic%>% 
  filter(Treatment == "Leber_Para")


# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leber_diabetic_para %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leber_diabetic_para,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "liver_para Comparison of ggt for Diabetic vs. Non-Diabetic Patients",
  xlab = "Patient group",
  ylab = "ggt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues/seperated by nsaid - violin einfügen
liver_ggt_full_para_comparison_diabetic_vs_nondiabetic <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leber_diabetic_para$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/seperated by nsaid - violin", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - violin/liver_ggt_full_para_comparison_diabetic_vs_nondiabetic.svg", height = 8, width = 6.5)
print(liver_ggt_full_para_comparison_diabetic_vs_nondiabetic)
dev.off()


```


### boxplot ###

```{r}
p1_diclo <- ggt_diabetic %>% 
  filter(Treatment == "Leber_Diclo")

p1_diclo_counts <- p1_diclo %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_diclo_plot <- p1_diclo %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_diclo_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ggt (U/L)",
    title = "Liver Diclo"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_ibu <- ggt_diabetic %>% 
  filter(Treatment == "Leber_Ibu")

p1_ibu_counts <- p1_ibu %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_ibu_plot <- p1_ibu %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_ibu_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ggt (U/L)",
    title = "Liver Ibu"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```


```{r}
p1_para <- ggt_diabetic %>% 
  filter(Treatment == "Leber_Para")

p1_para_counts <- p1_para %>% 
  group_by(Diabetes) %>%
  summarize(
    n_patients = n_distinct(`Edited_BfArM Nummer2`),
    ymax = max(labreads, na.rm = TRUE),
    .groups = "drop"
  )

p1_para_plot <- p1_para %>% 
  ggplot(aes(x = Diabetes, y = labreads)) +
  geom_boxplot() +
  geom_jitter(color = "red", width = 0.2, height = 0) +
  geom_text(data = p1_para_counts, 
            aes(x = Diabetes, 
                y = ymax, 
                label = paste0("n=", n_patients)), 
            color = "red", 
            vjust = -0.5) +  # leicht über dem Maximum
  labs(
    x = "Patient group",
    y = "ggt (U/L)",
    title = "Liver Para"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5)
  )
```

```{r}
liver_ggt_full_boxplot_diabetic_vs_nondiabetic <- p1_diclo_plot+p1_ibu_plot+p1_para_plot


dir.create("plots_all_labvalues/seperated by nsaid - box", showWarnings = FALSE)
svg("plots_all_labvalues/seperated by nsaid - box/liver_ggt_full_boxplot diabetic vs. nondiabetic.svg", height = 7, width = 12)
print(liver_ggt_full_boxplot_diabetic_vs_nondiabetic)
dev.off()
```





















































































































































































