---
title: "Untitled"
output: html_document
date: "2025-10-02"
---

```{r}
library(dplyr)
library(stringr)
```


```{r}
gender_data <- read_excel("E:/Daten(x)/Daten(lw-r)/Abc/Doktorarbeit SJS/Analyse R-Statistics/gender plots - bmi/gender_info_full.xlsx",
           sheet = 1, skip = 1)

gender_data1 <- gender_data %>%
  dplyr::select(1:4) %>%
  dplyr::mutate(
    Gender = dplyr::case_when(
      Male == 1 ~ "Male",
      Female == 1 ~ "Female"
    ),
    value = dplyr::case_when(
      Male == 1 ~ 1,
      Female == 1 ~ 0
    )
  ) %>% 
  dplyr::select(1,2,5,6)%>% 
  drop_na()
gender_data1
```


### gpt ##########################################################################

```{r}

gpt_diabetic_gender <- left_join(gender_data1,gpt_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

gpt_diabetic_gender
```
 
```{r}
gpt_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gpt_diabetic_gender)
```


# nsaid comparison peak labvlues #
```{r}
gpt_diabetic_gender_peak <- gpt_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

gpt_diabetic_gender_peak
```

```{r}
gpt_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gpt_diabetic_gender_peak)
```

## Female ##

```{r}
gpt_diabetic_female <- gpt_diabetic_gender %>% 
  dplyr::filter(Gender == "Female") 

gpt_diabetic_female
```

```{r}
gpt_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gpt_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- gpt_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = gpt_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "gpt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_gpt_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(gpt_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )
liver_gpt_all_labvalues_comp_diab_nondiab_for_female
dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_gpt_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_gpt_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
gpt_diabetic_male <- gpt_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

gpt_diabetic_male
```

```{r}
gpt_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gpt_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- gpt_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = gpt_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "gpt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_gpt_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(gpt_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )
liver_gpt_all_labvalues_comp_diab_nondiab_for_male
dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_gpt_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_gpt_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ## 

```{r}
gpt_diabetic_female_peak <- gpt_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

gpt_diabetic_female_peak
```

```{r}
gpt_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gpt_diabetic_female_peak)
```

```{r}
liver_gpt_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = gpt_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-gpt (U/L)",
  messages = FALSE
)

liver_gpt_peak_labvalues_comp_diab_nondiab_for_female
dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_gpt_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_gpt_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
gpt_diabetic_male_peak <- gpt_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

gpt_diabetic_male_peak
```

```{r}
gpt_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gpt_diabetic_male_peak)
```

```{r}
liver_gpt_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = gpt_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-gpt (U/L)",
  messages = FALSE
)

liver_gpt_peak_labvalues_comp_diab_nondiab_for_male
dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_gpt_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_gpt_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```

 

### got ##########################################################################

```{r}

got_diabetic_gender <- left_join(gender_data1,got_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

got_diabetic_gender
```
 
```{r}
got_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = got_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
got_diabetic_gender_peak <- got_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

got_diabetic_gender_peak
```

```{r}
got_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = got_diabetic_gender_peak)
```




## Female ##

```{r}
got_diabetic_female <- got_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

got_diabetic_female
```

```{r}
got_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = got_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- got_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = got_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "got (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_got_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(got_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )
liver_got_all_labvalues_comp_diab_nondiab_for_female
dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_got_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_got_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
got_diabetic_male <- got_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

got_diabetic_male
```

```{r}
got_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = got_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- got_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = got_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "got (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_got_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(got_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )
liver_got_all_labvalues_comp_diab_nondiab_for_male
dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_got_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_got_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
got_diabetic_female_peak <- got_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

got_diabetic_female_peak
```

```{r}
got_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = got_diabetic_female_peak)
```

```{r}
liver_got_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = got_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-got (U/L)",
  messages = FALSE
)

liver_got_peak_labvalues_comp_diab_nondiab_for_female
dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_got_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_got_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
got_diabetic_male_peak <- got_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

got_diabetic_male_peak
```

```{r}
got_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = got_diabetic_male_peak)
```

```{r}
liver_got_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = got_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-got (U/L)",
  messages = FALSE
)

liver_got_peak_labvalues_comp_diab_nondiab_for_male
dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_got_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_got_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```

 
### ggt ##########################################################################

```{r}

ggt_diabetic_gender <- left_join(gender_data1,ggt_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

ggt_diabetic_gender
```
 
```{r}
ggt_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ggt_diabetic_gender)
```




# nsaid comparison peak labvlues #
```{r}
ggt_diabetic_gender_peak <- ggt_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

ggt_diabetic_gender_peak
```

```{r}
ggt_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ggt_diabetic_gender_peak)
```




## Female ##

```{r}
ggt_diabetic_female <- ggt_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

ggt_diabetic_female
```

```{r}
ggt_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ggt_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ggt_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ggt_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "ggt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ggt_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ggt_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_ggt_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ggt_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ggt_diabetic_male <- ggt_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

ggt_diabetic_male
```

```{r}
ggt_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ggt_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ggt_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ggt_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "ggt (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ggt_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ggt_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_ggt_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ggt_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
ggt_diabetic_female_peak <- ggt_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

ggt_diabetic_female_peak
```

```{r}
ggt_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ggt_diabetic_female_peak)
```

```{r}
liver_ggt_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = ggt_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-ggt (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_ggt_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ggt_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ggt_diabetic_male_peak <- ggt_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

ggt_diabetic_male_peak
```

```{r}
ggt_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ggt_diabetic_male_peak)
```

```{r}
liver_ggt_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = ggt_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-ggt (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_ggt_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ggt_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```




### ldh ##########################################################################

```{r}

ldh_diabetic_gender <- left_join(gender_data1,ldh_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

ldh_diabetic_gender
```
 
```{r}
ldh_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ldh_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
ldh_diabetic_gender_peak <- ldh_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

ldh_diabetic_gender_peak
```

```{r}
ldh_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ldh_diabetic_gender_peak)
```




## Female ##

```{r}
ldh_diabetic_female <- ldh_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

ldh_diabetic_female
```

```{r}
ldh_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ldh_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ldh_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ldh_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "ldh (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ldh_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ldh_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_ldh_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ldh_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ldh_diabetic_male <- ldh_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

ldh_diabetic_male
```

```{r}
ldh_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ldh_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ldh_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ldh_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "ldh (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ldh_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ldh_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_ldh_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ldh_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
ldh_diabetic_female_peak <- ldh_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

ldh_diabetic_female_peak
```

```{r}
ldh_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ldh_diabetic_female_peak)
```

```{r}
liver_ldh_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = ldh_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-ldh (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_ldh_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ldh_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ldh_diabetic_male_peak <- ldh_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

ldh_diabetic_male_peak
```

```{r}
ldh_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ldh_diabetic_male_peak)
```

```{r}
liver_ldh_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = ldh_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-ldh (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_ldh_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ldh_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```


### ck ##########################################################################

```{r}

ck_diabetic_gender <- left_join(gender_data1,ck_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

ck_diabetic_gender
```
 
```{r}
ck_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ck_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
ck_diabetic_gender_peak <- ck_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

ck_diabetic_gender_peak
```

```{r}
ck_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ck_diabetic_gender_peak)
```




## Female ##

```{r}
ck_diabetic_female <- ck_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

ck_diabetic_female
```

```{r}
ck_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ck_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ck_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ck_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "ck (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ck_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ck_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_ck_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ck_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ck_diabetic_male <- ck_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

ck_diabetic_male
```

```{r}
ck_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
#oneway.test(labreads ~ Diabetes, data = ck_diabetic_male)
```

```{}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ck_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ck_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "ck (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ck_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ck_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_ck_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ck_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
ck_diabetic_female_peak <- ck_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

ck_diabetic_female_peak
```

```{r}
ck_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ck_diabetic_female_peak)
```

```{r}
liver_ck_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = ck_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-ck (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_ck_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ck_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ck_diabetic_male_peak <- ck_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

ck_diabetic_male_peak
```

```{r}
ck_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
#oneway.test(labreads ~ Diabetes, data = ck_diabetic_male_peak)
```

```{}
liver_ck_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = ck_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-ck (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_ck_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ck_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```




### ap ##########################################################################

```{r}

ap_diabetic_gender <- left_join(gender_data1,ap_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

ap_diabetic_gender
```
 
```{r}
ap_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ap_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
ap_diabetic_gender_peak <- ap_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

ap_diabetic_gender_peak
```

```{r}
ap_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ap_diabetic_gender_peak)
```




## Female ##

```{r}
ap_diabetic_female <- ap_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

ap_diabetic_female
```

```{r}
ap_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ap_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ap_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ap_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "ap (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ap_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ap_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_ap_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ap_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ap_diabetic_male <- ap_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

ap_diabetic_male
```

```{r}
ap_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ap_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ap_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ap_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "ap (U/L)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ap_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ap_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_ap_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ap_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
ap_diabetic_female_peak <- ap_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

ap_diabetic_female_peak
```

```{r}
ap_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ap_diabetic_female_peak)
```

```{r}
liver_ap_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = ap_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-ap (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_ap_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ap_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ap_diabetic_male_peak <- ap_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

ap_diabetic_male_peak
```

```{r}
ap_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ap_diabetic_male_peak)
```

```{r}
liver_ap_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = ap_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-ap (U/L)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_ap_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ap_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### ptt ##########################################################################

```{r}

ptt_diabetic_gender <- left_join(gender_data1,ptt_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

ptt_diabetic_gender
```
 
```{r}
ptt_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ptt_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
ptt_diabetic_gender_peak <- ptt_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

ptt_diabetic_gender_peak
```

```{r}
ptt_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ptt_diabetic_gender_peak)
```




## Female ##

```{r}
ptt_diabetic_female <- ptt_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

ptt_diabetic_female
```

```{r}
ptt_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = ptt_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ptt_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ptt_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ptt_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ptt_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_ptt_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ptt_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ptt_diabetic_male <- ptt_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

ptt_diabetic_male
```

```{r}
ptt_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ptt_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- ptt_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = ptt_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "ptt (Sec.)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_ptt_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(ptt_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_ptt_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ptt_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
ptt_diabetic_female_peak <- ptt_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

ptt_diabetic_female_peak
```

```{r}
ptt_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ptt_diabetic_female_peak)
```

```{r}
liver_ptt_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = ptt_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-ptt (Sec.)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_ptt_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_ptt_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
ptt_diabetic_male_peak <- ptt_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

ptt_diabetic_male_peak
```

```{r}
ptt_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = ptt_diabetic_male_peak)
```

```{r}
liver_ptt_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = ptt_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-ptt (Sec.)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_ptt_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_ptt_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```




### leukozyten ##########################################################################

```{r}

leukozyten_diabetic_gender <- left_join(gender_data1,Leukozyten_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

leukozyten_diabetic_gender
```
 
```{r}
leukozyten_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = leukozyten_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
leukozyten_diabetic_gender_peak <- leukozyten_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

leukozyten_diabetic_gender_peak
```

```{r}
leukozyten_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = leukozyten_diabetic_gender_peak)
```




## Female ##

```{r}
leukozyten_diabetic_female <- leukozyten_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

leukozyten_diabetic_female
```

```{r}
leukozyten_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = leukozyten_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leukozyten_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leukozyten_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_leukozyten_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leukozyten_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_leukozyten_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_leukozyten_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
leukozyten_diabetic_male <- leukozyten_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

leukozyten_diabetic_male
```

```{r}
leukozyten_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = leukozyten_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- leukozyten_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = leukozyten_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "leukozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_leukozyten_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(leukozyten_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_leukozyten_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_leukozyten_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
leukozyten_diabetic_female_peak <- leukozyten_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

leukozyten_diabetic_female_peak
```

```{r}
leukozyten_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = leukozyten_diabetic_female_peak)
```

```{r}
liver_leukozyten_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = leukozyten_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-leukozyten (cells/ul)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_leukozyten_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_leukozyten_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
leukozyten_diabetic_male_peak <- leukozyten_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

leukozyten_diabetic_male_peak
```

```{r}
leukozyten_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = leukozyten_diabetic_male_peak)
```

```{r}
liver_leukozyten_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = leukozyten_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-leukozyten (cells/ul)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_leukozyten_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_leukozyten_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### erythrozyten ##########################################################################

```{r}

erythrozyten_diabetic_gender <- left_join(gender_data1,Erythrozyten_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

erythrozyten_diabetic_gender
```
 
```{r}
erythrozyten_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = erythrozyten_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
erythrozyten_diabetic_gender_peak <- erythrozyten_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

erythrozyten_diabetic_gender_peak
```

```{r}
erythrozyten_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = erythrozyten_diabetic_gender_peak)
```




## Female ##

```{r}
erythrozyten_diabetic_female <- erythrozyten_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

erythrozyten_diabetic_female
```

```{r}
erythrozyten_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = erythrozyten_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- erythrozyten_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = erythrozyten_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_erythrozyten_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(erythrozyten_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_erythrozyten_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_erythrozyten_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
erythrozyten_diabetic_male <- erythrozyten_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

erythrozyten_diabetic_male
```

```{r}
erythrozyten_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = erythrozyten_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- erythrozyten_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = erythrozyten_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "erythrozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_erythrozyten_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(erythrozyten_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_erythrozyten_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_erythrozyten_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
erythrozyten_diabetic_female_peak <- erythrozyten_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

erythrozyten_diabetic_female_peak
```

```{r}
erythrozyten_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = erythrozyten_diabetic_female_peak)
```

```{r}
liver_erythrozyten_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = erythrozyten_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-erythrozyten (cells/ul)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_erythrozyten_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_erythrozyten_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
erythrozyten_diabetic_male_peak <- erythrozyten_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

erythrozyten_diabetic_male_peak
```

```{r}
erythrozyten_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = erythrozyten_diabetic_male_peak)
```

```{r}
liver_erythrozyten_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = erythrozyten_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-erythrozyten (cells/ul)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_erythrozyten_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_erythrozyten_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### thrombozyten ##########################################################################

```{r}

thrombozyten_diabetic_gender <- left_join(gender_data1,Thrombozyten_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

thrombozyten_diabetic_gender
```
 
```{r}
thrombozyten_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = thrombozyten_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
thrombozyten_diabetic_gender_peak <- thrombozyten_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

thrombozyten_diabetic_gender_peak
```

```{r}
thrombozyten_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = thrombozyten_diabetic_gender_peak)
```




## Female ##

```{r}
thrombozyten_diabetic_female <- thrombozyten_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

thrombozyten_diabetic_female
```

```{r}
thrombozyten_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = thrombozyten_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- thrombozyten_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = thrombozyten_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_thrombozyten_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(thrombozyten_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_thrombozyten_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_thrombozyten_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
thrombozyten_diabetic_male <- thrombozyten_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

thrombozyten_diabetic_male
```

```{r}
thrombozyten_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = thrombozyten_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- thrombozyten_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = thrombozyten_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "thrombozyten (cells/ul)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_thrombozyten_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(thrombozyten_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_thrombozyten_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_thrombozyten_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
thrombozyten_diabetic_female_peak <- thrombozyten_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

thrombozyten_diabetic_female_peak
```

```{r}
thrombozyten_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = thrombozyten_diabetic_female_peak)
```

```{r}
liver_thrombozyten_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = thrombozyten_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-thrombozyten (cells/ul)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_thrombozyten_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_thrombozyten_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
thrombozyten_diabetic_male_peak <- thrombozyten_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

thrombozyten_diabetic_male_peak
```

```{r}
thrombozyten_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = thrombozyten_diabetic_male_peak)
```

```{r}
liver_thrombozyten_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = thrombozyten_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-thrombozyten (cells/ul)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_thrombozyten_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_thrombozyten_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### hb ##########################################################################

```{r}

hb_diabetic_gender <- left_join(gender_data1,hb_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

hb_diabetic_gender
```
 
```{r}
hb_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hb_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
hb_diabetic_gender_peak <- hb_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

hb_diabetic_gender_peak
```

```{r}
hb_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hb_diabetic_gender_peak)
```




## Female ##

```{r}
hb_diabetic_female <- hb_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

hb_diabetic_female
```

```{r}
hb_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hb_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hb_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hb_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_hb_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(hb_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_hb_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_hb_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
hb_diabetic_male <- hb_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

hb_diabetic_male
```

```{r}
hb_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = hb_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hb_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hb_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "hb (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_hb_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(hb_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_hb_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_hb_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
hb_diabetic_female_peak <- hb_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

hb_diabetic_female_peak
```

```{r}
hb_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hb_diabetic_female_peak)
```

```{r}
liver_hb_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = hb_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-hb (g/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_hb_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_hb_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
hb_diabetic_male_peak <- hb_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

hb_diabetic_male_peak
```

```{r}
hb_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = hb_diabetic_male_peak)
```

```{r}
liver_hb_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = hb_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-hb (g/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_hb_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_hb_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### gesamteiweiß ##########################################################################

```{r}

gesamteiweiß_diabetic_gender <- left_join(gender_data1,Gesamteiweiß_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  filter(!grepl("_1|_2|_3|_4|_d", attribute)) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

gesamteiweiß_diabetic_gender
```
 
```{r}
gesamteiweiß_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gesamteiweiß_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
gesamteiweiß_diabetic_gender_peak <- gesamteiweiß_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

gesamteiweiß_diabetic_gender_peak
```

```{r}
gesamteiweiß_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = gesamteiweiß_diabetic_gender_peak)
```




## Female ##

```{r}
gesamteiweiß_diabetic_female <- gesamteiweiß_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

gesamteiweiß_diabetic_female
```

```{r}
gesamteiweiß_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = gesamteiweiß_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- gesamteiweiß_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = gesamteiweiß_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_gesamteiweiß_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(gesamteiweiß_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_gesamteiweiß_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_gesamteiweiß_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
gesamteiweiß_diabetic_male <- gesamteiweiß_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

gesamteiweiß_diabetic_male
```

```{r}
gesamteiweiß_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = gesamteiweiß_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- gesamteiweiß_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = gesamteiweiß_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "gesamteiweiß (g/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_gesamteiweiß_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(gesamteiweiß_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_gesamteiweiß_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_gesamteiweiß_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
gesamteiweiß_diabetic_female_peak <- gesamteiweiß_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

gesamteiweiß_diabetic_female_peak
```

```{r}
gesamteiweiß_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = gesamteiweiß_diabetic_female_peak)
```

```{r}
liver_gesamteiweiß_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = gesamteiweiß_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-gesamteiweiß (g/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_gesamteiweiß_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_gesamteiweiß_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
gesamteiweiß_diabetic_male_peak <- gesamteiweiß_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

gesamteiweiß_diabetic_male_peak
```

```{r}
gesamteiweiß_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = gesamteiweiß_diabetic_male_peak)
```

```{r}
liver_gesamteiweiß_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = gesamteiweiß_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-gesamteiweiß (g/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_gesamteiweiß_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_gesamteiweiß_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### total_bilirubin ##########################################################################

```{r}

total_bilirubin_diabetic_gender <- left_join(gender_data1,total_bilirubin_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

total_bilirubin_diabetic_gender
```
 
```{r}
total_bilirubin_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = total_bilirubin_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
total_bilirubin_diabetic_gender_peak <- total_bilirubin_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

total_bilirubin_diabetic_gender_peak
```

```{r}
total_bilirubin_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = total_bilirubin_diabetic_gender_peak)
```




## Female ##

```{r}
total_bilirubin_diabetic_female <- total_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

total_bilirubin_diabetic_female
```

```{r}
total_bilirubin_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = total_bilirubin_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- total_bilirubin_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = total_bilirubin_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_total_bilirubin_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(total_bilirubin_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_total_bilirubin_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_total_bilirubin_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
total_bilirubin_diabetic_male <- total_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

total_bilirubin_diabetic_male
```

```{r}
total_bilirubin_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = total_bilirubin_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- total_bilirubin_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = total_bilirubin_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "total_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_total_bilirubin_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(total_bilirubin_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_total_bilirubin_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_total_bilirubin_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
total_bilirubin_diabetic_female_peak <- total_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

total_bilirubin_diabetic_female_peak
```

```{r}
total_bilirubin_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = total_bilirubin_diabetic_female_peak)
```

```{r}
liver_total_bilirubin_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = total_bilirubin_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-total_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_total_bilirubin_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_total_bilirubin_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
total_bilirubin_diabetic_male_peak <- total_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

total_bilirubin_diabetic_male_peak
```

```{r}
total_bilirubin_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = total_bilirubin_diabetic_male_peak)
```

```{r}
liver_total_bilirubin_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = total_bilirubin_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-total_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_total_bilirubin_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_total_bilirubin_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### direct_bilirubin ##########################################################################

```{r}

direct_bilirubin_diabetic_gender <- left_join(gender_data1,direct_bilirubin_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

direct_bilirubin_diabetic_gender
```
 
```{r}
direct_bilirubin_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = direct_bilirubin_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
direct_bilirubin_diabetic_gender_peak <- direct_bilirubin_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

direct_bilirubin_diabetic_gender_peak
```

```{r}
direct_bilirubin_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = direct_bilirubin_diabetic_gender_peak)
```




## Female ##

```{r}
direct_bilirubin_diabetic_female <- direct_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

direct_bilirubin_diabetic_female
```

```{r}
direct_bilirubin_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = direct_bilirubin_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- direct_bilirubin_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = direct_bilirubin_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_direct_bilirubin_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(direct_bilirubin_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_direct_bilirubin_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_direct_bilirubin_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
direct_bilirubin_diabetic_male <- direct_bilirubin_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

direct_bilirubin_diabetic_male
```

```{r}
direct_bilirubin_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = direct_bilirubin_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- direct_bilirubin_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = direct_bilirubin_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "direct_bilirubin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_direct_bilirubin_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(direct_bilirubin_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_direct_bilirubin_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_direct_bilirubin_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
direct_bilirubin_diabetic_female_peak <- direct_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

direct_bilirubin_diabetic_female_peak
```

```{r}
direct_bilirubin_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = direct_bilirubin_diabetic_female_peak)
```

```{r}
liver_direct_bilirubin_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = direct_bilirubin_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-direct_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_direct_bilirubin_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_direct_bilirubin_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
direct_bilirubin_diabetic_male_peak <- direct_bilirubin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

direct_bilirubin_diabetic_male_peak
```

```{r}
direct_bilirubin_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = direct_bilirubin_diabetic_male_peak)
```

```{r}
liver_direct_bilirubin_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = direct_bilirubin_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-direct_bilirubin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_direct_bilirubin_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_direct_bilirubin_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### kreatinin ##########################################################################

```{r}

kreatinin_diabetic_gender <- left_join(gender_data1,kreatinin_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

kreatinin_diabetic_gender
```
 
```{r}
kreatinin_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kreatinin_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
kreatinin_diabetic_gender_peak <- kreatinin_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

kreatinin_diabetic_gender_peak
```

```{r}
kreatinin_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kreatinin_diabetic_gender_peak)
```




## Female ##

```{r}
kreatinin_diabetic_female <- kreatinin_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

kreatinin_diabetic_female
```

```{r}
kreatinin_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kreatinin_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kreatinin_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kreatinin_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kreatinin_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kreatinin_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_kreatinin_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_kreatinin_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
kreatinin_diabetic_male <- kreatinin_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

kreatinin_diabetic_male
```

```{r}
kreatinin_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = kreatinin_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kreatinin_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kreatinin_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "kreatinin (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kreatinin_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kreatinin_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_kreatinin_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_kreatinin_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
kreatinin_diabetic_female_peak <- kreatinin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

kreatinin_diabetic_female_peak
```

```{r}
kreatinin_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kreatinin_diabetic_female_peak)
```

```{r}
liver_kreatinin_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = kreatinin_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-kreatinin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_kreatinin_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_kreatinin_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
kreatinin_diabetic_male_peak <- kreatinin_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

kreatinin_diabetic_male_peak
```

```{r}
kreatinin_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = kreatinin_diabetic_male_peak)
```

```{r}
liver_kreatinin_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = kreatinin_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-kreatinin (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_kreatinin_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_kreatinin_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### harnstoff ##########################################################################

```{r}

harnstoff_diabetic_gender <- left_join(gender_data1,harnstoff_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From Start|_From start|DBS", attribute)) %>% 
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

harnstoff_diabetic_gender
```
 
```{r}
harnstoff_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = harnstoff_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
harnstoff_diabetic_gender_peak <- harnstoff_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

harnstoff_diabetic_gender_peak
```

```{r}
harnstoff_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = harnstoff_diabetic_gender_peak)
```




## Female ##

```{r}
harnstoff_diabetic_female <- harnstoff_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

harnstoff_diabetic_female
```

```{r}
harnstoff_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = harnstoff_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- harnstoff_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = harnstoff_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_harnstoff_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(harnstoff_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_harnstoff_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_harnstoff_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
harnstoff_diabetic_male <- harnstoff_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

harnstoff_diabetic_male
```

```{r}
harnstoff_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = harnstoff_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- harnstoff_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = harnstoff_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "harnstoff (mg/dl)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_harnstoff_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(harnstoff_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_harnstoff_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_harnstoff_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
harnstoff_diabetic_female_peak <- harnstoff_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

harnstoff_diabetic_female_peak
```

```{r}
harnstoff_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = harnstoff_diabetic_female_peak)
```

```{r}
liver_harnstoff_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = harnstoff_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-harnstoff (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_harnstoff_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_harnstoff_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
harnstoff_diabetic_male_peak <- harnstoff_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

harnstoff_diabetic_male_peak
```

```{r}
harnstoff_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = harnstoff_diabetic_male_peak)
```

```{r}
liver_harnstoff_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = harnstoff_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-harnstoff (mg/dl)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_harnstoff_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_harnstoff_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```


### crp ##########################################################################

```{r}

crp_diabetic_gender <- left_join(gender_data1,crp_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From StarBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

crp_diabetic_gender
```
 
```{r}
crp_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = crp_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
crp_diabetic_gender_peak <- crp_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

crp_diabetic_gender_peak
```

```{r}
crp_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = crp_diabetic_gender_peak)
```




## Female ##

```{r}
crp_diabetic_female <- crp_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

crp_diabetic_female
```

```{r}
crp_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = crp_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- crp_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = crp_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_crp_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(crp_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_crp_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_crp_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
crp_diabetic_male <- crp_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

crp_diabetic_male
```

```{r}
crp_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = crp_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- crp_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = crp_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "crp (mg/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_crp_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(crp_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_crp_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_crp_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
crp_diabetic_female_peak <- crp_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

crp_diabetic_female_peak
```

```{r}
crp_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = crp_diabetic_female_peak)
```

```{r}
liver_crp_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = crp_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-crp (mg/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_crp_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_crp_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
crp_diabetic_male_peak <- crp_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

crp_diabetic_male_peak
```

```{r}
crp_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = crp_diabetic_male_peak)
```

```{r}
liver_crp_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = crp_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-crp (mg/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_crp_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_crp_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### natrium ##########################################################################

```{r}

natrium_diabetic_gender <- left_join(gender_data1,natrium_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From StarBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  filter(!grepl("_1|_2|_3|_4|_d", attribute)) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

natrium_diabetic_gender
```
 
```{r}
natrium_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = natrium_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
natrium_diabetic_gender_peak <- natrium_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

natrium_diabetic_gender_peak
```

```{r}
natrium_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = natrium_diabetic_gender_peak)
```

```{r}
liver_natrium_peak_labvalues_comparison_nsaid_in_diabetic_group <- ggbetweenstats(
  data = natrium_diabetic_gender_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group",
  xlab = "Patient group",
  ylab = "Peak-natrium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison", showWarnings = FALSE)
svg("plots_peak/nsaid comparison/liver_natrium_peak_labvalues_comparison_nsaid_in_diabetic_group.svg", height = 6, width = 8)
print(liver_natrium_peak_labvalues_comparison_nsaid_in_diabetic_group)
dev.off()
```


## Female ##

```{r}
natrium_diabetic_female <- natrium_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

natrium_diabetic_female
```

```{r}
natrium_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = natrium_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- natrium_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = natrium_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_natrium_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(natrium_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_natrium_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_natrium_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
natrium_diabetic_male <- natrium_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

natrium_diabetic_male
```

```{r}
natrium_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = natrium_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- natrium_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = natrium_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "natrium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_natrium_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(natrium_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_natrium_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_natrium_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
natrium_diabetic_female_peak <- natrium_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

natrium_diabetic_female_peak
```

```{r}
natrium_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = natrium_diabetic_female_peak)
```

```{r}
liver_natrium_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = natrium_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-natrium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_natrium_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_natrium_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
natrium_diabetic_male_peak <- natrium_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

natrium_diabetic_male_peak
```

```{r}
natrium_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = natrium_diabetic_male_peak)
```

```{r}
liver_natrium_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = natrium_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-natrium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_natrium_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_natrium_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### kalium ##########################################################################

```{r}

kalium_diabetic_gender <- left_join(gender_data1,kalium_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From StarBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

kalium_diabetic_gender
```
 
```{r}
kalium_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalium_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
kalium_diabetic_gender_peak <- kalium_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

kalium_diabetic_gender_peak
```

```{r}
kalium_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalium_diabetic_gender_peak)
```

```{r}
liver_kalium_peak_labvalues_comparison_nsaid_in_diabetic_group <- ggbetweenstats(
  data = kalium_diabetic_gender_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group",
  xlab = "Patient group",
  ylab = "Peak-kalium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison", showWarnings = FALSE)
svg("plots_peak/nsaid comparison/liver_kalium_peak_labvalues_comparison_nsaid_in_diabetic_group.svg", height = 6, width = 8)
print(liver_kalium_peak_labvalues_comparison_nsaid_in_diabetic_group)
dev.off()
```


## Female ##

```{r}
kalium_diabetic_female <- kalium_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

kalium_diabetic_female
```

```{r}
kalium_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalium_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalium_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalium_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kalium_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kalium_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_kalium_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_kalium_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
kalium_diabetic_male <- kalium_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

kalium_diabetic_male
```

```{r}
kalium_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = kalium_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalium_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalium_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "kalium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kalium_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kalium_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_kalium_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_kalium_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
kalium_diabetic_female_peak <- kalium_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

kalium_diabetic_female_peak
```

```{r}
kalium_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalium_diabetic_female_peak)
```

```{r}
liver_kalium_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = kalium_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-kalium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_kalium_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_kalium_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
kalium_diabetic_male_peak <- kalium_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

kalium_diabetic_male_peak
```

```{r}
kalium_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = kalium_diabetic_male_peak)
```

```{r}
liver_kalium_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = kalium_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-kalium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_kalium_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_kalium_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### kalzium ##########################################################################

```{r}

kalzium_diabetic_gender <- left_join(gender_data1,kalzium_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From StarBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

kalzium_diabetic_gender
```
 
```{r}
kalzium_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalzium_diabetic_gender)
```

# nsaid comparison all labvalues #
```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalzium_diabetic_gender %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalzium_diabetic_gender,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison nsaid in diabetic group",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kalzium_all_labvalues_comparison_nsaid_in_diabetic_group <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kalzium_diabetic_gender$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/nsaid comparison", showWarnings = FALSE)
svg("plots_all_labvalues/nsaid comparison/liver_kalzium_all_labvalues_comparison_nsaid_in_diabetic_group.svg", height = 6, width = 8)
print(liver_kalzium_all_labvalues_comparison_nsaid_in_diabetic_group)
dev.off()
```


# nsaid comparison peak labvlues #
```{r}
kalzium_diabetic_gender_peak <- kalzium_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

kalzium_diabetic_gender_peak
```

```{r}
kalzium_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalzium_diabetic_gender_peak)
```

```{r}
liver_kalzium_peak_labvalues_comparison_nsaid_in_diabetic_group <- ggbetweenstats(
  data = kalzium_diabetic_gender_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak labvalues_comparison nsaid in diabetic group",
  xlab = "Patient group",
  ylab = "Peak-kalzium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/nsaid comparison", showWarnings = FALSE)
svg("plots_peak/nsaid comparison/liver_kalzium_peak_labvalues_comparison_nsaid_in_diabetic_group.svg", height = 6, width = 8)
print(liver_kalzium_peak_labvalues_comparison_nsaid_in_diabetic_group)
dev.off()
```


## Female ##

```{r}
kalzium_diabetic_female <- kalzium_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

kalzium_diabetic_female
```

```{r}
kalzium_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalzium_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalzium_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalzium_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kalzium_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kalzium_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_kalzium_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_kalzium_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
kalzium_diabetic_male <- kalzium_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

kalzium_diabetic_male
```

```{r}
kalzium_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = kalzium_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- kalzium_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = kalzium_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "kalzium (mmol/l)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_kalzium_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(kalzium_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_kalzium_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_kalzium_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
kalzium_diabetic_female_peak <- kalzium_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

kalzium_diabetic_female_peak
```

```{r}
kalzium_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = kalzium_diabetic_female_peak)
```

```{r}
liver_kalzium_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = kalzium_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-kalzium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_kalzium_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_kalzium_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
kalzium_diabetic_male_peak <- kalzium_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

kalzium_diabetic_male_peak
```

```{r}
kalzium_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = kalzium_diabetic_male_peak)
```

```{r}
liver_kalzium_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = kalzium_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-kalzium (mmol/l)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_kalzium_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_kalzium_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### quick ##########################################################################

```{r}

quick_diabetic_gender <- left_join(gender_data1,quick_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From StarBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

quick_diabetic_gender
```
 
```{r}
quick_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = quick_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
quick_diabetic_gender_peak <- quick_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

quick_diabetic_gender_peak
```

```{r}
quick_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = quick_diabetic_gender_peak)
```




## Female ##

```{r}
quick_diabetic_female <- quick_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

quick_diabetic_female
```

```{r}
quick_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = quick_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- quick_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = quick_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_quick_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(quick_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_quick_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_quick_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
quick_diabetic_male <- quick_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

quick_diabetic_male
```

```{r}
quick_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = quick_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- quick_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = quick_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "quick (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_quick_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(quick_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_quick_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_quick_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
quick_diabetic_female_peak <- quick_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

quick_diabetic_female_peak
```

```{r}
quick_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = quick_diabetic_female_peak)
```

```{r}
liver_quick_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = quick_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-quick (%)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_quick_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_quick_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
quick_diabetic_male_peak <- quick_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

quick_diabetic_male_peak
```

```{r}
quick_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = quick_diabetic_male_peak)
```

```{r}
liver_quick_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = quick_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-quick (%)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_quick_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_quick_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### hämatokrit ##########################################################################

```{r}

hämatokrit_diabetic_gender <- left_join(gender_data1,hämatokrit_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From StarBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

hämatokrit_diabetic_gender
```
 
```{r}
hämatokrit_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hämatokrit_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
hämatokrit_diabetic_gender_peak <- hämatokrit_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

hämatokrit_diabetic_gender_peak
```

```{r}
hämatokrit_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hämatokrit_diabetic_gender_peak)
```




## Female ##

```{r}
hämatokrit_diabetic_female <- hämatokrit_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

hämatokrit_diabetic_female
```

```{r}
hämatokrit_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hämatokrit_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hämatokrit_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hämatokrit_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_hämatokrit_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(hämatokrit_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_hämatokrit_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_hämatokrit_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
hämatokrit_diabetic_male <- hämatokrit_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

hämatokrit_diabetic_male
```

```{r}
hämatokrit_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = hämatokrit_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- hämatokrit_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = hämatokrit_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "hämatokrit (%)",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_hämatokrit_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(hämatokrit_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_hämatokrit_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_hämatokrit_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
hämatokrit_diabetic_female_peak <- hämatokrit_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

hämatokrit_diabetic_female_peak
```

```{r}
hämatokrit_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = hämatokrit_diabetic_female_peak)
```

```{r}
liver_hämatokrit_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = hämatokrit_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-hämatokrit (%)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_hämatokrit_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_hämatokrit_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
hämatokrit_diabetic_male_peak <- hämatokrit_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

hämatokrit_diabetic_male_peak
```

```{r}
hämatokrit_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = hämatokrit_diabetic_male_peak)
```

```{r}
liver_hämatokrit_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = hämatokrit_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-hämatokrit (%)",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_hämatokrit_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_hämatokrit_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



### inr ##########################################################################

```{r}

inr_diabetic_gender <- left_join(gender_data1,inr_diabetic,by = "Edited_BfArM Nummer2") %>% 
  filter(!grepl("_From StarBS", attribute)) %>%
  drop_na() %>% 
  filter(str_starts(Treatment.x, "Leber_")) %>% 
  mutate(Diabetes = as.factor(Diabetes),
         Gender = as.factor(Gender))

inr_diabetic_gender
```
 
```{r}
inr_diabetic_gender %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = inr_diabetic_gender)
```



# nsaid comparison peak labvlues #
```{r}
inr_diabetic_gender_peak <- inr_diabetic_gender %>% 
  group_by(Diabetes) %>%  
  group_by(`Edited_BfArM Nummer2`) %>%   
  filter(labreads == max(labreads, na.rm = TRUE)) %>%  
  slice(1) %>% 
  ungroup()

inr_diabetic_gender_peak
```

```{r}
inr_diabetic_gender_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = inr_diabetic_gender_peak)
```




## Female ##

```{r}
inr_diabetic_female <- inr_diabetic_gender %>% 
  dplyr::filter(Gender == "Female")

inr_diabetic_female
```

```{r}
inr_diabetic_female %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = inr_diabetic_female)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- inr_diabetic_female %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = inr_diabetic_female,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_inr_all_labvalues_comp_diab_nondiab_for_female <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(inr_diabetic_female$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison female", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison female/liver_inr_all_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_inr_all_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
inr_diabetic_male <- inr_diabetic_gender %>% 
  dplyr::filter(Gender == "Male")

inr_diabetic_male
```

```{r}
inr_diabetic_male %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = inr_diabetic_male)
```

```{r}
# Schritt 1: Anzahl einzigartiger Patienten pro Diabetes-Gruppe berechnen
n_patients <- inr_diabetic_male %>%
  distinct(`Edited_BfArM Nummer2`, Diabetes) %>%  # nur einzigartige Patienten
  count(Diabetes, name = "n") %>%
  mutate(label = paste0("N = ", n))

# Schritt 2: ggbetweenstats-Plot erstellen
plot_without_count <- ggbetweenstats(
  data = inr_diabetic_male,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "inr ",
  messages = FALSE
)

# Schritt 3: N-Werte oberhalb der Violinenplots_all_labvalues einfügen
liver_inr_all_labvalues_comp_diab_nondiab_for_male <- plot_without_count+ 
  geom_text(
    data = n_patients,
    aes(x = Diabetes, 
        y = max(inr_diabetic_male$labreads, na.rm = TRUE) * 1.05,  # Position leicht oberhalb
        label = label),
    inherit.aes = FALSE,
    size = 4
  )

dir.create("plots_all_labvalues/diab comparison male", showWarnings = FALSE)
svg("plots_all_labvalues/diab comparison male/liver_inr_all_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_inr_all_labvalues_comp_diab_nondiab_for_male)
dev.off()
```
 

## Female ##

```{r}
inr_diabetic_female_peak <- inr_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Female")

inr_diabetic_female_peak
```

```{r}
inr_diabetic_female_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{r}
oneway.test(labreads ~ Diabetes, data = inr_diabetic_female_peak)
```

```{r}
liver_inr_peak_labvalues_comp_diab_nondiab_for_female <- ggbetweenstats(
  data = inr_diabetic_female_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for female",
  xlab = "Patient group",
  ylab = "Peak-inr ",
  messages = FALSE
)

dir.create("plots_peak/diab comparison female", showWarnings = FALSE)
svg("plots_peak/diab comparison female/liver_inr_peak_labvalues_comp diab nondiab for female.svg", height = 6, width = 8)
print(liver_inr_peak_labvalues_comp_diab_nondiab_for_female)
dev.off()
```


## Male ##

```{r}
inr_diabetic_male_peak <- inr_diabetic_gender_peak %>% 
  dplyr::filter(Gender == "Male")

inr_diabetic_male_peak
```

```{r}
inr_diabetic_male_peak %>% 
  group_by(Diabetes) %>% 
  normality(labreads)
```

```{}
oneway.test(labreads ~ Diabetes, data = inr_diabetic_male_peak)
```

```{r}
liver_inr_peak_labvalues_comp_diab_nondiab_for_male <- ggbetweenstats(
  data = inr_diabetic_male_peak,
  x = "Diabetes",
  y = "labreads",
  type = "np",  # non-parametrisch
  title = "Liver_peak_all labvalues_comparison diabetic vs. nondiabetic for male",
  xlab = "Patient group",
  ylab = "Peak-inr ",
  messages = FALSE
)

dir.create("plots_peak/diab comparison male", showWarnings = FALSE)
svg("plots_peak/diab comparison male/liver_inr_peak_labvalues_comp diab nondiab for male.svg", height = 6, width = 8)
print(liver_inr_peak_labvalues_comp_diab_nondiab_for_male)
dev.off()
```



















