---
title: "values"
author: "Arun Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## change the path of file according your directory/folder


```{r, echo=FALSE}
library(tidyverse)
library(readxl)
library(ggplot2)
library(ggbreak)
```


```{r, echo = FALSE}
rawdosedata <- read_excel("data_19June/Übersicht Laborwerte (Rohdaten für Interimsanalyse 21.06.2023).xlsx",sheet=1, skip = 1)
```

## converted the data from tibble to dataframe

```{r, echo=FALSE}
rawdosedf1 <- as.data.frame(rawdosedata)
```


```{r}
rawdosedf1 %>% 
  select(1,2,2013,2027,2040)->dosetreatment
```


```{r}
colnames(dosetreatment) <- c("Edited_BfArM Nummer2", 
                  "Treatment", 
                  "Diclofenac_cumulative_dosis",
                  "Ibuprofen_Cumulative_Dosis",
                  "Paracetamol_Cumulative_Dosis")
```




## join the two data frame
```{r}

gotvalue_dose <- inner_join(got_long,dosetreatment, by="Edited_BfArM Nummer2")

```

## merge two column and create new
```{r}
 gotvalue_dose$patient_dose <- paste0(gotvalue_dose$Treatment2, gotvalue_dose$`Edited_BfArM Nummer2`)

```



```{r}
gotvalue_dose %>% 
  filter(Treatment2 == "Leber_Diclo"& Diclofenac_cumulative_dosis < 5000) %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads)


```


```{r}
#gotvalue_dose$patient_dose <- as.factor(gotvalue_dose$patient_dose)
```


```{r}
# gotvalue_dose %>% 
#   filter(Treatment == "Leber_Diclo") %>% 
#   select(patient_dose,Diclofenac_Dosis,cumulative_dose) %>%
#   drop_na() %>% 
#   ggplot(aes(x = patient_dose, y= cumulative_dose))+
#   geom_point(position = position_dodge(width = 0.2))+
#   scale_y_continuous(limits = c(0,100))+
#   labs(
#     x = "GOTPatient",
#     y = "cumulative dose",
#     title = "GoT in SJS Diclofenec")+
#   theme_classic()
```


```{r}
# gotvalue_dose1$cumulative_dose <- as.factor(gotvalue_dose1$cumulative_dose)
```



```{r, echo=FALSE, width = 50, height = 10}

gotvalue_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo"& Diclofenac_cumulative_dosis < 10000) %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "GOT Lab Values",
    y = "Cumulative dose (mg)",
    title = "GoT in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(0,7000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```







```{r}

gotvalue_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo"& Diclofenac_cumulative_dosis > 10000) %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "GOT Lab Values",
    y = "Cumulative dose (mg)",
    title = "GoT in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(10000,150000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_cumulative2.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```

##GPT liver diclo
## here we merge gptlong data with dosetreatment
## create new column

```{r}
gptvalue_dose <- inner_join(gpt_long,dosetreatment, by="Edited_BfArM Nummer2")

gptvalue_dose$patient_dose <- paste0(gptvalue_dose$Treatment2, gptvalue_dose$`Edited_BfArM Nummer2`)
```

```{r}
gptvalue_dose
```


```{r, echo=FALSE, width = 50, height = 10}

gptvalue_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "GPT Lab Values",
    y = "Cumulative dose (mg)",
    title = "GPT in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(0,6000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_gpt_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```

## GGT Liver Dicolo

```{r}
ggtvalue_dose <- inner_join(ggt_long,dosetreatment, by="Edited_BfArM Nummer2")

ggtvalue_dose$patient_dose <- paste0(ggtvalue_dose$Treatment2, ggtvalue_dose$`Edited_BfArM Nummer2`)


ggtvalue_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "GGT Lab Values",
    y = "Cumulative dose (mg)",
    title = "GGT in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(0,6000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_ggt_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

## LDH in LIver Diclo
```{r}
ldhvalue_dose <- inner_join(ldh_long,dosetreatment, by="Edited_BfArM Nummer2")

ldhvalue_dose$patient_dose <- paste0(ldhvalue_dose$Treatment2, ldhvalue_dose$`Edited_BfArM Nummer2`)


ldhvalue_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "LDH Lab Values",
    y = "Cumulative dose (mg)",
    title = "LDH in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(0,6000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_LDH_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

##TotalBilirubin

```{r}

total_bilirubin_value_dose <- inner_join(total_bilirubin_long,dosetreatment, by="Edited_BfArM Nummer2")

total_bilirubin_value_dose$patient_dose <- paste0(total_bilirubin_value_dose$Treatment2, total_bilirubin_value_dose$`Edited_BfArM Nummer2`)


total_bilirubin_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Total bilirubin Lab Values",
    y = "Cumulative dose (mg)",
    title = "Total Bilirubin in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(0,6000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_total_bilirubin_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

##DirectBilirubin

```{r}
directBilirubin_value_dose <- inner_join(direct_bilirubin_long,dosetreatment, by="Edited_BfArM Nummer2")

directBilirubin_value_dose$patient_dose <- paste0(directBilirubin_value_dose$Treatment2, directBilirubin_value_dose$`Edited_BfArM Nummer2`)


directBilirubin_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Direct Bilirubin Lab Values",
    y = "Cumulative dose (mg)",
    title = "Direct Bilirubin in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(0,6000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Direct_bilirubin_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```


##Gesamteiweiß


```{r}
gesamteiweiß_value_dose <- inner_join(gesamteiweiß_long,dosetreatment, by="Edited_BfArM Nummer2")

gesamteiweiß_value_dose$patient_dose <- paste0(gesamteiweiß_value_dose$Treatment2, gesamteiweiß_value_dose$`Edited_BfArM Nummer2`)


gesamteiweiß_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "gesamteiweiß Lab Values",
    y = "Cumulative dose (mg)",
    title = "gesamteiweiß in Liver Diclofenec", hjust = 0.5)+
  scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_gesamteiweiß_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

## CK

```{r}

ck_value_dose <- inner_join(ck_long,dosetreatment, by="Edited_BfArM Nummer2")

ck_value_dose$patient_dose <- paste0(ck_value_dose$Treatment2, ck_value_dose$`Edited_BfArM Nummer2`)


ck_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "CK Lab Values",
    y = "Cumulative dose (mg)",
    title = "CK in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_CK_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```

##Kreatinin

```{r}
keratinin_value_dose <- inner_join(kreatinin_long,dosetreatment, by="Edited_BfArM Nummer2")

keratinin_value_dose$patient_dose <- paste0(keratinin_value_dose$Treatment2, keratinin_value_dose$`Edited_BfArM Nummer2`)


keratinin_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Keratinin Lab Values",
    y = "Cumulative dose (mg)",
    title = "Keratinin in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Keratinin_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

##CRP

```{r}
crp_value_dose <- inner_join(kreatinin_long,dosetreatment, by="Edited_BfArM Nummer2")

keratinin_value_dose$patient_dose <- paste0(keratinin_value_dose$Treatment2, keratinin_value_dose$`Edited_BfArM Nummer2`)


keratinin_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Keratinin Lab Values",
    y = "Cumulative dose (mg)",
    title = "Keratinin in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Keratinin_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```



##Harnstoff

```{r}
harnstoff_value_dose <- inner_join(harnstoff_long,dosetreatment, by="Edited_BfArM Nummer2")

harnstoff_value_dose$patient_dose <- paste0(harnstoff_value_dose$Treatment2, harnstoff_value_dose$`Edited_BfArM Nummer2`)


harnstoff_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Harnstoff Lab Values",
    y = "Cumulative dose (mg)",
    title = "Harnstoff in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1,
                               face= "bold", color = "black", size = 10),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    axis.text.y = element_text (face= "bold", color = "black", size = 10),
    legend.text = element_text(size = 15, face = "bold"),
    axis.line = element_line(linewidth = 1))
#ggsave( "Visual/liverdiclo_Harnstoff_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```


##Harnsäure

```{r}
harnsaur_value_dose <- inner_join(harnsäure_long,dosetreatment, by="Edited_BfArM Nummer2")

harnsaur_value_dose$patient_dose <- paste0(harnsaur_value_dose$Treatment2, harnsaur_value_dose$`Edited_BfArM Nummer2`)

harnsaur_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Harnsäure Lab Values",
    y = "Cumulative dose (mg)",
    title = "Harnssäur in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Harnssäur_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

##Triglyceride

```{r}
triglyceride_value_dose <- inner_join(triglyceride_long,dosetreatment, by="Edited_BfArM Nummer2")

triglyceride_value_dose$patient_dose <- paste0(triglyceride_value_dose$Treatment2, triglyceride_value_dose$`Edited_BfArM Nummer2`)

triglyceride_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Triglyceride Lab Values",
    y = "Cumulative dose (mg)",
    title = "Triglyceride in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Triglyceride_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```

##Cholesterin



```{r}
cholesterin_value_dose <- inner_join(cholesterin_long,dosetreatment, by="Edited_BfArM Nummer2")

cholesterin_value_dose$patient_dose <- paste0(cholesterin_value_dose$Treatment2,cholesterin_value_dose$`Edited_BfArM Nummer2`)

cholesterin_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Cholesterin Lab Values",
    y = "Cumulative dose (mg)",
    title = "Cholesterin in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Cholesterin_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```


##AP


```{r}


ap_value_dose <- inner_join(ap_long,dosetreatment, by="Edited_BfArM Nummer2")

ap_value_dose$patient_dose<-paste0(ap_value_dose$Treatment2,ap_value_dose$`Edited_BfArM Nummer2`)

ap_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "AP Lab Values",
    y = "Cumulative dose (mg)",
    title = "AP in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_AP_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

##Amylase


```{r}
amylase_value_dose <- inner_join(amylase_long,dosetreatment, by="Edited_BfArM Nummer2")

amylase_value_dose$patient_dose<-paste0(amylase_value_dose$Treatment2,amylase_value_dose$`Edited_BfArM Nummer2`)

amylase_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Amylase Lab Values",
    y = "Cumulative dose (mg)",
    title = "Amylase in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Amylase_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```




##Lipase



```{r}
lipase_value_dose <- inner_join(lipase_long,dosetreatment, by="Edited_BfArM Nummer2")

lipase_value_dose$patient_dose<-paste0(lipase_value_dose$Treatment2,lipase_value_dose$`Edited_BfArM Nummer2`)

lipase_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Lipase Lab Values",
    y = "Cumulative dose (mg)",
    title = "Lipase in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Lipase_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```



##Natrium

```{r}
natrium_value_dose <- inner_join(natrium_long,dosetreatment, by="Edited_BfArM Nummer2")

natrium_value_dose$patient_dose<-paste0(natrium_value_dose$Treatment2,natrium_value_dose$`Edited_BfArM Nummer2`)

natrium_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Natrium Lab Values",
    y = "Cumulative dose (mg)",
    title = "Natrium in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Natrium_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```

##Kalzium

```{r}
kalzium_value_dose <- inner_join(kalium_long,dosetreatment, by="Edited_BfArM Nummer2")

kalzium_value_dose$patient_dose<-paste0(kalzium_value_dose$Treatment2,kalzium_value_dose$`Edited_BfArM Nummer2`)

kalzium_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Kalzium Lab Values",
    y = "Cumulative dose (mg)",
    title = "Kalzium in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_kalzium_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

##Glucose

```{r}

glucose_value_dose <- inner_join(glucose_long,dosetreatment, by="Edited_BfArM Nummer2")

glucose_value_dose$patient_dose<-paste0(glucose_value_dose$Treatment2,glucose_value_dose$`Edited_BfArM Nummer2`)

glucose_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Glucose Lab Values",
    y = "Cumulative dose (mg)",
    title = "Glucose in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Glucose_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```


##Ferritin

```{r}

ferritin_value_dose <- inner_join(ferritin_long,dosetreatment, by="Edited_BfArM Nummer2")

ferritin_value_dose$patient_dose<-paste0(ferritin_value_dose$Treatment2,ferritin_value_dose$`Edited_BfArM Nummer2`)

ferritin_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Ferritin Lab Values",
    y = "Cumulative dose (mg)",
    title = "Ferritin in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Ferritin_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)

```

##Albumin

```{r}
albumin_value_dose <- inner_join(albumin_long,dosetreatment, by="Edited_BfArM Nummer2")

albumin_value_dose$patient_dose<-paste0(albumin_value_dose$Treatment2,albumin_value_dose$`Edited_BfArM Nummer2`)

albumin_value_dose %>% mutate(labreads = as.factor(labreads)) %>% 
  filter(Treatment == "Leber_Diclo") %>% 
  select(patient_dose,Diclofenac_cumulative_dosis,labreads) %>% 
  group_by(patient_dose) %>% 
  drop_na() %>% 
  ggplot(aes(x = labreads, y= Diclofenac_cumulative_dosis))+
  geom_point(position = position_dodge(width = 0.2))+
    labs(
    x = "Albumin Lab Values",
    y = "Cumulative dose (mg)",
    title = "Albumin in Liver Diclofenec", hjust = 0.5)+
  #scale_y_continuous(limits = c(0,1000))+
  theme_classic()+
  theme(
    plot.title = element_text(margin = margin(b=10), 
                              color="black", face="bold", hjust = 0.5),
    axis.title.x = element_text(face= "bold", size = 15, colour = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(face = "bold", size = 15, colour = "black"),
    legend.position = c(0.2,0.9),
    legend.text = element_text(size = 15, face = "bold"))
ggsave( "Visual/liverdiclo_Albumin_cumulative1.png", plot=last_plot(), width = 8, height = 7, dpi = 600)
```


```{r}

```











































